### 2011-04-19 ssp2011.tex
ssp2011 initialization

\documentclass[draftcls]{IEEEtran}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{mathrsfs}
\usepackage{bm}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\usepackage[colorlinks=true,pagebackref,linkcolor=magenta]{hyperref}
\usepackage[colon,sort&compress]{natbib}
%\numberwithin{equation}{section}
\renewcommand\arraystretch{1.2}
\let\underbrace\LaTeXunderbrace
\let\overbrace\LaTeXoverbrace
\newcommand{\argmax}{\operatornamewithlimits{argmax}}
\newcommand{\argmin}{\operatornamewithlimits{argmin}}
\bibliographystyle{IEEEtran}
\begin{document}
\title{Attribute fusion in a latent process model for time series of
  graphs}
\author{Carey~E.~Priebe, Nam~H.~Lee, Youngser~Park, and Minh~Tang}%
%\thanks{Johns Hopkins University \\ Department of Applied Mathematics
%  and Statistics \\ Baltimore, Maryland 21218-2682 USA}%
\maketitle
\begin{abstract}
 We consider the problem of anomaly/change point detection given a
 time series of graphs with categorical attributes on the
 edges. Various attributed graph invariants are considered, and their
 power for detection as a function of a linear fusion parameter is
 presented.  
\end{abstract}
\begin{IEEEkeywords}
  Anomaly detection, Attributed Random Graphs, Fusion, Random Dot
  Product Graphs
\end{IEEEkeywords}
\section{Introduction}
\subsection{Latent Process Model}
The latent process model for time series of attributed graphs was
originally presented in
\cite{lee:_laten_proces_model_time_attrib_random_graph}. We summarized
here the ideas that are relevant to our discussion. We begin by
introducing some terminology. Let $\mathscr{S}$ be the unit simplex in
$\mathbb{R}^{K}$, i.e.,
\begin{equation}
  \mathscr{S} = \{ \xi \in [0,1]^{K}
  \colon \sum_{k = 1}^{K} \xi_k \leq 1 \}.
\end{equation}
A {\em random dot product space} for attributed graphs with vertices
in $[n]$ and edge attributes $\mathscr{K} = [K]
$ is then a pair $(\mathbf{X},G)$ of random elements such that
\begin{enumerate}
\item $\mathbf{X} = \{X_i\}_{i = 1}^{n}$ is a collection of
  $\mathscr{S}$-valued random vectors.
\item $G$ is a random graph with vertices set $[n]$ such that
  \begin{equation}
    \label{eq:1}
    \mathbb{P}(i \sim j \,|\, \mathbf{X} = (x_1, x_2, \dots,
    x_n)) = \langle x_i, x_j \rangle.
  \end{equation}
  and that $\mathbf{P}(i \sim j \,|\, \mathbf{X})$ and $\mathbf{P}(i' \sim
  j' \,|\, \mathbf{X})$ are independent whenever $(i,j) \not = (i',j')$. If
  $i \sim j$ in $G$, then the attribute of the edge $\{i,j\}$ is an
  element of $\mathscr{K}$. In particular, $\{i,j\}$ has attribute $k$
  with probability $x_{i,k} x_{j,k}$. 
\end{enumerate}
Let $\mathscr{K}_{+} = \{1,\dots,K+1\}$. We say that a c\'{a}dl\'{a}g
process $W \colon [0,\infty) \mapsto \mathscr{K}_{+}^{n}$ induces the
sequence of random dot product spaces $\mathscr{V} = \{X(t), G(t)\}_{t
  = 1}^{\infty}$ if
\begin{enumerate}
\item Each $(X(t), G(t))$ is a random dot product space with vertices
  $[n]$ and attributes $\mathscr{K}$. Furthermore, for each
  $i \in [n]$, $k \in \mathscr{K}$ and $t \in \mathbb{N}$, we have
  $X_{i,k}(t)  = \int_{t - 1}^{t}{ \mathbf{1}\{W_i(u) = k\}\, du}$.
\item  For each $t \in \mathbb{N}$, we have
  \begin{equation}
    \label{eq:2}
    \mathbb{P}(G(t) = g \,|\, \mathscr{F}_{\leq t}) = \mathbb{P}(G(t) = g \,|\, X(t))
  \end{equation}
where $\mathscr{F}_{\leq t}$ are the sigma fields generated by $\{W(s)
  \colon s \leq t\}$.
\end{enumerate}
We will call any pair $(\mathscr{V}, W)$ that satisfies the above
properties a random dot process model. In particular, we are
interested in the pairs $(\mathscr{V}, W)$ possessing the following
properties. 
\begin{enumerate}
\item For each time $t \in \mathbb{N}$ and vertex $i \in [n]$, there
  exists a matrix $\mathbf{Q}^{(i)}(t)$ such that for each $k,k' \in
  \mathscr{K}_{+}$
  \begin{equation}
    \label{eq:3}
    \mathbb{P}(W_{i}(t + \epsilon) = k' \, | \, W_{i}(t) = k)
    = \begin{cases}
      1 - \mathbf{Q}_{kk}^{(i)}(t)\epsilon + o(\epsilon) & \text{if $k
        = k'$} \\
      \mathbf{Q}_{kk}^{(i)}(t)\epsilon + o(\epsilon) &
      \text{otherwise}
    \end{cases}
  \end{equation}
\end{enumerate}

\bibliography{ssp2011}
\end{document}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2011-04-20 ssp2011.tex
Add section on second order approximation

@@
 \newtheorem{proposition}[theorem]{Proposition}
+\theoremstyle{definition}
+\newtheorem{definition}{Definition}
 \usepackage[colorlinks=true,pagebackref,linkcolor=magenta]{hyperref}
@@
 interested in the pairs $(\mathscr{V}, W)$ possessing the following
-properties. 
+properties:
 \begin{enumerate}
-\item For each time $t \in \mathbb{N}$ and vertex $i \in [n]$, there
-  exists a matrix $\mathbf{Q}^{(i)}(t)$ such that for each $k,k' \in
-  \mathscr{K}_{+}$
+\item For each $t \in \mathbb{N}$ and vertex $i \in [n]$, there exists
+  a matrix $\mathbf{Q}^{(i)}(t)$ such that $W_i$, when restricted to
+  the interval $[t, t+1)$, is a stationary, continuous-time Markov
+  chain with state space $\mathscr{K}_+$, intensity matrix
+  ${\mathbf{Q}^{(i)}(t)}$, and stationary distribution
+  $\pi^{(i)}(t)$. $W$ is thus a stationary, continuous-time Markov chain with state
+  space $\mathscr{K}_{+}^{n}$ and intentisy matrix
+  $\otimes_{i=1}^{n}\mathbf{Q}^{(i)}(t)$.
+\item There exists a $t^{*} \in \mathbb{N}$ and a $m < n$ such that 
+  \begin{enumerate}
+  \item for  $t < t^{*}$
+    \begin{gather*}
+      \pi^{(i)}(t) \equiv \pi_0 \\
+      Q^{(i)}(t) \equiv \mathbf{Q}_0
+    \end{gather*}
+  \item  for $t \geq t^{*}$
+    \begin{gather*}
+      \pi^{(1)}(t) = \dots = \pi^{(m)}(t) = \pi_1 \\
+      \pi^{(m+1)}(t)  = \dots = \pi^{(n)}(t) = \pi_0 \\
+      \mathbf{Q}^{(1)}(t)  = \dots = \mathbf{Q}^{(m)}(t) = \mathbf{Q}_1 \\
+      \mathbf{Q}^{(m+1)}(t) = \dots = \mathbf{Q}^{(n)}(t) = \mathbf{Q}_0 
+    \end{gather*}
+  \end{enumerate}
+\end{enumerate}
+The above properties characterize a random dot process model with a
+change-point phenomena. We will refer to $(t^{*}, m, \pi_0, \pi_1,
+\mathbf{Q}_0, \mathbf{Q}_1)$ as the change parameters. Because $W$ is completely
+determined by the change parameters, we often choose to omit $W$ and
+only mention $\mathscr{V}$ when referring to random dot process models
+with change-point phenomena. For a rdpm $\mathscr{V}$ with change
+parameters $(t^{*}, m, \pi_0, \pi_1, \mathbf{Q}_0, \mathbf{Q}_1)$, we can construct
+several approximations to $\mathscr{V}$. Of particular interests are the
+following two approximations.
+\begin{definition}
+  \label{def:1}
+  Let $\mathscr{V}$ be a rdpm with change parameters $(t^{*}, m,
+  \pi_0, \pi_1, \mathbf{Q}_0, \mathbf{Q}_1)$. The first order approximation
+  $\bar{\mathscr{V}}$ of $\mathscr{V}$ is the sequence $\{(\bar{X}(t),
+  \bar{G}(t)\}_{t = 1}^{\infty}$ of independent random dot product
+  spaces such that
+ \begin{enumerate}
+ \item For $t < t^{*}$,
    \begin{equation}
-    \label{eq:3}
-    \mathbb{P}(W_{i}(t + \epsilon) = k' \, | \, W_{i}(t) = k)
-    = \begin{cases}
-      1 - \mathbf{Q}_{kk}^{(i)}(t)\epsilon + o(\epsilon) & \text{if $k
-        = k'$} \\
-      \mathbf{Q}_{kk}^{(i)}(t)\epsilon + o(\epsilon) &
-      \text{otherwise}
-    \end{cases}
+     \label{eq:5}
+     \bar{X}_{i}(t) \equiv \bar{\pi}_0.
    \end{equation}
+ \item For $t \geq t^{*}$
+   \begin{gather*}
+     \bar{X}_{i}(t) \equiv \bar{\pi}_1 \quad \text{for $i \leq m$} \\
+     \bar{X}_{i}(t) \equiv \bar{\pi}_0 \quad \text{for $i > m$} 
+   \end{gather*}
  \end{enumerate}
-
+ where $\bar{\pi}_0$ and $\bar{\pi}_1$ are sub-probability vectors
+ obtained by removing the last coordinate of $\pi_0$ and $\pi_1$. 
+\end{definition}
+\begin{definition}
+  \label{def:2}
+  Let $\mathscr{V}$ be a rdpm with change parameters $(t^{*}, m,
+  \pi_0, \pi_1, Q_0, Q_1)$. Define $\mathbf{Z}_0$ and $\mathbf{Z}_1$
+  by
+  \begin{gather}
+    \mathbf{Z}_0 = (\mathbf{1}\mathbf{\pi}_0^{T} -
+    \mathbf{Q}_0)^{-1}(\mathbf{I} - \mathbf{1}\pi_0^{T}) \\
+    \mathbf{Z}_1 = (\mathbf{1}\mathbf{\pi}_1^{T} -
+    \mathbf{Q}_1)^{-1}(\mathbf{I} - \mathbf{1}\pi_1^{T})
+  \end{gather}
+  $\mathbf{Z}_0$ and $\mathbf{Z}_1$ are the fundamental matrices
+  for the continuous-time Markov chain on $\mathscr{K}$ with intensity
+  matrix $\mathbf{Q}_0$ and $\mathbf{Q}_1$ (see
+  e.g., \cite[p. 55]{asmussen03:_applied_probab_queues}). Let
+  $\Sigma_0$ and $\Sigma_1$ be given by
+  \begin{gather*}
+    \Sigma_0 = \mathrm{diag}(\pi_0) \mathbf{Z}_0 + \mathbf{Z}_0^{T}
+    \mathrm{diag}(\pi_0) \\
+    \Sigma_1 = \mathrm{diag}(\pi_1) \mathbf{Z}_1 + \mathbf{Z}_1^{T}
+    \mathrm{diag}(\pi_1)
+  \end{gather*}
+  A second order approximation $\hat{\mathscr{V}}$ of $\mathscr{V}$
+  is the sequence $\{\hat{X}(t), \hat{G}(t)\}_{t=1}^{\infty}$ where
+  \begin{enumerate}
+  \item For each $t$ and each $i \in [n]$, $\hat{X}^{i}(t)$ is a
+    random vector obtained by truncating a multivariate normal random
+    vector $Z_{i}(t)$ to $\mathscr{S}$.
+  \item For $t < t^{*}$,
+    \begin{gather}
+      \mathbb{E}[Z_i(t)] \equiv \bar{\pi}_0 \\
+      \mathrm{Var}[Z_i(t)] \equiv \hat{\Sigma^{0}}
+    \end{gather}
+  \item For $t \geq t^{*}$,  
+    \begin{gather*}
+      \mathbb{E}[Z_i(t)] \equiv \bar{\pi}_0, \quad \text{for $i \leq
+        m$}  \\
+      \mathbb{E}[Z_i(t)] \equiv \bar{\pi}_1, \quad \text{for $i > 
+        m$}  \\
+      \mathrm{Var}[Z_i(t)] \equiv \hat{\Sigma}_{0} \quad \text{for $i
+        \leq m$} \\
+      \mathrm{Var}[Z_i(t)] \equiv \hat{\Sigma}_{1} \quad \text{for $i
+        > m$}
+    \end{gather*}
+    where $\hat{\Sigma}_0$ and $\hat{\Sigma}_1$ are the matrices
+    obtained by removing last row and column of $\Sigma_0$ and
+    $\Sigma_1$. 
+  \end{enumerate}
+\end{definition}
 \bibliography{ssp2011}

### 2011-04-21 ssp2011.tex
ssp 2011 graph invariants

@@
 \end{definition}
+\section{Change-point detection}
+\subsection{Graphs Invariants}
+In this paper we consider the problem of detecting chatter anomalies
+in time series of graphs using attributed invariants. The particular
+invariants of interests are the size, max degree, scan, and number of
+triangles. Specifically, we consider linear attribute fusion with
+parameter $\lambda \in \mathbb{R}^{K}_{\geq 0}$ via
+\begin{gather}
+  \label{eq:6}
+  \mathrm{size}_{\lambda}(G(t)) = \sum_{k=1}^{K} \lambda_k \sum_{u,v}
+  \mathbf{1}\{ \phi(uv,t) = k \} \\
+  \Delta_{\lambda}(G(t)) = \max_{v \in V} \, \sum_{k = 1}^{K} \lambda_k
+  \sum_{u \in N(v)}{\mathbf{1}\{\phi(uv,t) = k\}} \\
+  \mathrm{scan}_{\lambda}(G(t)) = \max_{v \in V} \, \sum_{k = 1}^{K}
+  \lambda_k \sum_{u,w \in N(v)} \mathbf{1}\{\phi(uw,t) = k\} \\
+  \label{eq:3}
+  \tau_\lambda(G(t)) = \sum_{k=1}^{K} \lambda_k \sum_{(u,v,w) \in
+    \binom{V}{3}} h_k(u,v,w)
+\end{gather}
+where $h_k(u,v,w)$ is the indicator function that the argument, a set
+of three vertices, forms a triangle (3-clique) of type $k$. A triangle
+is of type $k$ provided that all edges in the triangle have attribute
+$k$. \\ \\
+\noindent
+Let $J_{\lambda}(t)$ be a statistic of the form as in Eq.~\eqref{eq:6}) through
+Eq.~\eqref{eq:3}. We define the normalization $\bar{J}^{m}_\lambda(t)$
+of $J_{\lambda}$ based on recent past as
+\begin{equation}
+  \label{eq:4}
+ \bar{J}^{m}_{\lambda}(t) = \frac{1}{m}\sum_{s = 1}^{m} J_{\lambda}(t - s) 
+\end{equation}
+where $m \in \mathbb{N}$ specified the width of the running-average
+window. The main object of our interests are then the normalized fusion
+statistic $T_{\lambda}^{m}(t)$ as defined by
+\begin{equation}
+  \label{eq:7}
+ T_{\lambda}^{m}(t) = % \begin{cases}
+   % J_{\lambda}(t) - J_{\lambda}(t - 1) & \text{if $m = 1$} \\
+   \frac{J_{\lambda}(t) -
+     \bar{J}_{\lambda}^{m}(t)}{\sqrt{\tfrac{1}{m-1}
+       \sum_{s=1}^{m}(J_{\lambda}(t - s) - \bar{J}_{\lambda}^{m}(t))^2}}
+%   & \text{if $m \geq 2$}
+ %  \end{cases}
+\end{equation}
+for $m \geq 2$. 
+\begin{theorem}
+  \label{thm:1}
+  Let $\lambda^{*}$ be the eigenvector corresponding to the largest
+  eigenvalue of $ \mathbf{A}^{-1/2} \mathbf{B} \mathbf{A}^{-1/2}$,
+  i.e., 
+ \begin{equation}
+   \label{eq:9}
+  \lambda^{*} = \argmax_{\lambda \colon \| \lambda \| = 1}
+  \lambda^{T} \mathbf{A}^{-1/2} \mathbf{B} \mathbf{A}^{-1/2}
+  \lambda.
+ \end{equation}
+ We then have
+ \begin{gather}
+   \label{eq:8}
+ \argmax_{\lambda \in \mathcal{B}}
+ \mu_{\lambda} \, \cap \, \{\lambda^{*}, - \lambda^{*}\} \not = \emptyset \\
+ \argmin_{\lambda \in \mathcal{B}} \mu_{\lambda} \, \cap \, \{\lambda^{*}, -
+ \lambda^{*}\} \not = \emptyset.
+ \end{gather}
+\end{theorem}
 \bibliography{ssp2011}

### 2011-04-26 ssp2011.tex
Add discussion of fusion statistics for max degree

@@
 \usepackage[colorlinks=true,pagebackref,linkcolor=magenta]{hyperref}
-\usepackage[colon,sort&compress]{natbib}
+%\usepackage[colon,sort&compress]{natbib}
 %\numberwithin{equation}{section}
@@
   \mathbf{1}\{ \phi(uv,t) = k \} \\
+  \tau_\lambda(G(t)) = \sum_{k=1}^{K} \lambda_k \!\! \sum_{(u,v,w) \in
+    \binom{V}{3}} h_k(u,v,w) \\
   \Delta_{\lambda}(G(t)) = \max_{v \in V} \, \sum_{k = 1}^{K} \lambda_k
   \sum_{u \in N(v)}{\mathbf{1}\{\phi(uv,t) = k\}} \\
-  \mathrm{scan}_{\lambda}(G(t)) = \max_{v \in V} \, \sum_{k = 1}^{K}
-  \lambda_k \sum_{u,w \in N(v)} \mathbf{1}\{\phi(uw,t) = k\} \\
   \label{eq:3}
-  \tau_\lambda(G(t)) = \sum_{k=1}^{K} \lambda_k \sum_{(u,v,w) \in
-    \binom{V}{3}} h_k(u,v,w)
+  \Psi_{\lambda}(G(t)) = \max_{v \in V} \sum_{k = 1}^{K}
+  \lambda_k \!\!\sum_{u,w \in N(v)}\!\!\! \mathbf{1}\{\phi(uw,t) = k\} 
   \end{gather}
 where $h_k(u,v,w)$ is the indicator function that the argument, a set
-of three vertices, forms a triangle (3-clique) of type $k$. A triangle
+of three vertices, forms a triangle of type $k$. A triangle
 is of type $k$ provided that all edges in the triangle have attribute
@@
 \noindent
-Let $J_{\lambda}(t)$ be a statistic of the form as in Eq.~\eqref{eq:6}) through
-Eq.~\eqref{eq:3}. We define the normalization $\bar{J}^{m}_\lambda(t)$
+Let $J_{\lambda}(t)$ be a statistic of the form as in Eq.~\eqref{eq:6} through
+Eq.~\eqref{eq:3}. We define the normalization $\bar{J}^{l}_\lambda(t)$
 of $J_{\lambda}$ based on recent past as
@@
   \label{eq:4}
- \bar{J}^{m}_{\lambda}(t) = \frac{1}{m}\sum_{s = 1}^{m} J_{\lambda}(t - s) 
+ \bar{J}^{l}_{\lambda}(t) = \frac{1}{l}\sum_{s = 1}^{l} J_{\lambda}(t - s) 
 \end{equation}
-where $m \in \mathbb{N}$ specified the width of the running-average
+where $l \in \mathbb{N}$ specified the width of the running-average
 window. The main object of our interests are then the normalized fusion
-statistic $T_{\lambda}^{m}(t)$ as defined by
+statistic $T_{\lambda}^{l}(t)$ as defined by
 \begin{equation}
   \label{eq:7}
- T_{\lambda}^{m}(t) = % \begin{cases}
+ T_{\lambda}^{l}(t) = % \begin{cases}
    % J_{\lambda}(t) - J_{\lambda}(t - 1) & \text{if $m = 1$} \\
    \frac{J_{\lambda}(t) -
-     \bar{J}_{\lambda}^{m}(t)}{\sqrt{\tfrac{1}{m-1}
-       \sum_{s=1}^{m}(J_{\lambda}(t - s) - \bar{J}_{\lambda}^{m}(t))^2}}
+     \bar{J}_{\lambda}^{l}(t)}{\sqrt{\tfrac{1}{l-1}
+       \sum_{s=1}^{l}(J_{\lambda}(t - s) - \bar{J}_{\lambda}^{l}(t))^2}}
 %   & \text{if $m \geq 2$}
@@
 \end{equation}
-for $m \geq 2$. 
+for $l \geq 2$. 
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=8cm]{graphics/Fig4-SSP2011.pdf}
+  \caption{Temporal standardization: when testing for change at time $t$, the recent past (graphs $G(t - l), \dots, G(t-1)$ is used to standardize the invariants}
+  \label{fig:temporal}
+\end{figure}
+It was shown in
+\cite{lee:_laten_proces_model_time_attrib_random_graph} that when
+$J_\lambda(t) = \mathrm{size}_{\lambda}(t)$, the normalized fusion
+statistic $T_{\lambda}^{l}(t)$ follows a $t$-distribution with $l - 1$
+degrees of freedom in the limit. Specifically, we have the following
+results
+\begin{lemma}
+  \label{lem:1}
+  Let $t \in \{l+1, \dots, t^{*}\}$ and $\lambda \in
+  \mathbb{R}^{K}$. Define the vector $\zeta$ and the matrix $\xi$ by
+  \begin{gather*}
+    \zeta = \tbinom{m}{2}(\pi_{11} - \pi_{00}) + (n-m)m(\pi_{01} -
+    \pi_{00}) \\
+    \xi = (1+1/l)\tbinom{n}{2} \eta_{00} +
+          \tbinom{m}{2}(\eta_{11} - \eta_{00}) + (n-m)m(\eta_{01} -
+          \eta_{00})
+  \end{gather*}
+As $n \rightarrow \infty$, the random variable
+  $\psi^{l}_{\lambda}(t)$ converges weakly to the Student
+  $t$-distribution with $l-1$ degrees of freedom and non-centrality
+  parameter $\mu_{\lambda}$, where
+  \begin{equation}
+    \label{eq:10}
+    \mu_{\lambda} = \begin{cases}
+      \frac{\langle \lambda, \zeta \rangle}{\sqrt{\langle \lambda, \xi \lambda \rangle}} & \text{if $t = t^{*}$} \\
+      0 & \text{otherwise}
+    \end{cases}
+  \end{equation}
+\end{lemma}
+
 \begin{theorem}
@@
    \label{eq:8}
- \argmax_{\lambda \in \mathcal{B}}
+ \argmax_{ \|\lambda\| = 1}
  \mu_{\lambda} \, \cap \, \{\lambda^{*}, - \lambda^{*}\} \not = \emptyset \\
- \argmin_{\lambda \in \mathcal{B}} \mu_{\lambda} \, \cap \, \{\lambda^{*}, -
+ \argmin_{ \| \lambda \| = 1} \mu_{\lambda} \, \cap \, \{\lambda^{*}, -
  \lambda^{*}\} \not = \emptyset.

### 2011-04-26 ssp2011.tex
Add section on max degree

@@
 \section{Change-point detection}
-\subsection{Graphs Invariants}
-In this paper we consider the problem of detecting chatter anomalies
-in time series of graphs using attributed invariants. The particular
-invariants of interests are the size, max degree, scan, and number of
-triangles. Specifically, we consider linear attribute fusion with
-parameter $\lambda \in \mathbb{R}^{K}_{\geq 0}$ via
+Let $\mathscr{V}$ be a random dot process model with change parameters
+$(t^{*}, m, \pi_0, \pi_1, \mathbf{Q}_0, \mathbf{Q}_1)$. The
+change-parameters encapsulate a notion of chatter anomalies, i.e., a
+subset of vertices of $\mathscr{V}$ with altered communication
+behaviour in an otherwise stationary setting as depicted in Fig.~\ref{fig:notional_change_point}. 
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=8cm]{graphics/Fig1-SSP2011.pdf}
+  \caption{Notional depiction of the problem of change-point detection in a time-series of graphs}
+  \label{fig:notional_change_point}
+\end{figure}
+\\ \noindent
+We are interested in
+the problem of testing, for a $t \in \mathbb{N}$, the hypotheses that
+$t$ is the change-point of $\mathscr{V}$, namely
+\begin{gather*}
+  \mathscr{H}_0 \colon t^{*} > t \\
+  \mathscr{H}_A \colon t^{*} = t
+\end{gather*}
+%\subsection{Graphs Invariants}
+%In this paper we consider the problem of detecting chatter anomalies
+This will be done using the notion of fusion of attributed graph
+invariants. The particular invariants of interests are the size
+$\mathcal{E}$, number of triangles $\tau_{\lambda}$, scan $\Psi$, and
+max degree $\Delta$. Specifically, we consider linear attribute
+fusion with parameter $\lambda \in \mathbb{R}^{K}$ via
 \begin{gather}
   \label{eq:6}
-  \mathrm{size}_{\lambda}(G(t)) = \sum_{k=1}^{K} \lambda_k \sum_{u,v}
+  \mathcal{E}_{\lambda}(G(t)) = \sum_{k=1}^{K} \lambda_k \sum_{u,v}
   \mathbf{1}\{ \phi(uv,t) = k \} \\
@@
 where $l \in \mathbb{N}$ specified the width of the running-average
-window. The main object of our interests are then the normalized fusion
-statistic $T_{\lambda}^{l}(t)$ as defined by
+window. Our main interests is in the normalized fusion
+statistic $T_{\lambda}^{l}(t)$ as depicted in Fig.~\ref{fig:temporal}, namely
 \begin{equation}
@@
   \includegraphics[width=8cm]{graphics/Fig4-SSP2011.pdf}
-  \caption{Temporal standardization: when testing for change at time $t$, the recent past (graphs $G(t - l), \dots, G(t-1)$ is used to standardize the invariants}
+  \caption{Temporal standardization: when testing for change at time $t$, the recent past (graphs $G(t - l), \dots, G(t-1))$ is used to standardize the invariants}
   \label{fig:temporal}
 \end{figure}
+\subsection{Power estimates for $\mathcal{E}_\lambda(t)$}
 It was shown in
-\cite{lee:_laten_proces_model_time_attrib_random_graph} that when
-$J_\lambda(t) = \mathrm{size}_{\lambda}(t)$, the normalized fusion
-statistic $T_{\lambda}^{l}(t)$ follows a $t$-distribution with $l - 1$
+\cite{lee:_laten_proces_model_time_attrib_random_graph} that for the
+case where $J_\lambda(t)$ is $\mathcal{E}_{\lambda}(t)$, $T_{\lambda}^{l}(t)$ 
+follows a $t$-distribution with $l - 1$
 degrees of freedom in the limit. Specifically, we have the following
@@
     \pi_{00}) \\
-    \xi = (1+1/l)\tbinom{n}{2} \eta_{00} +
+    \xi = \tfrac{l+1}{l}\tbinom{n}{2} \eta_{00} +
           \tbinom{m}{2}(\eta_{11} - \eta_{00}) + (n-m)m(\eta_{01} -
@@
   \end{gather*}
-As $n \rightarrow \infty$, the random variable
+  Define the random variable $\psi^{l}_{\lambda}(t)$ by
+  \begin{equation}
+    \label{eq:10}
+    \psi^{l}_{\lambda}(t) = \begin{cases}
+      \sqrt{\frac{\langle \lambda, \tbinom{n}{2} \eta_{00}
+            \lambda \rangle}{\langle \lambda, \xi
+            \lambda \rangle}} T_{\lambda}^{l}(t) & \text{if $t = t^{*}$} \\
+      \sqrt{\frac{l}{l + 1}} T_{\lambda}^{l}(t)& \text{if $t < t^{*}$}
+      \end{cases}
+  \end{equation}
+As $n \rightarrow \infty$,
   $\psi^{l}_{\lambda}(t)$ converges weakly to the Student
@@
       \frac{\langle \lambda, \zeta \rangle}{\sqrt{\langle \lambda, \xi \lambda \rangle}} & \text{if $t = t^{*}$} \\
-      0 & \text{otherwise}
+      0 & \text{if $t < t^{*}$}
     \end{cases}
@@
 \end{lemma}
-
+We are interested in finding the $\lambda$ that will maximize the
+power of the test. The power approximation is determined by various
+factors but the dominating factor is likely to be
+$\mu_{\lambda}$. Theorem \ref{thm:1} extends a result in
+\cite{lee:_laten_proces_model_time_attrib_random_graph} for $K = 2$ to the case
+where $K \geq 2$. 
 \begin{theorem}
   \label{thm:1}
-  Let $\lambda^{*}$ be the eigenvector corresponding to the largest
-  eigenvalue of $ \mathbf{A}^{-1/2} \mathbf{B} \mathbf{A}^{-1/2}$,
-  i.e., 
+  Let $\zeta$ and $\xi$ be as defined in Lemma \ref{lem:1}.  Suppose
+  that $\xi$ is also positive definite. Let $\nu^{*}$ be the
+  normalized eigenvector corresponding to the largest eigenvalue of $ \xi^{-1/2}
+  \zeta \zeta^{T} \xi^{-1/2}$, i.e.,
  \begin{equation}
    \label{eq:9}
-  \lambda^{*} = \argmax_{\lambda \colon \| \lambda \| = 1}
-  \lambda^{T} \mathbf{A}^{-1/2} \mathbf{B} \mathbf{A}^{-1/2}
-  \lambda.
+  \nu^{*} = \argmax_{\nu \colon \| \nu \| = 1}
+  \nu^{T} \xi^{-1/2} \zeta \zeta^{T} \xi^{-1/2}
+  \nu.
  \end{equation}
- We then have
+ Then $\lambda^{*} = \tfrac{\xi^{-1/2} \nu^{*}}{\|\xi^{-1/2} \nu^{*} \|}$ satisfies
  \begin{gather}
@@
 \end{theorem}
+\subsection{Power estimates for $\Delta_{\lambda}(t)$}
+The analysis of the power estimates for $\Delta_{\lambda}(t)$ depends
+on some preliminary results which we now state. We denote by
+$\mathcal{G}(\alpha, \beta)$ the Gumbel distribution with location
+parameter $\alpha$ and scale parameter $\beta$.  
+\begin{proposition}
+  \label{prop:3}
+  Let $a_n$ and $b_n$ be constants given by
+  \begin{align*}
+    a_n &= (2 \log{n})^{1/2}\Bigl(1 - \frac{\log{\log{n}}}{4 \log{n}} -
+    \frac{\log{2\pi^{1/2}}}{2 \log{n}} \Bigr) \\ 
+    b_n &= (2 \log{n})^{-1/2}
+  \end{align*}
+  Then as $n \rightarrow \infty$ and $m = \Omega( \sqrt{n \log{n}})$,
+  we have
+  \begin{equation}
+    \label{eq:6}
+    \Delta_{\lambda}(t) \rightsquigarrow \begin{cases}
+      \mathcal{G}(a_n \sigma_1 + \mu_1, b_n \sigma_1 ) & \text{for $t < t^{*}$.} \\
+     \mathcal{G}(a_n \sigma_2 + \mu_2, b_n \sigma_2) &
+     \text{for $t = t^{*}$.}
+     \end{cases}
+  \end{equation}
+  where
+  \begin{align*}
+    \mu_1 &= (n-1)\langle x, \pi_{00} \rangle \\
+    \sigma_1 &= \sqrt{(n-1)\langle x, \eta_{00} x \rangle} \\
+    \mu_2 &= \,\, (m - 1) \langle x, \pi_{11} \rangle + (n-
+    m)\langle x, \pi_{01} \rangle
+    \\ \sigma_2 &= \sqrt{ (m - 1) \langle x, (\eta_{11} x \rangle + (n -
+      m) \left<x, \eta_{01} x\right>}
+    \end{align*}
+\end{proposition}
+\begin{lemma}
+  \label{lem:2}
+  Let $t \in \{l+1, \dots, t^{*}\}$ and $\lambda \in
+  \mathbb{R}^{K}$. For sufficiently large $n$ and sufficiently large
+  $l$, the variable $T_{\lambda}^{l}(t)$ has approximately a Gumbel
+  distribution with location $\rho_{\lambda}$ and scale $\varsigma_{l}$ where
+\begin{equation}
+  \label{eq:8}
+  \rho_{\lambda} = \begin{cases}
+    \frac{ (a_n + b_n \gamma)(\sigma_2 - \sigma_1) + (\mu_2 -
+    \mu_1)}{\tfrac{\pi}{\sqrt{6}}\sqrt{(1 + 1/m)\sigma_1^2 +
+      (\sigma_2^2 - \sigma_1^2)}} & \text{if $t = t_1$} \\ 
+  0 & \text{if $t < t_1$}
+  \end{cases}
+\end{equation}
+$\gamma \approx 0.57721$ is the Euler-Mascheroni constant, and
+\end{lemma}
+\appendices
+\section{Proofs of some stated results}
+\begin{proof}[Theorem \ref{thm:1}]
+  The maximizer of $\mu_\lambda$ also maximizes
+  \begin{equation*}
+    \mu_{\lambda}^{2} = \frac{\lambda^{T} \zeta \zeta^{T}
+      \lambda}{\lambda^{T} \xi \lambda}
+  \end{equation*}
+  Because $\xi$ is positive definite, there exist a positive definite matrix
+  $\xi^{1/2}$ such that $\xi^{1/2} \xi^{1/2} = \xi$. Letting $\nu = \xi^{1/2}
+  \lambda$, the above expression can be rewritten as
+  \begin{equation*}
+    \mu_{\lambda}^{2} = \frac{\nu^{T} \xi^{-1/2} \zeta \zeta^{T}
+      \xi^{-1/2} \nu}{ \nu^{T} \nu}
+  \end{equation*}
+  The claim then follows directly from the Rayleigh-Ritz theorem for
+  Hermitean matrices.
+\end{proof}
 \bibliography{ssp2011}

### 2011-04-28 ssp2011.tex
Add proofs of multinormal approximation

@@
   \includegraphics[width=8cm]{graphics/Fig4-SSP2011.pdf}
-  \caption{Temporal standardization: when testing for change at time $t$, the recent past (graphs $G(t - l), \dots, G(t-1))$ is used to standardize the invariants}
+  \caption{Temporal standardization: when testing for change at time
+    $t$, the recent past (graphs $G(t - l), \dots, G(t-1))$ is used to
+    standardize the invariants}
   \label{fig:temporal}
@@
   \label{prop:3}
-  Let $a_n$ and $b_n$ be constants given by
+  Let $a_n$ and $b_n$ be functions of $n$ given by
   \begin{align*}
@@
       \mathcal{G}(a_n \sigma_1 + \mu_1, b_n \sigma_1 ) & \text{for $t < t^{*}$.} \\
-     \mathcal{G}(a_n \sigma_2 + \mu_2, b_n \sigma_2) &
+     \mathcal{G}(a_m \sigma_2 + \mu_2, b_m \sigma_2) &
      \text{for $t = t^{*}$.}
@@
   \begin{align*}
-    \mu_1 &= (n-1)\langle x, \pi_{00} \rangle \\
-    \sigma_1 &= \sqrt{(n-1)\langle x, \eta_{00} x \rangle} \\
+    \mu_1 &= (n-1)\langle \lambda, \pi_{00} \rangle \\
+    \sigma_1 &= \sqrt{(n-1)\langle \lambda, \eta_{00} \lambda \rangle} \\
     \mu_2 &= \,\, (m - 1) \langle x, \pi_{11} \rangle + (n-
-    m)\langle x, \pi_{01} \rangle
-    \\ \sigma_2 &= \sqrt{ (m - 1) \langle x, (\eta_{11} x \rangle + (n -
-      m) \left<x, \eta_{01} x\right>}
+    m)\langle \lambda, \pi_{01} \rangle
+    \\ \sigma_2 &= \sqrt{ (m - 1) \langle \lambda, \eta_{11} \lambda \rangle + (n -
+      m) \langle \lambda, \eta_{01} \lambda \rangle}
     \end{align*}
@@
   \mathbb{R}^{K}$. For sufficiently large $n$ and sufficiently large
-  $l$, the variable $T_{\lambda}^{l}(t)$ has approximately a Gumbel
-  distribution with location $\rho_{\lambda}$ and scale $\varsigma_{l}$ where
-\begin{equation}
+  $l$, the variable $T_{\lambda}^{l}(t)$ has approximately a
+  $\mathcal{G}(\rho_{\lambda}, \varsigma_{\lambda})$ distribution with
+\begin{align}
   \label{eq:8}
-  \rho_{\lambda} = \begin{cases}
-    \frac{ (a_n + b_n \gamma)(\sigma_2 - \sigma_1) + (\mu_2 -
-    \mu_1)}{\tfrac{\pi}{\sqrt{6}}\sqrt{(1 + 1/m)\sigma_1^2 +
-      (\sigma_2^2 - \sigma_1^2)}} & \text{if $t = t_1$} \\ 
-  0 & \text{if $t < t_1$}
+  \rho_{\lambda} &= \begin{cases}
+    \frac{\sqrt{\pi}}{6} \frac{\mu_2 - \mu_1 + a_m\sigma_2 - (a_n + b_n
+      \gamma)\sigma_1}{b_n \sigma_1} & \text{if $t =
+        t^{*}$} \\
+      - \frac{ \sqrt{\pi}}{6} \gamma & \text{if $t < t^{*}$}
+  \end{cases}\\
+  \varsigma_{\lambda} &= \begin{cases}
+    \frac{\sqrt{\pi} b_m \sigma_2}{6 b_n \sigma_1} & \text{if $t =
+      t^{*}$} \\
+    \frac{\sqrt{\pi}}{6} & \text{if $t < t^{*}$}
     \end{cases}
-\end{equation}
-$\gamma \approx 0.57721$ is the Euler-Mascheroni constant, and
+\end{align}
+$\gamma \approx 0.57721$ is the Euler-Mascheroni constant.
 \end{lemma}
+We are interested in finding the $\lambda$ that will maximize the
+power of the test using $\Delta_{\lambda}$. The power approximation is
+once again determined by various factors, but the dominating factor is
+likely to be $\tfrac{\rho_\lambda}{\varsigma_\lambda}$. For sufficiently large $n$
+and $m$, we also have
+\begin{equation*}
+  \begin{split}
+  \frac{\rho_\lambda}{\varsigma_\lambda} &= (1 + o(1)) \frac{\mu_2 - \mu_1}{b_m
+    \sigma_ 2} \\ &= \frac{\langle \lambda, (m-1)\pi_{11} + (n-m)\pi_{01} -
+    (n-1) \pi_{00} \rangle}{\sqrt{\langle \lambda, ((m-1) \eta_{11} +
+    (n-m)\eta_{01}) \lambda \rangle}}
+  \end{split}
+\end{equation*}
+We can thus find the maximum and minimum of
+$\tfrac{\rho_{\lambda}}{\varsigma_{\lambda}}$ by solving an 
+eigenvalue problem as in Theorem~\ref{thm:1}. 
 \appendices
@@
 \end{proof}
+\begin{proof}[Proposition~\ref{prop:3}]
+  Let $d_{\lambda}(v;t)$ be the (fused) degree of vertex $v$ at time
+  $t$, i.e.,
+  \begin{equation*}
+    d_{\lambda}(v;t) = \sum_{k = 1}^{K} \lambda_k \sum_{u \in N(v)}
+    \mathbf{1}\{ \phi(uv,t) = k \}
+  \end{equation*}
+  By applying the multivariate normal approximation to the
+  multinomial, 
+\end{proof}
+
 \bibliography{ssp2011}

### 2011-04-29 ssp2011.tex
Add discussion of scan statistic

@@
 \usepackage[colorlinks=true,pagebackref,linkcolor=magenta]{hyperref}
+\usepackage{cite}
 %\usepackage[colon,sort&compress]{natbib}
@@
   \mathcal{E}_{\lambda}(G(t)) = \sum_{k=1}^{K} \lambda_k \sum_{u,v}
-  \mathbf{1}\{ \phi(uv,t) = k \} \\
+  \mathbb{I}\{ \phi(uv,t) = k \} \\
   \tau_\lambda(G(t)) = \sum_{k=1}^{K} \lambda_k \!\! \sum_{(u,v,w) \in
@@
   \Delta_{\lambda}(G(t)) = \max_{v \in V} \, \sum_{k = 1}^{K} \lambda_k
-  \sum_{u \in N(v)}{\mathbf{1}\{\phi(uv,t) = k\}} \\
+  \sum_{u \in N(v)}{\mathbb{I}\{\phi(uv,t) = k\}} \\
   \label{eq:3}
   \Psi_{\lambda}(G(t)) = \max_{v \in V} \sum_{k = 1}^{K}
-  \lambda_k \!\!\sum_{u,w \in N(v)}\!\!\! \mathbf{1}\{\phi(uw,t) = k\} 
+  \lambda_k \!\!\sum_{u,w \in N(v)}\!\!\! \mathbb{I}\{\phi(uw,t) = k\} 
   \end{gather}
@@
   \begin{equation}
-    \label{eq:10}
+    \label{eq:15}
     \mu_{\lambda} = \begin{cases}
@@
   \begin{equation}
-    \label{eq:6}
+    \label{eq:14}
     \Delta_{\lambda}(t) \rightsquigarrow \begin{cases}
@@
 \begin{align}
-  \label{eq:8}
+  \label{eq:13}
   \rho_{\lambda} &= \begin{cases}
@@
 eigenvalue problem as in Theorem~\ref{thm:1}. 
+\subsection{Power estimates for $\Psi_{\lambda}(t)$}
+The limiting distribution for the scan statistics for unattributed
+random graphs was considered in
+\cite{rukhin:_limit_distr_graph_scan_statis}. This subsection is
+concerned with the extension of the results in
+\cite{rukhin:_limit_distr_graph_scan_statis} to attributed random
+graphs. We state here some the relevant results. Sketches of the
+proofs of these results will be provided in
+\S~\ref{sec:proofs-some-stated}. \\ \\
+\noindent
+Let $\psi_{\lambda}(v;t)$ be the (fused) locality statistics for
+vertex $v$ at time $t$, i.e.,
+\begin{equation}
+  \label{eq:11}
+  \psi_{\lambda}(v;t) = \sum_{k=1}^{K} \lambda_k \sum_{uw \in N(v)}
+  \mathbb{I}\{\phi(uw,t) = k\}.
+\end{equation}
+We consider first the case where $t < t^{*}$. Then, conditional on
+$|N(v)| = l$, we have
+\begin{equation*}
+  \psi_{\lambda}(v;t) = \sum_{k=1}^{K}{\lambda_k (y_k + z_k)}
+\end{equation*}
+where $(y_1, \dots, y_K)$ and $(z_1, \dots, z_K)$ are distributed as
+\begin{gather*}
+  (y_1,y_2,\dots,y_K) \sim \textrm{multinomial}\Bigl(
+  \tbinom{l}{2}, \pi_{00}\Bigr) \\ (z_1, z_2, \dots, z_K) \sim
+  \textrm{multinomial}\Bigl(l, \frac{\pi_{00}}{\langle \pi_{00},
+    1\rangle}\Bigr). 
+\end{gather*}
+Therefore, for sufficiently large $l$, by the multivariate central
+limit theorem, we have
+\begin{equation*}
+  \Bigl(\psi_\lambda(v;t) \, \lvert \, |N(v)| = l \Bigr) \sim
+  \mathcal{N}\Bigl(\tbinom{l}{2} \langle \lambda, \pi_{00} \rangle,
+  \tbinom{l}{2} \langle \lambda, \eta_{00} \lambda \rangle \Bigr)
+\end{equation*} 
+Let $\lambda^{(2)}$ be the vector whose entries are element-wise
+square of $\lambda$. Then it can be checked that 
+\begin{equation*}
+ \langle \lambda,
+\eta_{00} \lambda \rangle = \langle \lambda^{(2)}, \pi_{00} \rangle -
+  (\langle \lambda, \pi_{00} \rangle)^2
+\end{equation*}
+Suppose that $\eta_{00}$ is positive definite. We then have the
+following result
+\begin{proposition}
+  \label{prop:1}
+  Let $C = \tfrac{\langle \lambda^{(2)}, \pi_{00} \rangle}{\langle
+    \lambda, \pi_{00}\rangle}$ and $p = \tfrac{(\langle \lambda, \pi_{00}
+    \rangle)^{2}}{\langle x^{(2)} \pi_{00} \rangle}$. Then $p < 1$,
+  and for sufficiently large $l$ we have
+\begin{equation}
+  \label{eq:17}
+ \Bigl(\psi_\lambda(v;t) \,\lvert\,\, |N(v)| = l \Bigr) \sim C *  
+ \mathrm{Bin}\Bigl(\tbinom{l}{2}, p\Bigr)
+\end{equation} 
+\end{proposition}
+Proposition~\ref{prop:1} states that the locality
+statistics for the attributed random graphs model under consideration
+can be approximated by the locality statistics for an
+Erd\"{o}s-Renyi graph with edge probability $p$. By a result in
+\cite{rukhin:_limit_distr_graph_scan_statis}, we have
+\begin{theorem}
+  \label{thm:2}
+  Let $\Psi_{\lambda}(t)$ be the (fused) scan statistic. Let
+  $N_{0}$, $a_n$, and $b_n$ be defined by
+\begin{align*}
+   \mu_0 &= (n-1) \langle \pi_{00}, 1 \rangle \\
+ \sigma_0 &= \sqrt{(n-1) (\langle \pi_{00}, 1 \rangle - \langle
+   \pi_{00}, 1 \rangle^2)} \\ 
+ z_n &= \sqrt{2
+      \log{n}}\Bigl(1 - \frac{\log{\log{n}} + \log{4 \pi}}{4
+      \log{n}}\Bigr) \\
+    N_{0} &= \mu_0 + z_n \sigma_0 \\
+   a_n &= N_{0} \frac{\langle \lambda, \pi_{00} \rangle}{\langle 1,
+     \pi_{00} \rangle} + p\tbinom{N_{0}}{2} \\ 
+   b_n &= (1 - \tfrac{p}{2} + p N_{0}) \frac{\sigma_0}{\sqrt{2 \log
+     n}}
+\end{align*}
+Then we have
+\begin{equation}
+  \Psi_{\lambda}(t) \rightsquigarrow \mathcal{G}(C a_n, C b_n)
+\end{equation}
+\end{theorem}
+We now move to the case where $t = t^{*}$. Let $d_{\zeta}(v;t)$ be
+the number of neighbors of $v$ that lies in $[m]$ (the egg) and
+$d_{\xi}(v;t)$ be the number of neighbors of $v$ that lies in $[n]
+\setminus [m]$ (the kidney). Conditional on $d_{\zeta}(v;t^{*}) =
+l_{\zeta}$, $d_{\xi}(v;t^{*}) = l_{\xi}$, we have
+\begin{equation}
+  \psi_{\lambda}(v;t^{*}) = \sum_{k=1}^{K} \lambda_k ( y^{(\zeta)}_k + y^{(\xi)}_k +
+  y^{(\omega)}_k + z^{(\zeta)}_k + z^{(\xi)}_k)
+\end{equation}
+where $(y^{(\zeta)}_1, \dots, y^{(\zeta)}_m)$, $(y^{(\xi)}_1,\dots,
+ y^{(\xi)}_m)$, $(y^{(\omega)}_1, \dots, y^{(\omega)}_m)$ are
+ distributed as
+\begin{gather*}
+(y^{(\zeta)}_1,\dots,y^{(\zeta)}_m) \sim \textrm{multinomial}\Bigl(
+\tbinom{l_\zeta}{2}, \pi_{11}\Bigr) \\ 
+(y^{(\xi)}_1,\dots,y^{(\xi)}_m) \sim \textrm{multinomial}\Bigl(
+\tbinom{l_\xi}{2}, \pi_{00}\Bigr) \\
+(y^{(\omega)}_1,\dots,y^{(\omega)}_m) \sim \textrm{multinomial}\Bigl(
+l_\zeta l_\xi, \pi_{10}\Bigr)
+\end{gather*}
+and $(z^{(\zeta)}_1, \dots, z^{(\zeta)}_m)$, $(z^{(\xi)}_1, \dots,
+z^{(\xi)}_m)$ are distributed as
+\begin{gather*}
+(z^{(\zeta)}_1, \dots, z^{(\zeta)}_m) \sim
+\begin{cases}
+\textrm{multinomial}\Bigl(l_\zeta, \frac{\pi_{11}}{\langle \pi_{11},
+  1\rangle}\Bigr) & \text{if $v \in [m]$} \\
+\textrm{multinomial}\Bigl(l_\zeta, \frac{\pi_{10}}{\langle \pi_{10}, 1
+  \rangle} \Bigr) & \text{if $v \not\in [m]$}
+\end{cases} \\
+(z^{(\xi)}_1, \dots, z^{(\xi)}_m) \sim
+\begin{cases}
+\textrm{multinomial}\Bigl(l_\xi, \frac{\pi_{10}}{\langle \pi_{10},
+  1\rangle}\Bigr) & \text{if $v \in [m]$} \\
+\textrm{multinomial}\Bigl(l_\zeta, \frac{\pi_{00}}{\langle \pi_{00}, 1
+  \rangle} \Bigr) & \text{if $v \notin [m]$}
+\end{cases} 
+\end{gather*}
+Thus, for sufficiently large $l_{\zeta}$ and $l_{\xi}$, we have
+\begin{equation}
+  \begin{split}
+ \psi_{\lambda}(v;t^{*}) & \sim  \mathcal{N}\Bigl(\tbinom{l_\zeta}{2}
+ \langle \lambda, \pi_{11} \rangle,
+  \tbinom{l_\zeta}{2} \langle x, \eta_{11} \lambda \rangle \Bigr) \\ &+ 
+  \mathcal{N}\Bigl(\tbinom{l_\xi}{2} \langle \lambda, \pi_{00} \rangle,
+  \tbinom{l_\xi}{2} \langle \lambda, \eta_{00} \lambda \rangle \Bigr) \\ &+ 
+  \mathcal{N}\Bigl(l_\zeta l_\xi \langle \lambda, \pi_{10} \rangle,
+  l_\zeta l_\xi \langle \lambda, \eta_{10} \lambda \rangle \Bigr)
+\end{split}
+\end{equation}
+\begin{proposition}
+  \label{prop:2}
+  Let $C_1, C_2, C_3$ and $p_1$, $p_2$, $p_3$ be 
+  \begin{gather*}
+C_1 = \tfrac{\langle \lambda^{(2)}, \pi_{00} \rangle}{\langle \lambda,
+    \pi_{00}\rangle}; \quad p_1 = \tfrac{(\langle \lambda, \pi_{00}
+    \rangle)^{2}}{\langle \lambda^{(2)} \pi_{00} \rangle} \\
+C_2 = \tfrac{\langle \lambda^{(2)}, \pi_{11} \rangle}{\langle \lambda,
+    \pi_{11}\rangle}; \quad p_2 = \tfrac{(\langle \lambda, \pi_{11}
+    \rangle)^{2}}{\langle \lambda^{(2)} \pi_{11} \rangle} \\
+C_3 = \tfrac{\langle \lambda^{(2)}, \pi_{11} \rangle}{\langle \lambda,
+    \pi_{10}\rangle}; \quad p_1 = \tfrac{(\langle \lambda, \pi_{10}
+    \rangle)^{2}}{\langle \lambda^{(2)} \pi_{10} \rangle} 
+\end{gather*}
+  Then $p_1$, $p_2$, and $p_3$ are all at most $1$. Furthermore, for
+  sufficiently large $l_\zeta$ and $l_\xi$ we have
+\begin{equation*}
+  \begin{split}
+ \psi_{\lambda}(v;t_1) &\sim C_1 *  
+ \mathrm{Bin}\Bigl(\tbinom{l_\zeta}{2}, p_1\Bigr) + C_2 *  
+ \mathrm{Bin}\Bigl(\tbinom{l_\xi}{2}, p_2\Bigr) \\ &+ C_3 *
+ \mathrm{Bin}\Bigl(l_\zeta l_\xi, p_3\Bigr)
+ \end{split}
+\end{equation*} 
+\end{proposition}
+Proposition~\ref{prop:2} state that the locality statistics
+for the attributed random graphs model under consideration at time $t
+= t^{*}$ can be approximated by the locality
+statistics for an unattributed kidney and egg random graph model
+$\kappa(n,n_1,p_1,p_2,p_3)$. Let us define $B$, $C$, $E$ and $F$ by
+\begin{gather*}
+  B \sim \mathrm{Bin}(m, \langle 1, \pi_{00} \rangle); \quad C \sim \mathrm{Bin}(n-m-1,
+ \langle 1, \pi_{01} \rangle) \\
+  E \sim \mathrm{Bin}(m-1, \langle 1, \pi_{11} \rangle); \quad F \sim \mathrm{Bin}(n-m,
+  \langle 1, \pi_{01} \rangle)
+\end{gather*}
+For any random variable $X$, we let $\mu_X$ and $\sigma_X^{2}$ denote
+the mean and variance of $X$. If $X$ and $Y$ are independent random
+variables, we let $\mu_{X + Y}$ and $\sigma_{X + Y}^2$ denote the mean
+and variance of the convolution $X + Y$. \\
+\noindent Let $N_{\kappa}$ be the quantity defined by
+\begin{equation}
+  \label{eq:18}
+  N_{\kappa} = \mu_{E + F} + z_m \sigma_{E + F}
+\end{equation}
+where $z_m$ is
+\begin{equation*}
+  z_m = \sqrt{2 \log m}\Bigl(1 - \frac{\log{\log{m}} + \log{4
+      \pi}}{\log{m}}\Bigr)
+\end{equation*}
+The following result is adapted from \cite{rukhin:_limit_distr_graph_scan_statis}
+\begin{theorem}
+  \label{thm:3}
+  Let $a_{n,m}$ and $b_{n,m}$ be given by
+  \begin{gather}
+    \label{eq:28}
+    \begin{split}
+    a_{n,m} &= N_{\kappa} \frac{\langle x, \pi_{01} \rangle}{\langle 1, \pi_{01} \rangle} \\ &+ C_1 p_1 \binom{N_\kappa}{2} + (C_2 p_2 -
+    C_1 p_1)\binom{\mu_E}{2} \\ &+ (C_3 p_3 - C_1 p_1)\mu_E \mu_F 
+    \end{split} \\
+    b_{n,m} = (1 - \tfrac{C_1 p_1}{2} + C_1 p_1
+    N_\kappa)\frac{\sigma_{E + F}}{\sqrt{2 \log{n_1}}}
+  \end{gather}
+  If $m = \Omega(\sqrt{n \log n})$, then
+  \begin{equation}
+    \label{eq:29}
+    \Psi_{\lambda}(t^{*}) \rightsquigarrow \mathcal{G}(a_{n,m}, b_{n,m})
+  \end{equation}
+\end{theorem}
 \appendices
 \section{Proofs of some stated results}
+\label{sec:proofs-some-stated}
 \begin{proof}[Theorem \ref{thm:1}]
@@
   \begin{equation*}
-    d_{\lambda}(v;t) = \sum_{k = 1}^{K} \lambda_k \sum_{u \in N(v)}
-    \mathbf{1}\{ \phi(uv,t) = k \}
+    d_{\lambda}(v;t) = \sum_{k = 1}^{K} \lambda_k \sum_{w \in N(v)}
+    \mathbb{I}\{ \phi(vw,t) = k \}
   \end{equation*}
-  By applying the multivariate normal approximation to the
-  multinomial, 
+  Let $\Gamma^{(k)}(v;t) = |\{w \colon \mathbb{I}\{\phi(wv,t) =
+  k\}|$. The vector $\bm{\Gamma}(v;t) = (\Gamma^{(1)}(v;t), \dots,
+  \Gamma^{(K)}(v;t))$ for $t < t^{*}$ is distributed as a multinomial
+  with $n-1$ trials and probability vector $\pi_0$. The following
+  statements are made in the limit as $n \rightarrow \infty$ for fixed
+  $K$. By the multivariate
+  central limit theorem, we have
+  \begin{equation*}
+    \bm{\Gamma}(v;t) \sim \mathcal{N}((n-1)\pi_0,
+    (n-1)(\mathrm{diag}(\pi_0) - \pi_0 \pi_0^{T}))
+  \end{equation*}
+  Now, $d_{\lambda}(v;t) = \langle \lambda, \bm{\Gamma}(v;t) \rangle$
+  and therefore
+  \begin{equation}
+    \label{eq:12}
+    d_{\lambda}(v;t) \sim \mathcal{N}((n-1) \langle \lambda, \pi_0
+    \rangle, (n-1) \langle \lambda, \eta_{00} \lambda \rangle)
+  \end{equation}
+  where $\eta_{00} = \mathrm{diag}(\pi_0) - \pi_0
+  \pi_0^{T}$. $\Delta_{\lambda}(t)$ for $t < t^{*}$ is thus the
+  maximum of a sequence of {\em dependent} Gaussian random
+  variables. By an argument analogous to the argument for the maximum
+  degree of an Erd\"{o}s-Renyi random graph in \cite[\S
+  III.1]{bollobas85:_random_graph} we can show that the dependency
+  among the $d_{\lambda}(v,t)$ can be safely
+  ignored. $\Delta_{\lambda}(t)$ is then equivalent to the maximum of
+  a sequence of {\em independent} $\mathcal{N}((n-1) \langle \lambda,
+  \pi_0 \rangle, (n-1) \langle \lambda, \eta_{00} \lambda
+  \rangle)$. The resulting distribution is a Gumbel \cite[\S
+  2.3]{galambos87:_asymp_theor_extrem_order_statis} and we obtain 
+  Eq.~\eqref{eq:14} for $t < t^{*}$. The case when $t = t^{*}$ can be
+  derive in a similar manner, see e.g,
+  \cite{rukhin:_limit_distr_graph_scan_statis}.
 \end{proof}
-
+\begin{proof}[Lemma~\ref{lem:2}]
+  Let $ X \sim \mathcal{G}(\alpha, \beta)$. We consider the
+  normalization $\tfrac{X - \mu}{\sigma}$. We have
+  \begin{equation*}
+    \begin{split}
+    \mathbb{P}[ \frac{X - \mu}{\sigma} \leq z]  &= \mathbb{P}[X \leq z
+    \sigma + \mu] 
+    = e^{-e^{-(z \sigma + \mu - \alpha)/\beta}} \\
+      &= e^{- e^{-(z - (\alpha - \mu)/\sigma)/(\beta/\sigma)}}
+    \end{split}
+  \end{equation*}
+  Thus, $\tfrac{X - \mu}{\sigma} \sim \mathcal{G}(\tfrac{\alpha -
+    \mu}{\sigma}, \tfrac{\beta}{\sigma})$. Because the sample
+  mean and the sample variance are consistent estimators, the claims
+  follow after an application of Slutsky's theorem.
+\end{proof}
 \bibliography{ssp2011}

### 2011-04-29 ssp2011.tex
Revised some proofs

@@
 \cite{rukhin:_limit_distr_graph_scan_statis}. This subsection is
-concerned with the extension of the results in
+concerned with adpating the results in
 \cite{rukhin:_limit_distr_graph_scan_statis} to attributed random
-graphs. We state here some the relevant results. Sketches of the
-proofs of these results will be provided in
-\S~\ref{sec:proofs-some-stated}. \\ \\
+graphs. We state here only the relevant results. The proofs are
+delegated to the appendices. \\ \\
 \noindent
-Let $\psi_{\lambda}(v;t)$ be the (fused) locality statistics for
-vertex $v$ at time $t$, i.e.,
+The limiting distribution for $\Psi_{\lambda}(t)$ is Gumbel for both
+the case where $t < t^{*}$ and for $t = t^{*}$. To aid the exposition,
+we first introduce some notations. Let $\lambda^{(2)}$ be the
+element-wise square of $\lambda$. Define $C_{00}$, $C_{01}$, $C_{11}$
+and $p_{00}$, $p_{01}$, $p_{11}$ to be
+\begin{gather}
+  \label{eq:19}
+  C_{00} = \tfrac{\langle \lambda^{(2)}, \pi_{00} \rangle}{\langle \lambda,
+    \pi_{00}\rangle}; \quad p_{00} = \tfrac{(\langle \lambda, \pi_{00}
+    \rangle)^{2}}{\langle \lambda^{(2)},\, \pi_{00} \rangle} \\
+C_{11} = \tfrac{\langle \lambda^{(2)}, \pi_{11} \rangle}{\langle \lambda,
+    \pi_{11}\rangle}; \quad p_{11} = \tfrac{(\langle \lambda, \pi_{11}
+    \rangle)^{2}}{\langle \lambda^{(2)},\, \pi_{11} \rangle} \\
+C_{10} = \tfrac{\langle \lambda^{(2)}, \pi_{11} \rangle}{\langle \lambda,
+    \pi_{10}\rangle}; \quad p_{10} = \tfrac{(\langle \lambda, \pi_{10}
+    \rangle)^{2}}{\langle \lambda^{(2)},\, \pi_{10} \rangle} 
+\end{gather}
+Also let $z_n$ be defined, for any $n \in \mathbb{N}$, by
 \begin{equation}
-  \label{eq:11}
-  \psi_{\lambda}(v;t) = \sum_{k=1}^{K} \lambda_k \sum_{uw \in N(v)}
-  \mathbb{I}\{\phi(uw,t) = k\}.
+  \label{eq:20}
+   z_n = \sqrt{2
+      \log{n}}\Bigl(1 - \frac{\log{\log{n}} + \log{4 \pi}}{4
+      \log{n}}\Bigr)
 \end{equation}
-We consider first the case where $t < t^{*}$. Then, conditional on
-$|N(v)| = l$, we have
+\begin{theorem}
+  \label{thm:2}
+  Let $\Psi_{\lambda}(t)$ be the scan statistic for $t < t^{*}$. Let
+  $N_{0}$, $a_n$, and $b_n$ be defined by
+\begin{align*}
+   \mu_0 &= (n-1) \langle 1, \pi_{00} \rangle \\
+   \sigma_0 &= \sqrt{(n-1) (\langle 1, \pi_{00} \rangle - \langle
+     1, \pi_{00} \rangle^2)} \\ 
+    N_{0} &= \mu_0 + z_n \sigma_0 \\
+    a_n &= N_{0} \frac{\langle \lambda, \pi_{00} \rangle}{\langle
+      1, \pi_{00} \rangle} + C_{00}p_{00}\tbinom{N_{0}}{2} \\ 
+   b_n &= (1 - \tfrac{C_{00}p_{00}}{2} + C_{00}p_{00} N_{0}) \frac{\sigma_0}{\sqrt{2 \log
+     n}}
+\end{align*}
+Then we have
+\begin{equation}
+  \frac{\Psi_{\lambda}(t) - a_{n}}{b_n} \rightsquigarrow
+  \mathcal{G}(0, 1)
+\end{equation}
+\end{theorem}%
+We now move to the limiting distribution for $\Psi_{\lambda}(t^{*})$. 
+Let us define $E$ and $F$ by
+\begin{gather*}
+ %  B \sim \mathrm{Bin}(m, \langle 1, \pi_{00} \rangle); \quad C \sim \mathrm{Bin}(n-m-1,
+ % \langle 1, \pi_{01} \rangle) \\
+  E \sim \mathrm{Bin}(m-1, \langle \pi_{11}, 1 \rangle) \\ F \sim \mathrm{Bin}(n-m,
+  \langle \pi_{01}, 1 \rangle)
+\end{gather*}%
+For any random variable $X$, we let $\mu_X$ and $\sigma_X^{2}$ denote
+the mean and variance of $X$. If $X$ and $Y$ are independent random
+variables, we let $\mu_{X + Y}$ and $\sigma_{X + Y}^2$ denote the mean
+and variance of the convolution $X + Y$. \\
+\noindent Let $N_{\kappa}$ be the quantity defined by
+\begin{equation}
+  \label{eq:18}
+  N_{\kappa} = \mu_{E + F} + z_m \sigma_{E + F}
+\end{equation}
+\begin{theorem}
+  \label{thm:3}
+  Let $a_{n,m}$ and $b_{n,m}$ be given by
+  \begin{gather}
+    \label{eq:28}
+    \begin{split}
+    a_{n,m} &=%  N_{\kappa} \frac{\langle x, \pi_{01} \rangle}{\langle
+ %      1, \pi_{01} \rangle} \\
+ % & +
+    C_{00} p_{00} \Bigl(\tbinom{N_\kappa}{2} - \tbinom{\mu_E}{2} - \mu_E
+    \mu_F\Bigr) \\ 
+     & + C_{11} p_{11} \tbinom{\mu_E}{2} + C_{01} p_{01} \mu_E \mu_F 
+    \end{split} \\
+    b_{n,m} = (1 - \tfrac{C_{00} p_{00}}{2} + C_{00} p_{00}
+    N_\kappa)\frac{\sigma_{E + F}}{\sqrt{2 \log{n_1}}}
+  \end{gather}
+  If $m = \Omega(\sqrt{n \log n})$, then
+  \begin{equation}
+    \label{eq:29}
+    \frac{\Psi_{\lambda}(t^{*}) - a_{n,m}}{b_{n,m}}  \rightsquigarrow \mathcal{G}(0,1)  \end{equation}
+\end{theorem}
+\appendices
+\section{Proofs of some stated results}
+\label{sec:proofs-some-stated}
+\begin{proof}[Theorem \ref{thm:1}]
+  The maximizer of $\mu_\lambda$ also maximizes
   \begin{equation*}
-  \psi_{\lambda}(v;t) = \sum_{k=1}^{K}{\lambda_k (y_k + z_k)}
+    \mu_{\lambda}^{2} = \frac{\lambda^{T} \zeta \zeta^{T}
+      \lambda}{\lambda^{T} \xi \lambda}
   \end{equation*}
-where $(y_1, \dots, y_K)$ and $(z_1, \dots, z_K)$ are distributed as
-\begin{gather*}
-  (y_1,y_2,\dots,y_K) \sim \textrm{multinomial}\Bigl(
-  \tbinom{l}{2}, \pi_{00}\Bigr) \\ (z_1, z_2, \dots, z_K) \sim
-  \textrm{multinomial}\Bigl(l, \frac{\pi_{00}}{\langle \pi_{00},
-    1\rangle}\Bigr). 
-\end{gather*}
-Therefore, for sufficiently large $l$, by the multivariate central
-limit theorem, we have
+  Because $\xi$ is positive definite, there exist a positive definite matrix
+  $\xi^{1/2}$ such that $\xi^{1/2} \xi^{1/2} = \xi$. Letting $\nu = \xi^{1/2}
+  \lambda$, the above expression can be rewritten as
   \begin{equation*}
-  \Bigl(\psi_\lambda(v;t) \, \lvert \, |N(v)| = l \Bigr) \sim
-  \mathcal{N}\Bigl(\tbinom{l}{2} \langle \lambda, \pi_{00} \rangle,
-  \tbinom{l}{2} \langle \lambda, \eta_{00} \lambda \rangle \Bigr)
+    \mu_{\lambda}^{2} = \frac{\nu^{T} \xi^{-1/2} \zeta \zeta^{T}
+      \xi^{-1/2} \nu}{ \nu^{T} \nu}
   \end{equation*}
-Let $\lambda^{(2)}$ be the vector whose entries are element-wise
-square of $\lambda$. Then it can be checked that 
+  The claim then follows directly from the Rayleigh-Ritz theorem for
+  Hermitean matrices.
+\end{proof}
+\begin{proof}[Proposition~\ref{prop:3}]
+  Let $d_{\lambda}(v;t)$ be the (fused) degree of vertex $v$ at time
+  $t$, i.e.,
   \begin{equation*}
- \langle \lambda,
-\eta_{00} \lambda \rangle = \langle \lambda^{(2)}, \pi_{00} \rangle -
-  (\langle \lambda, \pi_{00} \rangle)^2
+    d_{\lambda}(v;t) = \sum_{k = 1}^{K} \lambda_k \sum_{w \in N(v)}
+    \mathbb{I}\{ \phi(vw,t) = k \}
   \end{equation*}
+  Let $\Gamma^{(k)}(v;t) = |\{w \colon \mathbb{I}\{\phi(wv,t) =
+  k\}|$. The vector $\bm{\Gamma}(v;t) = (\Gamma^{(1)}(v;t), \dots,
+  \Gamma^{(K)}(v;t))$ for $t < t^{*}$ is distributed as a multinomial
+  with $n-1$ trials and probability vector $\pi_0$. By the multivariate
+  normal approximation to the multinomial, we have
+  \begin{equation*}
+    \bm{\Gamma}(v;t) \approx \mathcal{N}((n-1)\pi_0,
+    (n-1)(\mathrm{diag}(\pi_0) - \pi_0 \pi_0^{T}))
+  \end{equation*}
+  Now, $d_{\lambda}(v;t) = \langle \lambda, \bm{\Gamma}(v;t) \rangle$
+  and thus, for sufficiently large $n$ we have
+  \begin{equation*}
+    d_{\lambda}(v;t) = (1 + o_P(1)) \mathcal{N}((n-1) \langle \lambda, \pi_0
+    \rangle, (n-1) \langle \lambda, \eta_{00} \lambda \rangle)
+  \end{equation*}
+  where $\eta_{00} = \mathrm{diag}(\pi_0) - \pi_0 \pi_0^{T}$ and
+  $o_P(1)$ denotes a random variables that converges to $0$ in
+  probability. We can thus take $\Delta_{\lambda}(t)$ for $t < t^{*}$
+  as the maximum of a sequence of {\em dependent} Gaussian random
+  variables. By an argument analogous to the argument for the maximum
+  degree of an Erd\"{o}s-Renyi random graph in \cite[\S
+  III.1]{bollobas85:_random_graph} we can show that the dependency
+  among the $d_{\lambda}(v,t)$ can be safely
+  ignored. $\Delta_{\lambda}(t)$ can thus be taken as the maximum of
+  {\em independent} $\mathcal{N}((n-1) \langle \lambda,
+  \pi_0 \rangle, (n-1) \langle \lambda, \eta_{00} \lambda
+  \rangle)$. The resulting distribution is a Gumbel \cite[\S
+  2.3]{galambos87:_asymp_theor_extrem_order_statis} and we obtain
+  Eq.~\eqref{eq:14} for $t < t^{*}$. The case when $t = t^{*}$ can be
+  derive in a similar manner, see e.g,
+  \cite{rukhin:_limit_distr_graph_scan_statis}.
+\end{proof}
+\begin{proof}[Lemma~\ref{lem:2}]
+  Let $ X \sim \mathcal{G}(\alpha, \beta)$. We consider the
+  normalization $\tfrac{X - \mu}{\sigma}$. We have
+  \begin{equation*}
+    \begin{split}
+    \mathbb{P}[ \frac{X - \mu}{\sigma} \leq z]  &= \mathbb{P}[X \leq z
+    \sigma + \mu] 
+    = e^{-e^{-(z \sigma + \mu - \alpha)/\beta}} \\
+      &= e^{- e^{-(z - (\alpha - \mu)/\sigma)/(\beta/\sigma)}}
+    \end{split}
+  \end{equation*}
+  Thus, $\tfrac{X - \mu}{\sigma} \sim \mathcal{G}(\tfrac{\alpha -
+    \mu}{\sigma}, \tfrac{\beta}{\sigma})$. Because the sample
+  mean and the sample variance are consistent estimators, the claims
+  follow after an application of Slutsky's theorem.
+\end{proof}
 Suppose that $\eta_{00}$ is positive definite. We then have the
@@
   and for sufficiently large $l$ we have
-\begin{equation}
-  \label{eq:17}
- \Bigl(\psi_\lambda(v;t) \,\lvert\,\, |N(v)| = l \Bigr) \sim C *  
- \mathrm{Bin}\Bigl(\tbinom{l}{2}, p\Bigr)
-\end{equation} 
 \end{proposition}
@@
 \cite{rukhin:_limit_distr_graph_scan_statis}, we have
-\begin{theorem}
-  \label{thm:2}
-  Let $\Psi_{\lambda}(t)$ be the (fused) scan statistic. Let
-  $N_{0}$, $a_n$, and $b_n$ be defined by
-\begin{align*}
-   \mu_0 &= (n-1) \langle \pi_{00}, 1 \rangle \\
- \sigma_0 &= \sqrt{(n-1) (\langle \pi_{00}, 1 \rangle - \langle
-   \pi_{00}, 1 \rangle^2)} \\ 
- z_n &= \sqrt{2
-      \log{n}}\Bigl(1 - \frac{\log{\log{n}} + \log{4 \pi}}{4
-      \log{n}}\Bigr) \\
-    N_{0} &= \mu_0 + z_n \sigma_0 \\
-   a_n &= N_{0} \frac{\langle \lambda, \pi_{00} \rangle}{\langle 1,
-     \pi_{00} \rangle} + p\tbinom{N_{0}}{2} \\ 
-   b_n &= (1 - \tfrac{p}{2} + p N_{0}) \frac{\sigma_0}{\sqrt{2 \log
-     n}}
-\end{align*}
-Then we have
-\begin{equation}
-  \Psi_{\lambda}(t) \rightsquigarrow \mathcal{G}(C a_n, C b_n)
-\end{equation}
-\end{theorem}
 We now move to the case where $t = t^{*}$. Let $d_{\zeta}(v;t)$ be
@@
 statistics for an unattributed kidney and egg random graph model
-$\kappa(n,n_1,p_1,p_2,p_3)$. Let us define $B$, $C$, $E$ and $F$ by
+\begin{proof}[Theorem~\ref{thm:2}]
+Let $\psi_{\lambda}(v;t)$ be the (fused) locality statistics for
+vertex $v$ at time $t$, i.e.,
+\begin{equation}
+  \label{eq:11}
+  \psi_{\lambda}(v;t) = \sum_{k=1}^{K} \lambda_k \sum_{uw \in N(v)}
+  \mathbb{I}\{\phi(uw,t) = k\}.
+\end{equation}
+The following statements are made conditional on $|N(v)| = l$. First
+of all, we have
+\begin{equation*}
+  \psi_{\lambda}(v;t) = \sum_{k=1}^{K}{\lambda_k (y_k + z_k)}
+\end{equation*}
+where $(y_1, \dots, y_K)$ and $(z_1, \dots, z_K)$ are distributed as
 \begin{gather*}
-  B \sim \mathrm{Bin}(m, \langle 1, \pi_{00} \rangle); \quad C \sim \mathrm{Bin}(n-m-1,
- \langle 1, \pi_{01} \rangle) \\
-  E \sim \mathrm{Bin}(m-1, \langle 1, \pi_{11} \rangle); \quad F \sim \mathrm{Bin}(n-m,
-  \langle 1, \pi_{01} \rangle)
+  (y_1,y_2,\dots,y_K) \sim \textrm{multinomial}\Bigl(
+  \tbinom{l}{2}, \pi_{00}\Bigr) \\ (z_1, z_2, \dots, z_K) \sim
+  \textrm{multinomial}\Bigl(l, \frac{\pi_{00}}{\langle \pi_{00},
+    1\rangle}\Bigr). 
 \end{gather*}
-For any random variable $X$, we let $\mu_X$ and $\sigma_X^{2}$ denote
-the mean and variance of $X$. If $X$ and $Y$ are independent random
-variables, we let $\mu_{X + Y}$ and $\sigma_{X + Y}^2$ denote the mean
-and variance of the convolution $X + Y$. \\
-\noindent Let $N_{\kappa}$ be the quantity defined by
-\begin{equation}
-  \label{eq:18}
-  N_{\kappa} = \mu_{E + F} + z_m \sigma_{E + F}
-\end{equation}
-where $z_m$ is
-\begin{equation*}
-  z_m = \sqrt{2 \log m}\Bigl(1 - \frac{\log{\log{m}} + \log{4
-      \pi}}{\log{m}}\Bigr)
-\end{equation*}
-The following result is adapted from \cite{rukhin:_limit_distr_graph_scan_statis}
-\begin{theorem}
-  \label{thm:3}
-  Let $a_{n,m}$ and $b_{n,m}$ be given by
-  \begin{gather}
-    \label{eq:28}
-    \begin{split}
-    a_{n,m} &= N_{\kappa} \frac{\langle x, \pi_{01} \rangle}{\langle 1, \pi_{01} \rangle} \\ &+ C_1 p_1 \binom{N_\kappa}{2} + (C_2 p_2 -
-    C_1 p_1)\binom{\mu_E}{2} \\ &+ (C_3 p_3 - C_1 p_1)\mu_E \mu_F 
-    \end{split} \\
-    b_{n,m} = (1 - \tfrac{C_1 p_1}{2} + C_1 p_1
-    N_\kappa)\frac{\sigma_{E + F}}{\sqrt{2 \log{n_1}}}
-  \end{gather}
-  If $m = \Omega(\sqrt{n \log n})$, then
-  \begin{equation}
-    \label{eq:29}
-    \Psi_{\lambda}(t^{*}) \rightsquigarrow \mathcal{G}(a_{n,m}, b_{n,m})
-  \end{equation}
-\end{theorem}
-\appendices
-\section{Proofs of some stated results}
-\label{sec:proofs-some-stated}
-\begin{proof}[Theorem \ref{thm:1}]
-  The maximizer of $\mu_\lambda$ also maximizes
-  \begin{equation*}
-    \mu_{\lambda}^{2} = \frac{\lambda^{T} \zeta \zeta^{T}
-      \lambda}{\lambda^{T} \xi \lambda}
-  \end{equation*}
-  Because $\xi$ is positive definite, there exist a positive definite matrix
-  $\xi^{1/2}$ such that $\xi^{1/2} \xi^{1/2} = \xi$. Letting $\nu = \xi^{1/2}
-  \lambda$, the above expression can be rewritten as
-  \begin{equation*}
-    \mu_{\lambda}^{2} = \frac{\nu^{T} \xi^{-1/2} \zeta \zeta^{T}
-      \xi^{-1/2} \nu}{ \nu^{T} \nu}
-  \end{equation*}
-  The claim then follows directly from the Rayleigh-Ritz theorem for
-  Hermitean matrices.
-\end{proof}
-\begin{proof}[Proposition~\ref{prop:3}]
-  Let $d_{\lambda}(v;t)$ be the (fused) degree of vertex $v$ at time
-  $t$, i.e.,
-  \begin{equation*}
-    d_{\lambda}(v;t) = \sum_{k = 1}^{K} \lambda_k \sum_{w \in N(v)}
-    \mathbb{I}\{ \phi(vw,t) = k \}
-  \end{equation*}
-  Let $\Gamma^{(k)}(v;t) = |\{w \colon \mathbb{I}\{\phi(wv,t) =
-  k\}|$. The vector $\bm{\Gamma}(v;t) = (\Gamma^{(1)}(v;t), \dots,
-  \Gamma^{(K)}(v;t))$ for $t < t^{*}$ is distributed as a multinomial
-  with $n-1$ trials and probability vector $\pi_0$. The following
-  statements are made in the limit as $n \rightarrow \infty$ for fixed
-  $K$. By the multivariate
-  central limit theorem, we have
-  \begin{equation*}
-    \bm{\Gamma}(v;t) \sim \mathcal{N}((n-1)\pi_0,
-    (n-1)(\mathrm{diag}(\pi_0) - \pi_0 \pi_0^{T}))
-  \end{equation*}
-  Now, $d_{\lambda}(v;t) = \langle \lambda, \bm{\Gamma}(v;t) \rangle$
-  and therefore
-  \begin{equation}
-    \label{eq:12}
-    d_{\lambda}(v;t) \sim \mathcal{N}((n-1) \langle \lambda, \pi_0
-    \rangle, (n-1) \langle \lambda, \eta_{00} \lambda \rangle)
-  \end{equation}
-  where $\eta_{00} = \mathrm{diag}(\pi_0) - \pi_0
-  \pi_0^{T}$. $\Delta_{\lambda}(t)$ for $t < t^{*}$ is thus the
-  maximum of a sequence of {\em dependent} Gaussian random
-  variables. By an argument analogous to the argument for the maximum
-  degree of an Erd\"{o}s-Renyi random graph in \cite[\S
-  III.1]{bollobas85:_random_graph} we can show that the dependency
-  among the $d_{\lambda}(v,t)$ can be safely
-  ignored. $\Delta_{\lambda}(t)$ is then equivalent to the maximum of
-  a sequence of {\em independent} $\mathcal{N}((n-1) \langle \lambda,
-  \pi_0 \rangle, (n-1) \langle \lambda, \eta_{00} \lambda
-  \rangle)$. The resulting distribution is a Gumbel \cite[\S
-  2.3]{galambos87:_asymp_theor_extrem_order_statis} and we obtain 
-  Eq.~\eqref{eq:14} for $t < t^{*}$. The case when $t = t^{*}$ can be
-  derive in a similar manner, see e.g,
-  \cite{rukhin:_limit_distr_graph_scan_statis}.
-\end{proof}
-\begin{proof}[Lemma~\ref{lem:2}]
-  Let $ X \sim \mathcal{G}(\alpha, \beta)$. We consider the
-  normalization $\tfrac{X - \mu}{\sigma}$. We have
+For large $l$, by the multivariate normal
+approximation to the multinomial we have
 \begin{equation*}
   \begin{split}
-    \mathbb{P}[ \frac{X - \mu}{\sigma} \leq z]  &= \mathbb{P}[X \leq z
-    \sigma + \mu] 
-    = e^{-e^{-(z \sigma + \mu - \alpha)/\beta}} \\
-      &= e^{- e^{-(z - (\alpha - \mu)/\sigma)/(\beta/\sigma)}}
+  \psi_\lambda(v;t) & = (1 + o_{P}(1)) \mathcal{N}\Bigl(\tbinom{l}{2} \langle \lambda, \pi_{00} \rangle,
+  \tbinom{l}{2} \langle \lambda, \eta_{00} \lambda \rangle \Bigr) \\ 
+  &= (1 + o_{P}(1)) C_{00} \mathcal{N}(\tbinom{l}{2} p_{00}, \tbinom{l}{2} p_{00}
+  (1 - p_{00}))
   \end{split}
 \end{equation*} 
-  Thus, $\tfrac{X - \mu}{\sigma} \sim \mathcal{G}(\tfrac{\alpha -
-    \mu}{\sigma}, \tfrac{\beta}{\sigma})$. Because the sample
-  mean and the sample variance are consistent estimators, the claims
-  follow after an application of Slutsky's theorem.
+Now $p_{00} \leq 1$ with strict inequality whenever $\eta_{00}$ is
+positive definite. We thus have, for sufficiently large $l$,
+\begin{equation}
+  \label{eq:17}
+ \psi_\lambda(v;t) = (1 + o_P(1)) C_{00} *  
+ \mathrm{Bin}\Bigl(\tbinom{l}{2}, p_{00}\Bigr)
+\end{equation} 
+Eq.~\eqref{eq:17} states that the locality statistics for the
+attributed random graphs model under considation with $t < t^{*}$ can
+be approximated by the locality statistics for an Erd\"{o}s-Renyi
+graph with edge probability $p_{00}$. The claim then follows from
+\cite[Theorem 1.1]{rukhin:_limit_distr_graph_scan_statis}.
 \end{proof}

### 2011-05-01 ssp2011.tex
Revise proof of scan statistics

--- 2011-04-28 ssp2011.tex
@@
 eigenvalue problem as in Theorem~\ref{thm:1}. 
+\subsection{Power estimates for $\Psi_{\lambda}(t)$}
+The limiting distribution for the scan statistics for unattributed
+random graphs was considered in
+\cite{rukhin:_limit_distr_graph_scan_statis}. This subsection is
+concerned with adpating the results in
+\cite{rukhin:_limit_distr_graph_scan_statis} to attributed random
+graphs. We state here only the relevant results. The proofs are
+delegated to the appendices. \\ \\
+\noindent
+The limiting distribution for $\Psi_{\lambda}(t)$ is Gumbel for both
+the case where $t < t^{*}$ and for $t = t^{*}$. To aid the exposition,
+we first introduce some notations. Let $\lambda^{(2)}$ be the
+element-wise square of $\lambda$. Define $C_{00}$, $C_{01}$, $C_{11}$
+and $p_{00}$, $p_{01}$, $p_{11}$ to be
+\begin{gather}
+  \label{eq:19}
+  C_{00} = \tfrac{\langle \lambda^{(2)}, \pi_{00} \rangle}{\langle \lambda,
+    \pi_{00}\rangle}; \quad p_{00} = \tfrac{(\langle \lambda, \pi_{00}
+    \rangle)^{2}}{\langle \lambda^{(2)},\, \pi_{00} \rangle} \\
+C_{11} = \tfrac{\langle \lambda^{(2)}, \pi_{11} \rangle}{\langle \lambda,
+    \pi_{11}\rangle}; \quad p_{11} = \tfrac{(\langle \lambda, \pi_{11}
+    \rangle)^{2}}{\langle \lambda^{(2)},\, \pi_{11} \rangle} \\
+C_{10} = \tfrac{\langle \lambda^{(2)}, \pi_{11} \rangle}{\langle \lambda,
+    \pi_{10}\rangle}; \quad p_{10} = \tfrac{(\langle \lambda, \pi_{10}
+    \rangle)^{2}}{\langle \lambda^{(2)},\, \pi_{10} \rangle} 
+\end{gather}
+Also let $z_n$ be defined, for any $n \in \mathbb{N}$, by
+\begin{equation}
+  \label{eq:20}
+   z_n = \sqrt{2
+      \log{n}}\Bigl(1 - \frac{\log{\log{n}} + \log{4 \pi}}{4
+      \log{n}}\Bigr)
+\end{equation}
+\begin{theorem}
+  \label{thm:2}
+  Let $\Psi_{\lambda}(t)$ be the scan statistic for $t < t^{*}$. Let
+  $N_{0}$, $a_n$, and $b_n$ be defined by
+\begin{align*}
+   \mu_0 &= (n-1) \langle 1, \pi_{00} \rangle \\
+   \sigma_0 &= \sqrt{(n-1) (\langle 1, \pi_{00} \rangle - \langle
+     1, \pi_{00} \rangle^2)} \\ 
+    N_{0} &= \mu_0 + z_n \sigma_0 \\
+    a_n &= N_{0} \frac{\langle \lambda, \pi_{00} \rangle}{\langle
+      1, \pi_{00} \rangle} + C_{00}p_{00}\tbinom{N_{0}}{2} \\ 
+   b_n &= (1 - \tfrac{C_{00}p_{00}}{2} + C_{00}p_{00} N_{0}) \frac{\sigma_0}{\sqrt{2 \log
+     n}}
+\end{align*}
+Then we have
+\begin{equation}
+  \frac{\Psi_{\lambda}(t) - a_{n}}{b_n} \rightsquigarrow
+  \mathcal{G}(0, 1)
+\end{equation}
+\end{theorem}%
+We now move to the limiting distribution for $\Psi_{\lambda}(t^{*})$. 
+Let us define $E$ and $F$ by
+\begin{gather*}
+ %  B \sim \mathrm{Bin}(m, \langle 1, \pi_{00} \rangle); \quad C \sim \mathrm{Bin}(n-m-1,
+ % \langle 1, \pi_{01} \rangle) \\
+  E \sim \mathrm{Bin}(m-1, \langle \pi_{11}, 1 \rangle) \\ F \sim \mathrm{Bin}(n-m,
+  \langle \pi_{01}, 1 \rangle)
+\end{gather*}%
+For any random variable $X$, we let $\mu_X$ and $\sigma_X^{2}$ denote
+the mean and variance of $X$. If $X$ and $Y$ are independent random
+variables, we let $\mu_{X + Y}$ and $\sigma_{X + Y}^2$ denote the mean
+and variance of the convolution $X + Y$. \\
+\noindent Let $N_{\kappa}$ be the quantity defined by
+\begin{equation}
+  \label{eq:18}
+  N_{\kappa} = \mu_{E + F} + z_m \sigma_{E + F}
+\end{equation}
+\begin{theorem}
+  \label{thm:3}
+  Let $a_{n,m}$ and $b_{n,m}$ be given by
+  \begin{gather}
+    \label{eq:28}
+    \begin{split}
+    a_{n,m} &=%  N_{\kappa} \frac{\langle x, \pi_{01} \rangle}{\langle
+ %      1, \pi_{01} \rangle} \\
+ % & +
+    C_{00} p_{00} \Bigl(\tbinom{N_\kappa}{2} - \tbinom{\mu_E}{2} - \mu_E
+    \mu_F\Bigr) \\ 
+     & + C_{11} p_{11} \tbinom{\mu_E}{2} + C_{01} p_{01} \mu_E \mu_F 
+    \end{split} \\
+    b_{n,m} = (1 - \tfrac{C_{00} p_{00}}{2} + C_{00} p_{00}
+    N_\kappa)\frac{\sigma_{E + F}}{\sqrt{2 \log{n_1}}}
+  \end{gather}
+  If $m = \Omega(\sqrt{n \log n})$, then
+  \begin{equation}
+    \label{eq:29}
+    \frac{\Psi_{\lambda}(t^{*}) - a_{n,m}}{b_{n,m}}  \rightsquigarrow \mathcal{G}(0,1)  \end{equation}
+\end{theorem}
 \appendices
 \section{Proofs of some stated results}
+\label{sec:proofs-some-stated}
 \begin{proof}[Theorem \ref{thm:1}]
@@
   \begin{equation*}
-    d_{\lambda}(v;t) = \sum_{k = 1}^{K} \lambda_k \sum_{u \in N(v)}
-    \mathbf{1}\{ \phi(uv,t) = k \}
+    d_{\lambda}(v;t) = \sum_{k = 1}^{K} \lambda_k \sum_{w \in N(v)}
+    \mathbb{I}\{ \phi(vw,t) = k \}
   \end{equation*}
-  By applying the multivariate normal approximation to the
-  multinomial, 
+  Let $\Gamma^{(k)}(v;t) = |\{w \colon \mathbb{I}\{\phi(wv,t) =
+  k\}|$. The vector $\bm{\Gamma}(v;t) = (\Gamma^{(1)}(v;t), \dots,
+  \Gamma^{(K)}(v;t))$ for $t < t^{*}$ is distributed as a multinomial
+  with $n-1$ trials and probability vector $\pi_{00}$. The folllowing
+  statements are made under the assumption that $n \rightarrow \infty$
+  for fixed $K$. By the multivariate central limit theorem, we have
+  \begin{equation*}
+    \frac{\bm{\Gamma}(v;t) - (n-1) \pi_{00}}{\sqrt{n-1}}
+    \rightsquigarrow \mathcal{N}(0, (\mathrm{diag}(\pi_{00}) -
+    \pi_{00} \pi_{00}^{T}))
+  \end{equation*}
+  Now $d_{\lambda}(v;t) = \langle \lambda, \bm{\Gamma}(v;t) \rangle$
+  and we have
+  \begin{equation*}
+    \frac{d_{\lambda}(v;t) - (n-1) \langle \lambda, \pi_{00}
+      \rangle}{\sqrt{n-1}} \rightsquigarrow \mathcal{N}(0, \langle \lambda, \eta_{00} \lambda \rangle)
+  \end{equation*}
+  Therefore, $\tfrac{d_{\lambda}(v;t) - (n-1) \langle \lambda,
+    \pi_{00} \rangle}{\sqrt{(n-1) \langle \lambda, \eta_{00} \lambda
+      \rangle}} \rightsquigarrow N(0,1)$. We can thus consider the
+  degree sequence of $G(t)$ for $t < t^{*}$ as a sequence of {\em
+    dependent} Gaussian random variables. By an argument analogous to
+  the argument for Erd\"{o}s-Renyi random graphs in \cite[\S
+  III.1]{bollobas85:_random_graph} we can show that the dependency
+  among the $d_{\lambda}(v,t)$ can be ignored. Let us define
+  $\xi_s$ for $s \in \mathbb{R}$ as the number of vertices $v$ such
+  that $\tfrac{d_\lambda(v;t) - (n-1) \langle \lambda, \pi_{00}
+    \rangle}{\sqrt{(n-1) \langle \lambda, \eta_{00} \lambda \rangle}}
+  \geq s$. Note that $\xi_s \leq k$ only if there are at most $k$
+  vertices with $\tfrac{d_{\lambda}(v;t) - (n-1) \langle \lambda,
+    \pi_{00} \rangle}{\sqrt{(n-1) \langle \lambda, \eta_{00} \lambda
+      \rangle}} \geq s$. Thus, $\tfrac{\Delta_{\lambda}(v;t) - (n-1)
+    \langle \lambda, \pi_{00} \rangle}{\sqrt{(n-1) \langle \lambda,
+      \eta_{00} \lambda \rangle}} < s$ only if $\xi_s = 0$. Because
+  the sample maximum of Gaussian random variables converges weakly to
+  a Gumbel \cite[\S 2.3]{galambos87:_asymp_theor_extrem_order_statis},
+  by taking $n \rightarrow \infty$ followed by $s \rightarrow \infty$,
+  we can show that $\tfrac{\Delta_{\lambda}(v;t) - (n-1) \langle \lambda,
+  \pi_{00} \rangle}{\sqrt{(n-1) \langle \lambda, \eta_{00} \lambda
+    \rangle}} \rightsquigarrow \mathcal{G}(a_n, b_n)$. We thus obtain
+Eq.~\eqref{eq:14} for $t < t^{*}$. The case when $t = t^{*}$ can be
+derive in a similar manner. We first apply Lemma 3.1 in
+\cite{rukhin:_limit_distr_graph_scan_statis} to show that if $m =
+\Omega(\sqrt{n \log{n}})$, then $\Delta_{\lambda}(v;t^{*}) \rightsquigarrow
+\max_{v \in [m]}{d_{\lambda}(v;t^{*})}$.  
+We then show, again by the multivariate
+central limit theorem that for $v \in [m]$, $\tfrac{d_{\lambda}(v;t^{*}) -
+  \mu_2}{\sigma_2} \rightsquigarrow N(0,1)$. It then follows that
+$\max_{v \in [m]} \tfrac{d_{\lambda}(v;t^{*}) -
+  \mu_2}{\sigma_2} \rightsquigarrow \mathcal{G}(a_m,b_m)$ and we obtain
+Eq.~\eqref{eq:14} for $t = t^{*}$.  
 \end{proof}
-
+\begin{proof}[Lemma~\ref{lem:2}]
+  Let $ X \sim \mathcal{G}(\alpha, \beta)$. We consider the
+  normalization $\tfrac{X - \mu}{\sigma}$. We have
+  \begin{equation*}
+    \begin{split}
+    \mathbb{P}[ \frac{X - \mu}{\sigma} \leq z]  &= \mathbb{P}[X \leq z
+    \sigma + \mu] 
+    = e^{-e^{-(z \sigma + \mu - \alpha)/\beta}} \\
+      &= e^{- e^{-(z - (\alpha - \mu)/\sigma)/(\beta/\sigma)}}
+    \end{split}
+  \end{equation*}
+  Thus, $\tfrac{X - \mu}{\sigma} \sim \mathcal{G}(\tfrac{\alpha -
+    \mu}{\sigma}, \tfrac{\beta}{\sigma})$. Because the sample
+  mean and the sample variance are consistent estimators, the claims
+  follow after an application of Slutsky's theorem.
+\end{proof}
+\begin{proof}[Theorem~\ref{thm:2}]
+Let $\phi_{\lambda}(v;t) = \psi_{\lambda}(v;t) - d_{\lambda}(v;t)$ be
+the (fused) locality statistics for
+vertex $v$ at time $t$ not including the (fused) degree of $v$, i.e.,
+\begin{equation}
+  \label{eq:11}
+  \phi_{\lambda}(v;t) = \sum_{k=1}^{K} \lambda_k \sum_{\substack{uw
+      \in N(v) \\ u,w \not = v}}
+  \mathbb{I}\{\phi(uw,t) = k\}.
+\end{equation}
+The following statements are made conditional on $|N(v)| = l$. First
+of all, we have
+\begin{equation*}
+  \phi_{\lambda}(v;t) = \sum_{k=1}^{K}{\lambda_k z_k}
+\end{equation*}
+where the $(z_1, \dots, z_K)$ are distributed as
+\begin{gather*}
+  (z_1,z_2,\dots,z_K) \sim \textrm{multinomial}\Bigl(
+  \tbinom{l}{2}, \pi_{00}\Bigr) 
+\end{gather*}
+By the multivariate CLT, we have
+\begin{equation*}
+  \frac{\phi_\lambda(v;t) - \tbinom{l}{2} \langle \lambda, \pi_{00}
+    \rangle}{\sqrt{\tbinom{l}{2} \langle \lambda, \eta_{00} \lambda \rangle}}
+ \rightsquigarrow \mathcal{N}(0,1) 
+\end{equation*}
+Let $Y_{l} = C_{00} \mathrm{Bin}(\tbinom{l}{2}, p_{00})$. Then $\mathbb{E}[Y_l] = \tbinom{l}{2} \langle \lambda, \pi_{00} \rangle$
+and $\mathrm{Var}[Y_l] = \tbinom{l}{2} \langle \lambda,
+\eta_{00} \lambda \rangle$ and by the CLT, we have
+\begin{equation}
+  \label{eq:12}
+  \frac{\psi_{\lambda}(v;t) - \tbinom{l}{2} \langle \lambda, \pi_{00}
+    \rangle}{\sqrt{\tbinom{l}{2} \langle \lambda, \eta_{00} \lambda
+      \rangle}} \rightsquigarrow \frac{Y_l - \tbinom{l}{2} \langle \lambda, \pi_{00} \rangle}{\sqrt{\tbinom{l}{2}
+    \langle \lambda, \eta_{00} \lambda \rangle}}
+\end{equation}
+Eq.~\eqref{eq:12} states that the locality statistics for our
+attributed random graphs model with $t < t^{*}$
+can be approximated by the locality statistics for an Erd\"{o}s-Renyi
+graph with edge probability $p_{00}$. Theorem~\ref{thm:2} then follows
+from Theorem~1.1 in \cite{rukhin:_limit_distr_graph_scan_statis}.
+\end{proof}
+\begin{proof}[Theorem~\ref{thm:3}]
+  Let $\phi_{\lambda}(v;t^{*}) = \psi_{\lambda}(v;t^{*}) -
+  d_{\lambda}(v;t^{*})$. Let $d_{\zeta}(v;t)$ be
+the number of neighbors of $v$ that lies in $[m]$ and
+$d_{\xi}(v;t)$ be the number of neighbors of $v$ that lies in $[n]
+\setminus [m]$. The following statements are made, conditional on $d_{\zeta}(v;t^{*}) =
+l_{\zeta}$ and $d_{\xi}(v;t^{*}) = l_{\xi}$. First of all, we have
+\begin{equation}
+  \phi_{\lambda}(v;t^{*}) = \sum_{k=1}^{K} \lambda_k ( y^{(\zeta)}_k +
+  y^{(\xi)}_k + y^{(\omega)}_k)
+\end{equation}
+where $(y^{(\zeta)}_1, \dots, y^{(\zeta)}_K)$, $(y^{(\xi)}_1,\dots,
+ y^{(\xi)}_K)$,  $(y^{(\omega)}_1, \dots, y^{(\omega)}_K)$ are
+ distributed as
+\begin{gather*}
+(y^{(\zeta)}_1,\dots,y^{(\zeta)}_K) \sim \textrm{multinomial}\Bigl(
+\tbinom{l_\zeta}{2}, \pi_{11}\Bigr) \\ 
+(y^{(\xi)}_1,\dots,y^{(\xi)}_K) \sim \textrm{multinomial}\Bigl(
+\tbinom{l_\xi}{2}, \pi_{00}\Bigr) \\
+(y^{(\omega)}_1,\dots,y^{(\omega)}_m) \sim \textrm{multinomial}\Bigl(
+l_\zeta l_\xi, \pi_{10}\Bigr)
+\end{gather*}
+Let $\rho$ and $\varsigma$ be defined as
+\begin{gather*}
+  \rho = \langle \lambda, \tbinom{l_{\zeta}}{2} \pi_{11} +
+  \tbinom{l_{\xi}}{2} \pi_{00} + l_{\zeta} l_{\xi} \pi_{10} \rangle \\
+  \varsigma = \langle \lambda, \Bigl(\tbinom{l_{\zeta}}{2} \eta_{11} +
+  \tbinom{l_{\xi}}{2} \eta_{00} + l_{\zeta} l_{\xi} \eta_{10}\Bigr) \lambda
+  \rangle
+\end{gather*}
+By the multivariate CLT, we have
+\begin{equation}
+  \label{eq:16}
+  \frac{\phi_{\lambda}(v;t^{*}) - \rho}{\varsigma} \rightsquigarrow
+  \mathcal{N}(0,1)
+\end{equation}
+Let $Y_{\zeta} \sim C_{11} \mathrm{Bin}\Bigl(\tbinom{l_{\zeta}}{2},
+p_{11}\Bigr)$, $Y_{\xi} \sim C_{00} \mathrm{Bin}\Bigl(\tbinom{l_\xi}{2},
+p_{00}\Bigr)$ and $Y_{\omega} \sim C_{10} \mathrm{Bin}\Bigl( l_{\zeta}
+l_{\xi}, p_{10} \Bigr)$. By the CLT, we have
+\begin{equation}
+  \label{eq:21}
+ \frac{\phi_{\lambda}(v;t^{*}) - \rho}{\varsigma} \rightsquigarrow
+ \frac{Y_{\zeta} + Y_{\xi} + Y_{\omega} - \rho}{\varsigma}
+\end{equation}
+Eq.~\eqref{eq:21} states that the locality statistics for our
+attributed random graphs model time $t = t^{*}$ can be approximated by
+the locality statistics for an unattributed kidney and egg model.
+\end{proof}
 \bibliography{ssp2011}

### 2011-05-11 ssp2011.tex
Fixed proof of max degree to use large deviation bounds

@@
   \begin{align*}
-    a_n &= (2 \log{n})^{1/2}\Bigl(1 - \frac{\log{\log{n}}}{4 \log{n}} -
-    \frac{\log{2\pi^{1/2}}}{2 \log{n}} \Bigr) \\ 
+    a_n &= (2 \log{n})^{1/2}\Bigl(1 - \frac{\log{\log{n}} + \log{4\pi}}{4 \log{n}} \Bigr) \\ 
     b_n &= (2 \log{n})^{-1/2}
@@
   Let $\Gamma^{(k)}(v;t) = |\{w \colon \mathbb{I}\{\phi(wv,t) =
-  k\}|$. The vector $\bm{\Gamma}(v;t) = (\Gamma^{(1)}(v;t), \dots,
-  \Gamma^{(K)}(v;t))$ for $t < t^{*}$ is distributed as a multinomial
-  with $n-1$ trials and probability vector $\pi_{00}$. The folllowing
-  statements are made under the assumption that $n \rightarrow \infty$
-  for fixed $K$. By the multivariate central limit theorem, we have
+  k\}|$. The vector $\bm{\Gamma}(v;t) = (\Gamma^{(k)}(v;t))_{k=1}^{K}$
+  for $t < t^{*}$ is distributed as a multinomial with $n-1$ trials
+  and probability vector $\pi_{00}$. The following statements are
+  made as $n \rightarrow \infty$ for fixed
+  $K$. Now $d_{\lambda}(v;t) = \langle \lambda, \bm{\Gamma}(v;t)
+  \rangle$ and
+  thus, by the central limit theorem, we have
+  \begin{equation}
+    \label{eq:17}
+    \frac{d_{\lambda}(v;t) - (n-1) \langle \lambda, \pi_{00}
+      \rangle}{\sqrt{(n-1) \langle \lambda, \eta_{00} \lambda \rangle}}
+      \rightsquigarrow \mathcal{N}(0, 1)
+    \end{equation}
+    We can thus consider the degree sequence of $G(t)$ for $t < t^{*}$
+    as a sequence of {\em dependent} normally distributed random
+    variables. By an argument analogous to the argument for
+    Erd\"{o}s-Renyi random graphs in \cite[\S
+    III.1]{bollobas85:_random_graph} we can show that the dependency
+    among the $d_{\lambda}(v,t)$ can be ignored. $d_{\lambda}(v;t)$,
+    when normalized, can thus be considered as a sequence of
+    independent random variables from the standard normal in the
+    limit. It is widely known that the sample maximum of standard
+    normal random variables converges weakly to a Gumbel distribution
+    \cite[\S 2.3]{galambos87:_asymp_theor_extrem_order_statis}. It is,
+    however, not clear whether the convergence of
+    $\Delta_{\lambda}(t)$ to a Gumbel distribution continues to hold
+    under the composition of weak convergence as
+    outlined above. We avoid this problem by showing
+    directly that 
+    \begin{equation}
+      \label{eq:22}
+  \mathbb{P}\Bigl(\tfrac{\Delta_{\lambda}(t) - (n-1)
+        \langle \lambda, \pi_{00} \rangle}{\sqrt{(n-1) \langle
+          \lambda, \eta_{00} \lambda \rangle}} \leq a_n + b_n x\Big)
+      \rightarrow 
+      e^{-e^{-x}} 
+    \end{equation}
+    Let $\zeta_v = \tfrac{d_{\lambda}(v;t) - (n-1) \langle \lambda,
+      \pi_{00} \rangle}{\sqrt{(n-1) \langle \lambda, \eta_{00} \lambda
+        \rangle}}$ and $F_n(u) = \mathbb{P}(\zeta_v \leq u)$. If $n
+    \rightarrow \infty$ and $u = o(\sqrt{n})$, we have the
+    following large deviations result \cite[Theorem~2, \S
+    XVI.7]{feller71:_introd_probab_theor_its_applic}.
+    \begin{equation}
+      \label{eq:23}
+      \frac{1 - F_{n}(u)}{1 - \Phi(u)} = \exp\Bigl(u^2
+      h(\tfrac{u}{\sqrt{n}})\Bigr) \Bigl[1 + O(\tfrac{u}{\sqrt{n}}) \Bigr]
+    \end{equation}
+    where $h(z)$ is a power series defined by
     \begin{equation*}
-    \frac{\bm{\Gamma}(v;t) - (n-1) \pi_{00}}{\sqrt{n-1}}
-    \rightsquigarrow \mathcal{N}(0, (\mathrm{diag}(\pi_{00}) -
-    \pi_{00} \pi_{00}^{T}))
+      z^{2} h(z) = h_0 z^3 + h_1 z^4 + \dots
     \end{equation*}
-  Now $d_{\lambda}(v;t) = \langle \lambda, \bm{\Gamma}(v;t) \rangle$
-  and we have
-  \begin{equation*}
-    \frac{d_{\lambda}(v;t) - (n-1) \langle \lambda, \pi_{00}
-      \rangle}{\sqrt{n-1}} \rightsquigarrow \mathcal{N}(0, \langle \lambda, \eta_{00} \lambda \rangle)
-  \end{equation*}
-  Therefore, $\tfrac{d_{\lambda}(v;t) - (n-1) \langle \lambda,
-    \pi_{00} \rangle}{\sqrt{(n-1) \langle \lambda, \eta_{00} \lambda
-      \rangle}} \rightsquigarrow N(0,1)$. We can thus consider the
-  degree sequence of $G(t)$ for $t < t^{*}$ as a sequence of {\em
-    dependent} Gaussian random variables. By an argument analogous to
-  the argument for Erd\"{o}s-Renyi random graphs in \cite[\S
-  III.1]{bollobas85:_random_graph} we can show that the dependency
-  among the $d_{\lambda}(v,t)$ can be ignored. Let us define
-  $\xi_s$ for $s \in \mathbb{R}$ as the number of vertices $v$ such
-  that $\tfrac{d_\lambda(v;t) - (n-1) \langle \lambda, \pi_{00}
-    \rangle}{\sqrt{(n-1) \langle \lambda, \eta_{00} \lambda \rangle}}
-  \geq s$. Note that $\xi_s \leq k$ only if there are at most $k$
-  vertices with $\tfrac{d_{\lambda}(v;t) - (n-1) \langle \lambda,
-    \pi_{00} \rangle}{\sqrt{(n-1) \langle \lambda, \eta_{00} \lambda
-      \rangle}} \geq s$. Thus, $\tfrac{\Delta_{\lambda}(v;t) - (n-1)
-    \langle \lambda, \pi_{00} \rangle}{\sqrt{(n-1) \langle \lambda,
-      \eta_{00} \lambda \rangle}} < s$ only if $\xi_s = 0$. Because
-  the sample maximum of Gaussian random variables converges weakly to
-  a Gumbel \cite[\S 2.3]{galambos87:_asymp_theor_extrem_order_statis},
-  by taking $n \rightarrow \infty$ followed by $s \rightarrow \infty$,
-  we can show that $\tfrac{\Delta_{\lambda}(v;t) - (n-1) \langle \lambda,
-  \pi_{00} \rangle}{\sqrt{(n-1) \langle \lambda, \eta_{00} \lambda
-    \rangle}} \rightsquigarrow \mathcal{G}(a_n, b_n)$. We thus obtain
-Eq.~\eqref{eq:14} for $t < t^{*}$. The case when $t = t^{*}$ can be
-derive in a similar manner. We first apply Lemma 3.1 in
-\cite{rukhin:_limit_distr_graph_scan_statis} to show that if $m =
+    and the $h_i$ are constants. Letting $u_n = a_n + b_n x$ in
+    Eq.~\eqref{eq:23}, we have
+    \begin{equation}
+      \label{eq:24}
+     1 - F_n(u_n) = (1 - \Phi(u_n))(1 + C \tfrac{u_n^{3}}{\sqrt{n}} +
+     O(\tfrac{u_n^{4}}{n}))
+    \end{equation}
+    for some constant $C$. We therefore have
+    \begin{equation}
+      \label{eq:25}
+      \begin{split}
+      \mathbb{P}(\max_{v \in [n]} \zeta(v) \leq u_n) &= (F_n(u_n))^{n}
+      \\
+      &= \Bigl[\Phi(u_n) + \Phi(u_n) 
+      \tilde{O}(\tfrac{1}{\sqrt{n}})\Bigr]^{n} \\
+      &= \Bigl[\Phi(u_n) + \tilde{O}(\tfrac{1}{n^{3/2}})\Bigr]^{n} \\
+      &= (\Phi(u_n))^{n} + \tilde{O}(\tfrac{1}{n^{1/2}}) \\
+      & \rightarrow e^{-e^{-x}} 
+      \end{split}
+    \end{equation}
+    where $\tilde{O}$ denote that the powers of $u_n =
+    O(\log{n})$ are ignored. Eq.~\eqref{eq:22} is established and
+    we obtain the limiting Gumbel distribution for
+    $\Delta_{\lambda}(t)$ for $t < t^{*}$ in Eq.~\eqref{eq:14}.
+    % Now $n(1 - \Phi(u_n)) = \exp(-x)(1 + o(u_n^{-1 + \theta}))$ for
+    % some small $\theta > 0$. We thus have
+    % \begin{equation}
+    %   \label{eq:26}
+    %   \begin{split}
+    %   \mathbb{P}(\max_{v \in [n]} \zeta(v) \leq u_n) &= \Bigl[ \Phi(u_n) - C
+    %   u_n^{3}n^{-3/2} e^{-x}(1 + o(u_n^{-1 + \theta})) + O(u_n^{4}/n)
+    %   n^{-1} e^{-x} \Bigr]^{n} \\
+    %   &= (\Phi(u_n))^{n}\Bigl[1 - C u_n^{3}n^{-1/2} e^{-x}(n \Phi(u_n))^{-1} +
+    %   o(u_n^{-4 + \theta})n^{-2} e^{-x}\Bigr]^{n} \\
+    %   &= (\Phi(u_n))^{n} - C u_n^{3}n^{-1/2} e^{-x} (\Phi(u_n))^{n-1} +
+    %   o(u_n^{-4 + \theta}n^{-1/2}) e^{-x} \\
+    %   &= (1 + o(1)) \Phi(u_n)^{n}
+    %   \end{split}
+    % \end{equation}
+    % where the term $o(1)$ can be made to be independent of
+    % $x$. Furthermore, we can verify that $\Phi(u_n)^{n} \rightarrow
+    % e^{e^{-x}}$ and thus Eq.~\eqref{eq:22} is established. 
+ % Let us define
+ %  $\xi_s$ for $s \in \mathbb{R}$ as the number of vertices $v$ such
+ %  that $\tfrac{d_\lambda(v;t) - (n-1) \langle \lambda, \pi_{00}
+ %    \rangle}{\sqrt{(n-1) \langle \lambda, \eta_{00} \lambda \rangle}}
+ %  \geq s$. Note that $\xi_s \leq k$ only if there are at most $k$
+ %  vertices with $\tfrac{d_{\lambda}(v;t) - (n-1) \langle \lambda,
+ %    \pi_{00} \rangle}{\sqrt{(n-1) \langle \lambda, \eta_{00} \lambda
+ %      \rangle}} \geq s$. Thus, $\tfrac{\Delta_{\lambda}(v;t) - (n-1)
+ %    \langle \lambda, \pi_{00} \rangle}{\sqrt{(n-1) \langle \lambda,
+ %      \eta_{00} \lambda \rangle}} < s$ only if $\xi_s = 0$. Because
+ %  the sample maximum of Gaussian random variables converges weakly to
+ %  a Gumbel \cite[\S 2.3]{galambos87:_asymp_theor_extrem_order_statis},
+ %  by taking $n \rightarrow \infty$ followed by $s \rightarrow \infty$,
+ %  we can show that $\tfrac{\Delta_{\lambda}(v;t) - (n-1) \langle \lambda,
+ %  \pi_{00} \rangle}{\sqrt{(n-1) \langle \lambda, \eta_{00} \lambda
+ %    \rangle}} \rightsquigarrow \mathcal{G}(a_n, b_n)$. 
+The case when $t = t^{*}$ can be
+derive in a similar manner. We first show that if $m =
 \Omega(\sqrt{n \log{n}})$, then $\Delta_{\lambda}(v;t^{*}) \rightsquigarrow
-\max_{v \in [m]}{d_{\lambda}(v;t^{*})}$.  
-We then show, again by the multivariate
+\max_{v \in [m]}{d_{\lambda}(v;t^{*})}$ \cite[Lemma
+3.1]{rukhin:_limit_distr_graph_scan_statis}.  
+We then show, again by the 
 central limit theorem that for $v \in [m]$, $\tfrac{d_{\lambda}(v;t^{*}) -
-  \mu_2}{\sigma_2} \rightsquigarrow N(0,1)$. It then follows that
+  \mu_2}{\sigma_2} \rightsquigarrow N(0,1)$. It then follows, similar
+to our previous reasoning for the case where $t < t^{*}$, that
 $\max_{v \in [m]} \tfrac{d_{\lambda}(v;t^{*}) -
@@
 \end{gather*}
-By the multivariate CLT, we have
+By the central limit theorem, we have
 \begin{equation*}
@@
 and $\mathrm{Var}[Y_l] = \tbinom{l}{2} \langle \lambda,
-\eta_{00} \lambda \rangle$ and by the CLT, we have
+\eta_{00} \lambda \rangle$ and again by the central limit theorem, we have
 \begin{equation}
@@
 \end{gather*}
-By the multivariate CLT, we have
+By the central limit theorem, we have
 \begin{equation}
@@
 p_{00}\Bigr)$ and $Y_{\omega} \sim C_{10} \mathrm{Bin}\Bigl( l_{\zeta}
-l_{\xi}, p_{10} \Bigr)$. By the CLT, we have
+l_{\xi}, p_{10} \Bigr)$. By the central limit theorem, we have
 \begin{equation}
@@
 attributed random graphs model time $t = t^{*}$ can be approximated by
-the locality statistics for an unattributed kidney and egg model.
+the locality statistics for an unattributed kidney and egg model. We
+thus define $Y(v) = Y_{\zeta}(v) + Y_{\xi}(v) + Y_{\omega}(v)$
+where $Y_{\zeta}(v) \sim C_{11}
+\mathrm{Bin}(\tbinom{d_{\zeta}(v;t)}{2}, p_{11})$ and $Y_{\xi},
+Y_{\omega}$ are defined accordingly. Let $G \sim \kappa(n,m,p_{11},
+p_{10}, p_{00})$ be an unattributed kidney-egg graph with the
+probability of egg-egg, egg-kidney, and kidney-kidney connections
+being $p_{11}$, $p_{10}$, and $p_{00}$, respectively. Let $M(v)$ and
+$W(v)$ denote the number of vertices adjacent to $v$ in $[m]$ and $[n]
+\setminus [m]$, respectively. $D(v) = M(v) + W(v)$ is then the degree
+of $v$ in $G$. We now show two
+inequalities relating the tail distribution of 
+$\Delta(G)$ and $\Upsilon(G) = \max_{v \in V(G)} Y(v)$.
+\begin{gather}
+  \label{eq:27}
+    \limsup \mathbb{P}( \Upsilon(G) \geq a_{n,m} ) \leq \lim
+   \mathbb{P}( \Delta(G) \geq N_\kappa) \\
+   \label{eq:30}
+  \liminf \mathbb{P}( \Upsilon(G) \geq a_{n,m} ) \geq \lim \mathbb{P}(
+  \Delta(G) \geq N_{\kappa})
+\end{gather}
+\begin{proof}[Eq.~\eqref{eq:27}]
+ Let $C^{*} = \max\{C_{11},
+C_{10}, C_{00}\}$ and $d_{n,m} = \sqrt{2 a_{n,m}/C^{*}}$. We first
+note that
+\begin{equation*}
+\Upsilon(G) \geq a_{n,m} \Rightarrow C^{*} \tbinom{D(v)}{2} \geq
+a_{n,m} \Rightarrow D(v) \geq d_{n,m} 
+\end{equation*}
+Let us define $h(v) = \mathbb{E}[Y(v)]$, i.e., 
+\begin{equation*}
+  \begin{split}
+  h(v) = C_{00}p_{00} \tbinom{D(v)}{2} &+ (C_{11} p_{11} - C_{00}
+  p_{00}) \tbinom{M(v)}{2} \\ &+ (C_{10} p_{10} - C_{00} p_{00}) M(v) W(v)
+  \end{split}
+\end{equation*}
+We then have
+  \begin{equation*}
+    \label{eq:31}
+    \begin{split}
+    \mathbb{P}(\Upsilon(G) \geq a_{n,m}) &= \mathbb{P}\Bigl( \bigcup_{v
+      \in V(G)} Y(v) \geq a_{n,m}\Bigr) \\
+    &= \mathbb{P}\Bigl( \bigcup_{v
+      \in V(G)} Y(v) \geq a_{n,m}, \, D(v) \geq d_{n,m} \Bigr) \\
+    &= P_1 + P_2
+    \end{split}
+  \end{equation*}
+  where 
+  \begin{align*}
+    \vartheta_n &= C_{00} \Bigl[ \tbinom{n}{2} p_{00} (1 -
+    p_{00})\Bigr]^{1/2} \log{n} \\
+    P_1 &= \mathbb{P}(\bigcup_{v \in V(G)} D(v) \geq d_{n,m}, h(v) \geq
+    a_{n,m} - \vartheta_n) \\
+    P_2 &= \mathbb{P}(\bigcup_{v \in V(G)} D(v) \geq d_{n,m},
+    Y(v) - h(v) \geq \vartheta_n)
+  \end{align*}
+  We now show that $P_2$ is negligible as $n \rightarrow \infty$. To
+  proceed, let $p_{e,f} = \mathbb{P}(M(v) = e, W(v) =
+f)$. $P_2$ can then be bounded as follows
+\begin{equation*}
+  \begin{split}
+    P_2 & \leq n \sum_{D(v) \geq
+        d_{n,m}}{\mathbb{P}\biggl( Y(v) - \mathbb{E}[Y(v)] \geq
+        \vartheta_n \biggr) p_{e,f}}
+  \\
+  &= n \sum_{D(v) \geq d_{n,m}}{\mathbb{P}\biggl(
+    \tfrac{Y(v) - \mathbb{E}[Y(v)]}{\sqrt{\mathrm{Var}[Y(v)]}} \geq
+    \tfrac{\vartheta_n}{\sqrt{\mathrm{Var}[Y(v)]}} \biggr) p_{e,f}} \\
+    &\leq n \sum_{D(v) \geq d_{n,m}} (1 + o(1)) \mathbb{P}(Z \geq \Theta(\log{n})) p_{e,f} \\
+    &= o(1)
+  \end{split}
+\end{equation*}
+
+\end{proof}
 \end{proof}

### 2011-05-12 ssp2011.tex
Written proof of limsup scan \leq lim max degree

@@
 \begin{proof}[Theorem~\ref{thm:3}]
-  Let $\phi_{\lambda}(v;t^{*}) = \psi_{\lambda}(v;t^{*}) -
-  d_{\lambda}(v;t^{*})$. Let $d_{\zeta}(v;t)$ be
-the number of neighbors of $v$ that lies in $[m]$ and
-$d_{\xi}(v;t)$ be the number of neighbors of $v$ that lies in $[n]
-\setminus [m]$. The following statements are made, conditional on $d_{\zeta}(v;t^{*}) =
-l_{\zeta}$ and $d_{\xi}(v;t^{*}) = l_{\xi}$. First of all, we have
+  For ease of exposition, we will drop the time index $t =
+  t^{*}$ from our notations and discussion. Let
+  $\phi_{\lambda}(v) = \psi_{\lambda}(v) - d_{\lambda}(v)$. Let
+  $M(v)$ be the number of neighbors of $v$ that lies in $[m]$ and
+  $W(v)$ be the number of neighbors of $v$ that lies in $[n]
+\setminus [m]$. The following statements are made, conditional on
+$M(v) = l_{\zeta}$ and $W(v) = l_{\xi}$. We have
 \begin{equation}
-  \phi_{\lambda}(v;t^{*}) = \sum_{k=1}^{K} \lambda_k ( y^{(\zeta)}_k +
+  \phi_{\lambda}(v) = \sum_{k=1}^{K} \lambda_k ( y^{(\zeta)}_k +
   y^{(\xi)}_k + y^{(\omega)}_k)
@@
 \end{gather*}
-By the central limit theorem, we have
+By the central limit theorem, as $l_{\zeta} \rightarrow
+\infty$ and $l_{\xi} \rightarrow \infty$
 \begin{equation}
   \label{eq:16}
-  \frac{\phi_{\lambda}(v;t^{*}) - \rho}{\varsigma} \rightsquigarrow
+  \frac{\phi_{\lambda}(v) - \rho}{\varsigma} \rightsquigarrow
   \mathcal{N}(0,1)
@@
 p_{00}\Bigr)$ and $Y_{\omega} \sim C_{10} \mathrm{Bin}\Bigl( l_{\zeta}
-l_{\xi}, p_{10} \Bigr)$. By the central limit theorem, we have
+l_{\xi}, p_{10} \Bigr)$. We also set $Y = Y_{\zeta} + Y_{\xi} +
+Y_{\omega}$. By the central limit theorem, we have
 \begin{equation}
   \label{eq:21}
- \frac{\phi_{\lambda}(v;t^{*}) - \rho}{\varsigma} \rightsquigarrow
- \frac{Y_{\zeta} + Y_{\xi} + Y_{\omega} - \rho}{\varsigma}
+ \frac{\phi_{\lambda}(v) - \rho}{\varsigma} \rightsquigarrow
+ \frac{Y - \rho}{\varsigma}
 \end{equation}
-Eq.~\eqref{eq:21} states that the locality statistics for our
-attributed random graphs model time $t = t^{*}$ can be approximated by
-the locality statistics for an unattributed kidney and egg model. We
-thus define $Y(v) = Y_{\zeta}(v) + Y_{\xi}(v) + Y_{\omega}(v)$
-where $Y_{\zeta}(v) \sim C_{11}
-\mathrm{Bin}(\tbinom{d_{\zeta}(v;t)}{2}, p_{11})$ and $Y_{\xi},
-Y_{\omega}$ are defined accordingly. Let $G \sim \kappa(n,m,p_{11},
-p_{10}, p_{00})$ be an unattributed kidney-egg graph with the
+Eq.~\eqref{eq:21} states that the locality statistics
+$\phi_\lambda(v)$ for our
+attributed random graphs model at time $t = t^{*}$ can be approximated by
+the locality statistics $Y(v)$ for an unattributed kidney and egg
+model. Let $G$ be an instance of $\kappa(n,m,p_{11},
+p_{10}, p_{00})$, an unattributed kidney-egg graph with the
 probability of egg-egg, egg-kidney, and kidney-kidney connections
-being $p_{11}$, $p_{10}$, and $p_{00}$, respectively. Let $M(v)$ and
-$W(v)$ denote the number of vertices adjacent to $v$ in $[m]$ and $[n]
-\setminus [m]$, respectively. $D(v) = M(v) + W(v)$ is then the degree
+being $p_{11}$, $p_{10}$, and $p_{00}$, respectively. $D(v) = M(v) + W(v)$ is then the degree
 of $v$ in $G$. We now show two
@@
       \in V(G)} Y(v) \geq a_{n,m}, \, D(v) \geq d_{n,m} \Bigr) \\
-    &= P_1 + P_2
+    &\leq P_1 + P_2
     \end{split}
@@
 \end{equation*}
+We now consider $P_1$. We note that $P_1 \leq R_1 + R_2$
+where
+\begin{align*}
+  R_1 &= \mathbb{P}\Bigl(\bigcup_{v \in [m]} D(v) \geq
+  d_{n,m}, h(v) \geq a_{n,m} - \vartheta_n \Bigr) \\  
+  R_2 &= \mathbb{P}\Bigl(\bigcup_{v \in [n] \setminus [m]} D(v) \geq
+  d_{n,m}, h(v) \geq a_{n,m} - \vartheta_n \Bigr)
+\end{align*}
+Let us define $g(v) = h(v) - C_{00}p_{00} \tbinom{D(v)}{2}$.
+$R_1$ is then bounded as follows
+\begin{equation}
+  \begin{split}
+    \label{eq:36}
+    R_1 &\leq \mathbb{P}\Bigl( \bigcup_{v \in [m]} h(v) \geq
+    a_{n,m} - \vartheta_{n} \Bigr) \\
+    % &\leq \mathbb{P}\Bigl( \bigcup_{v \in [n_1]}  C_{00} p_{00}
+    % \tbinom{D(v)}{2} \geq a_{n,m} - \vartheta_{n} - g(v) \Bigr) \\
+    &\leq \mathbb{P}\Bigl(\bigcup_{v \in [m]} D(v) \geq
+      \sqrt{\tfrac{2 (a_{n,m} - \vartheta_n -
+        g(v))}{C_{00} p_{00}}} \Bigr)
+  \end{split}
+\end{equation}
+We first consider the term $a_{n,m} - g(v)$. We have
+\begin{equation*}
+  \begin{split}
+  a_{n,m} - g(v) &= C_{00} p_{00} \tbinom{N_\kappa}{2} \\ &+ (C_{11}p_{11} -
+  C_{00} p_{00})(\tbinom{\mu_E}{2} - \tbinom{M(v)}{2})
+  \\ &+ (C_{10} p_{10} - C_{00} p_{00})(\mu_E\mu_F - M(v)W(v))
+  \end{split}
+\end{equation*}
+Let $\mathfrak{E}$ and $\mathfrak{F}$ be sets of vertices defined by
+\begin{align}
+\mathfrak{E} &=
+\{v \colon |M(v) - \mu_E| \leq \sigma_E \log{m}\} \\ \mathfrak{F} &=
+\{v \colon |W(v) - \mu_F| \leq \sigma_F \log{(n-m)}\}.
+\end{align}
+Then we have, for $v \in \mathfrak{E} \cap \mathfrak{F}$
+\begin{equation}
+  \label{eq:34}
+  \begin{split}
+  a_{n,m} - g(v) =  C_{00} p_{00} \tbinom{N_\kappa}{2} &+
+  \Theta(m^{3/2} \log{m}) \\ &+ 
+  \Theta(m \sqrt{n - m}) \\
+  \end{split}
+\end{equation}
+When $m = \Omega(\sqrt{n \log n})$, Eq.~\eqref{eq:34} gives
+\begin{equation}
+  \label{eq:35}
+  a_{n,m} - g(v) = N_{\kappa}^{2}\Bigl(\tfrac{C_{00}p_{00}}{2} + O(n^{-1/2 - a}
+  \log{n})\Bigr)
+\end{equation}
+for some $a > 0$. The set $\{v \in [m]\}$ can now be partitition into
+$\{v \in [m] \cap \mathfrak{E} \cap\mathfrak{F}\}$ and $\{v \in [m]
+\setminus (\mathfrak{E} \cap \mathfrak{F})\}$. We can show that
+$\mathbb{P}\{v \in [m] \setminus (\mathfrak{E} \cap \mathfrak{F})\} =
+o(n^{-1})$ by using a concentration inequality, e.g., Hoeffding's
+bound. We thus have
+\begin{equation}
+  \label{eq:37}
+  \begin{split}
+    R_1 &\leq \mathbb{P}\biggl( \bigcup_{\substack{v \in [m] \\ v
+        \in \mathfrak{E} \cap \mathfrak{F}}} D(v) \geq
+    N_{\kappa} \sqrt{1 + O(\tfrac{\log{n}}{n^{1/2+a}})} \Bigr) + o(n^{-1}) \\
+    & = \mathbb{P}\Bigl(\bigcup_{v \in [m]} D(v) \geq N_\kappa +
+    O(n^{1/2 - a} \log{n})\Bigr) + o(n^{-1}) \\
+    &= \mathbb{P}\Bigl(\Delta \geq \mu_{E+F} +
+    \sigma_{E+F}(z_m + O(\tfrac{\log{n}}{n^{a}}))\Bigr) + o(n^{-1}) \\ 
+    & \rightarrow \mathbb{P}(\Delta \geq N_{\kappa})
+    \end{split}
+\end{equation}
+The same argument can be applied to $R_2$ to show that
+\begin{equation}
+  \label{eq:38}
+  R_2 \leq \mathbb{P}\Bigl(\bigcup_{v \in [n] \setminus [m]} D(v) \geq
+  N_{\kappa}(1 + o(1))\Bigr) = o(1)
+\end{equation}
+Eq.~\eqref{eq:27} is therefore established.
+\end{proof}
+\begin{proof}[Eq.~\eqref{eq:28}]
+  We start by noting that
+  \begin{equation*}
+    \begin{split}
+      \mathbb{P}(\Upsilon(G) \geq a_{n,m}) &=
+      \mathbb{P}\Bigl(\bigcup_{v \in [n]}Y(v) \geq
+      a_{n,m}\Bigr) \\
+      & \geq \mathbb{P}\Bigl(\bigcup_{v \in [m]}Y(v) \geq
+      a_{n,m}, D(v) \geq N_\kappa \Bigr) \\
+      & \geq \mathbb{P}\Bigl(\bigcup_{v \in [m]} D(v) \geq
+      N_\kappa\Bigr) \\ &- \mathbb{P}\Bigl( \bigcup_{v
+        \in [m]} Y(v) < a_{n,m}, D(v) \geq N_\kappa\Bigr)
+    \end{split}
+  \end{equation*}
+  We first show $\mathbb{P}( \cup_{v
+        \in [m]} Y(v) < a_{n,m}, D(v) \geq N_\kappa) \rightarrow 0$ as
+      $n \rightarrow \infty$. Let $v \in [m]$ be arbitrary. It is then
+      sufficient to show that $m\mathbb{P}(Y(v) < a_{n,m}, D(v) \geq
+      N_{\kappa}) = o(1)$. 
+\end{proof}
 
-\end{proof}
 \end{proof}

### 2011-05-13 ssp2011.tex
Finish the proof of Eq.(42)

@@
 \documentclass[draftcls]{IEEEtran}
+\usepackage[utopia]{mathdesign}
 \usepackage{amsmath}
-\usepackage{amssymb}
+%\usepackage{amssymb}
 \usepackage{amsthm}
@@
         \rangle}}$ and $F_n(u) = \mathbb{P}(\zeta_v \leq u)$. If $n
-    \rightarrow \infty$ and $u = o(\sqrt{n})$, we have the
-    following large deviations result \cite[Theorem~2, \S
-    XVI.7]{feller71:_introd_probab_theor_its_applic}.
+    \rightarrow \infty$ and $u = O(\log{n})$, we have the
+    following moderate deviations result \cite[Theorem~2, \S
+    XVI.7]{feller71:_introd_probab_theor_its_applic,rubin65:_probab}.
     \begin{equation}
       \label{eq:23}
-      \frac{1 - F_{n}(u)}{1 - \Phi(u)} = \exp\Bigl(u^2
-      h(\tfrac{u}{\sqrt{n}})\Bigr) \Bigl[1 + O(\tfrac{u}{\sqrt{n}}) \Bigr]
+      \frac{1 - F_{n}(u)}{1 - \Phi(u)} = \Bigl[1 + (C\tfrac{u^{3}}{\sqrt{n}}) + O(\tfrac{u^{6}}{n}) \Bigr]
     \end{equation}
-    where $h(z)$ is a power series defined by
+    for some constant $C$. Letting $u_n = a_n + b_n x$ in
+    Eq.~\eqref{eq:23}, we have
     \begin{equation*}
-      z^{2} h(z) = h_0 z^3 + h_1 z^4 + \dots
+      \begin{split}
+     F_n(u_n) &= 1 - (1 - \Phi(u_n))(1 + C \tfrac{u_n^{3}}{\sqrt{n}} +
+     O(\tfrac{u_n^{6}}{n})) \\
+     &= \Phi(u_n) + (1 - \Phi(u_n))(C \tfrac{u_n^{3}}{\sqrt{n}} +
+     O(\tfrac{u_n^6}{n})) \\
+     &= \Phi(u_n) + O(\tfrac{1}{u_n n^{1- \delta}})(C \tfrac{u_n^{3}}{\sqrt{n}} +
+     O(\tfrac{u_n^6}{n})) \\
+     &= \Phi(u_n) + O(\tfrac{u_n^{5}}{n^{3/2 - \delta}})
+     \end{split}
     \end{equation*}
-    and the $h_i$ are constants. Letting $u_n = a_n + b_n x$ in
-    Eq.~\eqref{eq:23}, we have
-    \begin{equation}
-      \label{eq:24}
-     1 - F_n(u_n) = (1 - \Phi(u_n))(1 + C \tfrac{u_n^{3}}{\sqrt{n}} +
-     O(\tfrac{u_n^{4}}{n}))
-    \end{equation}
-    for some constant $C$. We therefore have
+    for some sufficiently small $\delta > 0$. We therefore have
     \begin{equation}
@@
       \begin{split}
-      \mathbb{P}(\max_{v \in [n]} \zeta(v) \leq u_n) &= (F_n(u_n))^{n}
-      \\
-      &= \Bigl[\Phi(u_n) + \Phi(u_n) 
-      \tilde{O}(\tfrac{1}{\sqrt{n}})\Bigr]^{n} \\
-      &= \Bigl[\Phi(u_n) + \tilde{O}(\tfrac{1}{n^{3/2}})\Bigr]^{n} \\
-      &= (\Phi(u_n))^{n} + \tilde{O}(\tfrac{1}{n^{1/2}}) \\
+      \mathbb{P}(\max_{v \in [n]} \zeta(v) \leq u_n) &= (F_n(u_n))^{n} \\
+      &= \Bigl[\Phi(u_n) + O(\tfrac{u_n^{5}}{n^{3/2 - \delta}})\Bigr]^{n} \\
+      &= (\Phi(u_n))^{n} + O(\tfrac{u_n^{5}}{n^{1/2 - \delta}}) \\
       & \rightarrow e^{-e^{-x}} 
@@
     \end{equation}
-    where $\tilde{O}$ denote that the powers of $u_n =
-    O(\log{n})$ are ignored. Eq.~\eqref{eq:22} is established and
-    we obtain the limiting Gumbel distribution for
+    Eq.~\eqref{eq:22} is established and we obtain the limiting Gumbel distribution for
     $\Delta_{\lambda}(t)$ for $t < t^{*}$ in Eq.~\eqref{eq:14}.
@@
 \begin{proof}[Theorem~\ref{thm:3}]
-  For ease of exposition, we will drop the time index $t =
-  t^{*}$ from our notations and discussion. Let
+  For ease of exposition we drop the index $t^{*}$ from our discussion. Let
   $\phi_{\lambda}(v) = \psi_{\lambda}(v) - d_{\lambda}(v)$. Let
@@
   \label{eq:27}
-    \limsup \mathbb{P}( \Upsilon(G) \geq a_{n,m} ) \leq \lim
+    \limsup\,\, \mathbb{P}( \Upsilon(G) \geq a_{n,m} ) \leq \lim
    \mathbb{P}( \Delta(G) \geq N_\kappa) \\
    \label{eq:30}
-  \liminf \mathbb{P}( \Upsilon(G) \geq a_{n,m} ) \geq \lim \mathbb{P}(
+  \liminf\,\, \mathbb{P}( \Upsilon(G) \geq a_{n,m} ) \geq \lim \mathbb{P}(
   \Delta(G) \geq N_{\kappa})
@@
   \begin{split}
-    P_2 & \leq n \sum_{D(v) \geq
-        d_{n,m}}{\mathbb{P}\biggl( Y(v) - \mathbb{E}[Y(v)] \geq
-        \vartheta_n \biggr) p_{e,f}}
+    \frac{P_2}{n} & \leq \sum_{e + f \geq
+        d_{n,m}}{\mathbb{P}( Y(v) - h(v) \geq
+      \vartheta_{n}, M(v) = e, W(v) = f) p_{e,f}}
   \\
-  &= n \sum_{D(v) \geq d_{n,m}}{\mathbb{P}\biggl(
-    \tfrac{Y(v) - \mathbb{E}[Y(v)]}{\sqrt{\mathrm{Var}[Y(v)]}} \geq
-    \tfrac{\vartheta_n}{\sqrt{\mathrm{Var}[Y(v)]}} \biggr) p_{e,f}} \\
-    &\leq n \sum_{D(v) \geq d_{n,m}} (1 + o(1)) \mathbb{P}(Z \geq \Theta(\log{n})) p_{e,f} \\
-    &= o(1)
+  &=  \sum_{e + f \geq d_{n,m}}{\mathbb{P}(
+    \tfrac{Y(v) - h(v)}{\mathrm{Var}[Y(v)]^{1/2}} \geq
+    \tfrac{\vartheta_n}{\mathrm{Var}[Y(v)]^{1/2}}, M(v) = e, W(v) = f) p_{e,f}} \\
+    &\leq \sum_{e + f \geq d_{n,m}} (1 + o(1))
+    \mathbb{P}(Z \geq \Theta(\log{n})) p_{e,f} = o(n^{-1})
   \end{split}
@@
 for some $a > 0$. The set $\{v \in [m]\}$ can now be partitition into
-$\{v \in [m] \cap \mathfrak{E} \cap\mathfrak{F}\}$ and $\{v \in [m]
+$\{v \in [m] \cap (\mathfrak{E} \cap\mathfrak{F})\}$ and $\{v \in [m]
 \setminus (\mathfrak{E} \cap \mathfrak{F})\}$. We can show that
@@
   \end{equation*}
-  We first show $\mathbb{P}( \cup_{v
+  We now show that $\mathbb{P}( \cup_{v
         \in [m]} Y(v) < a_{n,m}, D(v) \geq N_\kappa) \rightarrow 0$ as
@@
       sufficient to show that $m\mathbb{P}(Y(v) < a_{n,m}, D(v) \geq
-      N_{\kappa}) = o(1)$. 
+      N_{\kappa}) = o(1)$. We note that $\mathbb{P}(Y(v) < a_{n,m}, D(v) \geq
+      N_{\kappa})$ can be rewritten as
+      \begin{equation}
+        \label{eq:24}
+        \sum_{e + f \geq N_{\kappa}}{\mathbb{P}(Y(v) \leq a_{n,m}, M(v) = e, W(v) =
+          f)}p_{e,f}
+      \end{equation}
+We now split the indices set $e + f \geq N_{\kappa}$ in
+Eq.~\eqref{eq:24} into three parts $S_1$, $S_2$ and $S_3$, namely
+\begin{gather}
+  \label{eq:32}
+    S_1 = \{ \{e,f\}\colon e \geq
+        \mu_E + \sigma_E \log{m}\} \\
+    S_2 = \{ \{e,f\} \colon  e \leq
+        \mu_E + \sigma_E \log{m},e + f \leq
+        N_\kappa + \varphi(n)\} \\
+    S_3 = \{ \{e,f\} \colon e \leq \mu_E + \sigma_E \log{m}, e + f \geq
+        N_\kappa + \varphi(n)\}
+\end{gather}
+where $\varphi(n) = \Theta(n^{1/2 - a})$ for some $a > 0$. We can then
+show that $m\mathbb{P}(M(v) = e,
+W(v) =f, \{e,f\} \in S_1) = o(1)$ by applying a concentration
+inequality. Similarly, $e + f \geq N_{\kappa}$ and $e \leq \mu_{E}
++ \sigma_{E} \log{m}$ implies that
+\begin{equation}
+  \label{eq:33}
+  f \geq \mu_{F} + (z_{m} - o(1)) \sigma_F 
+\end{equation}
+and once again, by a concentration inequality, we can show that m
+$\mathbb{P}(M(v) = e, W(v) = f, \{e,f\} \in S_2) = o(1)$. As for
+$S_3$, from the fact that $e + f \geq N_{\kappa} + \varphi(n)$, we have the bound
+  \begin{equation}
+    \begin{split}
+    a_{n,m} - h(v) &\leq (C_{11} p_{11} - C_{10} p_{10})[m \sigma_E
+    \log{m} + \tbinom{\log{m}}{2}] \\ &- C_{00}p_{00} N_\kappa \varphi(n)
+    \end{split}
+  \end{equation}
+  As $\mathrm{Var}[Y(v)] = \Theta(N_\kappa)$ for $\{M(v), W(v)\} \in
+  S_3$, we have
+  \begin{equation}
+    \label{eq:39}
+    \begin{split}
+      p_{S_3} &= \sum_{\{e,f\} \in S_3} \mathbb{P}( Y(v) < a_{n,m}) p_{e,f} 
+      \\ &\leq \sum_{\{e,f\} \in S_3} \mathbb{P}\Bigl(\tfrac{Y(v) - h(v))}{\mathrm{Var}[Y(v)]^{1/2}} \leq \tfrac{a_{n,m} -
+      h(v)}{\mathrm{Var}[Y(v)]^{1/2}}\Bigr)p_{e,f} \\
+    &\leq \sum_{\{e,f\} \in S_3} \mathbb{P}\Bigl[Z \leq
+    O\bigl(\tfrac{m^{3/2} \log m}{N_{\kappa}} - \varphi(n)\bigr)\Bigr] p_{e,f}
+    \end{split}
+  \end{equation}
+  We now set $a = \tfrac{1}{2(k+1)}$. Then for $m =
+  O(n^{k/(k+1)})$ and $\varphi(n) = O(n^{1/2 - a})$ we have
+  \begin{equation}
+    \label{eq:41}
+    \tfrac{m^{3/2} \log m}{N_\kappa} - \varphi(n) =
+    -O(n^{k/2(k+1))})
+  \end{equation}
+  which then implies
+  \begin{equation}
+    \label{eq:27}
+    p_{S_3} \leq \sum_{\{e,f\} \in S_3} \mathbb{P} \Bigl[Z \leq
+    - O(n^{k/2(k+1)}\Bigr] p_{e,f} = o(1)
+  \end{equation}
+  Thus $\mathbb{P}(Y(v) < a_{n,m}, D(v) \geq
+      N_{\kappa}) \rightarrow 0$ as desired.
 \end{proof}
@@
 \end{document}
-
 %%% Local Variables: 

### 2011-05-13 ssp2011.tex
Add some mention of Rukhin&Priebe work for scan

@@
     N_{0} &= \mu_0 + z_n \sigma_0 \\
-    a_n &= N_{0} \frac{\langle \lambda, \pi_{00} \rangle}{\langle
-      1, \pi_{00} \rangle} + C_{00}p_{00}\tbinom{N_{0}}{2} \\ 
-   b_n &= (1 - \tfrac{C_{00}p_{00}}{2} + C_{00}p_{00} N_{0}) \frac{\sigma_0}{\sqrt{2 \log
+  %  a_n &= N_{0} \frac{\langle \lambda, \pi_{00} \rangle}{\langle
+  %    1, \pi_{00} \rangle} + C_{00}p_{00}\tbinom{N_{0}}{2} \\ 
+    a_n &=  C_{00}p_{00}\tbinom{N_{0}}{2} \\ 
+   b_n &= C_{00}p_{00} N_{0} \frac{\sigma_0}{\sqrt{2 \log
      n}}
+%   b_n &= (1 - \tfrac{C_{00}p_{00}}{2} + C_{00}p_{00} N_{0}) \frac{\sigma_0}{\sqrt{2 \log
+%     n}}
 \end{align*}
@@
     \begin{split}
-    a_{n,m} &=%  N_{\kappa} \frac{\langle x, \pi_{01} \rangle}{\langle
+    a_{n,m} =%  N_{\kappa} \frac{\langle x, \pi_{01} \rangle}{\langle
  %      1, \pi_{01} \rangle} \\
  % & + 
-    C_{00} p_{00} \Bigl(\tbinom{N_\kappa}{2} - \tbinom{\mu_E}{2} - \mu_E
-    \mu_F\Bigr) \\ 
-     & + C_{11} p_{11} \tbinom{\mu_E}{2} + C_{01} p_{01} \mu_E \mu_F 
+C_{00} p_{00} \tbinom{N_\kappa}{2} &+ (C_{11}p_{11} - C_{10} p_{10})
+\tbinom{\mu_E}{2} \\ &+ (C_{01} p_{01} - C_{00} p_{00}) \mu_E \mu_F 
     \end{split} \\
-    b_{n,m} = (1 - \tfrac{C_{00} p_{00}}{2} + C_{00} p_{00}
-    N_\kappa)\frac{\sigma_{E + F}}{\sqrt{2 \log{n_1}}}
+    b_{n,m} = C_{00} p_{00} N_\kappa \frac{\sigma_{E + F}}{\sqrt{2
+        \log{m}}}
+    %b_{n,m} = (1 - \tfrac{C_{00} p_{00}}{2} + C_{00} p_{00}
+    %N_\kappa)\frac{\sigma_{E + F}}{\sqrt{2 \log{n_1}}}
   \end{gather}
@@
     \begin{split}
-    \mathbb{P}[ \frac{X - \mu}{\sigma} \leq z]  &= \mathbb{P}[X \leq z
+    \mathbb{P}\Bigl[ \tfrac{X - \mu}{\sigma} \leq z\Bigr]  &= \mathbb{P}[X \leq z
     \sigma + \mu] 
@@
     \mu}{\sigma}, \tfrac{\beta}{\sigma})$. Because the sample
-  mean and the sample variance are consistent estimators, the claims
-  follow after an application of Slutsky's theorem.
+  mean and the sample variance are consistent estimators, the claim
+  follows after an application of Slutsky's theorem.
 \end{proof}
@@
 Eq.~\eqref{eq:21} states that the locality statistics
-$\phi_\lambda(v)$ for our
-attributed random graphs model at time $t = t^{*}$ can be approximated by
-the locality statistics $Y(v)$ for an unattributed kidney and egg
-model. Let $G$ be an instance of $\kappa(n,m,p_{11},
-p_{10}, p_{00})$, an unattributed kidney-egg graph with the
-probability of egg-egg, egg-kidney, and kidney-kidney connections
-being $p_{11}$, $p_{10}$, and $p_{00}$, respectively. $D(v) = M(v) + W(v)$ is then the degree
-of $v$ in $G$. We now show two
-inequalities relating the tail distribution of 
+$\phi_\lambda(v)$ for our attributed random graphs model at time $t =
+t^{*}$ can be approximated by the locality statistics $Y(v)$ for an
+unattributed kidney and egg model. The limiting distribution for the
+scan statistics in unattributed kidney-egg graphs had previously been
+considered in \cite{rukhin:_limit_distr_graph_scan_statis}. We have
+thus provided a sketch of the arguments from
+\cite{rukhin:_limit_distr_graph_scan_statis} below, along with some minor
+changes to handle the case where the probability of kidney-kidney and
+kidney-egg connections are different. \\ \\
+\noindent
+Let $G$ be an instance of
+$\kappa(n,m,p_{11}, p_{10}, p_{00})$, an unattributed kidney-egg graph
+with the probability of egg-egg, egg-kidney, and kidney-kidney
+connections being $p_{11}$, $p_{10}$, and $p_{00}$,
+respectively. $D(v) = M(v) + W(v)$ is then the degree of $v$ in
+$G$. We now show two inequalities relating the tail distribution of
 $\Delta(G)$ and $\Upsilon(G) = \max_{v \in V(G)} Y(v)$.
@@
 \end{equation}
-We first consider the term $a_{n,m} - g(v)$. We have
+We now consider the term $a_{n,m} - g(v)$. We have
 \begin{equation*}
@@
 \end{equation}
-for some $a > 0$. The set $\{v \in [m]\}$ can now be partitition into
+for some $a > 0$. The set $\{v \in [m]\}$ can be partitition into
 $\{v \in [m] \cap (\mathfrak{E} \cap\mathfrak{F})\}$ and $\{v \in [m]
@@
 $\mathbb{P}\{v \in [m] \setminus (\mathfrak{E} \cap \mathfrak{F})\} =
-o(n^{-1})$ by using a concentration inequality, e.g., Hoeffding's
+o(1)$ by using a concentration inequality, e.g., Hoeffding's
 bound. We thus have
@@
     \label{eq:27}
-    p_{S_3} \leq \sum_{\{e,f\} \in S_3} \mathbb{P} \Bigl[Z \leq
+    m p_{S_3} \leq m \sum_{\{e,f\} \in S_3} \mathbb{P} \Bigl[Z \leq
     - O(n^{k/2(k+1)}\Bigr] p_{e,f} = o(1)

### 2011-05-17 ssp2011.tex
Add section on number of triangles

@@
 \newcommand{\argmin}{\operatornamewithlimits{argmin}}
+\def\mathllap{\mathpalette\mathllapinternal}
+\def\mathllapinternal#1#2{%
+\llap{$\mathsurround=0pt#1{#2}$}% $
+}
+\def\clap#1{\hbox to 0pt{\hss#1\hss}}
+\def\mathclap{\mathpalette\mathclapinternal}
+\def\mathclapinternal#1#2{%
+\clap{$\mathsurround=0pt#1{#2}$}%
+}
+\def\mathrlap{\mathpalette\mathrlapinternal}
+\def\mathrlapinternal#1#2{%
+\rlap{$\mathsurround=0pt#1{#2}$}% $
+}
 \bibliographystyle{IEEEtran}
@@
   \mathbb{I}\{ \phi(uv,t) = k \} \\
-  \tau_\lambda(G(t)) = \sum_{k=1}^{K} \lambda_k \!\! \sum_{(u,v,w) \in
-    \binom{V}{3}} h_k(u,v,w) \\
+  \tau_{\lambda}(t) = \sum_{(i,j,k) \in K^{3}\vphantom{\tbinom{V}{3}}}
+  \, \, \sum_{(u,v,w)
+      \in \tbinom{V}{3}} \lambda_{i}\lambda_j \lambda_k h_{ijk}(u,v,w) \\
   \Delta_{\lambda}(G(t)) = \max_{v \in V} \, \sum_{k = 1}^{K} \lambda_k
@@
   \end{gather}
-where $h_k(u,v,w)$ is the indicator function that the argument, a set
-of three vertices, forms a triangle of type $k$. A triangle
-is of type $k$ provided that all edges in the triangle have attribute
-$k$. \\ \\
+where $h_{ijk}(u,v,w)$ is the indicator function that $u$, $v$, and
+$w$ form a triangle whose edges have attributes $i$, $j$, and $k$. \\ \\
 \noindent
@@
  \end{gather}
+\end{theorem}
+\subsection{Power estimates for $\tau_{\lambda}(t)$}
+The limiting distribution for the number of triangles in unattributed
+random graphs was considered in
+\cite{nowicki88:_subgr_u_statis_method} for the Erd\"{o}s-Renyi model
+and in \cite{rukhin09:_asymp_analy_various_statis_random_graph_infer}
+for the kidney-egg model.  
+\label{sec:power-estim-tau_l}
+\begin{theorem}
+  \label{thm:4}
+  Let $\rho$ and $\varsigma$ be defined by
+  \begin{gather}
+    \label{eq:42}
+    \begin{split}
+    \rho = \tbinom{m}{3} \langle \lambda, \pi_{AA} \rangle^{3} &+
+    \tbinom{m}{2}(n-m) \langle \lambda, \pi_{AA} \rangle \langle
+    \lambda, \pi_{0A} \rangle^{2} \\ &+ m \tbinom{n-m}{2} \langle \lambda,
+    \pi_{0A} \rangle^{2} \langle \lambda, \pi_{00} \rangle \\ &+
+    \tbinom{n-m}{3} \langle \lambda, \pi_{00} \rangle^{3}
+    \end{split} \\
+    \begin{split}
+    \varsigma^{2} &= \tbinom{m}{2} \langle \lambda, \eta_{AA} \lambda
+    \rangle \Bigl[(m-2) \langle \lambda, \pi_{AA} \rangle^{2} + (n-m)
+    \langle \pi_{0A} \rangle^{2} \Bigr]^{2} \\
+    &+ m(n-m) \langle \lambda, \eta_{0A} \lambda \rangle^{2} \Bigl[(m-1)
+    \langle \lambda, \pi_{AA} \rangle + (n-m-1) \langle \lambda, \pi_{00} \rangle \Bigr]^{2} \\
+    &+ \tbinom{n-m}{2} \langle \lambda, \eta_{00} \lambda \rangle
+    \Bigl[m \langle \lambda, \pi_{0A} \rangle^{2} + (n-m-2) \langle
+    \lambda, \pi_{00} \rangle^{2} \Bigr]^{2}
+    \end{split}
+  \end{gather}
+  As $n \rightarrow \infty$, we have
+  \begin{gather*}
+    \frac{\tau_{\lambda}(t) - \tbinom{n}{3}\langle \lambda, \pi_{00}
+      \rangle^{3}}{(n-2) \langle \lambda, \pi_{00} \rangle^{2}
+      \sqrt{\tbinom{n}{2} \langle \lambda, \eta_{00} \lambda \rangle}}
+    \rightsquigarrow \mathcal{N}(0,1) \qquad \text{for $t < t^{*}$} \\
+    \frac{\tau_{\lambda}(t) - \rho}{\varsigma} \rightsquigarrow
+    \mathcal{N}(0,1) \qquad \text{for $t = t^{*}$}
+  \end{gather*}
 \end{theorem}
@@
 \cite{rukhin:_limit_distr_graph_scan_statis}. This subsection is
-concerned with adpating the results in
+concerned with adapting the results in
 \cite{rukhin:_limit_distr_graph_scan_statis} to attributed random

### 2011-05-18 ssp2011.tex
State the power estimate for num triangle

--- 2011-05-13 ssp2011.tex
@@
-\documentclass[draftcls]{IEEEtran}
+\documentclass[final]{IEEEtran}
 \usepackage[utopia]{mathdesign}
@@
 \usepackage{subfigure}
-\usepackage{mathrsfs}
+%\usepackage{mathrsfs}
 \usepackage{bm}
@@
 \usepackage[colorlinks=true,pagebackref,linkcolor=magenta]{hyperref}
-\usepackage{cite}
+\usepackage[noadjust]{cite}
 %\usepackage[colon,sort&compress]{natbib}
@@
 subset of vertices of $\mathscr{V}$ with altered communication
-behaviour in an otherwise stationary setting as depicted in Fig.~\ref{fig:notional_change_point}. 
+behaviour in an otherwise stationary setting as depicted in
+Fig.~\ref{fig:notional_change_point}.
 \begin{figure}[htbp]
@@
   \includegraphics[width=8cm]{graphics/Fig1-SSP2011.pdf}
-  \caption{Notional depiction of the problem of change-point detection in a time-series of graphs}
+  \caption{Notional depiction of the problem of change-point detection
+    in a time-series of graphs}
   \label{fig:notional_change_point}
@@
 invariants.  The particular invariants of interests are the size
-$\mathcal{E}$, number of triangles $\tau_{\lambda}$, scan $\Psi$, and
-max degree $\Delta$. Specifically, we consider linear attribute
-fusion with parameter $\lambda \in \mathbb{R}^{K}$ via
-\begin{gather}
+$\mathcal{E}$, number of triangles $\tau$, scan $\Psi$, and
+max degree $\Delta$. Let $G = (V,E,\phi)$ be an attributed graph with 
+$\phi \colon \tbinom{V}{2} \mapsto \mathscr{K}_{+}$. For a given
+$\{u,v\} \in \tbinom{V}{2}$, we define a $\Gamma_{uv} \in
+\mathbb{R}^{K+1}$ by $\Gamma_{uv}(k) = \mathbb{I}\{\phi(\{u,v\}) =
+k\}$. Let $\widehat{\Gamma}_{uv}$ be the first $K$ coordinates of
+$\Gamma_{uv}$. Thus $\widehat{\Gamma}_{uv} = \bm{0}$ unless $\{u,v\}
+\in E$. Under the independent edges assumption, the
+$\Gamma_{uv}$ are independent, and hence the $\widehat{\Gamma}_{uv}$
+are also independent. We can consider linear attribute fusion of graph invariants with
+parameter $\lambda \in \mathbb{R}^{K}$ via
+%\begin{gather}
+%  \label{eq:6}
+%  \mathcal{E}_{\lambda}(G) = \sum_{k=1}^{K} \lambda_k \sum_{u,v}
+%  \mathbb{I}\{ \phi(uv) = k \} \\
+%  \tau_{\lambda}(G) = \sum_{(i,j,k) \in K^{3}\vphantom{\tbinom{V}{3}}}
+%  \, \, \sum_{(u,v,w)
+%      \in \tbinom{V}{3}} \lambda_{i}\lambda_j \lambda_k h_{ijk}(u,v,w) \\
+%  \Delta_{\lambda}(G) = \max_{v \in V} \, \sum_{k = 1}^{K} \lambda_k
+%  \sum_{u \in N(v)}{\mathbb{I}\{\phi(\{u,v\}) = k\}} \\
+%  \label{eq:3}
+%  \Psi_{\lambda}(G) = \max_{v \in V} \sum_{k = 1}^{K}
+%  \lambda_k \!\!\sum_{u,w \in N(v)}\!\!\! \mathbb{I}\{\phi(\{u,w\}) = k\} 
+%  \end{gather}
+
+\begin{align}
   \label{eq:6}
-  \mathcal{E}_{\lambda}(G(t)) = \sum_{k=1}^{K} \lambda_k \sum_{u,v}
-  \mathbb{I}\{ \phi(uv,t) = k \} \\
-  \tau_\lambda(G(t)) = \sum_{k=1}^{K} \lambda_k \!\! \sum_{(u,v,w) \in
-    \binom{V}{3}} h_k(u,v,w) \\
-  \Delta_{\lambda}(G(t)) = \max_{v \in V} \, \sum_{k = 1}^{K} \lambda_k
-  \sum_{u \in N(v)}{\mathbb{I}\{\phi(uv,t) = k\}} \\
+  \mathcal{E}_{\lambda}(G) &= \sum_{\mathclap{\{u,v\} \in
+      \tbinom{V}{2}}} \langle
+  \lambda, \widehat{\Gamma}_{uv} \rangle \\
+  \tau_{\lambda}(G) &= \sum_{\mathclap{\{u,v,w\} \in \tbinom{V}{3}}} \langle
+  \lambda, \widehat{\Gamma}_{uv} \rangle \langle \lambda,
+  \widehat{\Gamma}_{uw} \rangle \langle \lambda, \widehat{\Gamma}_{vw}
+  \rangle \\ 
+\Delta_{\lambda}(G) &= \max_{v \in V} \, \sum_{w \in N(v)} \langle
+\lambda, \widehat{\Gamma}_{vw} \rangle \\
 \label{eq:3}
-  \Psi_{\lambda}(G(t)) = \max_{v \in V} \sum_{k = 1}^{K}
-  \lambda_k \!\!\sum_{u,w \in N(v)}\!\!\! \mathbb{I}\{\phi(uw,t) = k\} 
-  \end{gather}
-where $h_k(u,v,w)$ is the indicator function that the argument, a set
-of three vertices, forms a triangle of type $k$. A triangle
-is of type $k$ provided that all edges in the triangle have attribute
-$k$. \\ \\
-\noindent
-Let $J_{\lambda}(t)$ be a statistic of the form as in Eq.~\eqref{eq:6} through
-Eq.~\eqref{eq:3}. We define the normalization $\bar{J}^{l}_\lambda(t)$
-of $J_{\lambda}$ based on recent past as
+  \Psi_{\lambda}(G) &= \max_{v \in V} \sum_{u,w \in N(v)} \langle
+  \lambda, \widehat{\Gamma}_{uw} \rangle
+  \end{align}
+  Let $\{G(t)\}$ be a time series of graphs. Let $J_{\lambda}(t)$ be a
+  statistic for $G(t)$ of the form as in Eq.~\eqref{eq:6} through
+  Eq.~\eqref{eq:3}. We define the normalization
+  $\bar{J}^{l}_\lambda(t)$ of $J_{\lambda}$ based on recent past as
 \begin{equation}
@@
 \end{figure}
-\subsection{Power estimates for $\mathcal{E}_\lambda(t)$}
+\subsection{Power estimates for $\mathcal{E}_\lambda$}
 It was shown in
-\cite{lee:_laten_proces_model_time_attrib_random_graph} that for the
-case where $J_\lambda(t)$ is $\mathcal{E}_{\lambda}(t)$, $T_{\lambda}^{l}(t)$ 
+\cite{lee:_laten_proces_model_time_attrib_random_graph} that if
+$J_\lambda(t) = \mathcal{E}_{\lambda}(G(t))$, then $T_{\lambda}^{l}(t)$ 
 follows a $t$-distribution with $l - 1$
@@
 \end{theorem}
+\subsection{Power estimates for $\tau_{\lambda}$}
+\label{sec:power-estim-tau_l}
+The limiting distribution for the number of triangles in unattributed
+random graphs was considered in
+\cite{nowicki88:_subgr_u_statis_method} for the Erd\"{o}s-Renyi 
+and in \cite{rukhin09:_asymp_analy_various_statis_random_graph_infer}
+for the kidney-egg model. We note here the small changes that allow us
+to extend the results in
+\cite{rukhin09:_asymp_analy_various_statis_random_graph_infer,%
+nowicki88:_subgr_u_statis_method}
+to our attributed graphs model. Let $Y_{uv} = \langle \lambda,
+\widehat{\Gamma}_{uv} \rangle$ for $\{u,v\} \in \tbinom{V(t)}{2}$. We
+can now write $\tau_{\lambda}(G(t))$ as
+\begin{equation}
+  \label{eq:45}
+  \begin{split}
+  \frac{\tau_{\lambda}(G(t))}{\tbinom{n}{3}} &= \tbinom{n}{3}^{-1}
+  \sum_{\mathclap{\{u,v,w\} \in \tbinom{V}{3}}} Y_{uv} Y_{uw} Y_{vw}
+  \\ &= \tbinom{n}{3}^{-1}
+  \sum_{\mathclap{\{e_1, e_2, e_3\} \in \tbinom{E(t)}{3}}} Y_{e_1}
+  Y_{e_2} Y_{e_3}
+  \end{split}
+\end{equation}
+$\tau_{\lambda}(G(t))/\tbinom{n}{3}$ is then an (incomplete)
+$U$-statistic on $\{Y_{e}\}$, with kernel function $h(Y_{1}, Y_{2},
+Y_{3}) = Y_{1} Y_{2} Y_{3}$. By using Hajek's projection method, we
+can show that $\tau_{\lambda}(G(t))$ converges to a normal
+distribution as $n \rightarrow \infty$. 
+\begin{lemma}
+  \label{lem:3}
+  Let $\tau_{\lambda}^{*}$ be the Hajek's projection of $\tau_{\lambda}$, i.e.,
+\begin{equation}
+  \label{eq:46}
+  \tau_{\lambda}^{*}(G(t)) = \sum_{e \in E(t)} \mathbb{E}[
+  \tau_{\lambda}(G(t)) \, \lvert \, Y_{e}]
+\end{equation}
+For $t < t^{*}$, we have
+\begin{align*}
+  \mu_0 = \mathbb{E}[\tau_{\lambda}^{*}(G(t))] &= \tbinom{n}{3} \langle 
+  \lambda, \pi_{00} \rangle^{3} \\
+  \sigma_0 = \sqrt{\mathrm{Var}[\tau_{\lambda}^{*}(G(t))]} &= (n-2) \langle \lambda,
+  \pi_{00} \rangle^{2} \sqrt{\tbinom{n}{2} \langle \lambda, \eta_{00}
+  \lambda \rangle}
+\end{align*}
+For $t = t^{*}$, we have
+  \begin{gather*}
+    \label{eq:42}
+    \begin{split}
+    \mu_A = \mathbb{E}[\tau_{\lambda}^{*}(G(t))] = \tbinom{m}{3}
+    \langle \lambda, \pi_{11} \rangle^{3} &+
+    \tbinom{m}{2}(n-m) \langle \lambda, \pi_{11} \rangle \langle
+    \lambda, \pi_{01} \rangle^{2} \\ &+ m \tbinom{n-m}{2} \langle \lambda,
+    \pi_{01} \rangle^{2} \langle \lambda, \pi_{00} \rangle \\ &+
+    \tbinom{n-m}{3} \langle \lambda, \pi_{00} \rangle^{3}
+    \end{split} \\
+    \begin{split}
+    \sigma_A^{2} = \mathrm{Var}[\tau_{\lambda}^{*}(G(t))] = \tbinom{m}{2} \langle \lambda, \eta_{11} \lambda
+    \rangle S_1  
+    &+ m(n-m) \langle \lambda, \eta_{01} \lambda \rangle S_2  \\
+    &+ \tbinom{n-m}{2} \langle \lambda, \eta_{00} \lambda \rangle S_3
+    \end{split}
+  \end{gather*}
+  where $S_1$, $S_2$, and $S_3$ are given by
+\begin{align*}
+    S_1 &= \Bigl[(m-2) \langle \lambda, \pi_{11} \rangle^{2} + (n-m)
+    \langle \pi_{01} \rangle^{2} \Bigr]^{2} \\ 
+    S_2 &= \Bigl[(m-1)
+    \langle \lambda, \pi_{11} \rangle \langle \lambda, \pi_{01}
+    \rangle + (n-m-1) \langle \lambda, \pi_{00} \rangle \langle
+    \lambda, \pi_{01} \rangle \Bigr]^{2} \\
+    S_3 &= \Bigl[m \langle \lambda, \pi_{01} \rangle^{2} + (n-m-2) \langle
+    \lambda, \pi_{00} \rangle^{2} \Bigr]^{2} 
+    \end{align*}
+  As $n \rightarrow \infty$ and $m = \Omega(\sqrt{n})$, we have
+  \begin{equation}
+    \label{eq:49}
+    \frac{\tau_{\lambda}(t) -
+      \mathbb{E}[\tau_{\lambda}^{*}(G(t))]}{\sqrt{\mathrm{Var}[\tau_{\lambda}^{*}(G(t))]}}
+      \rightsquigarrow \mathcal{N}(0,1)
+  \end{equation}
+\end{lemma}
+From Lemma~\ref{lem:3}, we can show that the limiting distribution of
+$T_{\lambda}^{l}(t)$ is, once again, a Student t-distribution with
+$l-1$ degrees of freedom.
+\begin{theorem}
+  \label{thm:5}
+  Let $t \in \{l+1, \dots, t^{*}\}$ and $\lambda \in
+  \mathbb{R}^{K}$. Define the random varialbel $\psi_{\lambda}^{l}(t)$
+  by
+  \begin{equation}
+    \label{eq:50}
+    \psi_{\lambda}^{l}(t) = \begin{cases}
+      \Bigl(\sqrt{\tfrac{l}{l+1}}\,\Bigr) T_{\lambda}^{l}(t) & \text{if $t <
+        t^{*}$} \\
+      \Bigl(\sqrt{\tfrac{l \sigma_0^{2}}{l \sigma_A^{2} + \sigma_0^{2}} }\,\Bigr)
+      T_{\lambda}^{l}(t) & \text{if $t = t^{*}$}
+        \end{cases}
+  \end{equation}
+  As $n \rightarrow \infty$, $\psi_{\lambda}^{l}(t)$ converges to a Student $t$-distribution with $l - 1$ degrees of freedom and
+  non-centrality parameter $\mu_{\lambda}$ where
+  \begin{equation}
+    \label{eq:51}
+    \mu_{\lambda} = \begin{cases} 0 & \text{if $t < t^{*}$} \\
+      \frac{\mu_A - \mu_0}{\sqrt{l \sigma_A^{2} + \sigma_0^{2}}} &
+       \text{if $t = t^{*}$}
+      \end{cases}
+  \end{equation}
+\end{theorem}
+The power approximation for $\tau_{\lambda}$ is determined by various
+factors, but similar to the power approximation for
+$\mathcal{E}_{\lambda}$, the dominating factor is likely to be
+  $\mu_\lambda$. Thus, we are also interested in finding the $\lambda$
+  that will maximize $\mu_\lambda$. However, because of the high power
+  of $\lambda$ in the expression for $\mu_{\lambda}$, an analytic
+  solution to $\argmax_{\lambda}{\mu_{\lambda}}$ might not be possible.
 \subsection{Power estimates for $\Delta_{\lambda}(t)$}
@@
     \Delta_{\lambda}(t) \rightsquigarrow \begin{cases}
-      \mathcal{G}(a_n \sigma_1 + \mu_1, b_n \sigma_1 ) & \text{for $t < t^{*}$.} \\
-     \mathcal{G}(a_m \sigma_2 + \mu_2, b_m \sigma_2) &
+      \mathcal{G}(a_n \sigma_0 + \mu_0, b_n \sigma_0 ) & \text{for $t < t^{*}$.} \\
+     \mathcal{G}(a_m \sigma_A + \mu_A, b_m \sigma_A) &
      \text{for $t = t^{*}$.}
@@
   \begin{align*}
-    \mu_1 &= (n-1)\langle \lambda, \pi_{00} \rangle \\
-    \sigma_1 &= \sqrt{(n-1)\langle \lambda, \eta_{00} \lambda \rangle} \\
-    \mu_2 &= \,\, (m - 1) \langle x, \pi_{11} \rangle + (n-
+    \mu_0 &= (n-1)\langle \lambda, \pi_{00} \rangle \\
+    \sigma_A &= \sqrt{(n-1)\langle \lambda, \eta_{00} \lambda \rangle} \\
+    \mu_0 &= \,\, (m - 1) \langle x, \pi_{11} \rangle + (n-
     m)\langle \lambda, \pi_{01} \rangle
-    \\ \sigma_2 &= \sqrt{ (m - 1) \langle \lambda, \eta_{11} \lambda \rangle + (n -
+    \\ \sigma_A &= \sqrt{ (m - 1) \langle \lambda, \eta_{11} \lambda \rangle + (n -
       m) \langle \lambda, \eta_{01} \lambda \rangle}
@@
   \rho_{\lambda} &= \begin{cases}
-    \frac{\sqrt{\pi}}{6} \frac{\mu_2 - \mu_1 + a_m\sigma_2 - (a_n + b_n
-      \gamma)\sigma_1}{b_n \sigma_1} & \text{if $t =
+    \frac{\sqrt{\pi}}{6} \frac{\mu_A - \mu_0 + a_m\sigma_A - (a_n + b_n
+      \gamma)\sigma_0}{b_n \sigma_0} & \text{if $t =
         t^{*}$} \\
@@
   \varsigma_{\lambda} &= \begin{cases}
-    \frac{\sqrt{\pi} b_m \sigma_2}{6 b_n \sigma_1} & \text{if $t =
+    \frac{\sqrt{\pi} b_m \sigma_A}{6 b_n \sigma_0} & \text{if $t =
       t^{*}$} \\
@@
 power of the test using $\Delta_{\lambda}$. The power approximation is
-once again determined by various factors, but the dominating factor is
+determined by various factors, but the dominating factor is
 likely to be $\tfrac{\rho_\lambda}{\varsigma_\lambda}$. For sufficiently large $n$
-and $m$, we also have
-\begin{equation*}
-  \begin{split}
-  \frac{\rho_\lambda}{\varsigma_\lambda} &= (1 + o(1)) \frac{\mu_2 - \mu_1}{b_m
-    \sigma_ 2} \\ &= \frac{\langle \lambda, (m-1)\pi_{11} + (n-m)\pi_{01} -
+and $m$, we have
+\begin{equation*}
+  \begin{split}
+  \frac{\rho_\lambda}{\varsigma_\lambda} &= (1 + o(1)) \frac{\mu_A - \mu_0}{b_m
+    \sigma_A} \\ &= \frac{\langle \lambda, (m-1)\pi_{11} + (n-m)\pi_{01} -
     (n-1) \pi_{00} \rangle}{\sqrt{\langle \lambda, ((m-1) \eta_{11} +
@@
 \cite{rukhin:_limit_distr_graph_scan_statis}. This subsection is
-concerned with adpating the results in
+concerned with adapting the results in
 \cite{rukhin:_limit_distr_graph_scan_statis} to attributed random
 graphs. We state here only the relevant results. The proofs are
-delegated to the appendices. \\ \\
+relegated to the appendices. \\ \\
 \noindent
 The limiting distribution for $\Psi_{\lambda}(t)$ is Gumbel for both
-the case where $t < t^{*}$ and for $t = t^{*}$. To aid the exposition,
-we first introduce some notations. Let $\lambda^{(2)}$ be the
-element-wise square of $\lambda$. Define $C_{00}$, $C_{01}$, $C_{11}$
-and $p_{00}$, $p_{01}$, $p_{11}$ to be
-\begin{gather}
-  \label{eq:19}
-  C_{00} = \tfrac{\langle \lambda^{(2)}, \pi_{00} \rangle}{\langle \lambda,
-    \pi_{00}\rangle}; \quad p_{00} = \tfrac{(\langle \lambda, \pi_{00}
-    \rangle)^{2}}{\langle \lambda^{(2)},\, \pi_{00} \rangle} \\
-C_{11} = \tfrac{\langle \lambda^{(2)}, \pi_{11} \rangle}{\langle \lambda,
-    \pi_{11}\rangle}; \quad p_{11} = \tfrac{(\langle \lambda, \pi_{11}
-    \rangle)^{2}}{\langle \lambda^{(2)},\, \pi_{11} \rangle} \\
-C_{10} = \tfrac{\langle \lambda^{(2)}, \pi_{11} \rangle}{\langle \lambda,
-    \pi_{10}\rangle}; \quad p_{10} = \tfrac{(\langle \lambda, \pi_{10}
-    \rangle)^{2}}{\langle \lambda^{(2)},\, \pi_{10} \rangle} 
-\end{gather}
-Also let $z_n$ be defined, for any $n \in \mathbb{N}$, by
+the cases when $t < t^{*}$ and $t = t^{*}$. To aid the exposition,
+ we first introduce some notations. Let $z_n$ be defined, for $n \in \mathbb{N}$, by
 \begin{equation}
@@
 \end{equation}
+Let us also define $E$ and $F$ by
+\begin{gather*}
+ %  B \sim \mathrm{Bin}(m, \langle 1, \pi_{00} \rangle); \quad C \sim \mathrm{Bin}(n-m-1,
+ % \langle 1, \pi_{01} \rangle) \\
+  E \sim \mathrm{Bin}(m-1, \langle 1, \pi_{11} \rangle) \\ F \sim \mathrm{Bin}(n-m,
+  \langle 1, \pi_{01} \rangle)
+\end{gather*}%
+Let $E + F$ be the convolution of $E$ and $F$. Denote by $\mu_{E+F}$ and
+$\sigma_{E+F}^{2}$ the mean and variance of $E + F$. Finally, let
+$N_{\kappa} = \mu_{E + F} + z_m \sigma_{E + F}$. We then have the
+following results.
+%Let $\lambda^{(2)}$ be the
+% element-wise square of $\lambda$. Define $C_{00}$, $C_{01}$, $C_{11}$
+% and $p_{00}$, $p_{01}$, $p_{11}$ to be
+% \begin{gather}
+%   \label{eq:19}
+%   C_{00} = \tfrac{\langle \lambda^{(2)}, \pi_{00} \rangle}{\langle \lambda,
+%     \pi_{00}\rangle}; \quad p_{00} = \tfrac{(\langle \lambda, \pi_{00}
+%     \rangle)^{2}}{\langle \lambda^{(2)},\, \pi_{00} \rangle} \\
+% C_{11} = \tfrac{\langle \lambda^{(2)}, \pi_{11} \rangle}{\langle \lambda,
+%     \pi_{11}\rangle}; \quad p_{11} = \tfrac{(\langle \lambda, \pi_{11}
+%     \rangle)^{2}}{\langle \lambda^{(2)},\, \pi_{11} \rangle} \\
+% C_{10} = \tfrac{\langle \lambda^{(2)}, \pi_{11} \rangle}{\langle \lambda,
+%     \pi_{10}\rangle}; \quad p_{10} = \tfrac{(\langle \lambda, \pi_{10}
+%     \rangle)^{2}}{\langle \lambda^{(2)},\, \pi_{10} \rangle} 
+% \end{gather}
 \begin{theorem}
@@
   %    1, \pi_{00} \rangle} + C_{00}p_{00}\tbinom{N_{0}}{2} \\ 
-    a_n &=  C_{00}p_{00}\tbinom{N_{0}}{2} \\ 
-   b_n &= C_{00}p_{00} N_{0} \frac{\sigma_0}{\sqrt{2 \log
+    a_n &=  \langle \lambda, \pi_{00} \rangle \tbinom{N_{0}}{2} \\ 
+   b_n &= \langle \lambda, \pi_{00} \rangle N_{0} \frac{\sigma_0}{\sqrt{2 \log
      n}}
@@
 \end{theorem}%
-We now move to the limiting distribution for $\Psi_{\lambda}(t^{*})$. 
-Let us define $E$ and $F$ by
-\begin{gather*}
- %  B \sim \mathrm{Bin}(m, \langle 1, \pi_{00} \rangle); \quad C \sim \mathrm{Bin}(n-m-1,
- % \langle 1, \pi_{01} \rangle) \\
-  E \sim \mathrm{Bin}(m-1, \langle \pi_{11}, 1 \rangle) \\ F \sim \mathrm{Bin}(n-m,
-  \langle \pi_{01}, 1 \rangle)
-\end{gather*}%
-For any random variable $X$, we let $\mu_X$ and $\sigma_X^{2}$ denote
-the mean and variance of $X$. If $X$ and $Y$ are independent random
-variables, we let $\mu_{X + Y}$ and $\sigma_{X + Y}^2$ denote the mean
-and variance of the convolution $X + Y$. \\
-\noindent Let $N_{\kappa}$ be the quantity defined by
-\begin{equation}
-  \label{eq:18}
-  N_{\kappa} = \mu_{E + F} + z_m \sigma_{E + F}
-\end{equation}
 \begin{theorem}
@@
  % & + 
-C_{00} p_{00} \tbinom{N_\kappa}{2} &+ (C_{11}p_{11} - C_{10} p_{10})
-\tbinom{\mu_E}{2} \\ &+ (C_{01} p_{01} - C_{00} p_{00}) \mu_E \mu_F 
+\langle \lambda, \pi_{00} \rangle \tbinom{N_\kappa}{2} &+
+\langle \lambda, \pi_{11} - \pi_{00} \rangle
+\tbinom{\mu_E}{2} \\ &+ \langle \lambda, \pi_{01} - \pi_{00} \rangle \mu_E \mu_F 
     \end{split} \\
-    b_{n,m} = C_{00} p_{00} N_\kappa \frac{\sigma_{E + F}}{\sqrt{2
+    b_{n,m} = \langle \lambda, \pi_{00} \rangle N_\kappa \frac{\sigma_{E + F}}{\sqrt{2
         \log{m}}}
@@
 \label{sec:proofs-some-stated}
-\begin{proof}[Theorem \ref{thm:1}]
+\begin{IEEEproof}[Theorem \ref{thm:1}]
   The maximizer of $\mu_\lambda$ also maximizes
@@
   Hermitean matrices.
-\end{proof}
-\begin{proof}[Proposition~\ref{prop:3}]
-  Let $d_{\lambda}(v;t)$ be the (fused) degree of vertex $v$ at time
-  $t$, i.e.,
-  \begin{equation*}
-    d_{\lambda}(v;t) = \sum_{k = 1}^{K} \lambda_k \sum_{w \in N(v)}
-    \mathbb{I}\{ \phi(vw,t) = k \}
-  \end{equation*}
-  Let $\Gamma^{(k)}(v;t) = |\{w \colon \mathbb{I}\{\phi(wv,t) =
-  k\}|$. The vector $\bm{\Gamma}(v;t) = (\Gamma^{(k)}(v;t))_{k=1}^{K}$
-  for $t < t^{*}$ is distributed as a multinomial with $n-1$ trials
-  and probability vector $\pi_{00}$. The following statements are
+\end{IEEEproof}
+\begin{IEEEproof}[Proposition~\ref{prop:3}]
+  Let $v \in V(t)$ and denote by $d_{\lambda}(v;t)$ the (fused) degree
+  of vertex $v$, i.e.,
+  \begin{equation*}
+    d_{\lambda}(v;t) = \sum_{w \in N(v)} \langle \lambda,
+    \widehat{\Gamma}_{vw} \rangle
+  \end{equation*}
+  For $t < t^{*}$, each of the $\widehat{\Gamma}_{vw}$ is a multinomial
+  trial with probability vector $\pi_{00}$. The following statements are
   made as $n \rightarrow \infty$ for fixed
-  $K$. Now $d_{\lambda}(v;t) = \langle \lambda, \bm{\Gamma}(v;t)
-  \rangle$ and
-  thus, by the central limit theorem, we have
+  $K$.  By the central limit theorem, we have
   \begin{equation}
@@
     III.1]{bollobas85:_random_graph} we can show that the dependency
-    among the $d_{\lambda}(v,t)$ can be ignored. $d_{\lambda}(v;t)$,
-    when normalized, can thus be considered as a sequence of
-    independent random variables from the standard normal in the
-    limit. It is widely known that the sample maximum of standard
-    normal random variables converges weakly to a Gumbel distribution
-    \cite[\S 2.3]{galambos87:_asymp_theor_extrem_order_statis}. It is,
-    however, not clear whether the convergence of
-    $\Delta_{\lambda}(t)$ to a Gumbel distribution continues to hold
-    under the composition of weak convergence as
-    outlined above. We avoid this problem by showing
-    directly that 
+    among the $\{d_{\lambda}(v;t)\}_{v \in V(t)}$ can be
+    ignored. $d_{\lambda}(v;t)$, can thus be considered as a sequence
+    of independent random variables from a normal distribution. It is
+    widely known that the sample maximum of standard normal random
+    variables converges weakly to a Gumbel distribution \cite[\S
+    2.3]{galambos87:_asymp_theor_extrem_order_statis}. It is, however,
+    not clear whether the convergence of $\Delta_{\lambda}(t)$ to a
+    Gumbel distribution continues to hold under the composition of
+    weak convergence as outlined above. We avoid this problem by
+    showing directly that
     \begin{equation}
@@
         \rangle}}$ and $F_n(u) = \mathbb{P}(\zeta_v \leq u)$. If $n
-    \rightarrow \infty$ and $u = O(\log{n})$, we have the
+    \rightarrow \infty$ and $u = O(\sqrt{\log{n}})$, we have the
     following moderate deviations result \cite[Theorem~2, \S
@@
 Eq.~\eqref{eq:14} for $t = t^{*}$.  
-\end{proof}
-\begin{proof}[Lemma~\ref{lem:2}]
+\end{IEEEproof}
+\begin{IEEEproof}[Lemma~\ref{lem:2}]
   Let $ X \sim \mathcal{G}(\alpha, \beta)$. We consider the
@@
   follows after an application of Slutsky's theorem.
-\end{proof}
-\begin{proof}[Theorem~\ref{thm:2}]
+\end{IEEEproof}
+\begin{IEEEproof}[Theorem~\ref{thm:2}]
 Let $\phi_{\lambda}(v;t) = \psi_{\lambda}(v;t) - d_{\lambda}(v;t)$ be
@@
 from Theorem~1.1 in \cite{rukhin:_limit_distr_graph_scan_statis}.
-\end{proof}
-\begin{proof}[Theorem~\ref{thm:3}]
+\end{IEEEproof}
+\begin{IEEEproof}[Theorem~\ref{thm:3}]
   For ease of exposition we drop the index $t^{*}$ from our discussion. Let
@@
 \end{gather}
-\begin{proof}[Eq.~\eqref{eq:27}]
+\begin{IEEEproof}[Eq.~\eqref{eq:27}]
  Let $C^{*} = \max\{C_{11},
@@
 Eq.~\eqref{eq:27} is therefore established.
-\end{proof}
-\begin{proof}[Eq.~\eqref{eq:28}]
+\end{IEEEproof}
+\begin{IEEEproof}[Eq.~\eqref{eq:30}]
   We start by noting that
@@
 \end{equation}
-and once again, by a concentration inequality, we can show that m
-$\mathbb{P}(M(v) = e, W(v) = f, \{e,f\} \in S_2) = o(1)$. As for
+and once again, by a concentration inequality, we can show that $m
+\mathbb{P}(M(v) = e, W(v) = f, \{e,f\} \in S_2) = o(1)$. As for
 $S_3$, from the fact that $e + f \geq N_{\kappa} + \varphi(n)$, we have the bound
@@
   \begin{equation}
-    \label{eq:27}
+    \label{eq:44}
     m p_{S_3} \leq m \sum_{\{e,f\} \in S_3} \mathbb{P} \Bigl[Z \leq
@@
       N_{\kappa}) \rightarrow 0$ as desired.
-\end{proof}
+\end{IEEEproof}
 
-\end{proof}
+\end{IEEEproof}
 \bibliography{ssp2011}

### 2011-05-18 ssp2011.tex
Revise introduction

@@
 \newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{corollary}[theorem]{Corollary}
 \newtheorem{proposition}[theorem]{Proposition}
@@
 \section{Introduction}
+
 \subsection{Latent Process Model}
 The latent process model for time series of attributed graphs was
-originally presented in
+presented in
 \cite{lee:_laten_proces_model_time_attrib_random_graph}. We summarized
@@
       \pi^{(i)}(t) \equiv \pi_0 \\
-      Q^{(i)}(t) \equiv \mathbf{Q}_0
+      \mathbf{Q}^{(i)}(t) \equiv \mathbf{Q}_0
     \end{gather*}
@@
      \label{eq:5}
-     \bar{X}_{i}(t) \equiv \bar{\pi}_0.
+     \bar{X}_{i}(t) \equiv \hat{\pi}_0.
    \end{equation}
@@
    \begin{gather*}
-     \bar{X}_{i}(t) \equiv \bar{\pi}_1 \quad \text{for $i \leq m$} \\
-     \bar{X}_{i}(t) \equiv \bar{\pi}_0 \quad \text{for $i > m$} 
+     \bar{X}_{i}(t) \equiv \hat{\pi}_1 \quad \text{for $i \leq m$} \\
+     \bar{X}_{i}(t) \equiv \hat{\pi}_0 \quad \text{for $i > m$} 
    \end{gather*}
  \end{enumerate}
- where $\bar{\pi}_0$ and $\bar{\pi}_1$ are sub-probability vectors
+ where $\hat{\pi}_0$ and $\hat{\pi}_1$ are sub-probability vectors
  obtained by removing the last coordinate of $\pi_0$ and $\pi_1$. 
@@
   Let $\mathscr{V}$ be a rdpm with change parameters $(t^{*}, m,
-  \pi_0, \pi_1, Q_0, Q_1)$. Define $\mathbf{Z}_0$ and $\mathbf{Z}_1$
-  by
+  \pi_0, \pi_1, \mathbf{Q}_0, \mathbf{Q}_1)$. Define
+  $\mathbf{Z}_0$ and $\mathbf{Z}_1$ by
   \begin{gather}
@@
   $\mathbf{Z}_0$ and $\mathbf{Z}_1$ are the fundamental matrices
-  for the continuous-time Markov chain on $\mathscr{K}$ with intensity
+  for the continuous-time Markov chain on $\mathscr{K}_{+}$ with intensity
   matrix $\mathbf{Q}_0$ and $\mathbf{Q}_1$ (see
@@
   \begin{gather*}
-    \Sigma_0 = \mathrm{diag}(\pi_0) \mathbf{Z}_0 + \mathbf{Z}_0^{T}
+    \Sigma_0 = \mathrm{diag}(\pi_0) \mathbf{Z}_0 +
+    \mathbf{Z}_0^{T}
     \mathrm{diag}(\pi_0) \\
-    \Sigma_1 = \mathrm{diag}(\pi_1) \mathbf{Z}_1 + \mathbf{Z}_1^{T}
+    \Sigma_1 = \mathrm{diag}(\pi_1) \mathbf{Z}_1 +
+    \mathbf{Z}_1^{T}
     \mathrm{diag}(\pi_1)
   \end{gather*}
-  A second order approximation $\hat{\mathscr{V}}$ of $\mathscr{V}$
-  is the sequence $\{\hat{X}(t), \hat{G}(t)\}_{t=1}^{\infty}$ where
+  The second order approximation $\widehat{\mathscr{V}}$ of
+  $\mathscr{V}$ is the sequence $\{\widehat{X}(t),
+  \widehat{G}(t)\}_{t=1}^{\infty}$ where
   \begin{enumerate}
-  \item For each $t$ and each $i \in [n]$, $\hat{X}^{i}(t)$ is a
+  \item For each $t$ and each $i \in [n]$, $\widehat{X}_i(t)$ is a
     random vector obtained by truncating a multivariate normal random
-    vector $Z_{i}(t)$ to $\mathscr{S}$.
+    vector $Z_{i}(t)$ to $\mathscr{S}$ with mean and covariance
+    matrices given below.
   \item For $t < t^{*}$,
     \begin{gather}
-      \mathbb{E}[Z_i(t)] \equiv \bar{\pi}_0 \\
-      \mathrm{Var}[Z_i(t)] \equiv \hat{\Sigma^{0}}
+      \mathbb{E}[Z_i(t)] \equiv \hat{\pi}_0 \\
+      \mathrm{Var}[Z_i(t)] \equiv \widehat{\Sigma}_0
     \end{gather}
@@
     \begin{gather*}
-      \mathbb{E}[Z_i(t)] \equiv \bar{\pi}_0, \quad \text{for $i \leq
+      \mathbb{E}[Z_i(t)] \equiv \hat{\pi}_0, \quad \text{for $i \leq
         m$}  \\
-      \mathbb{E}[Z_i(t)] \equiv \bar{\pi}_1, \quad \text{for $i > 
+      \mathbb{E}[Z_i(t)] \equiv \hat{\pi}_1, \quad \text{for $i > 
         m$}  \\
-      \mathrm{Var}[Z_i(t)] \equiv \hat{\Sigma}_{0} \quad \text{for $i
+      \mathrm{Var}[Z_i(t)] \equiv \widehat{\Sigma}_{0} \quad \text{for $i
         \leq m$} \\
-      \mathrm{Var}[Z_i(t)] \equiv \hat{\Sigma}_{1} \quad \text{for $i
+      \mathrm{Var}[Z_i(t)] \equiv \widehat{\Sigma}_{1} \quad \text{for $i
         > m$}
     \end{gather*}
-    where $\hat{\Sigma}_0$ and $\hat{\Sigma}_1$ are the matrices
-    obtained by removing last row and column of $\Sigma_0$ and
-    $\Sigma_1$. 
+    where $\widehat{\Sigma}_0$ and $\widehat{\Sigma}_1$ are the $K
+    \times K$ matrices
+    obtained by removing the last row and column of $\Sigma_0^{(r)}$ and
+    $\Sigma_1^{(r)}$, respectively. 
   \end{enumerate}
 \end{definition}
+Suppose that we have a sequence $\{\mathscr{V}^{r} \colon r > 0 \}$ of
+rdpm with vertices $[n]$ and attributes $\mathscr{K}$ where for each
+$r > 0$, $\mathscr{V}^{r}$ has change parameters $(t^{*}, m, \pi_0,
+\pi_1, r \mathbf{Q}_0, r \mathbf{Q}_1)$. The parameter $r$ can be
+thought of as the vertex process rate, i.e., the waiting time
+decreases exponentially as $r$ increases. Let us now consider the
+sequence of first approximation $\bar{\mathscr{V}}^{r}$ and second
+approximations $\widehat{\mathscr{V}}^{r}$ of $\mathscr{V}$. We note
+that $\bar{\mathscr{V}}^{r_1} = \bar{\mathscr{V}}^{r_2}$ for any $r_1,
+r_2 > 0$. Let us then denote by $\bar{\mathscr{V}}$ the (a.e.) unique
+first order approximation of $\mathscr{V}^{r}$ for $r > 0$. If we
+denote by $\widehat{\Sigma}_{0}^{(r)}$ and
+$\widehat{\Sigma}_{1}^{(r)}$ the matrices $\widehat{\Sigma}_0$ and
+$\widehat{\Sigma}_1$ for $\widehat{\mathscr{V}}^{r}$, then
+$\widehat{\Sigma}_0^{(r)} = \widehat{\Sigma}_0^{(1)}/r$ and
+$\widehat{\Sigma}_{1}^{(r)} = \widehat{\Sigma}_1^{(1)}/r$. Therefore,
+as $r \rightarrow \infty$, $\widehat{\Sigma}_0^{(r)} \rightarrow 0$
+and $\widehat{\Sigma}_1^{(r)} \rightarrow 0$ and so
+$\widehat{\mathscr{V}}^{r} \rightsquigarrow
+\bar{\mathscr{V}}$. This indicates that for sufficiently large $r$,
+there is little statistical difference amongst the $\bar{\mathscr{V}}$,
+$\mathscr{V}^{r}$ and $\widehat{\mathscr{V}}$ (\cite[Theorem
+2]{lee:_laten_proces_model_time_attrib_random_graph}). $\bar{\mathscr{V}}$
+will thus serve as the basis for our subsequent analysis on graph
+invariants for attributed random graphs. 
 \section{Change-point detection}
@@
 \end{equation}
-for $l \geq 2$. 
+for $l \geq 2$. As we have mentioned earlier, we will use the first
+approximation $\bar{\mathscr{V}}$ of $\mathscr{V}$ in our study of the 
+asymptotic theory for these graphs invariants.   
 \begin{figure}[htbp]
@@
 results
-\begin{lemma}
-  \label{lem:1}
+\begin{theorem}
+  \label{thm:9}
   Let $t \in \{l+1, \dots, t^{*}\}$ and $\lambda \in
@@
   \end{equation}
-\end{lemma}
+\end{theorem}
 We are interested in finding the $\lambda$ that will maximize the
@@
 factors but the dominating factor is likely to be
-$\mu_{\lambda}$. Theorem \ref{thm:1} extends a result in
+$\mu_{\lambda}$. The following corollary extends a result in
 \cite{lee:_laten_proces_model_time_attrib_random_graph} for $K = 2$ to the case
 where $K \geq 2$. 
-\begin{theorem}
-  \label{thm:1}
-  Let $\zeta$ and $\xi$ be as defined in Lemma \ref{lem:1}.  Suppose
+\begin{corollary}
+  \label{cor:1}
+  Let $\zeta$ and $\xi$ be as defined in Theorem~\ref{thm:9}. Suppose
   that $\xi$ is also positive definite. Let $\nu^{*}$ be the
@@
  \end{gather}
-\end{theorem}
+\end{corollary}
 \subsection{Power estimates for $\tau_{\lambda}$}
@@
 From Lemma~\ref{lem:3}, we can show that the limiting distribution of
-$T_{\lambda}^{l}(t)$ is, once again, a Student t-distribution with
+$T_{\lambda}^{l}(t)$ is once again a Student t-distribution with
 $l-1$ degrees of freedom.
@@
 \end{proposition}
-\begin{lemma}
-  \label{lem:2}
+\begin{theorem}
+  \label{thm:8}
   Let $t \in \{l+1, \dots, t^{*}\}$ and $\lambda \in
@@
 $\gamma \approx 0.57721$ is the Euler-Mascheroni constant.
-\end{lemma}
+\end{theorem}
 We are interested in finding the $\lambda$ that will maximize the
@@
 determined by various factors, but the dominating factor is
-likely to be $\tfrac{\rho_\lambda}{\varsigma_\lambda}$. For sufficiently large $n$
-and $m$, we have
+be $\tfrac{\rho_\lambda}{\varsigma_\lambda}$. For sufficiently large $n$
+and $m$, we have for $t = t^{*}$,
 \begin{equation*}
@@
   \frac{\rho_\lambda}{\varsigma_\lambda} &= (1 + o(1)) \frac{\mu_A - \mu_0}{b_m
-    \sigma_A} \\ &= \frac{\langle \lambda, (m-1)\pi_{11} + (n-m)\pi_{01} -
-    (n-1) \pi_{00} \rangle}{\sqrt{\langle \lambda, ((m-1) \eta_{11} +
+    \sigma_A} \\ &= (1 + o(1)) \frac{\langle \lambda, (m-1)\pi_{11} + (n-m)\pi_{01} -
+    (n-1) \pi_{00} \rangle}{b_m \sqrt{\langle \lambda, ((m-1) \eta_{11} +
     (n-m)\eta_{01}) \lambda \rangle}}
@@
 $\tfrac{\rho_{\lambda}}{\varsigma_{\lambda}}$ by solving an 
-eigenvalue problem as in Theorem~\ref{thm:1}. 
+eigenvalue problem as in Corollary~\ref{cor:1}.
 \subsection{Power estimates for $\Psi_{\lambda}(t)$}
@@
 % \end{gather}
-\begin{theorem}
-  \label{thm:2}
+\begin{lemma}
+  \label{lem:5}
   Let $\Psi_{\lambda}(t)$ be the scan statistic for $t < t^{*}$. Let
@@
 \end{equation}
-\end{theorem}%
-\begin{theorem}
-  \label{thm:3}
+\end{lemma}%
+\begin{lemma}
+  \label{lem:6}
   Let $a_{n,m}$ and $b_{n,m}$ be given by
@@
   \end{gather}
-  If $m = \Omega(\sqrt{n \log n})$, then
+  If $m = \Omega(\sqrt{n \log n})$ and $m = O(n^{k/(k+1)})$ for some
+  $k \in \mathbb{N}$ then
   \begin{equation}
     \label{eq:29}
-    \frac{\Psi_{\lambda}(t^{*}) - a_{n,m}}{b_{n,m}}  \rightsquigarrow \mathcal{G}(0,1)  \end{equation}
+    \frac{\Psi_{\lambda}(t^{*}) - a_{n,m}}{b_{n,m}}  \rightsquigarrow
+    \mathcal{G}(0,1)  \end{equation}
+\end{lemma}
+\begin{theorem}
+  \label{thm:6}
+  Let $t \in \{l+1, \dots, t^{*}$ and $\lambda \in
+  \mathbb{R}^{K}$. For sufficiently large $n$ and sufficiently large
+  $l$, $T_{\lambda}^{l}(t)$ has approximately a
+  $\mathcal{G}(\rho_{\lambda}, \varsigma_{l})$ distribution with
+  \begin{align}
+    \label{eq:52}
+    \rho_{\lambda} &= \begin{cases}
+      \tfrac{\sqrt{\pi}}{6} \tfrac{a_{n,m} - a_n - b_n \gamma}{b_n} & \text{if
+        $t = t^{*}$} \\
+      - \tfrac{\sqrt{\pi}}{6} \gamma & \text{if $t < t^{*}$} 
+    \end{cases} \\
+      \varsigma_{\lambda} &= \begin{cases}
+        \tfrac{\sqrt{\pi} b_{n,m}}{6 b_n} & \text{if $t = t^{*}$} \\
+        \tfrac{\sqrt{\pi}}{6} & \text{if $t < t^{*}$}
+      \end{cases}
+  \end{align}
 \end{theorem}
+The dominating factor in the power approximation for $\Psi_{\lambda}$
+is $\tfrac{\rho_{\lambda}}{\varsigma_{\lambda}}$. For $t = t^{*}$ and
+sufficiently large $n$ and $l$, we have
+\begin{equation}
+  \label{eq:53}
+  \begin{split}
+    \frac{\rho_{\lambda}}{\varsigma_{l}} &= \frac{a_{n,m} - a_n - b_n
+      \gamma}{b_{n,m}} \\
+    &= (1 + o(1)) \frac{ \langle \lambda, \xi \rangle}{\langle
+      \lambda, N_{\kappa} \tfrac{\sigma_{E+F}}{\sqrt{2 \log{n}}}
+      \pi_{00} \rangle}
+  \end{split}
+\end{equation}
+where $\xi$ is given by
+\begin{equation*}
+ \xi =  \Bigl(\tbinom{N_{\kappa}}{2} -
+    \tbinom{N_0}{2} - \tbinom{\mu_E}{2} - \mu_E \mu_F\Bigr)\pi_{00} +
+    \tbinom{\mu_{E}}{2} \pi_{11} + \mu_E \mu_F \pi_{10}  
+\end{equation*}
+From Eq.~\eqref{eq:53}, we see that the $\lambda$ that maximimizes
+$\tfrac{\rho_\lambda}{\varsigma_{\lambda}}$ would be on the boundary,
+i.e., $\lambda(k) \not = 0$ for exactly one $k$. Therefore the asymptotic theory
+for scan statistics, in contrast with the other graph invariants that
+were considered, indicates that there are no benefits in fusing attributes.  
 \appendices
@@
 \label{sec:proofs-some-stated}
-\begin{IEEEproof}[Theorem \ref{thm:1}]
+\begin{IEEEproof}[Corollary\ref{cor:1}]
   The maximizer of $\mu_\lambda$ also maximizes
@@
   Hermitean matrices.
+\end{IEEEproof}
+\begin{IEEEproof}[Lemma~\ref{lem:3}]
 \end{IEEEproof}
@@
 \end{IEEEproof}
-\begin{IEEEproof}[Lemma~\ref{lem:2}]
+\begin{IEEEproof}[Theorem~\ref{thm:8}]
   Let $ X \sim \mathcal{G}(\alpha, \beta)$. We consider the
@@
 \end{IEEEproof}
-\begin{IEEEproof}[Theorem~\ref{thm:2}]
+\begin{IEEEproof}[Lemma~\ref{lem:5}]
 Let $\phi_{\lambda}(v;t) = \psi_{\lambda}(v;t) - d_{\lambda}(v;t)$ be
@@
   \label{eq:11}
-  \phi_{\lambda}(v;t) = \sum_{k=1}^{K} \lambda_k \sum_{\substack{uw
-      \in N(v) \\ u,w \not = v}}
-  \mathbb{I}\{\phi(uw,t) = k\}.
-\end{equation}
-The following statements are made conditional on $|N(v)| = l$. First
+  \phi_{\lambda}(v;t) = \sum_{\substack{uw
+      \in N(v) \\ u,w \not = v}} \langle \lambda,
+  \widehat{\Gamma}_{uw} \rangle
+\end{equation}
+The following statements are conditional on $|N(v)| = l$. First
 of all, we have
@@
 can be approximated by the locality statistics for an Erd\"{o}s-Renyi
-graph with edge probability $p_{00}$. Theorem~\ref{thm:2} then follows
+graph with edge probability $p_{00}$. The lemma then follows
 from Theorem~1.1 in \cite{rukhin:_limit_distr_graph_scan_statis}.
 \end{IEEEproof}
-\begin{IEEEproof}[Theorem~\ref{thm:3}]
+\begin{IEEEproof}[Lemma~\ref{lem:6}]
   For ease of exposition we drop the index $t^{*}$ from our discussion. Let
@@
   $W(v)$ be the number of neighbors of $v$ that lies in $[n]
-\setminus [m]$. The following statements are made, conditional on
+\setminus [m]$. The following statements are conditional on
 $M(v) = l_{\zeta}$ and $W(v) = l_{\xi}$. We have
@@
 scan statistics in unattributed kidney-egg graphs had previously been
-considered in \cite{rukhin:_limit_distr_graph_scan_statis}. We have
-thus provided a sketch of the arguments from
-\cite{rukhin:_limit_distr_graph_scan_statis} below, along with some minor
-changes to handle the case where the probability of kidney-kidney and
+considered in \cite{rukhin:_limit_distr_graph_scan_statis}. We
+provided a sketch of the arguments from
+\cite{rukhin:_limit_distr_graph_scan_statis} below, along with some
+minor changes to handle the case where the probability of
+kidney-kidney and
 kidney-egg connections are different. \\ \\

### 2011-05-20 ssp2011.tex
Completed the proof of num triangle and scan statistics.

@@
 \section{Change-point detection}
-Let $\mathscr{V}$ be a random dot process model with change parameters
-$(t^{*}, m, \pi_0, \pi_1, \mathbf{Q}_0, \mathbf{Q}_1)$. The
-change-parameters encapsulate a notion of chatter anomalies, i.e., a
-subset of vertices of $\mathscr{V}$ with altered communication
-behaviour in an otherwise stationary setting as depicted in
-Fig.~\ref{fig:notional_change_point}.
 \begin{figure}[htbp]
@@
 \end{figure}
-\\ \noindent
-We are interested in
-the problem of testing, for a $t \in \mathbb{N}$, the hypotheses that
-$t$ is the change-point of $\mathscr{V}$, namely
+Let $\mathscr{V}$ be a random dot process model with change parameters
+$(t^{*}, m, \pi_0, \pi_1, \mathbf{Q}_0, \mathbf{Q}_1)$. The
+change-parameters encapsulate a notion of chatter anomalies, i.e., a
+subset of vertices of $\mathscr{V}$ with altered communication
+behaviour in an otherwise stationary setting as depicted in
+Fig.~\ref{fig:notional_change_point}. We are interested in the problem
+of testing, for a $t \in \mathbb{N}$, the hypotheses that $t$ is the
+change-point of $\mathscr{V}$, namely
 \begin{gather*}
@@
 \end{equation}
-for $l \geq 2$. As we have mentioned earlier, we will use the first
-approximation $\bar{\mathscr{V}}$ of $\mathscr{V}$ in our study of the 
-asymptotic theory for these graphs invariants.   
+for $l \geq 2$, i.e., we want to find a parameter $\lambda$ such that
+the power of the test using $T_{\lambda}^{l}$ is maximum. We note that
+$T_{\lambda}^{l}$ is scale invariant in $\lambda$ for all of our graph
+invariants. It was noted in
+\cite{lee:_laten_proces_model_time_attrib_random_graph} that the
+maximum of the power for scale invariant tests is
+attainable in $\{ \| \lambda \| \leq 1 \}$. \\ \\
+\noindent
+As we have mentioned earlier, we will assume that the
+number of vertices $n$ is large and that the use of the first order approximation
+ $\bar{\mathscr{V}}$ of $\mathscr{V}$ is appropriate in our study of the 
+asymptotic theory for these graphs invariants. We strive to
+obtain estimates for the power in testing $t^{*} > t$ against $t^{*} =
+t$ using $T_{\lambda}(t)$ and from these estimates, find the $\lambda$
+that maximize the power. We now introduce a few
+additional notations that will be used later on in the paper. First,
+let $\pi_{00}, \pi_{01}$, and $\pi_{11}$ be sub-probability vectors
+whose components are given by
+\begin{gather*}
+  \pi_{00}(k) = \pi_{0}(k) \pi_{0}(k) \\
+  \pi_{01}(k) = \pi_{0}(k) \pi_{1}(k) \\
+  \pi_{11}(k) = \pi_{1}(k) \pi_{1}(k)
+\end{gather*}
+where $k \in \mathscr{K}$. We also let $\eta_{00}, \eta_{01}$, and
+$\eta_{11}$ be matrices of size $K \times K$ defined by 
+\begin{gather*}
+  \eta_{00} = \mathrm{diag}(\pi_{00}) - \pi_{00} \pi_{00}^{T} \\
+  \eta_{01} = \mathrm{diag}(\pi_{01}) - \pi_{01} \pi_{01}^{T} \\
+  \eta_{11} = \mathrm{diag}(\pi_{11}) - \pi_{11} \pi_{11}^{T}
+\end{gather*}
+% The structure of the remaining sections of the paper is as follows. We
+% discussed the power estimates for $\mathcal{E}_{\lambda},
+% \tau_{\lambda}, \Delta_{\lambda}$ and $\Psi_{\lambda}$ in
+% \S~\ref{sec:power-estim-mathc}
+%  through \S~\ref{sec:power-estim-psi_l}. We illustrate our analysis with some
+% simulation experiments in \S~\ref{sec:experimental-results}  
 \begin{figure}[htbp]
@@
 \subsection{Power estimates for $\mathcal{E}_\lambda$}
+\label{sec:power-estim-mathc}
 It was shown in
@@
   \label{eq:45}
-  \begin{split}
-  \frac{\tau_{\lambda}(G(t))}{\tbinom{n}{3}} &= \tbinom{n}{3}^{-1}
+  \frac{\tau_{\lambda}(G(t))}{\tbinom{n}{3}} = \tbinom{n}{3}^{-1}
   \sum_{\mathclap{\{u,v,w\} \in \tbinom{V}{3}}} Y_{uv} Y_{uw} Y_{vw}
-  \\ &= \tbinom{n}{3}^{-1}
-  \sum_{\mathclap{\{e_1, e_2, e_3\} \in \tbinom{E(t)}{3}}} Y_{e_1}
-  Y_{e_2} Y_{e_3}
-  \end{split}
-\end{equation}
-$\tau_{\lambda}(G(t))/\tbinom{n}{3}$ is then an (incomplete)
+\end{equation}
+$\tau_{\lambda}(G(t))/\tbinom{n}{3}$ is then an
 $U$-statistic on $\{Y_{e}\}$, with kernel function $h(Y_{1}, Y_{2},
@@
   \label{eq:46}
-  \tau_{\lambda}^{*}(G(t)) = \sum_{e \in E(t)} \mathbb{E}[
-  \tau_{\lambda}(G(t)) \, \lvert \, Y_{e}]
+  \tau_{\lambda}^{*}(G) - \mathbb{E}[\tau_{\lambda}(G)] =
+  \sum_{\mathclap{\{u,v\} \in \tbinom{V(t)}{2}}} \, \Bigl(\mathbb{E}[
+  \tau_{\lambda}(G) \, \lvert \, Y_{uv}] -
+  \mathbb{E}[\tau_{\lambda}(G)]\Bigr)
 \end{equation}
@@
     S_1 &= \Bigl[(m-2) \langle \lambda, \pi_{11} \rangle^{2} + (n-m)
-    \langle \pi_{01} \rangle^{2} \Bigr]^{2} \\ 
+    \langle \lambda, \pi_{01} \rangle^{2} \Bigr]^{2} \\ 
     S_2 &= \Bigl[(m-1)
@@
 \subsection{Power estimates for $\Delta_{\lambda}(t)$}
+\label{sec:power-estim-delt}
 The analysis of the power estimates for $\Delta_{\lambda}(t)$ depends
@@
 \subsection{Power estimates for $\Psi_{\lambda}(t)$}
+\label{sec:power-estim-psi_l}
 The limiting distribution for the scan statistics for unattributed
@@
 were considered, indicates that there are no benefits in fusing attributes.  
+%\section{Experimental Results}
+%\label{sec:experimental-results}
 \appendices
@@
 \begin{IEEEproof}[Lemma~\ref{lem:3}]
+  $\tau_{\lambda}(G)$ is a U-statistics with kernel function
+  $h(Y_1, Y_2, Y_3) = Y_1 Y_2 Y_3$. By the theory of U-statistics, we
+  know that
+  \begin{equation}
+    \label{eq:48}
+    \frac{\tau_{\lambda}(G) -
+      \mathbb{E}[\tau_{\lambda}^{*}(G)]}{\sqrt{\mathrm{Var}[\tau_{\lambda}^{*}(G)]}}
+    \rightsquigarrow N(0,1)
+  \end{equation}
+  provided that $\mathrm{Var}[\tau_{\lambda}(G) -
+  \tau_{\lambda}^{*}(G)] = o(\mathrm{Var}[\tau_{\lambda}^{*}(G)]$. We
+  will not show this here. The deta
+
+By the independent edge
+  assumption, we have 
+  \begin{align}
+    \mathbb{E}[h(Y_i, Y_j, Y_k) &= \mathbb{E}[Y_i]
+  \mathbb{E}[Y_j] \mathbb{E}[Y_k] \\ 
+  \mathbb{E}[h(Y_i, Y_j, Y_k) |
+  Y_i] &= Y_i E[Y_j] \mathbb{E}[Y_k] 
+  \end{align}
+ Thus, for $t < t^{*}$, we have $\mathbb{E}[\tau_{\lambda}^{*}(G(t))] = \tbinom{n}{3} \langle
+  \lambda, \pi_{00} \rangle^{3}$ and
+  \begin{equation}
+    \begin{split}
+      \mathrm{Var}[\tau_{\lambda}^{*}(G(t))] &=
+      \mathrm{Var}\Bigl[\sum_{\{u,v,w\}} Y_{uv} \mathbb{E}[Y_{uw}]
+      \mathbb{E}[Y_{vw}]\Bigr] \\
+      &= (n-2)^{2} \langle \lambda, \pi_{00} \rangle^{4}
+      \mathrm{Var}\Bigl[\sum_{\{u,v\}} Y_{uv} \Bigr] \\
+      &= (n-2)^{2} \langle \lambda, \pi_{00} \rangle^{4} \tbinom{n}{2}
+      \langle \lambda, \eta_{00} \lambda \rangle
+    \end{split}
+  \end{equation}
+  The case when $t = t^{*}$ can be argued in a similar manner. We
+  sketch here the derivation of
+  $\mathrm{Var}[\tau_{\lambda}^{*}(G(t))]$. We can partition the set
+  $\{u,v\} \in \tbinom{V}{2}$ into the sets 
+\begin{align*}
+\mathcal{S}_1 &= \{ u,v \in [m]
+  \}, \\ \mathcal{S}_2 &= \{ u \in [m], v \in [n] \setminus [m]\}, \\
+  \mathcal{S}_3 &= \{ u, v \in [n] \setminus[m]\}
+\end{align*} Now, for $\{u,v\} \in \mathcal{S}_1$, we have
+\begin{equation}
+  \label{eq:58}
+  \begin{split}
+    \sqrt{S_1} &= \sum_{w \not \in \{u,v\}} \mathbb{E}[ h(Y_{uv},
+    Y_{uw}, Y_{vw}) | Y_{uv}] \\ & = ((m-2) \langle \lambda, \pi_{11}
+    \rangle^{2} + (n-m) \langle \lambda, \pi_{10} \rangle^{2})Y_{uv}
+  \end{split}
+\end{equation}
+The above expression is reasoned as follows. If $w \in [m]$, then
+$\mathbb{E}[Y_{uw}] = \mathbb{E}[Y_{vw}] = \langle \lambda,
+\pi_{11}$ and there are $m-2$ possible choices for $w \in [m]$
+different from $u$ and $v$. If $w \in [n] \setminus [m]$, then
+$\mathbb{E}[Y_{vw}] = \mathbb{E}[Y_{uw}] = \langle \lambda, \pi_{10}
+\rangle$ and there are $n - m$ possible choices for $w$. Analogous
+reasoning gives the expressions for $S_2$ and $S_3$ in the statement
+of the lemma. We therefore have
+\begin{equation}
+  \label{eq:60}
+  \begin{split}
+  \mathrm{Var}[\tau_{\lambda}^{*}(G(t))] &=  \mathrm{Var}\Bigl[\sum_{\{u,v,w\}} Y_{uv} \mathbb{E}[Y_{uw}]
+      \mathbb{E}[Y_{vw}]\Bigr] \\ &=
+      S_1 \mathrm{Var}[\sum_{\{u,v\} \in \mathcal{S}_1} Y_{uv}] + S_2
+      \mathrm{Var}[\sum_{\{u,v\} \in \mathcal{S}_1} Y_{uv}] \\ &+ S_3
+      \mathrm{Var}[\sum_{\{u,v\} \in \mathcal{S}_1} Y_{uv}] \\ &=
+      \tbinom{m}{2} \langle \lambda, \eta_{00} \lambda \rangle S_1 +
+      m(n-m) \langle \lambda, \eta_{01} \lambda \rangle S_2 \\ &+
+      \tbinom{n-m}{2} \langle \lambda, \eta_{00} \lambda \rangle S_3
+  \end{split}
+\end{equation}
+as desired. To complete the proof one must show that
+$\mathrm{Var}[\tau_{\lambda}(G) - \tau_{\lambda}^{*}(G)] =
+o(\mathrm{Var}[\tau_{\lambda}^{*}(G)]$ and this follows directly from
+the corresponding argument in \cite{nowicki88:_subgr_u_statis_method}
+or \cite{rukhin09:_asymp_analy_various_statis_random_graph_infer}.
 \end{IEEEproof}
@@
 \end{IEEEproof}
-
+From Eq.~\eqref{eq:27} and Eq.~\eqref{eq:30}, we have
+\begin{equation}
+  \label{eq:40}
+ \lim
+\mathbb{P}(\Upsilon(G) \geq a_{n,m}) = \lim \mathbb{P}(\Delta(G) \geq
+N_{\kappa})
+ \end{equation}
+Let $N_{\kappa,y} = N_\kappa + y \tfrac{\sigma_{E+F}}{\sqrt{2
+    \log{m}}}$. We now define $a_{n,m,y}$ as 
+\begin{equation}
+  \label{eq:18}
+  \begin{split}a_{n,m,y} &= \langle \lambda, \pi_{00} \rangle
+    \tbinom{N_{\kappa,y}}{2} +
+  \langle \lambda, \pi_{11} - \pi_{00} \rangle \tbinom{\mu_E}{2}  +
+  \langle \lambda, \pi_{10} - \pi_{00} \rangle \mu_E \mu_F \\
+  &= a_{n,m} + \langle \lambda, \pi_{00} \rangle y
+  \frac{\sigma_{E+F}}{\sqrt{2 \log m}} \Bigl(N_{\kappa} + y
+  \frac{\sigma_{E+F}^{2}}{2 \sqrt{2 \log{m}}} + O(1) \Bigr) \\
+  &= a_{n,m} + (y + o(1)) b_{n,m} 
+  \end{split}
+\end{equation}
+We therefore have
+\begin{equation}
+  \label{eq:43}
+  \begin{split}
+  \lim \mathbb{P}(\Upsilon(G) \geq a_{n,m,y}) &= 
+  \lim \mathbb{P}\Bigl(\frac{\Upsilon(G) - a_{n,m}}{b_{n,m}} \geq y \Bigr) \\
+  &= \lim \mathbb{P}(\Delta(G) \geq N_{\kappa,y}) \\
+  &= \lim \mathbb{P}\Bigl(\frac{\Delta(G) -
+    N_{\kappa}}{\sigma_{E+F}} \geq \frac{y}{\sqrt{2 \log{m}}} \Bigr) \\
+  \end{split}
+\end{equation}
+Because $\Delta(G)$ converges weakly to a Gumbel
+distribution in the limit
+(\cite{bollobas85:_random_graph,rukhin:_limit_distr_graph_scan_statis}),
+we have
+\begin{equation}
+  \label{eq:47}
+  \mathbb{P}\Big(\frac{\Upsilon(G) - a_{n,m}}{b_{n,m}} \leq
+    y\Bigr) \rightarrow e^{- e^{-y}} 
+\end{equation}
+and Eq.~\eqref{eq:29} follows.
 \end{IEEEproof}

### 2011-10-30 ssp2011.tex
Draft of Journal version completed

--- 2011-05-18 ssp2011.tex
@@
-\documentclass[final]{IEEEtran}
-\usepackage[utopia]{mathdesign}
-\usepackage{amsmath}
-%\usepackage{amssymb}
+\documentclass[10pt,journal,compsoc]{IEEEtran}
+\usepackage{fontenc}
+%\usepackage{lmodern}
+%\usepackage[utopia]{mathdesign}
+\usepackage{graphicx}
+\usepackage{xltxtra}
+\setmainfont[Mapping=tex-text]{Linux Libertine}
+\usepackage[cmex10]{amsmath}
+\interdisplaylinepenalty=2500
+\usepackage{array}
+\usepackage{amssymb}
 \usepackage{amsthm}
-\usepackage{graphicx}
-\usepackage{subfigure}
-%\usepackage{mathrsfs}
+%\usepackage[tight,normalsize,sf,SF]{subfigure}
+\ifCLASSOPTIONcompsoc
+\usepackage[font=normalsize,labelfont=sf,textfont=sf]{subfig}
+\else
+\usepackage[font=footnotesize]{subfig}
+\fi
+\usepackage{subfig}
+\usepackage{parskip}
+\usepackage{mathrsfs}
 \usepackage{bm}
@@
 \usepackage[noadjust]{cite}
-%\usepackage[colon,sort&compress]{natbib}
-%\numberwithin{equation}{section}
 \renewcommand\arraystretch{1.2}
-\let\underbrace\LaTeXunderbrace
-\let\overbrace\LaTeXoverbrace
 \newcommand{\argmax}{\operatornamewithlimits{argmax}}
@@
   graphs}
-\author{Carey~E.~Priebe, Nam~H.~Lee, Youngser~Park, and Minh~Tang}%
-%\thanks{Johns Hopkins University \\ Department of Applied Mathematics
-%  and Statistics \\ Baltimore, Maryland 21218-2682 USA}%
-\maketitle
+\author{Minh~Tang, Youngser~Park, Nam~H.~Lee, and Carey~E.~Priebe%
+\IEEEcompsocitemizethanks{\IEEEcompsocthanksitem Minh~Tang, Nam~H.~Lee
+ and Carey~E.~Priebe are with the Department of Applied Mathematics
+ and Statistics, Johns Hopkins University.\protect \\
+  Email: \{mtang10, nhlee, cep\}@jhu.edu
+\IEEEcompsocthanksitem Youngser Park is with the Center for Imaging
+Science , Johns Hopkins University.\protect \\
+  Email: youngser@jhu.edu}%
+\thanks{}}
+\markboth{IEEE Transactions on Pattern Analysis and Machine
+  Intelligence (TPAMI)}{}
+\IEEEcompsoctitleabstractindextext{%
 \begin{abstract}
- We consider the problem of anomaly/change point detection given a
- time series of graphs with categorical attributes on the
- edges. Various attributed graph invariants are considered, and their
- power for detection as a function of a linear fusion parameter is
- presented.  
+  Hypothesis testing on time series of attributed graphs has
+  applications in diverse areas, e.g., social network analysis
+  (wherein vertices represent individual actors or organizations),
+  connectome inference (wherein vertices are neurons or brain regions)
+  and text processing (wherein vertices represent authors or
+  documents).  We consider the problem of anomaly/change point
+  detection given the latent process model for time series of graphs
+  with categorical attributes on the edges presented in \cite{lee11}.
+  Various attributed graph invariants are considered, and their power
+  for detection as a function of a linear fusion parameter is
+  presented.  Our main result is that inferential performance in
+  mathematically tractable first-order and second-order approximation
+  models does provide guidance for methodological choices applicable
+  to the exact (realistic but intractable) model. Furthermore, to the
+  extent that the exact model is realistic, we may tentatively
+  conclude that approximation model investigations have some bearing
+  on real data applications.
 \end{abstract}
 \begin{IEEEkeywords}
-  Anomaly detection, Attributed Random Graphs, Fusion, Random Dot
-  Product Graphs
-\end{IEEEkeywords}
+  Anomaly detection, Attributed Random Graphs, Random Dot
+  Product Graphs.
+\end{IEEEkeywords}}
+\maketitle
 \section{Introduction}
@@
 The latent process model for time series of attributed graphs was
-presented in
-\cite{lee:_laten_proces_model_time_attrib_random_graph}. We summarized
-here the ideas that are relevant to our discussion. We begin by
-introducing some terminology. Let $\mathscr{S}$ be the unit simplex in
+presented in \cite{lee11}. We summarize here the ideas that are
+relevant to our discussion.  Let $G = (V,E)$ be an undirected graph,
+equipped with an edge-attribution function $\phi \colon \tbinom{V}{2}
+\mapsto \{1,2,\dots, K+1\}$ for some $K$ such that $\phi(e) \leq K$
+for $e \in E$ and $\phi(e) \equiv K+1$ for $e \not \in E$. We refer to
+$\phi(e)$ as the attribute of edge $e \in E$, and the pair $(G,\phi)$
+as an attributed graph. Let $\mathscr{S}$ be the unit simplex in
 $\mathbb{R}^{K}$, i.e.,
@@
 A {\em random dot product space} for attributed graphs with vertices
-in $[n]$ and edge attributes $\mathscr{K} = [K]
-$ is then a pair $(\mathbf{X},G)$ of random elements such that
+in $[n]$ and edge attributes $[K]$ is a pair $(\mathbf{X},G)$ of
+random elements such that
 \begin{enumerate}
-\item $\mathbf{X} = \{X_i\}_{i = 1}^{n}$ is a collection of
+\item $\mathbf{X} = \{X_v\}_{v = 1}^{n}$ is a collection of
   $\mathscr{S}$-valued random vectors.
-\item $G$ is a random graph with vertices set $[n]$ such that
+\item $G$ is a random undirected graph with vertex set $[n]$ such that
   \begin{equation}
     \label{eq:1}
-    \mathbb{P}(i \sim j \,|\, \mathbf{X} = (x_1, x_2, \dots,
-    x_n)) = \langle x_i, x_j \rangle.
-  \end{equation}
-  and that $\mathbf{P}(i \sim j \,|\, \mathbf{X})$ and $\mathbf{P}(i' \sim
-  j' \,|\, \mathbf{X})$ are independent whenever $(i,j) \not = (i',j')$. If
-  $i \sim j$ in $G$, then the attribute of the edge $\{i,j\}$ is an
-  element of $\mathscr{K}$. In particular, $\{i,j\}$ has attribute $k$
-  with probability $x_{i,k} x_{j,k}$. 
+    \mathbb{P}(u \sim v \,|\, \mathbf{X}) = \mathbb{P}(u \sim v \, |
+    \, X_u,X_v) = \langle x_u, x_v \rangle
+  \end{equation}
+  and $\bm{1}(u \sim v \,|\, \mathbf{X})$ and $\bm{1}(u' \sim
+  v' \,|\, \mathbf{X})$ are independent whenever $(u,v) \not =
+  (u',v')$. Furthermore, we also have 
+  \begin{equation*}
+    \mathbb{P}(\phi(\{u,v\} = k \, | \, u \sim
+    v) = x_{u,k} x_{v,k}. 
+  \end{equation*}
 \end{enumerate}
-Let $\mathscr{K}_{+} = \{1,\dots,K+1\}$. We say that a c\'{a}dl\'{a}g
-process $W \colon [0,\infty) \mapsto \mathscr{K}_{+}^{n}$ induces the
-sequence of random dot product spaces $\mathscr{V} = \{X(t), G(t)\}_{t
-  = 1}^{\infty}$ if
+We say that a c\'{a}dl\'{a}g process $W \colon [0,\infty) \mapsto
+[K+1]^{n}$ induces the sequence of random dot product spaces
+$\mathscr{V} = (\mathbf{X}(t), G(t))_{t = 1}^{\infty}$ if
 \begin{enumerate}
-\item Each $(X(t), G(t))$ is a random dot product space with vertices
-  $[n]$ and attributes $\mathscr{K}$. Furthermore, for each
-  $i \in [n]$, $k \in \mathscr{K}$ and $t \in \mathbb{N}$, we have
-  $X_{i,k}(t)  = \int_{t - 1}^{t}{ \mathbf{1}\{W_i(u) = k\}\, du}$.
+\item Each $(\mathbf{X}(t), G(t))$ is a random dot product space with
+  vertices $[n]$ and edge attributes $[K]$. Furthermore, for each $v
+  \in [n]$, $k \in [K]$ and $t \in \mathbb{N}$, we have
+  \begin{equation}
+    \label{eq:54}
+  X_{v,k}(t)  = \int_{t - 1}^{t}{ \mathbf{1}\{W_v(\omega) = k\}\, d\omega}
+  \end{equation}
+  where we denote $W_{v}(\omega)$ as the $v$-th component of $W(\omega)$ and
+  $X_{v,k}$ as the $k$-th component of $X_v$.  
 \item  For each $t \in \mathbb{N}$, we have
@@
     \label{eq:2}
-    \mathbb{P}(G(t) = g \,|\, \mathscr{F}_{\leq t}) = \mathbb{P}(G(t) = g \,|\, X(t))
-  \end{equation}
-where $\mathscr{F}_{\leq t}$ are the sigma fields generated by $\{W(s)
+    \mathbb{P}(G(t) = g \,|\, \mathscr{F}_{\leq t}) = \mathbb{P}(G(t)
+    = g \,|\, \mathbf{X}(t))
+  \end{equation}
+where $\mathscr{F}_{\leq t}$ is the $\sigma$-field generated by $\{W(s)
   \colon s \leq t\}$.
@@
 \begin{enumerate}
-\item For each $t \in \mathbb{N}$ and vertex $i \in [n]$, there exists
-  a matrix $\mathbf{Q}^{(i)}(t)$ such that $W_i$, when restricted to
+\item For each $t \in \mathbb{N}$ and vertex $v \in [n]$, there exists
+  a matrix $\mathbf{Q}^{(v)}(t)$ such that $W_v$, when restricted to
   the interval $[t, t+1)$, is a stationary, continuous-time Markov
-  chain with state space $\mathscr{K}_+$, intensity matrix
-  ${\mathbf{Q}^{(i)}(t)}$, and stationary distribution
-  $\pi^{(i)}(t)$. $W$ is thus a stationary, continuous-time Markov chain with state
-  space $\mathscr{K}_{+}^{n}$ and intentisy matrix
-  $\otimes_{i=1}^{n}\mathbf{Q}^{(i)}(t)$.
-\item There exists a $t^{*} \in \mathbb{N}$ and a $m < n$ such that 
+  chain with state space $[K+1]$, intensity matrix
+  ${\mathbf{Q}^{(v)}(t)}$, and stationary distribution
+  $\pi^{(v)}(t)$. $W$ is thus a piecewise stationary, continuous-time
+  Markov chain with state space $[K+1]^{n}$ and intensity matrix
+  $\otimes_{v=1}^{n}\mathbf{Q}^{(v)}(t)$.
+\item There exists a $t^{*} \in \mathbb{N}$ and a $m < n$ such that,
+  for some $\pi_0, \pi_1, \mathbf{Q}_0$ and $\mathbf{Q}_1$ we have
   \begin{enumerate}
-  \item for  $t < t^{*}$
+  \item for $t < t^{*} - 1$,
     \begin{gather*}
-      \pi^{(i)}(t) \equiv \pi_0 \\
-      \mathbf{Q}^{(i)}(t) \equiv \mathbf{Q}_0
+      \pi^{(1)}(t) = \dots = \pi^{(n)}(t) = \pi_0 \\
+      \mathbf{Q}^{(1)}(t) = \dots = \mathbf{Q}^{(n)}(t) = \mathbf{Q}_0,
     \end{gather*}
-  \item  for $t \geq t^{*}$
+  \item  for $t \geq t^{*} - 1$,
     \begin{gather*}
@@
 The above properties characterize a random dot process model with a
-change-point phenomena. We will refer to $(t^{*}, m, \pi_0, \pi_1,
-\mathbf{Q}_0, \mathbf{Q}_1)$ as the change parameters. Because $W$ is completely
-determined by the change parameters, we often choose to omit $W$ and
-only mention $\mathscr{V}$ when referring to random dot process models
-with change-point phenomena. For a rdpm $\mathscr{V}$ with change
-parameters $(t^{*}, m, \pi_0, \pi_1, \mathbf{Q}_0, \mathbf{Q}_1)$, we can construct
-several approximations to $\mathscr{V}$. Of particular interests are the
-following two approximations.
+change-point phenomena at time $t = t^{*}$. We chose $\{1,2,\dots,m\}$
+as the set of vertices with a change in the stationary distribution
+and intensity matrix at time $t = t^{*} - 1$ for ease of
+discussion. Permutation of the vertex labels does not affect our
+subsequent analysis. We will refer to $(t^{*}, m, \pi_0, \pi_1,
+\mathbf{Q}_0, \mathbf{Q}_1)$ as the change parameters.  Because $W$ is
+completely determined by the change parameters, we often choose to
+omit $W$ and only mention $\mathscr{V}$ when referring to random dot
+process models (rdpm) with change-point phenomena. For a rdpm
+$\mathscr{V}$ with change parameters $(t^{*}, m, \pi_0, \pi_1,
+\mathbf{Q}_0, \mathbf{Q}_1)$, we can construct several approximations
+to $\mathscr{V}$. Of particular interests are the following two
+approximations.
 \begin{definition}
@@
   $\bar{\mathscr{V}}$ of $\mathscr{V}$ is the sequence $\{(\bar{X}(t),
-  \bar{G}(t)\}_{t = 1}^{\infty}$ of independent random dot product
+  \bar{G}(t)\}_{t = 1}^{\infty}$ of {\em independent} random dot product
   spaces such that
  \begin{enumerate}
- \item For $t < t^{*}$,
+ \item for $t < t^{*} - 1$,
    \begin{equation}
      \label{eq:5}
-     \bar{X}_{i}(t) \equiv \hat{\pi}_0.
-   \end{equation}
- \item For $t \geq t^{*}$
+     \bar{X}_{v}(t)  \equiv \hat{\pi}_0 \quad \text{for all $v \in [n]$}
+   \end{equation}
+ \item for $t \geq t^{*} - 1$
    \begin{gather*}
-     \bar{X}_{i}(t) \equiv \hat{\pi}_1 \quad \text{for $i \leq m$} \\
-     \bar{X}_{i}(t) \equiv \hat{\pi}_0 \quad \text{for $i > m$} 
+     \bar{X}_{v}(t) \equiv \hat{\pi}_1 \quad \text{for $v \leq m$} \\
+     \bar{X}_{v}(t) \equiv \hat{\pi}_0 \quad \text{for $v > m$} 
    \end{gather*}
@@
 \end{definition}
+The first approximation yields a sequence of independent random graphs
+with independent edges. For $t \leq t^{*} - 1$, $G(t)$ is an
+attributed instance of the Erd\"{o}s-Renyi random graphs. For $t \geq
+t^{*}$, $G(t)$ is an attributed instance of the kidney-egg model
+\cite{rukhin11} (see \figurename~\ref{fig:kidney-egg}), which in
+itself is a special instance of the mixed membership stochastic
+blockmodel \cite{airoldi08:_mixed}. The unattributed kidney-egg model
+can be denoted as $\kappa(n,m,p,q,s)$ with the quantities $p$, $q$,
+and $s$ representing
+\begin{gather*}
+p = \mathbb{P}(u \sim v \, | \, u \leq m, v \leq m) = \langle
+\hat{\pi}_1, \hat{\pi}_1 \rangle \\ q =
+\mathbb{P}(u \sim v \, | \, u \leq m, v > m) = \langle \hat{\pi}_1,
+\hat{\pi}_0 \rangle \\ s = \mathbb{P}(u
+\sim v \, | \, u > m, v > m) = \langle \hat{\pi}_0, \hat{\pi}_0
+\rangle . 
+\end{gather*}
+\begin{figure}[!tp]
+  \centering
+  \includegraphics[width=5cm]{graphics/Fig2-SSP2011.pdf}
+  \caption{An illustration of the kidney-egg model for $G(t^{*})$.}
+  \label{fig:kidney-egg}
+\end{figure}
  \begin{definition}
@@
     \mathbf{Z}_1 = (\mathbf{1}\mathbf{\pi}_1^{T} -
-     \mathbf{Q}_1)^{-1}(\mathbf{I} - \mathbf{1}\pi_1^{T})
+     \mathbf{Q}_1)^{-1}(\mathbf{I} - \mathbf{1}\pi_1^{T}).
   \end{gather}
   $\mathbf{Z}_0$ and $\mathbf{Z}_1$ are the fundamental matrices
-  for the continuous-time Markov chain on $\mathscr{K}_{+}$ with intensity
+  for the continuous-time Markov chain on $[K+1]$ with intensity
   matrix $\mathbf{Q}_0$ and $\mathbf{Q}_1$ (see
-  e.g., \cite[p. 55]{asmussen03:_applied_probab_queues}). Let
+  e.g. \cite[p. 55]{asmussen03:_applied_probab_queues}). Let
   $\Sigma_0$ and $\Sigma_1$ be given by
@@
     \mathbf{Z}_1^{T}
-    \mathrm{diag}(\pi_1)
+    \mathrm{diag}(\pi_1).
   \end{gather*}
@@
   \begin{enumerate}
-  \item For each $t$ and each $i \in [n]$, $\widehat{X}_i(t)$ is a
+  \item For each $t$ and each $v \in [n]$, $\widehat{X}_v(t)$ is a
     random vector obtained by truncating a multivariate normal random
-    vector $Z_{i}(t)$ to $\mathscr{S}$ with mean and covariance
+    vector $Z_{v}(t)$ to $\mathscr{S}$ with mean and covariance
     matrices given below.
-  \item For $t < t^{*}$,
+  \item For $t < t^{*} - 1$,
     \begin{gather}
-      \mathbb{E}[Z_i(t)] \equiv \hat{\pi}_0 \\
-      \mathrm{Var}[Z_i(t)] \equiv \widehat{\Sigma}_0
+      \mathbb{E}[Z_v(t)] \equiv \hat{\pi}_0 \\
+      \mathrm{Var}[Z_v(t)] \equiv \widehat{\Sigma}_0.
     \end{gather}
-  \item For $t \geq t^{*}$,  
+  \item For $t \geq t^{*} - 1$,  
     \begin{gather*}
-      \mathbb{E}[Z_i(t)] \equiv \hat{\pi}_0, \quad \text{for $i \leq
+      \mathbb{E}[Z_v(t)] \equiv \hat{\pi}_0, \quad \text{for $v \leq
         m$}  \\
-      \mathbb{E}[Z_i(t)] \equiv \hat{\pi}_1, \quad \text{for $i > 
+      \mathbb{E}[Z_v(t)] \equiv \hat{\pi}_1, \quad \text{for $v > 
         m$}  \\
-      \mathrm{Var}[Z_i(t)] \equiv \widehat{\Sigma}_{0} \quad \text{for $i
+      \mathrm{Var}[Z_i(t)] \equiv \widehat{\Sigma}_{0} \quad \text{for $v
         \leq m$} \\
-      \mathrm{Var}[Z_i(t)] \equiv \widehat{\Sigma}_{1} \quad \text{for $i
+      \mathrm{Var}[Z_i(t)] \equiv \widehat{\Sigma}_{1} \quad \text{for $v
         > m$}
@@
     \times K$ matrices
-    obtained by removing the last row and column of $\Sigma_0^{(r)}$ and
-    $\Sigma_1^{(r)}$, respectively. 
+    obtained by removing the last row and column of $\Sigma_0$ and
+    $\Sigma_1$, respectively. 
   \end{enumerate}
 \end{definition}
+A second-order approximation yields a sequence of independent latent
+position graphs \cite{marchette08:_predic,scheinerman10:_model,hoff02:_laten}.
+
 Suppose that we have a sequence $\{\mathscr{V}^{r} \colon r > 0 \}$ of
-rdpm with vertices $[n]$ and attributes $\mathscr{K}$ where for each
-$r > 0$, $\mathscr{V}^{r}$ has change parameters $(t^{*}, m, \pi_0,
-\pi_1, r \mathbf{Q}_0, r \mathbf{Q}_1)$. The parameter $r$ can be
-thought of as the vertex process rate, i.e., the waiting time
-decreases exponentially as $r$ increases. Let us now consider the
-sequence of first approximation $\bar{\mathscr{V}}^{r}$ and second
-approximations $\widehat{\mathscr{V}}^{r}$ of $\mathscr{V}$. We note
-that $\bar{\mathscr{V}}^{r_1} = \bar{\mathscr{V}}^{r_2}$ for any $r_1,
-r_2 > 0$. Let us then denote by $\bar{\mathscr{V}}$ the (a.e.) unique
+rdpm with vertices $[n]$ and attributes $[K]$ where for each $r > 0$,
+$\mathscr{V}^{r}$ has change parameters $(t^{*}, m, \pi_0, \pi_1, r
+\mathbf{Q}_0, r \mathbf{Q}_1)$. The parameter $r$ can be thought of as
+the vertex process rate, i.e., the waiting time decreases
+exponentially as $r$ increases. Let us now consider the sequence of
+first approximations $\bar{\mathscr{V}}^{r}$ and second approximations
+$\widehat{\mathscr{V}}^{r}$ of $\mathscr{V}^{r}$. We note that
+$\bar{\mathscr{V}}^{r_1} = \bar{\mathscr{V}}^{r_2}$ for any $r_1, r_2
+> 0$. Let us then denote by $\bar{\mathscr{V}}$ the (a.e.) unique
 first order approximation of $\mathscr{V}^{r}$ for $r > 0$. If we
@@
 $\widehat{\Sigma}_{1}^{(r)} = \widehat{\Sigma}_1^{(1)}/r$. Therefore,
-as $r \rightarrow \infty$, $\widehat{\Sigma}_0^{(r)} \rightarrow 0$
-and $\widehat{\Sigma}_1^{(r)} \rightarrow 0$ and so
-$\widehat{\mathscr{V}}^{r} \rightsquigarrow
+as $r \rightarrow \infty$, $\widehat{\Sigma}_0^{(r)} \rightarrow
+\bm{0}$ and $\widehat{\Sigma}_1^{(r)} \rightarrow \bm{0}$ and so
+$\widehat{\mathscr{V}}^{r} \overset{\mathrm{d}}{\longrightarrow}
 \bar{\mathscr{V}}$. This indicates that for sufficiently large $r$,
-there is little statistical difference amongst the $\bar{\mathscr{V}}$,
-$\mathscr{V}^{r}$ and $\widehat{\mathscr{V}}$ (\cite[Theorem
-2]{lee:_laten_proces_model_time_attrib_random_graph}). $\bar{\mathscr{V}}$
-will thus serve as the basis for our subsequent analysis on graph
-invariants for attributed random graphs. 
-\section{Change-point detection}
-Let $\mathscr{V}$ be a random dot process model with change parameters
-$(t^{*}, m, \pi_0, \pi_1, \mathbf{Q}_0, \mathbf{Q}_1)$. The
-change-parameters encapsulate a notion of chatter anomalies, i.e., a
-subset of vertices of $\mathscr{V}$ with altered communication
-behaviour in an otherwise stationary setting as depicted in
-Fig.~\ref{fig:notional_change_point}.
+there is little statistical difference amongst the
+$\bar{\mathscr{V}}$, $\mathscr{V}^{r}$ and $\widehat{\mathscr{V}}^{r}$
+(\cite[Theorem 2]{lee11}). The behavior of
+$\widehat{\mathscr{V}}^{r}$ for ``small'' $r$ is less
+clear. $\bar{\mathscr{V}}$ will thus serve as the basis for our
+subsequent analysis on graph invariants for attributed random graphs.
+\subsection{Change-point detection}
 \begin{figure}[htbp]
@@
 \end{figure}
-\\ \noindent
-We are interested in
-the problem of testing, for a $t \in \mathbb{N}$, the hypotheses that
-$t$ is the change-point of $\mathscr{V}$, namely
+Let $\mathscr{V}$ be a random dot process model with change parameters
+$(t^{*}, m, \pi_0, \pi_1, \mathbf{Q}_0, \mathbf{Q}_1)$. The
+change-parameters encapsulate a notion of chatter anomalies, i.e., a
+subset of vertices of $\mathscr{V}$ with altered communication
+behavior in an otherwise stationary setting as depicted in
+Fig.~\ref{fig:notional_change_point}. We are interested in the problem
+of testing, for a $t \in \mathbb{N}$, the hypotheses that $t$ is the
+change-point of $\mathscr{V}$, namely
 \begin{gather*}
@@
 \end{gather*}
-%\subsection{Graphs Invariants}
-%In this paper we consider the problem of detecting chatter anomalies
 This will be done using the notion of fusion of attributed graph
 invariants. The particular invariants of interests are the size
-$\mathcal{E}$, number of triangles $\tau$, scan $\Psi$, and
-max degree $\Delta$. Let $G = (V,E,\phi)$ be an attributed graph with 
-$\phi \colon \tbinom{V}{2} \mapsto \mathscr{K}_{+}$. For a given
-$\{u,v\} \in \tbinom{V}{2}$, we define a $\Gamma_{uv} \in
-\mathbb{R}^{K+1}$ by $\Gamma_{uv}(k) = \mathbb{I}\{\phi(\{u,v\}) =
-k\}$. Let $\widehat{\Gamma}_{uv}$ be the first $K$ coordinates of
-$\Gamma_{uv}$. Thus $\widehat{\Gamma}_{uv} = \bm{0}$ unless $\{u,v\}
-\in E$. Under the independent edges assumption, the
-$\Gamma_{uv}$ are independent, and hence the $\widehat{\Gamma}_{uv}$
-are also independent. We can consider linear attribute fusion of graph invariants with
-parameter $\lambda \in \mathbb{R}^{K}$ via
+$\mathcal{E}$, number of triangles $\tau$, scan $\Psi$, and max degree
+$\Delta$. The scan statistics $\Psi$ are introduced and applied to the
+problem of detecting chatter anomalies in
+\cite{priebe05:_scan_statis_enron_graph}. The use of various graph
+invariants as test statistics was considered in
+\cite{pao11:_statis_infer_random_graph} and it was shown there, via
+Monte Carlo analysis, that no single invariant is uniformly most
+powerful.
+
+Let $(G,\phi)$ be an attributed graph. For a given $\{u,v\}
+\in \tbinom{V}{2}$, we define a $\Gamma_{uv} \in \mathbb{R}^{K}$ by
+$\Gamma_{uv}(k) = \mathbb{I}\{\phi(\{u,v\}) = k\}$. Thus $\Gamma_{uv}
+= \bm{0}$ unless $\{u,v\} \in E$. Under the independent edges
+assumption, the $\Gamma_{uv}$ are independent. We consider linear
+attribute fusion of graph invariants with parameter $\lambda \in
+\mathbb{R}^{K}$ via
 %\begin{gather}
@@
       \tbinom{V}{2}}} \langle
-  \lambda, \widehat{\Gamma}_{uv} \rangle \\
+  \lambda, \Gamma_{uv} \rangle \\
   \tau_{\lambda}(G) &= \sum_{\mathclap{\{u,v,w\} \in \tbinom{V}{3}}} \langle
-  \lambda, \widehat{\Gamma}_{uv} \rangle \langle \lambda,
-  \widehat{\Gamma}_{uw} \rangle \langle \lambda, \widehat{\Gamma}_{vw}
+  \lambda, \Gamma_{uv} \rangle \langle \lambda,
+  \Gamma_{uw} \rangle \langle \lambda, \Gamma_{vw}
   \rangle \\ 
 \Delta_{\lambda}(G) &= \max_{v \in V} \, \sum_{w \in N(v)} \langle
-\lambda, \widehat{\Gamma}_{vw} \rangle \\
+\lambda, \Gamma_{vw} \rangle \\
 \label{eq:3}
-  \Psi_{\lambda}(G) &= \max_{v \in V} \sum_{u,w \in N(v)} \langle
-  \lambda, \widehat{\Gamma}_{uw} \rangle
+  \Psi_{\lambda}(G) &= \max_{v \in V} \sum_{u,w \in N[v]} \langle
+  \lambda, \Gamma_{uw} \rangle.
   \end{align}
+  where $N(v) = \{u \colon u \sim v\}$ is the set of neighbors of
+  $v$ and $N[v] = v \cup N(v)$.
+
   Let $\{G(t)\}$ be a time series of graphs. Let $J_{\lambda}(t)$ be a
   statistic for $G(t)$ of the form as in Eq.~\eqref{eq:6} through
-  Eq.~\eqref{eq:3}. We define the normalization
-  $\bar{J}^{l}_\lambda(t)$ of $J_{\lambda}$ based on recent past as
+  Eq.~\eqref{eq:3}. We define the running average 
+  $\bar{J}^{l}_\lambda(t)$ of $J_{\lambda}$ as
 \begin{equation}
@@
 where $l \in \mathbb{N}$ specified the width of the running-average
-window. Our main interests is in the normalized fusion
-statistic $T_{\lambda}^{l}(t)$ as depicted in Fig.~\ref{fig:temporal}, namely
+window. Our main interest is in the normalized fusion statistic
+$T_{\lambda}^{l}(t)$ as depicted in Fig.~\ref{fig:temporal}, namely
 \begin{equation}
@@
 \end{equation}
-for $l \geq 2$. As we have mentioned earlier, we will use the first
-approximation $\bar{\mathscr{V}}$ of $\mathscr{V}$ in our study of the 
-asymptotic theory for these graphs invariants.   
+for $l \geq 2$, i.e., we want to find a parameter $\lambda$ such that
+the power of the test using $T_{\lambda}^{l}$ is maximum. We note that
+$T_{\lambda}^{l}$ is scale invariant in $\lambda$ for all of our graph
+invariants. It was noted in \cite{lee11} that the maximum of the power
+for scale invariant tests is attainable in $\{ \lambda \colon \|
+\lambda \| = 1 \}$. \\ \\
+
+As we have mentioned earlier, we will assume that the number of
+vertices $n$ is large and that the use of the first order
+approximation $\bar{\mathscr{V}}$ of $\mathscr{V}$ is appropriate in
+our study of the asymptotic theory for these graphs invariants. We
+strive to obtain approximations for the power in testing $t^{*} > t$
+against $t^{*} = t$ using $T_{\lambda}(t)$ and from these
+approximations, find the $\lambda$ that maximize the power. We now
+introduce additional notation that will be used later on in the
+paper. First, let $\pi_{00}, \pi_{01}$, and $\pi_{11}$ be
+sub-probability vectors whose components are given by
+\begin{gather*}
+  \pi_{00}(k) = \pi_{0}(k) \pi_{0}(k) \\
+  \pi_{01}(k) = \pi_{0}(k) \pi_{1}(k) \\
+  \pi_{11}(k) = \pi_{1}(k) \pi_{1}(k)
+\end{gather*}
+where $k \in [K]$. We also let $\eta_{00}, \eta_{01}$, and
+$\eta_{11}$ be matrices of size $K \times K$ defined by 
+\begin{gather*}
+  \eta_{00} = \mathrm{diag}(\pi_{00}) - \pi_{00} \pi_{00}^{T} \\
+  \eta_{01} = \mathrm{diag}(\pi_{01}) - \pi_{01} \pi_{01}^{T} \\
+  \eta_{11} = \mathrm{diag}(\pi_{11}) - \pi_{11} \pi_{11}^{T}.
+\end{gather*}
+% The structure of the remaining sections of the paper is as follows. We
+% discussed the power estimates for $\mathcal{E}_{\lambda},
+% \tau_{\lambda}, \Delta_{\lambda}$ and $\Psi_{\lambda}$ in
+% \S~\ref{sec:power-estim-mathc}
+%  through \S~\ref{sec:power-estim-psi_l}. We illustrate our analysis with some
+% simulation experiments in \S~\ref{sec:experimental-results}  
 \begin{figure}[htbp]
@@
 \end{figure}
+\section{Power estimates}
 \subsection{Power estimates for $\mathcal{E}_\lambda$}
-It was shown in
-\cite{lee:_laten_proces_model_time_attrib_random_graph} that if
-$J_\lambda(t) = \mathcal{E}_{\lambda}(G(t))$, then $T_{\lambda}^{l}(t)$ 
-follows a $t$-distribution with $l - 1$
-degrees of freedom in the limit. Specifically, we have the following
-results
+\label{sec:power-estim-mathc}
+It was shown in \cite{lee11} that if $J_\lambda(t) =
+\mathcal{E}_{\lambda}(G(t))$, then $T_{\lambda}^{l}(t)$ follows a
+$t$-distribution with $l - 1$ degrees of freedom in the
+limit. Specifically, we have the following results
 \begin{theorem}
@@
           \tbinom{m}{2}(\eta_{11} - \eta_{00}) + (n-m)m(\eta_{01} -
-          \eta_{00})
+          \eta_{00}).
   \end{gather*}
@@
             \lambda \rangle}} T_{\lambda}^{l}(t) & \text{if $t = t^{*}$} \\
-      \sqrt{\frac{l}{l + 1}} T_{\lambda}^{l}(t)& \text{if $t < t^{*}$}
+      \sqrt{\frac{l}{l + 1}} T_{\lambda}^{l}(t)& \text{if $t <
+        t^{*}$}.
       \end{cases}
@@
       \frac{\langle \lambda, \zeta \rangle}{\sqrt{\langle \lambda, \xi \lambda \rangle}} & \text{if $t = t^{*}$} \\
-      0 & \text{if $t < t^{*}$}
+      0 & \text{if $t < t^{*}$}.
     \end{cases}
@@
 power of the test. The power approximation is determined by various
-factors but the dominating factor is likely to be
-$\mu_{\lambda}$. The following corollary extends a result in
-\cite{lee:_laten_proces_model_time_attrib_random_graph} for $K = 2$ to the case
+factors but the dominating factor is $\mu_{\lambda}$ (for large $n$). 
+The following corollary extends a result in
+\cite{lee11} for $K = 2$ to the case
 where $K \geq 2$. 
@@
 random graphs was considered in
-\cite{nowicki88:_subgr_u_statis_method} for the Erd\"{o}s-Renyi 
-and in \cite{rukhin09:_asymp_analy_various_statis_random_graph_infer}
-for the kidney-egg model. We note here the small changes that allow us
-to extend the results in
+\cite{nowicki88:_subgr_u_statis_method} for the Erd\"{o}s-Renyi and in
+\cite{rukhin09:_asymp_analy_various_statis_random_graph_infer} for the
+kidney-egg model. We note here the small changes that allow us to
+extend the results in
 \cite{rukhin09:_asymp_analy_various_statis_random_graph_infer,%
-nowicki88:_subgr_u_statis_method}
-to our attributed graphs model. Let $Y_{uv} = \langle \lambda,
-\widehat{\Gamma}_{uv} \rangle$ for $\{u,v\} \in \tbinom{V(t)}{2}$. We
-can now write $\tau_{\lambda}(G(t))$ as
+nowicki88:_subgr_u_statis_method} to our attributed graphs model. Let
+$Y_{uv} = \langle \lambda, \Gamma_{uv} \rangle$ for $\{u,v\} \in
+\tbinom{V}{2}$. We can now write $\tau_{\lambda}(G(t))$ as
 \begin{equation}
   \label{eq:45}
-  \begin{split}
-  \frac{\tau_{\lambda}(G(t))}{\tbinom{n}{3}} &= \tbinom{n}{3}^{-1}
-  \sum_{\mathclap{\{u,v,w\} \in \tbinom{V}{3}}} Y_{uv} Y_{uw} Y_{vw}
-  \\ &= \tbinom{n}{3}^{-1}
-  \sum_{\mathclap{\{e_1, e_2, e_3\} \in \tbinom{E(t)}{3}}} Y_{e_1}
-  Y_{e_2} Y_{e_3}
-  \end{split}
-\end{equation}
-$\tau_{\lambda}(G(t))/\tbinom{n}{3}$ is then an (incomplete)
+  \frac{\tau_{\lambda}(G(t))}{\tbinom{n}{3}} = \tbinom{n}{3}^{-1}
+  \sum_{\mathclap{\{u,v,w\} \in \tbinom{V}{3}}} Y_{uv} Y_{uw} Y_{vw};
+\end{equation}
+$\tau_{\lambda}(G(t))/\tbinom{n}{3}$ is then an
 $U$-statistic on $\{Y_{e}\}$, with kernel function $h(Y_{1}, Y_{2},
@@
   \label{eq:46}
-  \tau_{\lambda}^{*}(G(t)) = \sum_{e \in E(t)} \mathbb{E}[
-  \tau_{\lambda}(G(t)) \, \lvert \, Y_{e}]
+  \tau_{\lambda}^{*}(G) - \mathbb{E}[\tau_{\lambda}(G)] =
+  \sum_{\mathclap{\{u,v\} \in \tbinom{V}{2}}} \, \Bigl(\mathbb{E}[
+  \tau_{\lambda}(G) \, \lvert \, Y_{uv}] -
+  \mathbb{E}[\tau_{\lambda}(G)]\Bigr).
 \end{equation}
@@
 \begin{align*}
-  \mu_0 = \mathbb{E}[\tau_{\lambda}^{*}(G(t))] &= \tbinom{n}{3} \langle 
+  \mathbb{E}[\tau_{\lambda}^{*}(G(t))] &= \tbinom{n}{3} \langle 
   \lambda, \pi_{00} \rangle^{3} \\
-  \sigma_0 = \sqrt{\mathrm{Var}[\tau_{\lambda}^{*}(G(t))]} &= (n-2) \langle \lambda,
+  \sqrt{\mathrm{Var}[\tau_{\lambda}^{*}(G(t))]} &= (n-2) \langle \lambda,
   \pi_{00} \rangle^{2} \sqrt{\tbinom{n}{2} \langle \lambda, \eta_{00}
-  \lambda \rangle}
+  \lambda \rangle}.
 \end{align*}
@@
     \begin{split}
-    \mu_A = \mathbb{E}[\tau_{\lambda}^{*}(G(t))] = \tbinom{m}{3}
+    \mathbb{E}[\tau_{\lambda}^{*}(G(t))] = \tbinom{m}{3}
     \langle \lambda, \pi_{11} \rangle^{3} &+
@@
     \begin{split}
-    \sigma_A^{2} = \mathrm{Var}[\tau_{\lambda}^{*}(G(t))] = \tbinom{m}{2} \langle \lambda, \eta_{11} \lambda
-    \rangle S_1  
-    &+ m(n-m) \langle \lambda, \eta_{01} \lambda \rangle S_2  \\
-    &+ \tbinom{n-m}{2} \langle \lambda, \eta_{00} \lambda \rangle S_3
+    \mathrm{Var}[\tau_{\lambda}^{*}(G(t))] = \tbinom{m}{2} \langle \lambda, \eta_{11} \lambda
+    \rangle S_1^2  
+    &+ m(n-m) \langle \lambda, \eta_{01} \lambda \rangle S_2^2  \\
+    &+ \tbinom{n-m}{2} \langle \lambda, \eta_{00} \lambda \rangle
+    S_3^2
     \end{split}
@@
 \begin{align*}
-    S_1 &= \Bigl[(m-2) \langle \lambda, \pi_{11} \rangle^{2} + (n-m)
-    \langle \pi_{01} \rangle^{2} \Bigr]^{2} \\ 
-    S_2 &= \Bigl[(m-1)
+    S_1 &= (m-2) \langle \lambda, \pi_{11} \rangle^{2} + (n-m)
+    \langle \lambda, \pi_{01} \rangle^{2} \\ 
+    S_2 &= (m-1)
     \langle \lambda, \pi_{11} \rangle \langle \lambda, \pi_{01}
     \rangle + (n-m-1) \langle \lambda, \pi_{00} \rangle \langle
-    \lambda, \pi_{01} \rangle \Bigr]^{2} \\
-    S_3 &= \Bigl[m \langle \lambda, \pi_{01} \rangle^{2} + (n-m-2) \langle
-    \lambda, \pi_{00} \rangle^{2} \Bigr]^{2} 
+    \lambda, \pi_{01} \rangle \\
+    S_3 &= m \langle \lambda, \pi_{01} \rangle^{2} + (n-m-2) \langle
+    \lambda, \pi_{00} \rangle^{2}.
     \end{align*}
-  As $n \rightarrow \infty$ and $m = \Omega(\sqrt{n})$, we have
+  As $n \rightarrow \infty$, we have
   \begin{equation}
@@
       \mathbb{E}[\tau_{\lambda}^{*}(G(t))]}{\sqrt{\mathrm{Var}[\tau_{\lambda}^{*}(G(t))]}}
-      \rightsquigarrow \mathcal{N}(0,1)
+\overset{\mathrm{d}}{\longrightarrow}  \mathcal{N}(0,1).
   \end{equation}
@@
   Let $t \in \{l+1, \dots, t^{*}\}$ and $\lambda \in
-  \mathbb{R}^{K}$. Define the random varialbel $\psi_{\lambda}^{l}(t)$
-  by
+  \mathbb{R}^{K}$. Let $\mu_0 = \mathbb{E}[\tau_{\lambda}^{*}(G(t))]$
+  and $\sigma_0^{2} = \mathrm{Var}[\tau_{\lambda}^{*}(G(t))]$ for $t <
+  t^{*}$. Let $\mu_A = \mathbb{E}[\tau_{\lambda}^{*}(G(t^{*}))]$ and
+  $\sigma_{A}^{2} = \mathrm{Var}[\tau_{\lambda}^{*}(G(t^{*}))]$. Define
+  the random variable $\psi_{\lambda}^{l}(t)$ by
   \begin{equation}
@@
       \Bigl(\sqrt{\tfrac{l \sigma_0^{2}}{l \sigma_A^{2} + \sigma_0^{2}} }\,\Bigr)
-      T_{\lambda}^{l}(t) & \text{if $t = t^{*}$}
+      T_{\lambda}^{l}(t) & \text{if $t = t^{*}$}.
         \end{cases}
@@
       \frac{\mu_A - \mu_0}{\sqrt{l \sigma_A^{2} + \sigma_0^{2}}} &
-       \text{if $t = t^{*}$}
+       \text{if $t = t^{*}$}.
       \end{cases}
@@
 factors, but similar to the power approximation for
-$\mathcal{E}_{\lambda}$, the dominating factor is likely to be
-  $\mu_\lambda$. Thus, we are also interested in finding the $\lambda$
+$\mathcal{E}_{\lambda}$, the dominating factor is $\mu_\lambda$ (for
+large $n$). Thus, we are also interested in finding the $\lambda$
 that will maximize $\mu_\lambda$. However, because of the high power
-  of $\lambda$ in the expression for $\mu_{\lambda}$, an analytic
-  solution to $\argmax_{\lambda}{\mu_{\lambda}}$ might not be possible.
+of $\lambda$ in the expression for $\mu_{\lambda}$, an exact 
+solution to $\argmax_{\lambda}{\mu_{\lambda}}$ is more challenging for
+$\tau$ than for $\mathcal{E}$. 
 \subsection{Power estimates for $\Delta_{\lambda}(t)$}
-The analysis of the power estimates for $\Delta_{\lambda}(t)$ depends
-on some preliminary results which we now state. We denote by
-$\mathcal{G}(\alpha, \beta)$ the Gumbel distribution with location
-parameter $\alpha$ and scale parameter $\beta$.  
+\label{sec:power-estim-delt}
+The limiting distribution for maximum degree in unattributed random
+graphs was considered in \cite{bollobas85:_random_graph} for the
+Erd\"{o}s-Renyi and in \cite{rukhin11} for the kidney-egg model. We
+note here the necessary changes that allow us to to extend the results
+in \cite{bollobas85:_random_graph,rukhin11} to our attributed graphs
+model. We denote by $\mathcal{G}(\alpha,\beta)$ the Gumbel
+distribution with location parameter $\alpha$ and scale parameter
+$\beta$.
 \begin{proposition}
@@
     a_n &= (2 \log{n})^{1/2}\Bigl(1 - \frac{\log{\log{n}} + \log{4\pi}}{4 \log{n}} \Bigr) \\ 
-    b_n &= (2 \log{n})^{-1/2}
+    b_n &= (2 \log{n})^{-1/2}.
   \end{align*}
@@
   we have
-  \begin{equation}
+  \begin{gather}
     \label{eq:14}
-    \Delta_{\lambda}(t) \rightsquigarrow \begin{cases}
-      \mathcal{G}(a_n \sigma_0 + \mu_0, b_n \sigma_0 ) & \text{for $t < t^{*}$.} \\
-     \mathcal{G}(a_m \sigma_A + \mu_A, b_m \sigma_A) &
-     \text{for $t = t^{*}$.}
-     \end{cases}
-  \end{equation}
+    \frac{\Delta_{\lambda}(t) - a_{n} \sigma_0 - \mu_0}{b_n \sigma_0}
+   \overset{\mathrm{d}}{\longrightarrow}  \mathcal{G}(0,1) \quad \text{for $t < t^{*}$ } \\
+    \frac{\Delta_{\lambda}(t) - a_{m} \sigma_A - \mu_A}{b_m \sigma_A}
+       \overset{\mathrm{d}}{\longrightarrow}\mathcal{G}(0,1) \quad \text{for $t = t^{*}$ }
+  \end{gather}
   where
@@
     \\ \sigma_A &= \sqrt{ (m - 1) \langle \lambda, \eta_{11} \lambda \rangle + (n -
-      m) \langle \lambda, \eta_{01} \lambda \rangle}
+      m) \langle \lambda, \eta_{01} \lambda \rangle}.
     \end{align*}
 \end{proposition}
+$T_{\lambda}^{l}(t)$ based on the Gumbel distributed
+$\Delta_{\lambda}(t)$, in contrast to $T_{\lambda}^{l}(t)$ based on
+the normally distributed $\mathcal{E}_{\lambda}$ and
+$\tau_{\lambda}(t)$, does not have a simple distribution for small or
+moderate values of $l$. The following result give the limiting
+distribution for $T_{\lambda}^{l}(t)$ under the assumption that $l$ is
+sufficiently large. 
 \begin{theorem}
@@
       t^{*}$} \\
-    \frac{\sqrt{\pi}}{6} & \text{if $t < t^{*}$}
+    \frac{\sqrt{\pi}}{6} & \text{if $t < t^{*}$};
     \end{cases}
@@
 determined by various factors, but the dominating factor is
-be $\tfrac{\rho_\lambda}{\varsigma_\lambda}$. For sufficiently large $n$
+$\tfrac{\rho_\lambda}{\varsigma_\lambda}$. For sufficiently large $n$
 and $m$, we have for $t = t^{*}$,
@@
     (n-1) \pi_{00} \rangle}{b_m \sqrt{\langle \lambda, ((m-1) \eta_{11} +
-    (n-m)\eta_{01}) \lambda \rangle}}
+    (n-m)\eta_{01}) \lambda \rangle}}.
   \end{split}
@@
 \subsection{Power estimates for $\Psi_{\lambda}(t)$}
-The limiting distribution for the scan statistics for unattributed
+\label{sec:power-estim-psi_l}
+The limiting distribution for the scan statistics in unattributed
 random graphs was considered in
-\cite{rukhin:_limit_distr_graph_scan_statis}. This subsection is
-concerned with adapting the results in
-\cite{rukhin:_limit_distr_graph_scan_statis} to attributed random
-graphs. We state here only the relevant results. The proofs are
-relegated to the appendices. \\ \\
-\noindent
-The limiting distribution for $\Psi_{\lambda}(t)$ is Gumbel for both
-the cases when $t < t^{*}$ and $t = t^{*}$. To aid the exposition,
- we first introduce some notations. Let $z_n$ be defined, for $n \in \mathbb{N}$, by
+\cite{rukhin:_limit_distr_graph_scan_statis}. We note here the changes
+that allow us to extend the results in
+\cite{rukhin:_limit_distr_graph_scan_statis} to our attributed graphs
+model. Let $z_n$ be defined, for $n \in \mathbb{N}$, by
 \begin{equation}
@@
       \log{n}}\Bigl(1 - \frac{\log{\log{n}} + \log{4 \pi}}{4
-      \log{n}}\Bigr)
+      \log{n}}\Bigr).
 \end{equation}
@@
   E \sim \mathrm{Bin}(m-1, \langle 1, \pi_{11} \rangle) \\ F \sim \mathrm{Bin}(n-m,
-  \langle 1, \pi_{01} \rangle)
+  \langle 1, \pi_{01} \rangle).
 \end{gather*}%
 Let $E + F$ be the convolution of $E$ and $F$. Denote by $\mu_{E+F}$ and
-$\sigma_{E+F}^{2}$ the mean and variance of $E + F$. Finally, let
+$\sigma_{E+F}^{2}$ the mean and variance of $E + F$. Let
 $N_{\kappa} = \mu_{E + F} + z_m \sigma_{E + F}$. We then have the
 following results.
-%Let $\lambda^{(2)}$ be the
-% element-wise square of $\lambda$. Define $C_{00}$, $C_{01}$, $C_{11}$
-% and $p_{00}$, $p_{01}$, $p_{11}$ to be
-% \begin{gather}
-%   \label{eq:19}
-%   C_{00} = \tfrac{\langle \lambda^{(2)}, \pi_{00} \rangle}{\langle \lambda,
-%     \pi_{00}\rangle}; \quad p_{00} = \tfrac{(\langle \lambda, \pi_{00}
-%     \rangle)^{2}}{\langle \lambda^{(2)},\, \pi_{00} \rangle} \\
-% C_{11} = \tfrac{\langle \lambda^{(2)}, \pi_{11} \rangle}{\langle \lambda,
-%     \pi_{11}\rangle}; \quad p_{11} = \tfrac{(\langle \lambda, \pi_{11}
-%     \rangle)^{2}}{\langle \lambda^{(2)},\, \pi_{11} \rangle} \\
-% C_{10} = \tfrac{\langle \lambda^{(2)}, \pi_{11} \rangle}{\langle \lambda,
-%     \pi_{10}\rangle}; \quad p_{10} = \tfrac{(\langle \lambda, \pi_{10}
-%     \rangle)^{2}}{\langle \lambda^{(2)},\, \pi_{10} \rangle} 
-% \end{gather}
 \begin{lemma}
@@
    b_n &= \langle \lambda, \pi_{00} \rangle N_{0} \frac{\sigma_0}{\sqrt{2 \log
-     n}}
+     n}}.
 %   b_n &= (1 - \tfrac{C_{00}p_{00}}{2} + C_{00}p_{00} N_{0}) \frac{\sigma_0}{\sqrt{2 \log
@@
 \begin{equation}
-  \frac{\Psi_{\lambda}(t) - a_{n}}{b_n} \rightsquigarrow
-  \mathcal{G}(0, 1)
+  \frac{\Psi_{\lambda}(t) - a_{n}}{b_n}
+  \overset{\mathrm{d}}{\longrightarrow}  \mathcal{G}(0, 1).
 \end{equation}
@@
     b_{n,m} = \langle \lambda, \pi_{00} \rangle N_\kappa \frac{\sigma_{E + F}}{\sqrt{2
-        \log{m}}}
+        \log{m}}}.
     %b_{n,m} = (1 - \tfrac{C_{00} p_{00}}{2} + C_{00} p_{00}
@@
     \label{eq:29}
-    \frac{\Psi_{\lambda}(t^{*}) - a_{n,m}}{b_{n,m}}  \rightsquigarrow
-    \mathcal{G}(0,1)  \end{equation}
+    \frac{\Psi_{\lambda}(t^{*}) - a_{n,m}}{b_{n,m}}
+    \overset{\mathrm{d}}{\longrightarrow} \mathcal{G}(0,1).
+  \end{equation}
 \end{lemma}
+The next result is analogous to Theorem \ref{thm:8} and gives 
+the limiting distribution for
+$T_{\lambda}^{l}(t)$ based on $\Psi_{\lambda}$ for the case of large
+$l$.
 \begin{theorem}
   \label{thm:6}
-  Let $t \in \{l+1, \dots, t^{*}$ and $\lambda \in
+  Let $t \in \{l+1, \dots, t^{*}\} $ and $\lambda \in
   \mathbb{R}^{K}$. For sufficiently large $n$ and sufficiently large
@@
         \tfrac{\sqrt{\pi} b_{n,m}}{6 b_n} & \text{if $t = t^{*}$} \\
-        \tfrac{\sqrt{\pi}}{6} & \text{if $t < t^{*}$}
+        \tfrac{\sqrt{\pi}}{6} & \text{if $t < t^{*}$}.
       \end{cases}
@@
     \tbinom{N_0}{2} - \tbinom{\mu_E}{2} - \mu_E \mu_F\Bigr)\pi_{00} +
-    \tbinom{\mu_{E}}{2} \pi_{11} + \mu_E \mu_F \pi_{10}  
-\end{equation*}
-From Eq.~\eqref{eq:53}, we see that the $\lambda$ that maximimizes
-$\tfrac{\rho_\lambda}{\varsigma_{\lambda}}$ would be on the boundary,
+    \tbinom{\mu_{E}}{2} \pi_{11} + \mu_E \mu_F \pi_{10}.
+\end{equation*}
+From Eq.~\eqref{eq:53}, we see that there exists (as $n \rightarrow
+\infty$) a $\lambda$ that maximizes
+$\tfrac{\rho_\lambda}{\varsigma_{\lambda}}$ and is on the boundary,
 i.e., $\lambda(k) \not = 0$ for exactly one $k$. Therefore the asymptotic theory
 for scan statistics, in contrast with the other graph invariants that
-were considered, indicates that there are no benefits in fusing attributes.  
+were considered, indicates that there may be no benefits in fusing
+attributes. However, as \figurename~\ref{fig5:subfig_scan} shows, this
+phenomenon does not hold in general for moderate values of
+$n$. Similar observations about potential inaccuracies in using
+asymptotic results to predict finite but large samples behavior
+in testing using graph invariants were discussed in
+\cite{rukhin11,priebe10:_you_i}.   
+%\section{Experimental Results}
+%\label{sec:experimental-results}
+\section{Inference Example}
+We present here an inference example with the following
+parameters
+\begin{equation*}
+  K = 2, n = 100, m = 9, l = 10,
+\end{equation*}
+transition matrices
+\begin{equation*}
+  \label{eq:55}
+  \begin{matrix}
+  \mathbf{Q}_0 = \begin{bmatrix}
+    -\tfrac{2}{3} & \tfrac{1}{6} & \tfrac{1}{2} \\
+    1 & -1 & 0 \\
+    -1 & 0 & -1 
+  \end{bmatrix},
+  & \mathbf{Q}_1 = \begin{bmatrix}
+    -\tfrac{13}{7} & \tfrac{5}{7} & \tfrac{8}{7} \\
+    1 & -1 & 0 \\
+    1 & 0 & -1
+  \end{bmatrix}
+  \end{matrix}
+\end{equation*}
+and stationary probability vectors
+\begin{equation*}
+  \pi_0 = (0.10,0.30,0.60)^{T}, \quad \pi_1 = (0.25,0.40,0.35)^{T}
+\end{equation*}
+Power estimates for our attribute fusion statistics for this example
+are presented in \figurename~\ref{fig:power-scale} and
+\figurename~\ref{fig:power-estimate}. We consider the asymptotic,
+first approximation, second approximation, and exact model power
+estimates. \figurename~\ref{fig:power-scale} shows power as a function
+of the vertex process parameter $r$ at a specific point, namely at
+$\lambda^{*} = \argmax_{\lambda} \beta(\lambda)$.
+\figurename~\ref{fig:power-estimate} shows power as a function of
+angle $\theta$, where $\lambda = (cos(\theta), sin(\theta))$.
+
+The main implication that can
+be inferred from \figurename~\ref{fig:power-scale} and
+\figurename~\ref{fig:power-estimate}
+is that inferential performance in the
+mathematically tractable first-order and second-order approximation
+models does provide guidance for methodological choices applicable to
+the exact (realistic but intractable) model. Furthermore, to the
+extent that the exact model is realistic, we may tentatively conclude
+that approximation model investigations have some bearing on real
+data applications.
+\begin{figure*}[!t]
+  \centering
+  \subfloat[$\mathcal{E}_{\lambda}$]{
+    \includegraphics[width=7cm]{graphics/pwr-scale-size.pdf}
+  }
+  \hfil
+  \subfloat[$\Delta_{\lambda}$]{
+    \includegraphics[width=7cm]{graphics/pwr-scale-maxd.pdf}
+  }
+  \hfil
+  \subfloat[$\tau_{\lambda}$]{
+    \includegraphics[width=7cm]{graphics/pwr-scale-scan.pdf}
+  }
+  \hfil
+  \subfloat[$\Psi_{\lambda}$]{
+    \includegraphics[width=7cm]{graphics/pwr-scale-ntri.pdf}
+  }
+  \caption{Power $\beta(\theta^{*}_r,r)$ at $\theta_{r}^{*} =
+    \argmax_{\theta} \beta(\theta,r)$ as a function of $r$ for the
+    four invariants at test size $\alpha = 0.05$. The horizontal lines
+    represents first-order approximation $\pm$ three
+    standard deviations, and the two curves represent the second
+    approximation (green) and exact model (blue). The 10000 Monte
+    Carlo replicates yields standard deviations not exceeding $0.005$ for the power
+    estimates . The second approximation results match well with the exact model results, and
+    both match well for large $r$ with the first-order approximation results.
+  }
+  \label{fig:power-scale}
+\end{figure*}
+\begin{figure*}[!t]
+  \centering
+  \subfloat[$\mathcal{E}_{\lambda}$]{
+    \includegraphics[width=7cm]{graphics/pwr-size.pdf}
+  }
+  \hfil
+  \subfloat[$\Delta_{\lambda}$]{
+    \includegraphics[width=7cm]{graphics/pwr-maxd.pdf}
+  }
+  \hfil
+  \subfloat[$\Psi_{\lambda}$]{
+    \includegraphics[width=7cm]{graphics/pwr-scan.pdf}
+    \label{fig5:subfig_scan}
+  }
+  \hfil
+  \subfloat[$\tau_{\lambda}$]{
+    \includegraphics[width=7cm]{graphics/pwr-ntri.pdf}
+  }
+  \caption{Power $\beta$ as a function of angle $\theta$ for $\lambda
+    = (cos(\theta),sin(\theta))$. The plot shows analytic asymptotic
+    result (black), and first approximation (red), second
+    approximation (green), and exact model (blue) estimates for the
+    various invariants via Monte Carlo. The 10000 Monte Carlo
+    replicates yields standard deviations not exceeding $0.005$ for
+    the power estimates. The four vertical lines in each plot
+    correspond to $\theta \in \{0, \pi/2, \pi/4,
+    \theta^{*}\}$. Because we are considering a one-sided test and
+    because $\pi_{1,k} > \pi_{0,k}$ for both $k = 1$ and $k = 2$, the
+    power is maximized in the first quadrant, i.e., $\theta \in (0,
+    \pi/2)$. The second approximation results match well
+    with the exact model results, and both match well for large $r$
+    with the first order approximation and the asymptotic results. The
+    optimal $\theta^{*}$ is apparently different for the four different graph
+    invariants.  
+  }
+  \label{fig:power-estimate}
+  \end{figure*}
+\section{Conclusions}
+We have presented an analysis of change-point detection for time
+series of attributed graphs through the use of test statistics which
+are based on linear attribute fusion of some graph invariants. 
+We derived the limiting distribution of these test statistics under
+the assumptions that $n$, the number of vertices, is sufficiently
+large and $r$, the process parameter rate, is also sufficiently
+large. The limiting distribution for these test statistics are then
+used to derive estimates for the power of the tests.
+
+The experiment in \S \ref{eq:55} indicates that the power estimates are accurate, even
+for the moderate value of $n = 100$. Furthermore, it was also
+indicated that the optimal linear fusion parameter depends on the
+graph invariant considered. In particular, the results depicted in
+\figurename~\ref{fig:power-estimate} yield
+  $\theta^{*}_{\mathcal{E}_{\lambda}} \approx 0.24$,
+  $\theta^{*}_{\Delta_{\lambda}} \approx 0.32$,
+  $\theta^{*}_{\Psi_{\lambda}} \approx 0.14$ and
+  $\theta^{*}_{\tau_{\lambda}} \approx 0.38$. These optimal fusion
+  parameter differences are statistically significant, and combining
+  this result with the ``no uniformly most powerful invariant'' result
+  \cite{pao11:_statis_infer_random_graph}, we conclude that optimal
+  linear attribute fusion theory requires significant additional
+  development. Toward this end, the approximation models from
+  \cite{lee11} promise to
+  be of assistance.
+
+  Hypothesis testing on time series of attributed graphs has
+  applications in diverse areas, e.g., social network analysis
+  (wherein vertices represent individual actors or organizations), connectome
+  inference (wherein vertices are neurons or brain regions) and text
+  processing (wherein vertices represent authors or documents). These
+  and many other applications may benefit from generalizations of our
+  results and the
+  model in \cite{lee11} to
+  directed, multi, and weighted graphs, as well as the consideration
+  of inference with errorful edge attributes through an attribute
+  confusion matrix.
   \appendices
@@
 \label{sec:proofs-some-stated}
-\begin{IEEEproof}[Corollary\ref{cor:1}]
+\begin{IEEEproof}[Corollary~\ref{cor:1}]
   The maximizer of $\mu_\lambda$ also maximizes
@@
   \end{equation*}
-  Because $\xi$ is positive definite, there exist a positive definite matrix
+  Because $\xi$ is positive definite, there exists a positive definite matrix
   $\xi^{1/2}$ such that $\xi^{1/2} \xi^{1/2} = \xi$. Letting $\nu = \xi^{1/2}
@@
   The claim then follows directly from the Rayleigh-Ritz theorem for
-  Hermitean matrices.
+  Hermitian matrices.
 \end{IEEEproof}
 \begin{IEEEproof}[Lemma~\ref{lem:3}]
+  $\tau_{\lambda}(G)$ is a U-statistics with kernel function
+  $h(Y_1, Y_2, Y_3) = Y_1 Y_2 Y_3$. By the theory of U-statistics, we
+  know that
+  \begin{equation}
+    \label{eq:48}
+    \frac{\tau_{\lambda}(G) -
+      \mathbb{E}[\tau_{\lambda}^{*}(G)]}{\sqrt{\mathrm{Var}[\tau_{\lambda}^{*}(G)]}}
+       \overset{\mathrm{d}}{\longrightarrow}  N(0,1)
+  \end{equation}
+  provided that $\mathrm{Var}[\tau_{\lambda}(G) -
+  \tau_{\lambda}^{*}(G)] = o(\mathrm{Var}[\tau_{\lambda}^{*}(G)])$.
+
+  By the independent edge assumption, we have
+  \begin{align}
+    \mathbb{E}[h(Y_i, Y_j, Y_k) &= \mathbb{E}[Y_i]
+  \mathbb{E}[Y_j] \mathbb{E}[Y_k] \\ 
+  \mathbb{E}[h(Y_i, Y_j, Y_k) |
+  Y_i] &= Y_i \mathbb{E}[Y_j] \mathbb{E}[Y_k].
+  \end{align}
+ Thus, for $t < t^{*}$, we have $\mathbb{E}[\tau_{\lambda}^{*}(G(t))] = \tbinom{n}{3} \langle
+  \lambda, \pi_{00} \rangle^{3}$ and
+  \begin{equation}
+    \begin{split}
+      \mathrm{Var}[\tau_{\lambda}^{*}(G(t))] &=
+      \mathrm{Var}\Bigl[\sum_{\{u,v,w\}} Y_{uv} \mathbb{E}[Y_{uw}]
+      \mathbb{E}[Y_{vw}]\Bigr] \\
+      &= (n-2)^{2} \langle \lambda, \pi_{00} \rangle^{4}
+      \mathrm{Var}\Bigl[\sum_{\{u,v\}} Y_{uv} \Bigr] \\
+      &= (n-2)^{2} \langle \lambda, \pi_{00} \rangle^{4} \tbinom{n}{2}
+      \langle \lambda, \eta_{00} \lambda \rangle.
+    \end{split}
+  \end{equation}
+  We now sketch the derivation of
+  $\mathrm{Var}[\tau_{\lambda}^{*}(G(t))]$ for $t = t^{*}$. We partition the set
+  $\{u,v\} \in \tbinom{V}{2}$ into the sets 
+\begin{gather*}
+\mathcal{S}_1 = \{ u,v \in [m]
+  \}, \\ \mathcal{S}_2 = \{ u \in [m], v \in [n] \setminus [m]\}, \\
+  \mathcal{S}_3 = \{ u, v \in [n] \setminus[m]\}.
+\end{gather*} Now, for $\{u,v\} \in \mathcal{S}_1$, we have
+\begin{equation}
+  \label{eq:58}
+  \begin{split}
+S_1 Y_{uv} &=\sum_{w \not = u,v} \mathbb{E}[h(Y_{uv}, Y_{uw}, Y_{vw})
+\, | \, Y_{uv}] \\
+ &= ((m-2) \langle \lambda, \pi_{11} \rangle^{2} + (n-m)
+    \langle \lambda, \pi_{10} \rangle^{2})Y_{uv}.
+  \end{split}
+\end{equation}
+The above expression is reasoned as follows. If $w \in [m]$, then
+$\mathbb{E}[Y_{uw}] = \mathbb{E}[Y_{vw}] = \langle \lambda,
+\pi_{11} \rangle$ and there are $m-2$ possible choices for $w \in [m]$
+different from $u$ and $v$. If $w \in [n] \setminus [m]$, then
+$\mathbb{E}[Y_{vw}] = \mathbb{E}[Y_{uw}] = \langle \lambda, \pi_{10}
+\rangle$ and there are $n - m$ possible choices for $w$. Analogous
+reasoning gives the expressions for $S_2$ and $S_3$ in the statement
+of the lemma. % We also have
+% \begin{equation}
+%   \label{eq:56}
+%   \mathrm{Var}[Y_{uv}] = \begin{cases}
+%     \langle \lambda, \eta_{00} \lambda \rangle & \text{if $\{u,v\} \in
+%       \mathcal{S}_1$} \\
+%     \langle \lambda, \eta_{01} \lambda \rangle & \text{if $\{u,v\} \in
+%       \mathcal{S}_2$} \\
+%     \langle \lambda, \eta_{11} \lambda \rangle & \text{if $\{u,v\} \in
+%       \mathcal{S}_3$} \\
+%     \end{cases}.
+% \end{equation}
+
+We therefore have
+\begin{equation*}
+%  \label{eq:60}
+  \begin{split}
+  \mathrm{Var}[\tau_{\lambda}^{*}(G(t))] &= %\mathrm{Var}\Bigl[\sum_{\{u,v,w\}} Y_{uv} \mathbb{E}[Y_{uw}]
+      % \mathbb{E}[Y_{vw}]\Bigr] \\ &=
+      S_1^{2} \mathrm{Var}[\sum_{\{u,v\} \in \mathcal{S}_1} Y_{uv}] +
+      S_2^{2}
+      \mathrm{Var}[\sum_{\{u,v\} \in \mathcal{S}_2} Y_{uv}] \\ &+
+      S_3^{2}
+      \mathrm{Var}[\sum_{\{u,v\} \in \mathcal{S}_3} Y_{uv}]  \\ &=
+       \tbinom{m}{2} \langle \lambda, \eta_{00} \lambda \rangle S_1^{2} +
+       m(n-m) \langle \lambda, \eta_{01} \lambda \rangle S_2^{2} \\ &+
+       \tbinom{n-m}{2} \langle \lambda, \eta_{00} \lambda \rangle S_3^{2}
+  \end{split}
+\end{equation*}
+as desired. To complete the proof one must show that
+$\mathrm{Var}[\tau_{\lambda}(G) - \tau_{\lambda}^{*}(G)] =
+o(\mathrm{Var}[\tau_{\lambda}^{*}(G)])$ and this follows directly from
+the argument in \cite{nowicki88:_subgr_u_statis_method}
+or \cite{rukhin09:_asymp_analy_various_statis_random_graph_infer}.
 \end{IEEEproof}
@@
     d_{\lambda}(v;t) = \sum_{w \in N(v)} \langle \lambda,
-    \widehat{\Gamma}_{vw} \rangle
-  \end{equation*}
-  For $t < t^{*}$, each of the $\widehat{\Gamma}_{vw}$ is a multinomial
+    \Gamma_{vw} \rangle.
+  \end{equation*}
+  For $t < t^{*}$, each of the $\Gamma_{vw}$ is a multinomial
   trial with probability vector $\pi_{00}$. The following statements are
@@
       \rangle}{\sqrt{(n-1) \langle \lambda, \eta_{00} \lambda \rangle}}
-      \rightsquigarrow \mathcal{N}(0, 1)
+    \overset{\mathrm{d}}{\longrightarrow} \mathcal{N}(0, 1).
   \end{equation}
@@
   among the $\{d_{\lambda}(v;t)\}_{v \in V(t)}$ can be
-    ignored. $d_{\lambda}(v;t)$, can thus be considered as a sequence
+  ignored. Another way of doing this is to note that the covariance
+  between $X_u$ and $X_v$, where $X_u$ and $X_v$ are the ratio in
+  Eq.~\eqref{eq:17} for vertices $u$ and $v$, is given by
+  \begin{equation}
+    \label{eq:63}
+    r = \mathrm{Cov}(X_u,X_v) = 
+    \frac{3 \langle \lambda, \pi_{00} \rangle}{\sqrt{(n-1)
+        \langle \lambda, \eta_{00} \lambda \rangle}}.
+  \end{equation}
+  Because $r \log{n} \rightarrow 0$ as $n \rightarrow \infty$, the
+  sample maximum of the $X_u$ converges to the sample maximum of a
+  sequence of {\em independent} $\mathcal{N}(0,1)$ random variables.
+  $d_{\lambda}(v;t)$, can thus be considered as a sequence
   of independent random variables from a normal distribution. It is
-    widely known that the sample maximum of standard normal random
+  well known that the sample maximum of standard normal random
   variables converges weakly to a Gumbel distribution \cite[\S
@@
     \rightarrow 
-      e^{-e^{-x}} 
+    e^{-e^{-x}}. 
   \end{equation}
@@
       &= (\Phi(u_n))^{n} + O(\tfrac{u_n^{5}}{n^{1/2 - \delta}}) \\
-      & \rightarrow e^{-e^{-x}} 
+      & \rightarrow e^{-e^{-x}}. 
     \end{split}
@@
   $\Delta_{\lambda}(t)$ for $t < t^{*}$ in Eq.~\eqref{eq:14}.
-    % Now $n(1 - \Phi(u_n)) = \exp(-x)(1 + o(u_n^{-1 + \theta}))$ for
-    % some small $\theta > 0$. We thus have
-    % \begin{equation}
-    %   \label{eq:26}
-    %   \begin{split}
-    %   \mathbb{P}(\max_{v \in [n]} \zeta(v) \leq u_n) &= \Bigl[ \Phi(u_n) - C
-    %   u_n^{3}n^{-3/2} e^{-x}(1 + o(u_n^{-1 + \theta})) + O(u_n^{4}/n)
-    %   n^{-1} e^{-x} \Bigr]^{n} \\
-    %   &= (\Phi(u_n))^{n}\Bigl[1 - C u_n^{3}n^{-1/2} e^{-x}(n \Phi(u_n))^{-1} +
-    %   o(u_n^{-4 + \theta})n^{-2} e^{-x}\Bigr]^{n} \\
-    %   &= (\Phi(u_n))^{n} - C u_n^{3}n^{-1/2} e^{-x} (\Phi(u_n))^{n-1} +
-    %   o(u_n^{-4 + \theta}n^{-1/2}) e^{-x} \\
-    %   &= (1 + o(1)) \Phi(u_n)^{n}
-    %   \end{split}
-    % \end{equation}
-    % where the term $o(1)$ can be made to be independent of
-    % $x$. Furthermore, we can verify that $\Phi(u_n)^{n} \rightarrow
-    % e^{e^{-x}}$ and thus Eq.~\eqref{eq:22} is established. 
- % Let us define
- %  $\xi_s$ for $s \in \mathbb{R}$ as the number of vertices $v$ such
- %  that $\tfrac{d_\lambda(v;t) - (n-1) \langle \lambda, \pi_{00}
- %    \rangle}{\sqrt{(n-1) \langle \lambda, \eta_{00} \lambda \rangle}}
- %  \geq s$. Note that $\xi_s \leq k$ only if there are at most $k$
- %  vertices with $\tfrac{d_{\lambda}(v;t) - (n-1) \langle \lambda,
- %    \pi_{00} \rangle}{\sqrt{(n-1) \langle \lambda, \eta_{00} \lambda
- %      \rangle}} \geq s$. Thus, $\tfrac{\Delta_{\lambda}(v;t) - (n-1)
- %    \langle \lambda, \pi_{00} \rangle}{\sqrt{(n-1) \langle \lambda,
- %      \eta_{00} \lambda \rangle}} < s$ only if $\xi_s = 0$. Because
- %  the sample maximum of Gaussian random variables converges weakly to
- %  a Gumbel \cite[\S 2.3]{galambos87:_asymp_theor_extrem_order_statis},
- %  by taking $n \rightarrow \infty$ followed by $s \rightarrow \infty$,
- %  we can show that $\tfrac{\Delta_{\lambda}(v;t) - (n-1) \langle \lambda,
- %  \pi_{00} \rangle}{\sqrt{(n-1) \langle \lambda, \eta_{00} \lambda
- %    \rangle}} \rightsquigarrow \mathcal{G}(a_n, b_n)$. 
+
   The case when $t = t^{*}$ can be
   derive in a similar manner. We first show that if $m =
-\Omega(\sqrt{n \log{n}})$, then $\Delta_{\lambda}(v;t^{*}) \rightsquigarrow
-\max_{v \in [m]}{d_{\lambda}(v;t^{*})}$ \cite[Lemma
+  \Omega(\sqrt{n \log{n}})$, then $\Delta_{\lambda}(v;t^{*})
+  \overset{\mathrm{d}}{\longrightarrow} \max_{v \in [m]}{d_{\lambda}(v;t^{*})}$ \cite[Lemma
   3.1]{rukhin:_limit_distr_graph_scan_statis}.  
@@
   central limit theorem that for $v \in [m]$, $\tfrac{d_{\lambda}(v;t^{*}) -
-  \mu_2}{\sigma_2} \rightsquigarrow N(0,1)$. It then follows, similar
+    \mu_2}{\sigma_2} \overset{\mathrm{d}}{\longrightarrow} N(0,1)$. It then follows, similar
   to our previous reasoning for the case where $t < t^{*}$, that
   $\max_{v \in [m]} \tfrac{d_{\lambda}(v;t^{*}) -
-  \mu_2}{\sigma_2} \rightsquigarrow \mathcal{G}(a_m,b_m)$ and we obtain
+    \mu_2}{\sigma_2} \overset{\mathrm{d}}{\longrightarrow}\mathcal{G}(a_m,b_m)$ and we obtain
   Eq.~\eqref{eq:14} for $t = t^{*}$.  
@@
     = e^{-e^{-(z \sigma + \mu - \alpha)/\beta}} \\
-      &= e^{- e^{-(z - (\alpha - \mu)/\sigma)/(\beta/\sigma)}}
+      &= e^{- e^{-(z - (\alpha - \mu)/\sigma)/(\beta/\sigma)}}.
     \end{split}
@@
       \in N(v) \\ u,w \not = v}} \langle \lambda,
-  \widehat{\Gamma}_{uw} \rangle
+  \Gamma_{uw} \rangle.
 \end{equation}
@@
   (z_1,z_2,\dots,z_K) \sim \textrm{multinomial}\Bigl(
-  \tbinom{l}{2}, \pi_{00}\Bigr) 
+  \tbinom{l}{2}, \pi_{00}\Bigr). 
 \end{gather*}
@@
     \rangle}{\sqrt{\tbinom{l}{2} \langle \lambda, \eta_{00} \lambda \rangle}}
- \rightsquigarrow \mathcal{N}(0,1) 
+  \overset{\mathrm{d}}{\longrightarrow} \mathcal{N}(0,1).
 \end{equation*}
@@
     \rangle}{\sqrt{\tbinom{l}{2} \langle \lambda, \eta_{00} \lambda
-      \rangle}} \rightsquigarrow \frac{Y_l - \tbinom{l}{2} \langle \lambda, \pi_{00} \rangle}{\sqrt{\tbinom{l}{2}
-    \langle \lambda, \eta_{00} \lambda \rangle}}
+      \rangle}}   \overset{\mathrm{d}}{\longrightarrow} \frac{Y_l - \tbinom{l}{2} \langle \lambda, \pi_{00} \rangle}{\sqrt{\tbinom{l}{2}
+    \langle \lambda, \eta_{00} \lambda \rangle}}.
 \end{equation}
@@
 (y^{(\omega)}_1,\dots,y^{(\omega)}_m) \sim \textrm{multinomial}\Bigl(
-l_\zeta l_\xi, \pi_{10}\Bigr)
+l_\zeta l_\xi, \pi_{10}\Bigr).
 \end{gather*}
@@
   \varsigma = \langle \lambda, \Bigl(\tbinom{l_{\zeta}}{2} \eta_{11} +
-  \tbinom{l_{\xi}}{2} \eta_{00} + l_{\zeta} l_{\xi} \eta_{10}\Bigr) \lambda
+  \tbinom{l_{\xi}}{2} \eta_{00} + l_{\zeta} l_{\xi} \eta_{10}\Bigr)
+  \lambda.
   \rangle
@@
   \label{eq:16}
-  \frac{\phi_{\lambda}(v) - \rho}{\varsigma} \rightsquigarrow
-  \mathcal{N}(0,1)
+  \frac{\phi_{\lambda}(v) - \rho}{\varsigma}  \overset{\mathrm{d}}{\longrightarrow}  \mathcal{N}(0,1)
 \end{equation}
@@
   \label{eq:21}
- \frac{\phi_{\lambda}(v) - \rho}{\varsigma} \rightsquigarrow
- \frac{Y - \rho}{\varsigma}
+ \frac{\phi_{\lambda}(v) - \rho}{\varsigma}
+ \overset{\mathrm{d}}{\longrightarrow}  \frac{Y - \rho}{\varsigma}.
 \end{equation}
@@
     \limsup\,\, \mathbb{P}( \Upsilon(G) \geq a_{n,m} ) \leq \lim
-   \mathbb{P}( \Delta(G) \geq N_\kappa) \\
+   \mathbb{P}( \Delta(G) \geq N_\kappa), \\
    \label{eq:30}
   \liminf\,\, \mathbb{P}( \Upsilon(G) \geq a_{n,m} ) \geq \lim \mathbb{P}(
-  \Delta(G) \geq N_{\kappa})
+  \Delta(G) \geq N_{\kappa}).
 \end{gather}
@@
 \Upsilon(G) \geq a_{n,m} \Rightarrow C^{*} \tbinom{D(v)}{2} \geq
-a_{n,m} \Rightarrow D(v) \geq d_{n,m} 
+a_{n,m} \Rightarrow D(v) \geq d_{n,m}.
 \end{equation*}
@@
   h(v) = C_{00}p_{00} \tbinom{D(v)}{2} &+ (C_{11} p_{11} - C_{00}
-  p_{00}) \tbinom{M(v)}{2} \\ &+ (C_{10} p_{10} - C_{00} p_{00}) M(v) W(v)
+  p_{00}) \tbinom{M(v)}{2} \\ &+ (C_{10} p_{10} - C_{00} p_{00}) M(v)
+  W(v).
   \end{split}
@@
     P_2 &= \mathbb{P}(\bigcup_{v \in V(G)} D(v) \geq d_{n,m},
-    Y(v) - h(v) \geq \vartheta_n)
+    Y(v) - h(v) \geq \vartheta_n).
   \end{align*}
   We now show that $P_2$ is negligible as $n \rightarrow \infty$. To
-  proceed, let $p_{e,f} = \mathbb{P}(M(v) = e, W(v) =
-f)$. $P_2$ can then be bounded as follows
+  proceed, let $A$ be the event $\{M(v) = e, W(v) = f\}$ and let
+  $p_{e,f} = \mathbb{P}(A)$. $P_2$ can then be bounded as follows
 \begin{equation*}
@@
         d_{n,m}}{\mathbb{P}( Y(v) - h(v) \geq
-      \vartheta_{n}, M(v) = e, W(v) = f) p_{e,f}}
-  \\
-  &=  \sum_{e + f \geq d_{n,m}}{\mathbb{P}(
+      \vartheta_{n} \, | \, A)} p_{e,f}  \\
+  &=  \sum_{e + f \geq d_{n,m}}{\mathbb{P}\Bigl(
     \tfrac{Y(v) - h(v)}{\mathrm{Var}[Y(v)]^{1/2}} \geq
-    \tfrac{\vartheta_n}{\mathrm{Var}[Y(v)]^{1/2}}, M(v) = e, W(v) = f) p_{e,f}} \\
+    \tfrac{\vartheta_n}{\mathrm{Var}[Y(v)]^{1/2}} \, \Bigl| \, A\Bigr) p_{e,f}} \\
     &\leq \sum_{e + f \geq d_{n,m}} (1 + o(1))
-    \mathbb{P}(Z \geq \Theta(\log{n})) p_{e,f} = o(n^{-1})
+    \mathbb{P}(Z \geq \Theta(\log{n})) p_{e,f} \\ &= o(n^{-1}).
   \end{split}
@@
   R_1 &= \mathbb{P}\Bigl(\bigcup_{v \in [m]} D(v) \geq
-  d_{n,m}, h(v) \geq a_{n,m} - \vartheta_n \Bigr) \\  
+  d_{n,m}, h(v) \geq a_{n,m} - \vartheta_n \Bigr), \\  
   R_2 &= \mathbb{P}\Bigl(\bigcup_{v \in [n] \setminus [m]} D(v) \geq
-  d_{n,m}, h(v) \geq a_{n,m} - \vartheta_n \Bigr)
+  d_{n,m}, h(v) \geq a_{n,m} - \vartheta_n \Bigr).
 \end{align*}
@@
       \sqrt{\tfrac{2 (a_{n,m} - \vartheta_n -
-        g(v))}{C_{00} p_{00}}} \Bigr)
+        g(v))}{C_{00} p_{00}}} \Bigr).
   \end{split}
@@
   C_{00} p_{00})(\tbinom{\mu_E}{2} - \tbinom{M(v)}{2})
-  \\ &+ (C_{10} p_{10} - C_{00} p_{00})(\mu_E\mu_F - M(v)W(v))
+  \\ &+ (C_{10} p_{10} - C_{00} p_{00})(\mu_E\mu_F - M(v)W(v)).
   \end{split}
@@
   a_{n,m} - g(v) = N_{\kappa}^{2}\Bigl(\tfrac{C_{00}p_{00}}{2} + O(n^{-1/2 - a}
-  \log{n})\Bigr)
-\end{equation}
-for some $a > 0$. The set $\{v \in [m]\}$ can be partitition into
+  \log{n})\Bigr).
+\end{equation}
+for some $a > 0$. The set $\{v \in [m]\}$ can be partition into
 $\{v \in [m] \cap (\mathfrak{E} \cap\mathfrak{F})\}$ and $\{v \in [m]
@@
     \sigma_{E+F}(z_m + O(\tfrac{\log{n}}{n^{a}}))\Bigr) + o(n^{-1}) \\ 
-    & \rightarrow \mathbb{P}(\Delta \geq N_{\kappa})
+    & \rightarrow \mathbb{P}(\Delta \geq N_{\kappa}).
     \end{split}
@@
   R_2 \leq \mathbb{P}\Bigl(\bigcup_{v \in [n] \setminus [m]} D(v) \geq
-  N_{\kappa}(1 + o(1))\Bigr) = o(1)
+  N_{\kappa}(1 + o(1))\Bigr) = o(1).
 \end{equation}
@@
       N_\kappa\Bigr) \\ &- \mathbb{P}\Bigl( \bigcup_{v
-        \in [m]} Y(v) < a_{n,m}, D(v) \geq N_\kappa\Bigr)
+        \in [m]} Y(v) < a_{n,m}, D(v) \geq N_\kappa\Bigr).
     \end{split}
@@
         \label{eq:24}
-        \sum_{e + f \geq N_{\kappa}}{\mathbb{P}(Y(v) \leq a_{n,m}, M(v) = e, W(v) =
-          f)}p_{e,f}
+        \sum_{e + f \geq N_{\kappa}}{\mathbb{P}(Y(v) \leq a_{n,m} \, |
+          \, M(v) = e, W(v) =
+          f)}p_{e,f}.
       \end{equation}
@@
   \label{eq:32}
-    S_1 = \{ \{e,f\}\colon e \geq
+    S_1 = \{  e \geq
         \mu_E + \sigma_E \log{m}\} \\
-    S_2 = \{ \{e,f\} \colon  e \leq
+    S_2 = \{  e \leq
         \mu_E + \sigma_E \log{m},e + f \leq
         N_\kappa + \varphi(n)\} \\
-    S_3 = \{ \{e,f\} \colon e \leq \mu_E + \sigma_E \log{m}, e + f \geq
+    S_3 = \{ e \leq \mu_E + \sigma_E \log{m}, e + f \geq
         N_\kappa + \varphi(n)\}
@@
     a_{n,m} - h(v) &\leq (C_{11} p_{11} - C_{10} p_{10})[m \sigma_E
-    \log{m} + \tbinom{\log{m}}{2}] \\ &- C_{00}p_{00} N_\kappa \varphi(n)
+    \log{m} + \tbinom{\log{m}}{2}] \\ &- C_{00}p_{00} N_\kappa
+    \varphi(n).
     \end{split}
@@
     &\leq \sum_{\{e,f\} \in S_3} \mathbb{P}\Bigl[Z \leq
-    O\bigl(\tfrac{m^{3/2} \log m}{N_{\kappa}} - \varphi(n)\bigr)\Bigr] p_{e,f}
+    O\bigl(\tfrac{m^{3/2} \log m}{N_{\kappa}} - \varphi(n)\bigr)\Bigr]
+    p_{e,f}.
     \end{split}
@@
     m p_{S_3} \leq m \sum_{\{e,f\} \in S_3} \mathbb{P} \Bigl[Z \leq
-    - O(n^{k/2(k+1)}\Bigr] p_{e,f} = o(1)
+    - O(n^{k/2(k+1)}\Bigr] p_{e,f} = o(1).
   \end{equation}
@@
 \end{IEEEproof}
-
+From Eq.~\eqref{eq:27} and Eq.~\eqref{eq:30}, we have
+\begin{equation}
+  \label{eq:40}
+ \lim
+\mathbb{P}(\Upsilon(G) \geq a_{n,m}) = \lim \mathbb{P}(\Delta(G) \geq
+N_{\kappa}).
+ \end{equation}
+Let $N_{\kappa,y} = N_\kappa + y \tfrac{\sigma_{E+F}}{\sqrt{2
+    \log{m}}}$. We now define $a_{n,m,y}$ as 
+\begin{equation*}
+  \langle \lambda, \pi_{00} \rangle
+    \tbinom{N_{\kappa,y}}{2} +
+  \langle \lambda, \pi_{11} - \pi_{00} \rangle \tbinom{\mu_E}{2}  +
+  \langle \lambda, \pi_{10} - \pi_{00} \rangle \mu_E \mu_F.
+\end{equation*}
+The above expression is equal to 
+\begin{equation}
+  \label{eq:57}
+ a_{n,m} + \langle \lambda, \pi_{00} \rangle y
+  \frac{\sigma_{E+F}}{\sqrt{2 \log m}} \Bigl(N_{\kappa} + y
+  \frac{\sigma_{E+F}^{2}}{2 \sqrt{2 \log{m}}} + O(1) \Bigr).
+\end{equation}
+We thus have
+\begin{equation*}
+   a_{n,m,y} = a_{n,m} + (y + o(1)) b_{n,m}.
+\end{equation*}
+We therefore have
+\begin{equation*}
+  \begin{split}
+  \lim \mathbb{P}(\Upsilon(G) \geq a_{n,m,y}) &= 
+  \lim \mathbb{P}\Bigl(\frac{\Upsilon(G) - a_{n,m}}{b_{n,m}} \geq y \Bigr) \\
+  &= \lim \mathbb{P}(\Delta(G) \geq N_{\kappa,y}) \\
+  &= \lim \mathbb{P}\Bigl(\frac{\Delta(G) -
+    N_{\kappa}}{\sigma_{E+F}} \geq \frac{y}{\sqrt{2 \log{m}}} \Bigr). \\
+  \end{split}
+\end{equation*}
+Because $\Delta(G)$ converges weakly to a Gumbel
+distribution in the limit
+(\cite{bollobas85:_random_graph,rukhin:_limit_distr_graph_scan_statis}),
+we have
+\begin{equation}
+  \label{eq:47}
+  \mathbb{P}\Big(\frac{\Upsilon(G) - a_{n,m}}{b_{n,m}} \leq
+    y\Bigr) \rightarrow e^{- e^{-y}} 
+\end{equation}
+and Eq.~\eqref{eq:29} follows.
 \end{IEEEproof}

### 2011-10-30 Rcodes/attributed_graph.R

@@ -1,0 +1,98 @@
+library("evd")
+
+kidney.egg.attributed <- function(n,m,pi0,piA){
+  
+  pi00 <- pi0*pi0
+  pi0A <- pi0*piA; piA0 <- pi0A
+  piAA <- piA*piA
+  
+  runif.mat <- matrix(0,nrow = n, ncol = n)
+  runif.mat[col(runif.mat) > row(runif.mat)] <- runif(n*(n-1)/2)
+  runif.mat <- (runif.mat + t(runif.mat))
+
+  edge.mat <- matrix(0, nrow = n, ncol =n)
+  edge.mat[1:m,1:m] <- sum(piAA)
+  edge.mat[1:m,(m+1):n] <- sum(pi0A) 
+  edge.mat[(m+1):n,1:m] <- sum(pi0A)
+  edge.mat[(m+1):n,(m+1):n] <- sum(pi00)
+
+  red.mat <- matrix(0, nrow = n, ncol = n)
+  red.mat[1:m,1:m] <- piAA[1]
+  red.mat[1:m,(m+1):n] <- pi0A[1]
+  red.mat[(m+1):n,1:m] <- pi0A[1]
+  red.mat[(m+1):n,(m+1):n] <- pi00[1]
+
+  adjacency.mat <- matrix(0,nrow = n, ncol = n)
+  red.idx <- (runif.mat <= red.mat)
+  green.idx <- (runif.mat > red.mat & runif.mat <= edge.mat)
+
+  adjacency.mat[red.idx] <- 1
+  adjacency.mat[green.idx] <- 2
+  diag(adjacency.mat) <- 0
+
+  vertex.colors <- c(rep("red",length.out=m),
+                     rep("green",length.out=(n-m)))
+
+  return(list(adjacency=adjacency.mat,
+              v.colors = vertex.colors))
+}
+
+maxd.statistic <- function(x,g){
+  t1 <- rowSums(g$adjacency == 1)
+  t2 <- rowSums(g$adjacency == 2)
+  t <- t1*x[1] + t2*x[2]
+  return(max(t))
+}
+
+num.triangle.trace <- function(w, g){
+  A <- g$adjacency
+  A1 <- (A == 1) + 0
+  A2 <- (A == 2) + 0
+  A.weighted <- w[1]*A1 + w[2]*A2
+
+  return(sum(diag(A.weighted %*% A.weighted %*% A.weighted))/6)
+}
+
+scan.statistic <- function(x,g){
+  x.red <- x[1]
[…]

### 2011-10-30 Rcodes/lp2010.R

@@ -1,0 +1,72 @@
+#library("igraph")
+
+namasy <- function(a=c(0.6,0.1,0.3),b=c(0.35,0.25,0.4))
+{
+# oripi <- pi
+#  a = c(0.6, 0.1, 0.3)
+#  b = c(0.35, 0.25, 0.40)
+
+ pi = c(1-sum((a * a)[2:3]), (a * a)[2:3])
+ phi = c(1-sum((a * b)[2:3]), (a * b)[2:3])
+ nu = c(1-sum((b * b)[2:3]), (b * b)[2:3])
+
+ W = rbind(
+   c(0,1,1),
+   c(0,1,0),
+   c(0,2,1)
+   )
+
+ x1seq = seq(0,2*3.14,by=0.01)
+ W=matrix(0,nrow=length(x1seq),ncol=3)
+
+ for(i in 1:length(x1seq))
+   W[i,] = c(0,cos(x1seq[i]),sin(x1seq[i]))
+
+
+ for( scale in 1:1 ) {
+
+   n =10
+   nvertex = 100*scale
+   abnorm = 9#*scale
+   chart = numeric(abnorm)
+
+   my = matrix(nrow=abnorm,ncol=length(x1seq))
+
+   for (row in 1:length(x1seq)) {
+     for ( i in abnorm:abnorm) {
+       alpha = 0.05
+       m = i
+
+       xi_pi = t(W[row,])%*% out(pi) %*% W[row,]
+       xi_phi = t(W[row,])%*% out(phi) %*% W[row,]
+       xi_nu = t(W[row,])%*% out(nu) %*% W[row,]
+
+       quartile_1 = qt(alpha,n-1,ncp = 0, lower.tail = FALSE)
+       quartile_2 = 1 + (n/(n+1))*(choose(m,2)/choose(nvertex,2)*(xi_nu/xi_pi - 1) +
+         m*(nvertex - m)/choose(nvertex,2)*(xi_phi/xi_pi - 1))
+       quartile = quartile_1 / sqrt(quartile_2)
+
+       kappa_num = choose(m,2) * W[row,] %*% (nu-pi) + m * (nvertex -m) * W[row,] %*% (phi-pi)
+       kappa_den_1 = (1+1/n)*choose(nvertex,2)* xi_pi
+       kappa_den_2 = choose(m,2) * ( xi_nu - xi_pi )
+       kappa_den_3 = m*(nvertex -m)*( xi_phi - xi_pi)
[…]

### 2011-10-30 Rcodes/maxd.R

@@ -1,0 +1,485 @@
+max.asy <- function(nvertex, nvertex.abnormal, pi0, piA, past.len, mc,
+                        from.egg = TRUE, adjustment = 0){
+  
+  pi00 <- c(1 - sum((pi0*pi0)[2:3]), (pi0*pi0)[2:3])
+  pi0A <- c(1 - sum((pi0*piA)[2:3]), (pi0*piA)[2:3])
+  piA0 <- pi0A
+  piAA <- c(1 - sum((piA*piA)[2:3]), (piA*piA)[2:3])
+
+  gamma <- 0.577215665
+  alpha <- 0.05
+  x1seq <- seq(0,pi/2, by = 0.01)
+  W <- matrix(0,nrow = length(x1seq), ncol = 3)
+  cv <- numeric(length(x1seq))
+  power <- numeric(length(x1seq))
+  
+  for(i in 1:length(x1seq))
+    W[i,] <- c(0,cos(x1seq[i]), sin(x1seq[i]))
+
+  for(i in 1:length(x1seq)){
+    params.list <- maxd.0A.params(nvertex, nvertex.abnormal, pi00, pi0A,
+                                  piAA, W[i,], from.egg)
+
+    an0 <- params.list$an0
+    anA <- params.list$anA
+    bn0 <- params.list$bn0
+    bnA <- params.list$bnA
+
+    ## sigma0 <- pi/sqrt(6)*bn0
+    ## sigmaA <- pi/sqrt(6)*bnA
+
+    ## ncp <- (anA - an0 + (bnA - bn0)*gamma)/sqrt(sigma0^2/past.len + sigmaA^2)
+    ## scale <- bnA/(pi/sqrt(6)*bn0)
+
+    ## quartile.1<- qt(alpha, df = past.len - 1, ncp = 0, lower.tail = FALSE)
+    ## quartile.2 <- (1 + (past.len)/(past.len + 1)*(sigmaA^2/sigma0^2 - 1))
+    ## quartile <- quartile.1/sqrt(quartile.2) + adjustment
+
+    tmp <- gumbel.power.test(an0, bn0, anA, bnA, past.len, mc)
+    cv[i] <- tmp$cv
+    #power[i] <- pt(quartile, df = past.len - 1, ncp = ncp, lower.tail = FALSE)
+    power[i] <- tmp$power
+  }
[…]

### 2011-10-30 Rcodes/numtri.R

@@ -1,0 +1,97 @@
+normal.power.test <- function(mu0,sd0,mu1,sd1,past.len,mc,cv){
+  g0.normalized <- seq(0,0,length.out = mc)
+  gA.normalized <- seq(0,0,length.out = mc)
+
+  g0mat <- matrix(rnorm(mc*(past.len + 1), mu0, sd0), nrow = mc, ncol = past.len + 1)
+  g0seq.mean1 <- rowMeans(g0mat[,1:past.len])
+  g0seq.sd1 <- sd(t(g0mat[,1:past.len]))
+  g0.normalized <-  (g0mat[,past.len+1] - g0seq.mean1)/g0seq.sd1
+
+  gAvec <- rnorm(mc,mu1,sd1)
+  g0seq.mean2 <- rowMeans(g0mat[,2:(past.len+1)])
+  g0seq.sd2 <- sd(t(g0mat[,2:(past.len+1)]))
+  gA.normalized <- (gAvec - g0seq.mean2)/g0seq.sd2
+
+  power <- length(which(gA.normalized > cv))/mc
+  return(list(cv = cv, power = power))
+}
+
+## numtri.pwr <- numeric(158)
+## numtri.cv <- numeric(158)
+## for(i in 1:158){
+##   tmp <-  normal.power.test(numtri.null.mean[i],numtri.null.sd[i],numtri.alt.mean[i],
+##                             numtri.alt.sd[i], 10,10000,numtri.stat$cv[i])
+##   numtri.cv[i] <- tmp$cv
+##   numtri.pwr[i] <- tmp$power
+## }
+  
+num.triangles.asy <- function(nvertex, nvertex.abnormal, pi0, piA,past.len){
+  
+  pi00 <- c(1 - sum((pi0*pi0)[-1]), (pi0*pi0)[-1])
+  pi0A <- c(1 - sum((pi0*piA)[-1]), (pi0*piA)[-1])
+  piA0 <- pi0A
+  piAA <- c(1 - sum((piA*piA)[-1]), (piA*piA)[-1])
+
+  alpha <- 0.05
+  x1seq <- seq(0, pi/2, by = 0.01)
+  W <- matrix(0, nrow = length(x1seq), ncol = 3)
+  cv <- numeric(length(x1seq))
+  power <- numeric(length(x1seq))
+
+  for(i in 1:length(x1seq))
[…]

### 2011-10-30 Rcodes/scan.R

@@ -1,0 +1,449 @@
+youngser1 <- function(tstat.mat, past.len, mc){
+  gamma <- 0.577215665
+  d1 <- dim(tstat.mat)[1]
+  d2 <- dim(tstat.mat)[2]
+  power.vec <- numeric(d2)
+  cv.vec <- numeric(d2)
+  for(i in 1:d2){
+    a.i <- tstat.mat[,i,]
+    a.i.null <- a.i[1:(d1-1),]
+    a.i.null.mean <- mean(a.i.null)
+    a.i.null.sd <- sd(as.vector(a.i.null))
+
+    a.i.alt <- a.i[d1,]
+    a.i.alt.mean <- mean(a.i.alt)
+    a.i.alt.sd <- sd(a.i.alt)
+
+    bn0 <- a.i.null.sd*sqrt(6)/pi
+    an0 <- a.i.null.mean - bn0*gamma
+
+    bnA <- a.i.alt.sd*sqrt(6)/pi
+    anA <- a.i.alt.mean - bnA*gamma
+
+    gpt <- gumbel.power.test(an0, bn0, anA, bnA, past.len, mc)
+    power.vec[i] <- gpt$power
+    cv.vec[i] <- gpt$cv
+  }
+  return(list(cv = cv.vec, power = power.vec))
+}
+
+pwr1.test <- function(){
+  theta.seq <- seq(from = 0, to = pi/4, by = 0.01)
+  power.vec <- seq(0,0,length.out = length(theta.seq))
+  cv.vec <- seq(0,0,length.out = length(theta.seq))
+  for(i in 1:length(theta.seq)){
+    print(i)
+    tmp <- power.test(theta.seq[i])
+    power.vec[i] <- tmp$power
+    cv.vec[i] <- tmp$cv
+  }
+  return(list(cv = cv.vec, power = power.vec))
+}
+
+scan.mc.mat <- function(nvertex,nvertex.abnormal,pi0.vec, piA.vec, mc){
+  theta.seq <- seq(from = 0, to = pi/4, by = 0.01)
+  g0.mat <- matrix(0,nrow=length(theta.seq), ncol = mc)
+  gA.mat <- matrix(0,nrow=length(theta.seq), ncol = mc)
+
+  print("Long ass computation: theta = ")
+  for(i in 1:length(theta.seq)){
+    print(theta.seq[i])
[…]

### 2011-10-30 Rcodes/snippet.R

@@ -1,0 +1,153 @@
+kidney.egg.attributed <- function(n,m,theta,pi0,piA){
+  
+  pi00 <- pi0*pi0
+  pi0A <- pi0*piA
+  piA0 <- pi0A
+  piAA <- piA*piA
+  x.red <- cos(theta)
+  x.green <- sin(theta)
+  
+  runif.mat <- matrix(0,nrow = n, ncol = n)
+  runif.mat[col(runif.mat) > row(runif.mat)] <- runif(n*(n-1)/2)
+  runif.mat <- (runif.mat + t(runif.mat))
+
+  edge.mat <- matrix(0, nrow = n, ncol =n)
+  edge.mat[1:m,1:m] <- sum(piAA)
+  edge.mat[1:m,(m+1):n] <- sum(pi0A) 
+  edge.mat[(m+1):n,1:m] <- sum(pi0A)
+  edge.mat[(m+1):n,(m+1):n] <- sum(pi00)
+
+  red.mat <- matrix(0, nrow = n, ncol = n)
+  red.mat[1:m,1:m] <- piAA[1]
+  red.mat[1:m,(m+1):n] <- pi0A[1]
+  red.mat[(m+1):n,1:m] <- pi0A[1]
+  red.mat[(m+1):n,(m+1):n] <- pi00[1]
+
+  adjacency.mat <- matrix(0,nrow = n, ncol = n)
+  edge.idx <- (runif.mat < edge.mat)
+  adjacency.mat[edge.idx] <- 1
+
+  labels.mat <- matrix("none", nrow = n, ncol = n)
+  red.idx <- (runif.mat <= red.mat)
+  green.idx <- (runif.mat > red.mat & runif.mat <= edge.mat)
+
+  labels.mat[red.idx] <- "red"
+  labels.mat[green.idx] <- "green"
+  diag(labels.mat) <- "none"
+  diag(adjacency.mat) <- 0
+
+  d.red <- x.red*apply(labels.mat,1, count.red)
+  d.green <- x.green*apply(labels.mat, 1, count.green)
+  deg <- d.red + d.green
+  
+  vertex.colors <- c(seq("red","red",length.out=m),
+                     seq("green","green",length.out=(n-m)))
+
+  return(list(adjacency=adjacency.mat,
+              labels=labels.mat,
+              dred=d.red,
+              dgreen=d.green,
+              degree=deg,
+              v.colors = vertex.colors))
+}
+
+## Compute the scan statistics
+## If the scan statistic belong
[…]

### 2011-10-30 Rcodes/tstat0-MC10k-1st-maxd-n100-m9.R

@@ -1,0 +1,171 @@
+read.maxd <- function(){
+
+  load("tstat0-MC10k-1st-maxd-n100-m9.RData")
+
+  maxd0.mat <- matrix(0, ncol = 11*length(tstat0), nrow = length(tstat0[[1]]))
+
+  for(i in 1:nrow(maxd0.mat)){
+    for(j in 1:length(tstat0)){
+      maxd0.mat[i,((j-1)*11+1):(11*j)] <- tstat0[[j]][[i]][1:11]
+    }
+  }
+
+  maxdA.mat <- matrix(0, ncol = length(tstat0), nrow = length(tstat0[[1]]))
+  for(i in 1:nrow(maxdA.mat)){
+    for(j in 1:length(tstat0)){
+      maxdA.mat[i,j] <- tstat0[[j]][[i]][12]
+    }
+  }
+}
+
+read.scan <- function(){
+  
+  load("tstat1-MC10k-1st-scan-n100-m9.Rbin")
+  scan.null.mat <- matrix(0, ncol = 11*length(tstat1), nrow = length(tstat1[[1]]))
+
+  for(i in 1:nrow(scan.null.mat)){
+    for(j in 1:(ncol(scan.null.mat)/11)){
+      scan.null.mat[i,((j-1)*11+1):(j*11)] <- tstat1[[j]][[i]][1:11]
+    }
+  }
+
+  scan.alt.mat <- matrix(0, ncol = length(tstat1), nrow = length(tstat1[[1]]))
+  for(i in 1:nrow(scan.alt.mat)){
+    for(j in 1:ncol(scan.alt.mat)){
+      scan.alt.mat[i,j] <- tstat1[[j]][[i]][12]
+    }
+  }
+}
+
+
+read.numtri <- function(){
+  tstat3 <- dget("tstat3-MC10k-1st-ntri-n100-m9.RData.gz")
+  numtri.null.mat <- matrix(0, ncol = 11*length(tstat2), nrow = length(tstat2[[1]]))
+
+  for(i in 1:nrow(numtri.null.mat)){
+    for(j in 1:(ncol(numtri.null.mat)/11)){
+      numtri.null.mat[i,((j-1)*11+1):(j*11)] <- tstat2[[j]][[i]][1:11]
+    }
+  }
+
+  numtri.alt.mat <- matrix(0, ncol = length(tstat2), nrow = length(tstat2[[1]]))
[…]

### 2011-11-13 changes.tex
Submitted to TPAMI

\documentclass{article}
\begin{document}
\title{Summary of changes}
\maketitle
The manuscript for this submission is based on a paper that
was presented at the 2011 IEEE Workshop on Statistical Signal
Processing (June 28 - June 30, 2011) in Nice, France. The original
paper that was presented at the workshop is of 4 double column pages
in length and contains a brief discussion of the methodology along
with an example for inference on time series of graphs.

The main differences between the current manuscript and the paper from the
workshop are:
\begin{itemize}
\item A more comprehensive introduction and discussion of
  methodology. We describe the underlying model in more details.
\item Theoretical results and their derivations are now included. They
  account for most of the changes.
\item The experimental results are further refined. The main running example
  is expanded to include power approximations for number of triangles.
\end{itemize}
\end{document}
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2011-11-13 ssp2011.tex
Submitted to TPAMI

@@
 \usepackage{fontenc}
+\pdfminorversion=4
 %\usepackage{lmodern}
-%\usepackage[utopia]{mathdesign}
+\usepackage[utopia]{mathdesign}
 \usepackage{graphicx}
-\usepackage{xltxtra}
-\setmainfont[Mapping=tex-text]{Linux Libertine}
+%\usepackage{xltxtra}
+%\setmainfont[Mapping=tex-text]{Linux Libertine}
 \usepackage[cmex10]{amsmath}
@@
 \usepackage{array}
-\usepackage{amssymb}
+%\usepackage{amssymb}
 \usepackage{amsthm}
@@
 \item $\mathbf{X} = \{X_v\}_{v = 1}^{n}$ is a collection of
-  $\mathscr{S}$-valued random vectors.
+  independent $\mathscr{S}$-valued random vectors.
 \item $G$ is a random undirected graph with vertex set $[n]$ such that
@@
 The above properties characterize a random dot process model with a
-change-point phenomena at time $t = t^{*}$. We chose $\{1,2,\dots,m\}$
+change-point phenomena for $(X(t),G(t))$ at time $t = t^{*}$. We chose $\{1,2,\dots,m\}$
 as the set of vertices with a change in the stationary distribution
@@
   \centering
-  \includegraphics[width=5cm]{graphics/Fig2-SSP2011.pdf}
+  \includegraphics[width=5cm]{graphics/Fig2-SSP2011-hat1.pdf}
   \caption{An illustration of the kidney-egg model for $G(t^{*})$.}
@@
   \item For $t < t^{*} - 1$,
-    \begin{gather}
-      \mathbb{E}[Z_v(t)] \equiv \hat{\pi}_0 \\
-      \mathrm{Var}[Z_v(t)] \equiv \widehat{\Sigma}_0.
-    \end{gather}
+    \begin{equation}
+      \mathbb{E}[Z_v(t)] \equiv \hat{\pi}_0, \,\, 
+  \mathrm{Var}[Z_v(t)] \equiv \widehat{\Sigma}_0 \quad \text{for all
+    $v$}.
+    \end{equation}
   \item For $t \geq t^{*} - 1$,  
     \begin{gather*}
-      \mathbb{E}[Z_v(t)] \equiv \hat{\pi}_0, \quad \text{for $v \leq
-        m$}  \\
-      \mathbb{E}[Z_v(t)] \equiv \hat{\pi}_1, \quad \text{for $v > 
-        m$}  \\
-      \mathrm{Var}[Z_i(t)] \equiv \widehat{\Sigma}_{0} \quad \text{for $v
+      \mathbb{E}[Z_v(t)] \equiv \hat{\pi}_1, \,\, 
+\mathrm{Var}[Z_v(t)] \equiv \widehat{\Sigma}_{1} \quad \text{for $v
   \leq m$} \\
-      \mathrm{Var}[Z_i(t)] \equiv \widehat{\Sigma}_{1} \quad \text{for $v
+  \mathbb{E}[Z_v(t)] \equiv \hat{\pi}_0, \,\, \mathrm{Var}[Z_v(t)] \equiv \widehat{\Sigma}_{0} \quad \text{for $v
         > m$}
@@
 for $l \geq 2$, i.e., we want to find a parameter $\lambda$ such that
-the power of the test using $T_{\lambda}^{l}$ is maximum. We note that
+the power of the test using $T_{\lambda}^{l}$ is maximized. We note that
 $T_{\lambda}^{l}$ is scale invariant in $\lambda$ for all of our graph
 invariants. It was noted in \cite{lee11} that the maximum of the power
-for scale invariant tests is attainable in $\{ \lambda \colon \|
+for scale invariant test statistics is attainable in the set $\{ \lambda \colon \|
 \lambda \| = 1 \}$. \\ \\
@@
 strive to obtain approximations for the power in testing $t^{*} > t$
-against $t^{*} = t$ using $T_{\lambda}(t)$ and from these
+against $t^{*} = t$ using $T_{\lambda}^{l}(t)$ and from these
 approximations, find the $\lambda$ that maximize the power. We now
@@
     \psi^{l}_{\lambda}(t) = \begin{cases}
-      \sqrt{\frac{\langle \lambda, \tbinom{n}{2} \eta_{00}
+      \sqrt{\frac{l}{l + 1}} T_{\lambda}^{l}(t)& \text{if $t < t^{*}$}
+      \\ \sqrt{\frac{\langle \lambda, \tbinom{n}{2} \eta_{00}
             \lambda \rangle}{\langle \lambda, \xi
-            \lambda \rangle}} T_{\lambda}^{l}(t) & \text{if $t = t^{*}$} \\
-      \sqrt{\frac{l}{l + 1}} T_{\lambda}^{l}(t)& \text{if $t <
+            \lambda \rangle}} T_{\lambda}^{l}(t) & \text{if $t =
           t^{*}$}.
@@
     \mu_{\lambda} = \begin{cases}
-      \frac{\langle \lambda, \zeta \rangle}{\sqrt{\langle \lambda, \xi \lambda \rangle}} & \text{if $t = t^{*}$} \\
-      0 & \text{if $t < t^{*}$}.
+      0 & \text{if $t < t^{*}$} \\
+      \frac{\langle \lambda, \zeta \rangle}{\sqrt{\langle \lambda, \xi \lambda \rangle}} & \text{if $t = t^{*}$} 
     \end{cases}
@@
     \psi_{\lambda}^{l}(t) = \begin{cases}
-      \Bigl(\sqrt{\tfrac{l}{l+1}}\,\Bigr) T_{\lambda}^{l}(t) & \text{if $t <
+      \sqrt{\tfrac{l}{l+1}}\, T_{\lambda}^{l}(t) & \text{if $t <
         t^{*}$} \\
-      \Bigl(\sqrt{\tfrac{l \sigma_0^{2}}{l \sigma_A^{2} + \sigma_0^{2}} }\,\Bigr)
+      \sqrt{\tfrac{l \sigma_0^{2}}{l \sigma_A^{2} + \sigma_0^{2}} }\,
       T_{\lambda}^{l}(t) & \text{if $t = t^{*}$}.
@@
     \sigma_A &= \sqrt{(n-1)\langle \lambda, \eta_{00} \lambda \rangle} \\
-    \mu_0 &= \,\, (m - 1) \langle x, \pi_{11} \rangle + (n-
+    \mu_0 &= \,\, (m - 1) \langle \lambda, \pi_{11} \rangle + (n-
     m)\langle \lambda, \pi_{01} \rangle
@@
   \rho_{\lambda} &= \begin{cases}
+      - \frac{ \sqrt{\pi}}{6} \gamma & \text{if $t < t^{*}$} \\
     \frac{\sqrt{\pi}}{6} \frac{\mu_A - \mu_0 + a_m\sigma_A - (a_n + b_n
       \gamma)\sigma_0}{b_n \sigma_0} & \text{if $t =
-        t^{*}$} \\
-      - \frac{ \sqrt{\pi}}{6} \gamma & \text{if $t < t^{*}$}
+        t^{*}$} 
   \end{cases}\\
   \varsigma_{\lambda} &= \begin{cases}
+    \frac{\sqrt{\pi}}{6} & \text{if $t < t^{*}$} \\
     \frac{\sqrt{\pi} b_m \sigma_A}{6 b_n \sigma_0} & \text{if $t =
       t^{*}$} \\
-    \frac{\sqrt{\pi}}{6} & \text{if $t < t^{*}$};
     \end{cases}
 \end{align}
-$\gamma \approx 0.57721$ is the Euler-Mascheroni constant.
+where $\gamma \approx 0.57721$ is the Euler-Mascheroni constant.
 \end{theorem}
@@
     \rho_{\lambda} &= \begin{cases}
+      - \tfrac{\sqrt{\pi}}{6} \gamma & \text{if $t < t^{*}$} \\
       \tfrac{\sqrt{\pi}}{6} \tfrac{a_{n,m} - a_n - b_n \gamma}{b_n} & \text{if
-        $t = t^{*}$} \\
-      - \tfrac{\sqrt{\pi}}{6} \gamma & \text{if $t < t^{*}$} 
+        $t = t^{*}$} 
     \end{cases} \\
       \varsigma_{\lambda} &= \begin{cases}
-        \tfrac{\sqrt{\pi} b_{n,m}}{6 b_n} & \text{if $t = t^{*}$} \\
-        \tfrac{\sqrt{\pi}}{6} & \text{if $t < t^{*}$}.
+        \tfrac{\sqrt{\pi}}{6} & \text{if $t < t^{*}$} \\
+        \tfrac{\sqrt{\pi} b_{n,m}}{6 b_n} & \text{if $t = t^{*}$}. \\
       \end{cases}
@@
 $\tfrac{\rho_\lambda}{\varsigma_{\lambda}}$ and is on the boundary,
-i.e., $\lambda(k) \not = 0$ for exactly one $k$. Therefore the asymptotic theory
+i.e., $\lambda_k \not = 0$ for exactly one $k$. Therefore the asymptotic theory
 for scan statistics, in contrast with the other graph invariants that
@@
 
-The experiment in \S \ref{eq:55} indicates that the power estimates are accurate, even
-for the moderate value of $n = 100$. Furthermore, it was also
-indicated that the optimal linear fusion parameter depends on the
-graph invariant considered. In particular, the results depicted in
-\figurename~\ref{fig:power-estimate} yield
+The experiment in \S \ref{eq:55} indicates that the power estimates
+are accurate, even for the moderate value of $n = 100$. Furthermore,
+it was also indicated that the optimal linear fusion parameter depends
+on the graph invariant considered. In particular, the results depicted
+in \figurename~\ref{fig:power-estimate} yield
 $\theta^{*}_{\mathcal{E}_{\lambda}} \approx 0.24$,
@@
 development. Toward this end, the approximation models from
-  \cite{lee11} promise to
-  be of assistance.
+\cite{lee11} promise to be of assistance.
 
 Hypothesis testing on time series of attributed graphs has
-  applications in diverse areas, e.g., social network analysis
-  (wherein vertices represent individual actors or organizations), connectome
+applications in diverse areas, e.g., social network analysis (wherein
+vertices represent individual actors or organizations), connectome
 inference (wherein vertices are neurons or brain regions) and text
@@
 and many other applications may benefit from generalizations of our
-  results and the
-  model in \cite{lee11} to
-  directed, multi, and weighted graphs, as well as the consideration
-  of inference with errorful edge attributes through an attribute
-  confusion matrix.
-  \appendices
-\section{Proofs of some stated results}
-\label{sec:proofs-some-stated}
-\begin{IEEEproof}[Corollary~\ref{cor:1}]
-  The maximizer of $\mu_\lambda$ also maximizes
-  \begin{equation*}
-    \mu_{\lambda}^{2} = \frac{\lambda^{T} \zeta \zeta^{T}
-      \lambda}{\lambda^{T} \xi \lambda}
-  \end{equation*}
-  Because $\xi$ is positive definite, there exists a positive definite matrix
-  $\xi^{1/2}$ such that $\xi^{1/2} \xi^{1/2} = \xi$. Letting $\nu = \xi^{1/2}
-  \lambda$, the above expression can be rewritten as
-  \begin{equation*}
-    \mu_{\lambda}^{2} = \frac{\nu^{T} \xi^{-1/2} \zeta \zeta^{T}
-      \xi^{-1/2} \nu}{ \nu^{T} \nu}
-  \end{equation*}
-  The claim then follows directly from the Rayleigh-Ritz theorem for
-  Hermitian matrices.
-\end{IEEEproof}
-\begin{IEEEproof}[Lemma~\ref{lem:3}]
-  $\tau_{\lambda}(G)$ is a U-statistics with kernel function
-  $h(Y_1, Y_2, Y_3) = Y_1 Y_2 Y_3$. By the theory of U-statistics, we
-  know that
-  \begin{equation}
-    \label{eq:48}
-    \frac{\tau_{\lambda}(G) -
-      \mathbb{E}[\tau_{\lambda}^{*}(G)]}{\sqrt{\mathrm{Var}[\tau_{\lambda}^{*}(G)]}}
-       \overset{\mathrm{d}}{\longrightarrow}  N(0,1)
-  \end{equation}
-  provided that $\mathrm{Var}[\tau_{\lambda}(G) -
-  \tau_{\lambda}^{*}(G)] = o(\mathrm{Var}[\tau_{\lambda}^{*}(G)])$.
+results and the model in \cite{lee11} to directed, multi, and weighted
+graphs, as well as the consideration of inference with errorful edge
+attributes through an attribute confusion matrix.
+% \appendix[Proofs of some stated results]
+% \label{sec:proofs-some-stated}
+% \begin{IEEEproof}[Corollary~\ref{cor:1}]
+%   The maximizer of $\mu_\lambda$ also maximizes
+%   \begin{equation*}
+%     \mu_{\lambda}^{2} = \frac{\lambda^{T} \zeta \zeta^{T}
+%       \lambda}{\lambda^{T} \xi \lambda}
+%   \end{equation*}
+%   Because $\xi$ is positive definite, there exists a positive definite matrix
+%   $\xi^{1/2}$ such that $\xi^{1/2} \xi^{1/2} = \xi$. Letting $\nu = \xi^{1/2}
+%   \lambda$, the above expression can be rewritten as
+%   \begin{equation*}
+%     \mu_{\lambda}^{2} = \frac{\nu^{T} \xi^{-1/2} \zeta \zeta^{T}
+%       \xi^{-1/2} \nu}{ \nu^{T} \nu}
+%   \end{equation*}
+%   The claim then follows directly from the Rayleigh-Ritz theorem for
+%   Hermitian matrices.
+% \end{IEEEproof}
+% \begin{IEEEproof}[Lemma~\ref{lem:3}]
+%   $\tau_{\lambda}(G)$ is a U-statistics with kernel function
+%   $h(Y_1, Y_2, Y_3) = Y_1 Y_2 Y_3$. By the theory of U-statistics, we
+%   know that
+%   \begin{equation}
+%     \label{eq:48}
+%     \frac{\tau_{\lambda}(G) -
+%       \mathbb{E}[\tau_{\lambda}^{*}(G)]}{\sqrt{\mathrm{Var}[\tau_{\lambda}^{*}(G)]}}
+%        \overset{\mathrm{d}}{\longrightarrow}  N(0,1)
+%   \end{equation}
+%   provided that $\mathrm{Var}[\tau_{\lambda}(G) -
+%   \tau_{\lambda}^{*}(G)] = o(\mathrm{Var}[\tau_{\lambda}^{*}(G)])$.
 
-  By the independent edge assumption, we have
-  \begin{align}
-    \mathbb{E}[h(Y_i, Y_j, Y_k) &= \mathbb{E}[Y_i]
-  \mathbb{E}[Y_j] \mathbb{E}[Y_k] \\ 
-  \mathbb{E}[h(Y_i, Y_j, Y_k) |
-  Y_i] &= Y_i \mathbb{E}[Y_j] \mathbb{E}[Y_k].
-  \end{align}
- Thus, for $t < t^{*}$, we have $\mathbb{E}[\tau_{\lambda}^{*}(G(t))] = \tbinom{n}{3} \langle
-  \lambda, \pi_{00} \rangle^{3}$ and
-  \begin{equation}
-    \begin{split}
-      \mathrm{Var}[\tau_{\lambda}^{*}(G(t))] &=
-      \mathrm{Var}\Bigl[\sum_{\{u,v,w\}} Y_{uv} \mathbb{E}[Y_{uw}]
-      \mathbb{E}[Y_{vw}]\Bigr] \\
-      &= (n-2)^{2} \langle \lambda, \pi_{00} \rangle^{4}
-      \mathrm{Var}\Bigl[\sum_{\{u,v\}} Y_{uv} \Bigr] \\
-      &= (n-2)^{2} \langle \lambda, \pi_{00} \rangle^{4} \tbinom{n}{2}
-      \langle \lambda, \eta_{00} \lambda \rangle.
-    \end{split}
-  \end{equation}
-  We now sketch the derivation of
-  $\mathrm{Var}[\tau_{\lambda}^{*}(G(t))]$ for $t = t^{*}$. We partition the set
-  $\{u,v\} \in \tbinom{V}{2}$ into the sets 
-\begin{gather*}
-\mathcal{S}_1 = \{ u,v \in [m]
-  \}, \\ \mathcal{S}_2 = \{ u \in [m], v \in [n] \setminus [m]\}, \\
-  \mathcal{S}_3 = \{ u, v \in [n] \setminus[m]\}.
-\end{gather*} Now, for $\{u,v\} \in \mathcal{S}_1$, we have
-\begin{equation}
-  \label{eq:58}
-  \begin{split}
-S_1 Y_{uv} &=\sum_{w \not = u,v} \mathbb{E}[h(Y_{uv}, Y_{uw}, Y_{vw})
-\, | \, Y_{uv}] \\
- &= ((m-2) \langle \lambda, \pi_{11} \rangle^{2} + (n-m)
-    \langle \lambda, \pi_{10} \rangle^{2})Y_{uv}.
-  \end{split}
-\end{equation}
-The above expression is reasoned as follows. If $w \in [m]$, then
-$\mathbb{E}[Y_{uw}] = \mathbb{E}[Y_{vw}] = \langle \lambda,
-\pi_{11} \rangle$ and there are $m-2$ possible choices for $w \in [m]$
-different from $u$ and $v$. If $w \in [n] \setminus [m]$, then
-$\mathbb{E}[Y_{vw}] = \mathbb{E}[Y_{uw}] = \langle \lambda, \pi_{10}
-\rangle$ and there are $n - m$ possible choices for $w$. Analogous
-reasoning gives the expressions for $S_2$ and $S_3$ in the statement
-of the lemma. % We also have
+%   By the independent edge assumption, we have
+%   \begin{align}
+%     \mathbb{E}[h(Y_i, Y_j, Y_k) &= \mathbb{E}[Y_i]
+%   \mathbb{E}[Y_j] \mathbb{E}[Y_k] \\ 
+%   \mathbb{E}[h(Y_i, Y_j, Y_k) |
+%   Y_i] &= Y_i \mathbb{E}[Y_j] \mathbb{E}[Y_k].
+%   \end{align}
+%  Thus, for $t < t^{*}$, we have $\mathbb{E}[\tau_{\lambda}^{*}(G(t))] = \tbinom{n}{3} \langle
+%   \lambda, \pi_{00} \rangle^{3}$ and
+%   \begin{equation}
+%     \begin{split}
+%       \mathrm{Var}[\tau_{\lambda}^{*}(G(t))] &=
+%       \mathrm{Var}\Bigl[\sum_{\{u,v,w\}} Y_{uv} \mathbb{E}[Y_{uw}]
+%       \mathbb{E}[Y_{vw}]\Bigr] \\
+%       &= (n-2)^{2} \langle \lambda, \pi_{00} \rangle^{4}
+%       \mathrm{Var}\Bigl[\sum_{\{u,v\}} Y_{uv} \Bigr] \\
+%       &= (n-2)^{2} \langle \lambda, \pi_{00} \rangle^{4} \tbinom{n}{2}
+%       \langle \lambda, \eta_{00} \lambda \rangle.
+%     \end{split}
+%   \end{equation}
+%   We now sketch the derivation of
+%   $\mathrm{Var}[\tau_{\lambda}^{*}(G(t))]$ for $t = t^{*}$. We partition the set
+%   $\{u,v\} \in \tbinom{V}{2}$ into the sets 
+% \begin{gather*}
+% \mathcal{S}_1 = \{ u,v \in [m]
+%   \}, \\ \mathcal{S}_2 = \{ u \in [m], v \in [n] \setminus [m]\}, \\
+%   \mathcal{S}_3 = \{ u, v \in [n] \setminus[m]\}.
+% \end{gather*} 
+% We can thus decompose $\mathrm{Var}[\tau_{\lambda}^{*}(G(t))]$ as 
+% \begin{equation}
+%   \begin{split}
+%   \mathrm{Var}[\tau_{\lambda}^{*}(G(t))] &= S_1^{2} \mathrm{Var}[\sum_{\{u,v\} \in \mathcal{S}_1} Y_{uv}] +
+%   S_2^{2}
+%   \mathrm{Var}[\sum_{\{u,v\} \in \mathcal{S}_2} Y_{uv}] \\ &+
+%   S_3^{2}
+%   \mathrm{Var}[\sum_{\{u,v\} \in \mathcal{S}_3} Y_{uv}] 
+%   \end{split}
+% \end{equation}
+% Now, for $\{u,v\} \in \mathcal{S}_1$, we have
+% \begin{equation}
+%   \label{eq:58}
+%   \begin{split}
+% S_1 Y_{uv} &=\sum_{w \not = u,v} \mathbb{E}[h(Y_{uv}, Y_{uw}, Y_{vw})
+% \, | \, Y_{uv}] \\
+%  &= ((m-2) \langle \lambda, \pi_{11} \rangle^{2} + (n-m)
+%     \langle \lambda, \pi_{10} \rangle^{2})Y_{uv}.
+%   \end{split}
+% \end{equation}
+% The above expression is reasoned as follows. If $w \in [m]$, then
+% $\mathbb{E}[Y_{uw}] = \mathbb{E}[Y_{vw}] = \langle \lambda,
+% \pi_{11} \rangle$ and there are $m-2$ possible choices for $w \in [m]$
+% different from $u$ and $v$. If $w \in [n] \setminus [m]$, then
+% $\mathbb{E}[Y_{vw}] = \mathbb{E}[Y_{uw}] = \langle \lambda, \pi_{10}
+% \rangle$ and there are $n - m$ possible choices for $w$. Analogous
+% reasoning gives the expressions for $S_2$ and $S_3$ in the statement
+% of the lemma.
+
+% We also have
 %  \begin{equation}
@@
 %  \end{equation}
+% and thus
+% \begin{equation*}
+%   \begin{split}
+%     \mathrm{Var}[\tau_{\lambda}^{*}(G(t))] &=
+%     \tbinom{m}{2} \langle \lambda, \eta_{00} \lambda \rangle S_1^{2} +
+%     m(n-m) \langle \lambda, \eta_{01} \lambda \rangle S_2^{2} \\ &+
+%     \tbinom{n-m}{2} \langle \lambda, \eta_{00} \lambda \rangle S_3^{2}
+%   \end{split}
+% \end{equation*}
+% as desired. To complete the proof one must show that
+% $\mathrm{Var}[\tau_{\lambda}(G) - \tau_{\lambda}^{*}(G)] =
+% o(\mathrm{Var}[\tau_{\lambda}^{*}(G)])$ and this follows directly from
+% the argument in \cite{nowicki88:_subgr_u_statis_method}
+% or \cite{rukhin09:_asymp_analy_various_statis_random_graph_infer}.
+% \end{IEEEproof}
+% \begin{IEEEproof}[Proposition~\ref{prop:3}]
+%   Let $v \in V(t)$ and denote by $d_{\lambda}(v;t)$ the (fused) degree
+%   of vertex $v$, i.e.,
+%   \begin{equation*}
+%     d_{\lambda}(v;t) = \sum_{w \in N(v)} \langle \lambda,
+%     \Gamma_{vw} \rangle.
+%   \end{equation*}
+%   For $t < t^{*}$, each of the $\Gamma_{vw}$ is a multinomial
+%   trial with probability vector $\pi_{00}$. The following statements are
+%   made as $n \rightarrow \infty$ for fixed
+%   $K$.  By the central limit theorem, we have
+%   \begin{equation}
+%     \label{eq:17}
+%     \frac{d_{\lambda}(v;t) - (n-1) \langle \lambda, \pi_{00}
+%       \rangle}{\sqrt{(n-1) \langle \lambda, \eta_{00} \lambda \rangle}}
+%     \overset{\mathrm{d}}{\longrightarrow} \mathcal{N}(0, 1).
+%   \end{equation}
+%   We can thus consider the degree sequence of $G(t)$ for $t < t^{*}$
+%   as a sequence of {\em dependent} normally distributed random
+%   variables. By an argument analogous to the argument for
+%   Erd\"{o}s-Renyi random graphs in \cite[\S
+%   III.1]{bollobas85:_random_graph} we can show that the dependency
+%   among the $\{d_{\lambda}(v;t)\}_{v \in V(t)}$ can be
+%   ignored. Another way of doing this is to note that the covariance
+%   between $X_u$ and $X_v$, where $X_u$ and $X_v$ are the ratio in
+%   Eq.~\eqref{eq:17} for vertices $u$ and $v$, is given by
+%   \begin{equation}
+%     \label{eq:63}
+%     r = \mathrm{Cov}(X_u,X_v) = 
+%     \frac{3 \langle \lambda, \pi_{00} \rangle}{\sqrt{(n-1)
+%         \langle \lambda, \eta_{00} \lambda \rangle}}.
+%   \end{equation}
+%   Because $r \log{n} \rightarrow 0$ as $n \rightarrow \infty$, the
+%   sample maximum of the $X_u$ converges to the sample maximum of a
+%   sequence of {\em independent} $\mathcal{N}(0,1)$ random variables.
+%   $d_{\lambda}(v;t)$, can thus be considered as a sequence
+%   of independent random variables from a normal distribution. It is
+%   well known that the sample maximum of standard normal random
+%   variables converges weakly to a Gumbel distribution \cite[\S
+%   2.3]{galambos87:_asymp_theor_extrem_order_statis}. It is, however,
+%   not clear whether the convergence of $\Delta_{\lambda}(t)$ to a
+%   Gumbel distribution continues to hold under the composition of
+%   weak convergence as outlined above. We avoid this problem by
+%   showing directly that
+%   \begin{equation}
+%     \label{eq:22}
+%     \mathbb{P}\Bigl(\tfrac{\Delta_{\lambda}(t) - (n-1)
+%       \langle \lambda, \pi_{00} \rangle}{\sqrt{(n-1) \langle
+%         \lambda, \eta_{00} \lambda \rangle}} \leq a_n + b_n x\Big)
+%     \rightarrow 
+%     e^{-e^{-x}}. 
+%   \end{equation}
+%   Let $\zeta_v = \tfrac{d_{\lambda}(v;t) - (n-1) \langle \lambda,
+%     \pi_{00} \rangle}{\sqrt{(n-1) \langle \lambda, \eta_{00} \lambda
+%       \rangle}}$ and $F_n(u) = \mathbb{P}(\zeta_v \leq u)$. If $n
+%   \rightarrow \infty$ and $u = O(\sqrt{\log{n}})$, we have the
+%   following moderate deviations result \cite[Theorem~2, \S
+%   XVI.7]{feller71:_introd_probab_theor_its_applic,rubin65:_probab}.
+%   \begin{equation}
+%     \label{eq:23}
+%     \frac{1 - F_{n}(u)}{1 - \Phi(u)} = \Bigl[1 + (C\tfrac{u^{3}}{\sqrt{n}}) + O(\tfrac{u^{6}}{n}) \Bigr]
+%   \end{equation}
+%   for some constant $C$. Letting $u_n = a_n + b_n x$ in
+%   Eq.~\eqref{eq:23}, we have
+%   \begin{equation*}
+%     \begin{split}
+%       F_n(u_n) &= 1 - (1 - \Phi(u_n))(1 + C \tfrac{u_n^{3}}{\sqrt{n}} +
+%       O(\tfrac{u_n^{6}}{n})) \\
+%       &= \Phi(u_n) + (1 - \Phi(u_n))(C \tfrac{u_n^{3}}{\sqrt{n}} +
+%       O(\tfrac{u_n^6}{n})) \\
+%       &= \Phi(u_n) + O(\tfrac{1}{u_n n^{1- \delta}})(C \tfrac{u_n^{3}}{\sqrt{n}} +
+%       O(\tfrac{u_n^6}{n})) \\
+%       &= \Phi(u_n) + O(\tfrac{u_n^{5}}{n^{3/2 - \delta}})
+%     \end{split}
+%   \end{equation*}
+%   for some sufficiently small $\delta > 0$. We therefore have
+%   \begin{equation}
+%     \label{eq:25}
+%     \begin{split}
+%       \mathbb{P}(\max_{v \in [n]} \zeta(v) \leq u_n) &= (F_n(u_n))^{n} \\
+%       &= \Bigl[\Phi(u_n) + O(\tfrac{u_n^{5}}{n^{3/2 - \delta}})\Bigr]^{n} \\
+%       &= (\Phi(u_n))^{n} + O(\tfrac{u_n^{5}}{n^{1/2 - \delta}}) \\
+%       & \rightarrow e^{-e^{-x}}. 
+%     \end{split}
+%   \end{equation}
+%   Eq.~\eqref{eq:22} is established and we obtain the limiting Gumbel distribution for
+%   $\Delta_{\lambda}(t)$ for $t < t^{*}$ in Eq.~\eqref{eq:14}.
 
-We therefore have
-\begin{equation*}
-%  \label{eq:60}
-  \begin{split}
-  \mathrm{Var}[\tau_{\lambda}^{*}(G(t))] &= %\mathrm{Var}\Bigl[\sum_{\{u,v,w\}} Y_{uv} \mathbb{E}[Y_{uw}]
-      % \mathbb{E}[Y_{vw}]\Bigr] \\ &=
-      S_1^{2} \mathrm{Var}[\sum_{\{u,v\} \in \mathcal{S}_1} Y_{uv}] +
-      S_2^{2}
-      \mathrm{Var}[\sum_{\{u,v\} \in \mathcal{S}_2} Y_{uv}] \\ &+
-      S_3^{2}
-      \mathrm{Var}[\sum_{\{u,v\} \in \mathcal{S}_3} Y_{uv}]  \\ &=
-       \tbinom{m}{2} \langle \lambda, \eta_{00} \lambda \rangle S_1^{2} +
-       m(n-m) \langle \lambda, \eta_{01} \lambda \rangle S_2^{2} \\ &+
-       \tbinom{n-m}{2} \langle \lambda, \eta_{00} \lambda \rangle S_3^{2}
-  \end{split}
-\end{equation*}
-as desired. To complete the proof one must show that
-$\mathrm{Var}[\tau_{\lambda}(G) - \tau_{\lambda}^{*}(G)] =
-o(\mathrm{Var}[\tau_{\lambda}^{*}(G)])$ and this follows directly from
-the argument in \cite{nowicki88:_subgr_u_statis_method}
-or \cite{rukhin09:_asymp_analy_various_statis_random_graph_infer}.
-\end{IEEEproof}
-\begin{IEEEproof}[Proposition~\ref{prop:3}]
-  Let $v \in V(t)$ and denote by $d_{\lambda}(v;t)$ the (fused) degree
-  of vertex $v$, i.e.,
-  \begin{equation*}
-    d_{\lambda}(v;t) = \sum_{w \in N(v)} \langle \lambda,
-    \Gamma_{vw} \rangle.
-  \end{equation*}
-  For $t < t^{*}$, each of the $\Gamma_{vw}$ is a multinomial
-  trial with probability vector $\pi_{00}$. The following statements are
-  made as $n \rightarrow \infty$ for fixed
-  $K$.  By the central limit theorem, we have
-  \begin{equation}
-    \label{eq:17}
-    \frac{d_{\lambda}(v;t) - (n-1) \langle \lambda, \pi_{00}
-      \rangle}{\sqrt{(n-1) \langle \lambda, \eta_{00} \lambda \rangle}}
-    \overset{\mathrm{d}}{\longrightarrow} \mathcal{N}(0, 1).
-  \end{equation}
-  We can thus consider the degree sequence of $G(t)$ for $t < t^{*}$
-  as a sequence of {\em dependent} normally distributed random
-  variables. By an argument analogous to the argument for
-  Erd\"{o}s-Renyi random graphs in \cite[\S
-  III.1]{bollobas85:_random_graph} we can show that the dependency
-  among the $\{d_{\lambda}(v;t)\}_{v \in V(t)}$ can be
-  ignored. Another way of doing this is to note that the covariance
-  between $X_u$ and $X_v$, where $X_u$ and $X_v$ are the ratio in
-  Eq.~\eqref{eq:17} for vertices $u$ and $v$, is given by
-  \begin{equation}
-    \label{eq:63}
-    r = \mathrm{Cov}(X_u,X_v) = 
-    \frac{3 \langle \lambda, \pi_{00} \rangle}{\sqrt{(n-1)
-        \langle \lambda, \eta_{00} \lambda \rangle}}.
-  \end{equation}
-  Because $r \log{n} \rightarrow 0$ as $n \rightarrow \infty$, the
-  sample maximum of the $X_u$ converges to the sample maximum of a
-  sequence of {\em independent} $\mathcal{N}(0,1)$ random variables.
-  $d_{\lambda}(v;t)$, can thus be considered as a sequence
-  of independent random variables from a normal distribution. It is
-  well known that the sample maximum of standard normal random
-  variables converges weakly to a Gumbel distribution \cite[\S
-  2.3]{galambos87:_asymp_theor_extrem_order_statis}. It is, however,
-  not clear whether the convergence of $\Delta_{\lambda}(t)$ to a
-  Gumbel distribution continues to hold under the composition of
-  weak convergence as outlined above. We avoid this problem by
-  showing directly that
-  \begin{equation}
-    \label{eq:22}
-    \mathbb{P}\Bigl(\tfrac{\Delta_{\lambda}(t) - (n-1)
-      \langle \lambda, \pi_{00} \rangle}{\sqrt{(n-1) \langle
-        \lambda, \eta_{00} \lambda \rangle}} \leq a_n + b_n x\Big)
-    \rightarrow 
-    e^{-e^{-x}}. 
-  \end{equation}
-  Let $\zeta_v = \tfrac{d_{\lambda}(v;t) - (n-1) \langle \lambda,
-    \pi_{00} \rangle}{\sqrt{(n-1) \langle \lambda, \eta_{00} \lambda
-      \rangle}}$ and $F_n(u) = \mathbb{P}(\zeta_v \leq u)$. If $n
-  \rightarrow \infty$ and $u = O(\sqrt{\log{n}})$, we have the
-  following moderate deviations result \cite[Theorem~2, \S
-  XVI.7]{feller71:_introd_probab_theor_its_applic,rubin65:_probab}.
-  \begin{equation}
-    \label{eq:23}
-    \frac{1 - F_{n}(u)}{1 - \Phi(u)} = \Bigl[1 + (C\tfrac{u^{3}}{\sqrt{n}}) + O(\tfrac{u^{6}}{n}) \Bigr]
-  \end{equation}
-  for some constant $C$. Letting $u_n = a_n + b_n x$ in
-  Eq.~\eqref{eq:23}, we have
-  \begin{equation*}
-    \begin{split}
-      F_n(u_n) &= 1 - (1 - \Phi(u_n))(1 + C \tfrac{u_n^{3}}{\sqrt{n}} +
-      O(\tfrac{u_n^{6}}{n})) \\
-      &= \Phi(u_n) + (1 - \Phi(u_n))(C \tfrac{u_n^{3}}{\sqrt{n}} +
-      O(\tfrac{u_n^6}{n})) \\
-      &= \Phi(u_n) + O(\tfrac{1}{u_n n^{1- \delta}})(C \tfrac{u_n^{3}}{\sqrt{n}} +
-      O(\tfrac{u_n^6}{n})) \\
-      &= \Phi(u_n) + O(\tfrac{u_n^{5}}{n^{3/2 - \delta}})
-    \end{split}
-  \end{equation*}
-  for some sufficiently small $\delta > 0$. We therefore have
-  \begin{equation}
-    \label{eq:25}
-    \begin{split}
-      \mathbb{P}(\max_{v \in [n]} \zeta(v) \leq u_n) &= (F_n(u_n))^{n} \\
-      &= \Bigl[\Phi(u_n) + O(\tfrac{u_n^{5}}{n^{3/2 - \delta}})\Bigr]^{n} \\
-      &= (\Phi(u_n))^{n} + O(\tfrac{u_n^{5}}{n^{1/2 - \delta}}) \\
-      & \rightarrow e^{-e^{-x}}. 
-    \end{split}
-  \end{equation}
-  Eq.~\eqref{eq:22} is established and we obtain the limiting Gumbel distribution for
-  $\Delta_{\lambda}(t)$ for $t < t^{*}$ in Eq.~\eqref{eq:14}.
-
-  The case when $t = t^{*}$ can be
-  derive in a similar manner. We first show that if $m =
-  \Omega(\sqrt{n \log{n}})$, then $\Delta_{\lambda}(v;t^{*})
-  \overset{\mathrm{d}}{\longrightarrow} \max_{v \in [m]}{d_{\lambda}(v;t^{*})}$ \cite[Lemma
-  3.1]{rukhin:_limit_distr_graph_scan_statis}.  
-  We then show, again by the 
-  central limit theorem that for $v \in [m]$, $\tfrac{d_{\lambda}(v;t^{*}) -
-    \mu_2}{\sigma_2} \overset{\mathrm{d}}{\longrightarrow} N(0,1)$. It then follows, similar
-  to our previous reasoning for the case where $t < t^{*}$, that
-  $\max_{v \in [m]} \tfrac{d_{\lambda}(v;t^{*}) -
-    \mu_2}{\sigma_2} \overset{\mathrm{d}}{\longrightarrow}\mathcal{G}(a_m,b_m)$ and we obtain
-  Eq.~\eqref{eq:14} for $t = t^{*}$.  
-\end{IEEEproof}
-\begin{IEEEproof}[Theorem~\ref{thm:8}]
-  Let $ X \sim \mathcal{G}(\alpha, \beta)$. We consider the
-  normalization $\tfrac{X - \mu}{\sigma}$. We have
-  \begin{equation*}
-    \begin{split}
-    \mathbb{P}\Bigl[ \tfrac{X - \mu}{\sigma} \leq z\Bigr]  &= \mathbb{P}[X \leq z
-    \sigma + \mu] 
-    = e^{-e^{-(z \sigma + \mu - \alpha)/\beta}} \\
-      &= e^{- e^{-(z - (\alpha - \mu)/\sigma)/(\beta/\sigma)}}.
-    \end{split}
-  \end{equation*}
-  Thus, $\tfrac{X - \mu}{\sigma} \sim \mathcal{G}(\tfrac{\alpha -
-    \mu}{\sigma}, \tfrac{\beta}{\sigma})$. Because the sample
-  mean and the sample variance are consistent estimators, the claim
-  follows after an application of Slutsky's theorem.
-\end{IEEEproof}
-\begin{IEEEproof}[Lemma~\ref{lem:5}]
-Let $\phi_{\lambda}(v;t) = \psi_{\lambda}(v;t) - d_{\lambda}(v;t)$ be
-the (fused) locality statistics for
-vertex $v$ at time $t$ not including the (fused) degree of $v$, i.e.,
-\begin{equation}
-  \label{eq:11}
-  \phi_{\lambda}(v;t) = \sum_{\substack{uw
-      \in N(v) \\ u,w \not = v}} \langle \lambda,
-  \Gamma_{uw} \rangle.
-\end{equation}
-The following statements are conditional on $|N(v)| = l$. First
-of all, we have
-\begin{equation*}
-  \phi_{\lambda}(v;t) = \sum_{k=1}^{K}{\lambda_k z_k}
-\end{equation*}
-where the $(z_1, \dots, z_K)$ are distributed as
-\begin{gather*}
-  (z_1,z_2,\dots,z_K) \sim \textrm{multinomial}\Bigl(
-  \tbinom{l}{2}, \pi_{00}\Bigr). 
-\end{gather*}
-By the central limit theorem, we have
-\begin{equation*}
-  \frac{\phi_\lambda(v;t) - \tbinom{l}{2} \langle \lambda, \pi_{00}
-    \rangle}{\sqrt{\tbinom{l}{2} \langle \lambda, \eta_{00} \lambda \rangle}}
-  \overset{\mathrm{d}}{\longrightarrow} \mathcal{N}(0,1).
-\end{equation*}
-Let $Y_{l} = C_{00} \mathrm{Bin}(\tbinom{l}{2}, p_{00})$. Then $\mathbb{E}[Y_l] = \tbinom{l}{2} \langle \lambda, \pi_{00} \rangle$
-and $\mathrm{Var}[Y_l] = \tbinom{l}{2} \langle \lambda,
-\eta_{00} \lambda \rangle$ and again by the central limit theorem, we have
-\begin{equation}
-  \label{eq:12}
-  \frac{\psi_{\lambda}(v;t) - \tbinom{l}{2} \langle \lambda, \pi_{00}
-    \rangle}{\sqrt{\tbinom{l}{2} \langle \lambda, \eta_{00} \lambda
-      \rangle}}   \overset{\mathrm{d}}{\longrightarrow} \frac{Y_l - \tbinom{l}{2} \langle \lambda, \pi_{00} \rangle}{\sqrt{\tbinom{l}{2}
-    \langle \lambda, \eta_{00} \lambda \rangle}}.
-\end{equation}
-Eq.~\eqref{eq:12} states that the locality statistics for our
-attributed random graphs model with $t < t^{*}$
-can be approximated by the locality statistics for an Erd\"{o}s-Renyi
-graph with edge probability $p_{00}$. The lemma then follows
-from Theorem~1.1 in \cite{rukhin:_limit_distr_graph_scan_statis}.
-\end{IEEEproof}
-\begin{IEEEproof}[Lemma~\ref{lem:6}]
-  For ease of exposition we drop the index $t^{*}$ from our discussion. Let
-  $\phi_{\lambda}(v) = \psi_{\lambda}(v) - d_{\lambda}(v)$. Let
-  $M(v)$ be the number of neighbors of $v$ that lies in $[m]$ and
-  $W(v)$ be the number of neighbors of $v$ that lies in $[n]
-\setminus [m]$. The following statements are conditional on
-$M(v) = l_{\zeta}$ and $W(v) = l_{\xi}$. We have
-\begin{equation}
-  \phi_{\lambda}(v) = \sum_{k=1}^{K} \lambda_k ( y^{(\zeta)}_k +
-  y^{(\xi)}_k + y^{(\omega)}_k)
-\end{equation}
-where $(y^{(\zeta)}_1, \dots, y^{(\zeta)}_K)$, $(y^{(\xi)}_1,\dots,
- y^{(\xi)}_K)$,  $(y^{(\omega)}_1, \dots, y^{(\omega)}_K)$ are
- distributed as
-\begin{gather*}
-(y^{(\zeta)}_1,\dots,y^{(\zeta)}_K) \sim \textrm{multinomial}\Bigl(
-\tbinom{l_\zeta}{2}, \pi_{11}\Bigr) \\ 
-(y^{(\xi)}_1,\dots,y^{(\xi)}_K) \sim \textrm{multinomial}\Bigl(
-\tbinom{l_\xi}{2}, \pi_{00}\Bigr) \\
-(y^{(\omega)}_1,\dots,y^{(\omega)}_m) \sim \textrm{multinomial}\Bigl(
-l_\zeta l_\xi, \pi_{10}\Bigr).
-\end{gather*}
-Let $\rho$ and $\varsigma$ be defined as
-\begin{gather*}
-  \rho = \langle \lambda, \tbinom{l_{\zeta}}{2} \pi_{11} +
-  \tbinom{l_{\xi}}{2} \pi_{00} + l_{\zeta} l_{\xi} \pi_{10} \rangle \\
-  \varsigma = \langle \lambda, \Bigl(\tbinom{l_{\zeta}}{2} \eta_{11} +
-  \tbinom{l_{\xi}}{2} \eta_{00} + l_{\zeta} l_{\xi} \eta_{10}\Bigr)
-  \lambda.
-  \rangle
-\end{gather*}
-By the central limit theorem, as $l_{\zeta} \rightarrow
-\infty$ and $l_{\xi} \rightarrow \infty$
-\begin{equation}
-  \label{eq:16}
-  \frac{\phi_{\lambda}(v) - \rho}{\varsigma}  \overset{\mathrm{d}}{\longrightarrow}  \mathcal{N}(0,1)
-\end{equation}
-Let $Y_{\zeta} \sim C_{11} \mathrm{Bin}\Bigl(\tbinom{l_{\zeta}}{2},
-p_{11}\Bigr)$, $Y_{\xi} \sim C_{00} \mathrm{Bin}\Bigl(\tbinom{l_\xi}{2},
-p_{00}\Bigr)$ and $Y_{\omega} \sim C_{10} \mathrm{Bin}\Bigl( l_{\zeta}
-l_{\xi}, p_{10} \Bigr)$. We also set $Y = Y_{\zeta} + Y_{\xi} +
-Y_{\omega}$. By the central limit theorem, we have
-\begin{equation}
-  \label{eq:21}
- \frac{\phi_{\lambda}(v) - \rho}{\varsigma}
- \overset{\mathrm{d}}{\longrightarrow}  \frac{Y - \rho}{\varsigma}.
-\end{equation}
-Eq.~\eqref{eq:21} states that the locality statistics
-$\phi_\lambda(v)$ for our attributed random graphs model at time $t =
-t^{*}$ can be approximated by the locality statistics $Y(v)$ for an
-unattributed kidney and egg model. The limiting distribution for the
-scan statistics in unattributed kidney-egg graphs had previously been
-considered in \cite{rukhin:_limit_distr_graph_scan_statis}. We
-provided a sketch of the arguments from
-\cite{rukhin:_limit_distr_graph_scan_statis} below, along with some
-minor changes to handle the case where the probability of
-kidney-kidney and
-kidney-egg connections are different. \\ \\
-\noindent
-Let $G$ be an instance of
-$\kappa(n,m,p_{11}, p_{10}, p_{00})$, an unattributed kidney-egg graph
-with the probability of egg-egg, egg-kidney, and kidney-kidney
-connections being $p_{11}$, $p_{10}$, and $p_{00}$,
-respectively. $D(v) = M(v) + W(v)$ is then the degree of $v$ in
-$G$. We now show two inequalities relating the tail distribution of
-$\Delta(G)$ and $\Upsilon(G) = \max_{v \in V(G)} Y(v)$.
-\begin{gather}
-  \label{eq:27}
-    \limsup\,\, \mathbb{P}( \Upsilon(G) \geq a_{n,m} ) \leq \lim
-   \mathbb{P}( \Delta(G) \geq N_\kappa), \\
-   \label{eq:30}
-  \liminf\,\, \mathbb{P}( \Upsilon(G) \geq a_{n,m} ) \geq \lim \mathbb{P}(
-  \Delta(G) \geq N_{\kappa}).
-\end{gather}
-\begin{IEEEproof}[Eq.~\eqref{eq:27}]
- Let $C^{*} = \max\{C_{11},
-C_{10}, C_{00}\}$ and $d_{n,m} = \sqrt{2 a_{n,m}/C^{*}}$. We first
-note that
-\begin{equation*}
-\Upsilon(G) \geq a_{n,m} \Rightarrow C^{*} \tbinom{D(v)}{2} \geq
-a_{n,m} \Rightarrow D(v) \geq d_{n,m}.
-\end{equation*}
-Let us define $h(v) = \mathbb{E}[Y(v)]$, i.e., 
-\begin{equation*}
-  \begin{split}
-  h(v) = C_{00}p_{00} \tbinom{D(v)}{2} &+ (C_{11} p_{11} - C_{00}
-  p_{00}) \tbinom{M(v)}{2} \\ &+ (C_{10} p_{10} - C_{00} p_{00}) M(v)
-  W(v).
-  \end{split}
-\end{equation*}
-We then have
-  \begin{equation*}
-    \label{eq:31}
-    \begin{split}
-    \mathbb{P}(\Upsilon(G) \geq a_{n,m}) &= \mathbb{P}\Bigl( \bigcup_{v
-      \in V(G)} Y(v) \geq a_{n,m}\Bigr) \\
-    &= \mathbb{P}\Bigl( \bigcup_{v
-      \in V(G)} Y(v) \geq a_{n,m}, \, D(v) \geq d_{n,m} \Bigr) \\
-    &\leq P_1 + P_2
-    \end{split}
-  \end{equation*}
-  where 
-  \begin{align*}
-    \vartheta_n &= C_{00} \Bigl[ \tbinom{n}{2} p_{00} (1 -
-    p_{00})\Bigr]^{1/2} \log{n} \\
-    P_1 &= \mathbb{P}(\bigcup_{v \in V(G)} D(v) \geq d_{n,m}, h(v) \geq
-    a_{n,m} - \vartheta_n) \\
-    P_2 &= \mathbb{P}(\bigcup_{v \in V(G)} D(v) \geq d_{n,m},
-    Y(v) - h(v) \geq \vartheta_n).
-  \end{align*}
-  We now show that $P_2$ is negligible as $n \rightarrow \infty$. To
-  proceed, let $A$ be the event $\{M(v) = e, W(v) = f\}$ and let
-  $p_{e,f} = \mathbb{P}(A)$. $P_2$ can then be bounded as follows
-\begin{equation*}
-  \begin{split}
-    \frac{P_2}{n} & \leq \sum_{e + f \geq
-        d_{n,m}}{\mathbb{P}( Y(v) - h(v) \geq
-      \vartheta_{n} \, | \, A)} p_{e,f}  \\
-  &=  \sum_{e + f \geq d_{n,m}}{\mathbb{P}\Bigl(
-    \tfrac{Y(v) - h(v)}{\mathrm{Var}[Y(v)]^{1/2}} \geq
-    \tfrac{\vartheta_n}{\mathrm{Var}[Y(v)]^{1/2}} \, \Bigl| \, A\Bigr) p_{e,f}} \\
-    &\leq \sum_{e + f \geq d_{n,m}} (1 + o(1))
-    \mathbb{P}(Z \geq \Theta(\log{n})) p_{e,f} \\ &= o(n^{-1}).
-  \end{split}
-\end{equation*}
-We now consider $P_1$. We note that $P_1 \leq R_1 + R_2$
-where
-\begin{align*}
-  R_1 &= \mathbb{P}\Bigl(\bigcup_{v \in [m]} D(v) \geq
-  d_{n,m}, h(v) \geq a_{n,m} - \vartheta_n \Bigr), \\  
-  R_2 &= \mathbb{P}\Bigl(\bigcup_{v \in [n] \setminus [m]} D(v) \geq
-  d_{n,m}, h(v) \geq a_{n,m} - \vartheta_n \Bigr).
-\end{align*}
-Let us define $g(v) = h(v) - C_{00}p_{00} \tbinom{D(v)}{2}$.
-$R_1$ is then bounded as follows
-\begin{equation}
-  \begin{split}
-    \label{eq:36}
-    R_1 &\leq \mathbb{P}\Bigl( \bigcup_{v \in [m]} h(v) \geq
-    a_{n,m} - \vartheta_{n} \Bigr) \\
-    % &\leq \mathbb{P}\Bigl( \bigcup_{v \in [n_1]}  C_{00} p_{00}
-    % \tbinom{D(v)}{2} \geq a_{n,m} - \vartheta_{n} - g(v) \Bigr) \\
-    &\leq \mathbb{P}\Bigl(\bigcup_{v \in [m]} D(v) \geq
-      \sqrt{\tfrac{2 (a_{n,m} - \vartheta_n -
-        g(v))}{C_{00} p_{00}}} \Bigr).
-  \end{split}
-\end{equation}
-We now consider the term $a_{n,m} - g(v)$. We have
-\begin{equation*}
-  \begin{split}
-  a_{n,m} - g(v) &= C_{00} p_{00} \tbinom{N_\kappa}{2} \\ &+ (C_{11}p_{11} -
-  C_{00} p_{00})(\tbinom{\mu_E}{2} - \tbinom{M(v)}{2})
-  \\ &+ (C_{10} p_{10} - C_{00} p_{00})(\mu_E\mu_F - M(v)W(v)).
-  \end{split}
-\end{equation*}
-Let $\mathfrak{E}$ and $\mathfrak{F}$ be sets of vertices defined by
-\begin{align}
-\mathfrak{E} &=
-\{v \colon |M(v) - \mu_E| \leq \sigma_E \log{m}\} \\ \mathfrak{F} &=
-\{v \colon |W(v) - \mu_F| \leq \sigma_F \log{(n-m)}\}.
-\end{align}
-Then we have, for $v \in \mathfrak{E} \cap \mathfrak{F}$
-\begin{equation}
-  \label{eq:34}
-  \begin{split}
-  a_{n,m} - g(v) =  C_{00} p_{00} \tbinom{N_\kappa}{2} &+
-  \Theta(m^{3/2} \log{m}) \\ &+ 
-  \Theta(m \sqrt{n - m}) \\
-  \end{split}
-\end{equation}
-When $m = \Omega(\sqrt{n \log n})$, Eq.~\eqref{eq:34} gives
-\begin{equation}
-  \label{eq:35}
-  a_{n,m} - g(v) = N_{\kappa}^{2}\Bigl(\tfrac{C_{00}p_{00}}{2} + O(n^{-1/2 - a}
-  \log{n})\Bigr).
-\end{equation}
-for some $a > 0$. The set $\{v \in [m]\}$ can be partition into
-$\{v \in [m] \cap (\mathfrak{E} \cap\mathfrak{F})\}$ and $\{v \in [m]
-\setminus (\mathfrak{E} \cap \mathfrak{F})\}$. We can show that
-$\mathbb{P}\{v \in [m] \setminus (\mathfrak{E} \cap \mathfrak{F})\} =
-o(1)$ by using a concentration inequality, e.g., Hoeffding's
-bound. We thus have
-\begin{equation}
-  \label{eq:37}
-  \begin{split}
-    R_1 &\leq \mathbb{P}\biggl( \bigcup_{\substack{v \in [m] \\ v
-        \in \mathfrak{E} \cap \mathfrak{F}}} D(v) \geq
-    N_{\kappa} \sqrt{1 + O(\tfrac{\log{n}}{n^{1/2+a}})} \Bigr) + o(n^{-1}) \\
-    & = \mathbb{P}\Bigl(\bigcup_{v \in [m]} D(v) \geq N_\kappa +
-    O(n^{1/2 - a} \log{n})\Bigr) + o(n^{-1}) \\
-    &= \mathbb{P}\Bigl(\Delta \geq \mu_{E+F} +
-    \sigma_{E+F}(z_m + O(\tfrac{\log{n}}{n^{a}}))\Bigr) + o(n^{-1}) \\ 
-    & \rightarrow \mathbb{P}(\Delta \geq N_{\kappa}).
-    \end{split}
-\end{equation}
-The same argument can be applied to $R_2$ to show that
-\begin{equation}
-  \label{eq:38}
-  R_2 \leq \mathbb{P}\Bigl(\bigcup_{v \in [n] \setminus [m]} D(v) \geq
-  N_{\kappa}(1 + o(1))\Bigr) = o(1).
-\end{equation}
-Eq.~\eqref{eq:27} is therefore established.
-\end{IEEEproof}
-\begin{IEEEproof}[Eq.~\eqref{eq:30}]
-  We start by noting that
-  \begin{equation*}
-    \begin{split}
-      \mathbb{P}(\Upsilon(G) \geq a_{n,m}) &=
-      \mathbb{P}\Bigl(\bigcup_{v \in [n]}Y(v) \geq
-      a_{n,m}\Bigr) \\
-      & \geq \mathbb{P}\Bigl(\bigcup_{v \in [m]}Y(v) \geq
-      a_{n,m}, D(v) \geq N_\kappa \Bigr) \\
-      & \geq \mathbb{P}\Bigl(\bigcup_{v \in [m]} D(v) \geq
-      N_\kappa\Bigr) \\ &- \mathbb{P}\Bigl( \bigcup_{v
-        \in [m]} Y(v) < a_{n,m}, D(v) \geq N_\kappa\Bigr).
-    \end{split}
-  \end{equation*}
-  We now show that $\mathbb{P}( \cup_{v
-        \in [m]} Y(v) < a_{n,m}, D(v) \geq N_\kappa) \rightarrow 0$ as
-      $n \rightarrow \infty$. Let $v \in [m]$ be arbitrary. It is then
-      sufficient to show that $m\mathbb{P}(Y(v) < a_{n,m}, D(v) \geq
-      N_{\kappa}) = o(1)$. We note that $\mathbb{P}(Y(v) < a_{n,m}, D(v) \geq
-      N_{\kappa})$ can be rewritten as
-      \begin{equation}
-        \label{eq:24}
-        \sum_{e + f \geq N_{\kappa}}{\mathbb{P}(Y(v) \leq a_{n,m} \, |
-          \, M(v) = e, W(v) =
-          f)}p_{e,f}.
-      \end{equation}
-We now split the indices set $e + f \geq N_{\kappa}$ in
-Eq.~\eqref{eq:24} into three parts $S_1$, $S_2$ and $S_3$, namely
-\begin{gather}
-  \label{eq:32}
-    S_1 = \{  e \geq
-        \mu_E + \sigma_E \log{m}\} \\
-    S_2 = \{  e \leq
-        \mu_E + \sigma_E \log{m},e + f \leq
-        N_\kappa + \varphi(n)\} \\
-    S_3 = \{ e \leq \mu_E + \sigma_E \log{m}, e + f \geq
-        N_\kappa + \varphi(n)\}
-\end{gather}
-where $\varphi(n) = \Theta(n^{1/2 - a})$ for some $a > 0$. We can then
-show that $m\mathbb{P}(M(v) = e,
-W(v) =f, \{e,f\} \in S_1) = o(1)$ by applying a concentration
-inequality. Similarly, $e + f \geq N_{\kappa}$ and $e \leq \mu_{E}
-+ \sigma_{E} \log{m}$ implies that
-\begin{equation}
-  \label{eq:33}
-  f \geq \mu_{F} + (z_{m} - o(1)) \sigma_F 
-\end{equation}
-and once again, by a concentration inequality, we can show that $m
-\mathbb{P}(M(v) = e, W(v) = f, \{e,f\} \in S_2) = o(1)$. As for
-$S_3$, from the fact that $e + f \geq N_{\kappa} + \varphi(n)$, we have the bound
-  \begin{equation}
-    \begin{split}
-    a_{n,m} - h(v) &\leq (C_{11} p_{11} - C_{10} p_{10})[m \sigma_E
-    \log{m} + \tbinom{\log{m}}{2}] \\ &- C_{00}p_{00} N_\kappa
-    \varphi(n).
-    \end{split}
-  \end{equation}
-  As $\mathrm{Var}[Y(v)] = \Theta(N_\kappa)$ for $\{M(v), W(v)\} \in
-  S_3$, we have
-  \begin{equation}
-    \label{eq:39}
-    \begin{split}
-      p_{S_3} &= \sum_{\{e,f\} \in S_3} \mathbb{P}( Y(v) < a_{n,m}) p_{e,f} 
-      \\ &\leq \sum_{\{e,f\} \in S_3} \mathbb{P}\Bigl(\tfrac{Y(v) - h(v))}{\mathrm{Var}[Y(v)]^{1/2}} \leq \tfrac{a_{n,m} -
-      h(v)}{\mathrm{Var}[Y(v)]^{1/2}}\Bigr)p_{e,f} \\
-    &\leq \sum_{\{e,f\} \in S_3} \mathbb{P}\Bigl[Z \leq
-    O\bigl(\tfrac{m^{3/2} \log m}{N_{\kappa}} - \varphi(n)\bigr)\Bigr]
-    p_{e,f}.
-    \end{split}
-  \end{equation}
-  We now set $a = \tfrac{1}{2(k+1)}$. Then for $m =
-  O(n^{k/(k+1)})$ and $\varphi(n) = O(n^{1/2 - a})$ we have
-  \begin{equation}
-    \label{eq:41}
-    \tfrac{m^{3/2} \log m}{N_\kappa} - \varphi(n) =
-    -O(n^{k/2(k+1))})
-  \end{equation}
-  which then implies
-  \begin{equation}
-    \label{eq:44}
-    m p_{S_3} \leq m \sum_{\{e,f\} \in S_3} \mathbb{P} \Bigl[Z \leq
-    - O(n^{k/2(k+1)}\Bigr] p_{e,f} = o(1).
-  \end{equation}
-  Thus $\mathbb{P}(Y(v) < a_{n,m}, D(v) \geq
-      N_{\kappa}) \rightarrow 0$ as desired.
-\end{IEEEproof}
-From Eq.~\eqref{eq:27} and Eq.~\eqref{eq:30}, we have
-\begin{equation}
-  \label{eq:40}
- \lim
-\mathbb{P}(\Upsilon(G) \geq a_{n,m}) = \lim \mathbb{P}(\Delta(G) \geq
-N_{\kappa}).
- \end{equation}
-Let $N_{\kappa,y} = N_\kappa + y \tfrac{\sigma_{E+F}}{\sqrt{2
-    \log{m}}}$. We now define $a_{n,m,y}$ as 
-\begin{equation*}
-  \langle \lambda, \pi_{00} \rangle
-    \tbinom{N_{\kappa,y}}{2} +
-  \langle \lambda, \pi_{11} - \pi_{00} \rangle \tbinom{\mu_E}{2}  +
-  \langle \lambda, \pi_{10} - \pi_{00} \rangle \mu_E \mu_F.
-\end{equation*}
-The above expression is equal to 
-\begin{equation}
-  \label{eq:57}
- a_{n,m} + \langle \lambda, \pi_{00} \rangle y
-  \frac{\sigma_{E+F}}{\sqrt{2 \log m}} \Bigl(N_{\kappa} + y
-  \frac{\sigma_{E+F}^{2}}{2 \sqrt{2 \log{m}}} + O(1) \Bigr).
-\end{equation}
-We thus have
-\begin{equation*}
-   a_{n,m,y} = a_{n,m} + (y + o(1)) b_{n,m}.
-\end{equation*}
-We therefore have
-\begin{equation*}
-  \begin{split}
-  \lim \mathbb{P}(\Upsilon(G) \geq a_{n,m,y}) &= 
-  \lim \mathbb{P}\Bigl(\frac{\Upsilon(G) - a_{n,m}}{b_{n,m}} \geq y \Bigr) \\
-  &= \lim \mathbb{P}(\Delta(G) \geq N_{\kappa,y}) \\
-  &= \lim \mathbb{P}\Bigl(\frac{\Delta(G) -
-    N_{\kappa}}{\sigma_{E+F}} \geq \frac{y}{\sqrt{2 \log{m}}} \Bigr). \\
-  \end{split}
-\end{equation*}
-Because $\Delta(G)$ converges weakly to a Gumbel
-distribution in the limit
-(\cite{bollobas85:_random_graph,rukhin:_limit_distr_graph_scan_statis}),
-we have
-\begin{equation}
-  \label{eq:47}
-  \mathbb{P}\Big(\frac{\Upsilon(G) - a_{n,m}}{b_{n,m}} \leq
-    y\Bigr) \rightarrow e^{- e^{-y}} 
-\end{equation}
-and Eq.~\eqref{eq:29} follows.
-\end{IEEEproof}
+%   The case when $t = t^{*}$ can be derive in a similar manner. We
+%   first show that if $m = \Omega(\sqrt{n \log n})$ then
+%   $\Delta_{\lambda}(v;t^{*}) \overset{\mathrm{d}}{\longrightarrow}
+%   \max_{v \in [m]}{d_{\lambda}(v;t^{*})}$ \cite[Lemma
+%   3.1]{rukhin:_limit_distr_graph_scan_statis}. We then show, again by
+%   the central limit theorem, that for $v \in [m]$,
+%   $\tfrac{d_{\lambda}(v;t^{*}) - \mu_2}{\sigma_2}
+%   \overset{\mathrm{d}}{\longrightarrow} \mathcal{N}(0,1)$. It then
+%   follows, similar to our previous reasoning for the case where $t <
+%   t^{*}$, that $\max_{v \in [m]} \tfrac{d_{\lambda}(v;t^{*}) -
+%     \mu_2}{\sigma_2}
+%   \overset{\mathrm{d}}{\longrightarrow}\mathcal{G}(a_m,b_m)$ and we
+%   obtain Eq.~\eqref{eq:14} for $t = t^{*}$.
+% \end{IEEEproof}
+% \begin{IEEEproof}[Theorem~\ref{thm:8}]
+%   Let $ X \sim \mathcal{G}(\alpha, \beta)$. We consider the
+%   normalization $\tfrac{X - \mu}{\sigma}$. We have
+%   \begin{equation*}
+%     \begin{split}
+%     \mathbb{P}\Bigl[ \tfrac{X - \mu}{\sigma} \leq z\Bigr]  &= \mathbb{P}[X \leq z
+%     \sigma + \mu] 
+%     = e^{-e^{-(z \sigma + \mu - \alpha)/\beta}} \\
+%       &= e^{- e^{-(z - (\alpha - \mu)/\sigma)/(\beta/\sigma)}}.
+%     \end{split}
+%   \end{equation*}
+%   Thus, $\tfrac{X - \mu}{\sigma} \sim \mathcal{G}(\tfrac{\alpha -
+%     \mu}{\sigma}, \tfrac{\beta}{\sigma})$. Because the sample
+%   mean and the sample variance are consistent estimators, the claim
+%   follows after an application of Slutsky's theorem.
+% \end{IEEEproof}
+% \begin{IEEEproof}[Lemma~\ref{lem:5}]
+% Let $\phi_{\lambda}(v;t) = \psi_{\lambda}(v;t) - d_{\lambda}(v;t)$ be
+% the (fused) locality statistics for
+% vertex $v$ at time $t$ not including the (fused) degree of $v$, i.e.,
+% \begin{equation}
+%   \label{eq:11}
+%   \phi_{\lambda}(v;t) = \sum_{\substack{uw
+%       \in N(v) \\ u,w \not = v}} \langle \lambda,
+%   \Gamma_{uw} \rangle.
+% \end{equation}
+% The following statements are conditional on $|N(v)| = l$. First
+% of all, we have
+% \begin{equation*}
+%   \phi_{\lambda}(v;t) = \sum_{k=1}^{K}{\lambda_k z_k}
+% \end{equation*}
+% where the $(z_1, \dots, z_K)$ are distributed as
+% \begin{gather*}
+%   (z_1,z_2,\dots,z_K) \sim \textrm{multinomial}\Bigl(
+%   \tbinom{l}{2}, \pi_{00}\Bigr). 
+% \end{gather*}
+% By the central limit theorem, we have
+% \begin{equation*}
+%   \frac{\phi_\lambda(v;t) - \tbinom{l}{2} \langle \lambda, \pi_{00}
+%     \rangle}{\sqrt{\tbinom{l}{2} \langle \lambda, \eta_{00} \lambda \rangle}}
+%   \overset{\mathrm{d}}{\longrightarrow} \mathcal{N}(0,1).
+% \end{equation*}
+% Let $\lambda^{(2)}$ be the element-wise square of $\lambda$. Define
+% $C_{00}$ and $p_{00}$ to be 
+%  \begin{gather}
+%    \label{eq:26}
+%    C_{00} = \tfrac{\langle \lambda^{(2)}, \pi_{00} \rangle}{\langle \lambda,
+%      \pi_{00}\rangle}, \quad p_{00} = \tfrac{(\langle \lambda, \pi_{00}
+%      \rangle)^{2}}{\langle \lambda^{(2)},\, \pi_{00} \rangle}.
+%  \end{gather}
+%  We note that $p_{00} \in [0,1]$. Now let $Y_{l} = C_{00}
+%  \mathrm{Bin}(\tbinom{l}{2}, p_{00})$. Then $\mathbb{E}[Y_l] =
+%  \tbinom{l}{2} \langle \lambda, \pi_{00} \rangle$ and
+%  $\mathrm{Var}[Y_l] = \tbinom{l}{2} \langle \lambda, \eta_{00} \lambda
+%  \rangle$ and again by the central limit theorem, we have
+% \begin{equation}
+%   \label{eq:12}
+%   \frac{\psi_{\lambda}(v;t) - \tbinom{l}{2} \langle \lambda, \pi_{00}
+%     \rangle}{\sqrt{\tbinom{l}{2} \langle \lambda, \eta_{00} \lambda
+%       \rangle}}   \overset{\mathrm{d}}{\longrightarrow} \frac{Y_l -
+%     \tbinom{l}{2} \langle \lambda, \pi_{00} \rangle}{\sqrt{\tbinom{l}{2}
+%     \langle \lambda, \eta_{00} \lambda \rangle}}.
+% \end{equation}
+% Eq.~\eqref{eq:12} states that the locality statistics for our
+% attributed random graphs model with $t < t^{*}$
+% can be approximated by the locality statistics for an Erd\"{o}s-Renyi
+% graph with edge probability $p_{00}$. The lemma then follows
+% from Theorem~1.1 in \cite{rukhin:_limit_distr_graph_scan_statis}.
+% \end{IEEEproof}
+% \begin{IEEEproof}[Lemma~\ref{lem:6}]
+%   For ease of exposition we drop the index $t^{*}$ from our discussion. Let
+%   $\phi_{\lambda}(v) = \psi_{\lambda}(v) - d_{\lambda}(v)$. Let
+%   $M(v)$ be the number of neighbors of $v$ that lies in $[m]$ and
+%   $W(v)$ be the number of neighbors of $v$ that lies in $[n]
+% \setminus [m]$. The following statements are conditional on
+% $M(v) = l_{\zeta}$ and $W(v) = l_{\xi}$. We have
+% \begin{equation}
+%   \phi_{\lambda}(v) = \sum_{k=1}^{K} \lambda_k ( y^{(\zeta)}_k +
+%   y^{(\xi)}_k + y^{(\omega)}_k)
+% \end{equation}
+% where $(y^{(\zeta)}_1, \dots, y^{(\zeta)}_K)$, $(y^{(\xi)}_1,\dots,
+%  y^{(\xi)}_K)$,  $(y^{(\omega)}_1, \dots, y^{(\omega)}_K)$ are
+%  distributed as
+% \begin{gather*}
+% (y^{(\zeta)}_1,\dots,y^{(\zeta)}_K) \sim \textrm{multinomial}\Bigl(
+% \tbinom{l_\zeta}{2}, \pi_{11}\Bigr) \\ 
+% (y^{(\xi)}_1,\dots,y^{(\xi)}_K) \sim \textrm{multinomial}\Bigl(
+% \tbinom{l_\xi}{2}, \pi_{00}\Bigr) \\
+% (y^{(\omega)}_1,\dots,y^{(\omega)}_m) \sim \textrm{multinomial}\Bigl(
+% l_\zeta l_\xi, \pi_{10}\Bigr).
+% \end{gather*}
+% Let $\rho$ and $\varsigma$ be defined as
+% \begin{gather*}
+%   \rho = \langle \lambda, \tbinom{l_{\zeta}}{2} \pi_{11} +
+%   \tbinom{l_{\xi}}{2} \pi_{00} + l_{\zeta} l_{\xi} \pi_{10} \rangle \\
+%   \varsigma = \langle \lambda, \Bigl(\tbinom{l_{\zeta}}{2} \eta_{11} +
+%   \tbinom{l_{\xi}}{2} \eta_{00} + l_{\zeta} l_{\xi} \eta_{10}\Bigr)
+%   \lambda.
+%   \rangle
+% \end{gather*}
+% By the central limit theorem, as $l_{\zeta} \rightarrow
+% \infty$ and $l_{\xi} \rightarrow \infty$
+% \begin{equation}
+%   \label{eq:16}
+%   \frac{\phi_{\lambda}(v) - \rho}{\varsigma}  \overset{\mathrm{d}}{\longrightarrow}  \mathcal{N}(0,1)
+% \end{equation}
+% Let $\lambda^{(2)}$ be the
+% element-wise square of $\lambda$. Define $C_{00}$, $C_{01}$, $C_{11}$
+% and $p_{00}$, $p_{01}$, $p_{11}$ to be
+%  \begin{gather}
+%    \label{eq:18}
+%    C_{00} = \tfrac{\langle \lambda^{(2)}, \pi_{00} \rangle}{\langle \lambda,
+%      \pi_{00}\rangle}; \quad p_{00} = \tfrac{(\langle \lambda, \pi_{00}
+%      \rangle)^{2}}{\langle \lambda^{(2)},\, \pi_{00} \rangle} \\
+%  C_{11} = \tfrac{\langle \lambda^{(2)}, \pi_{11} \rangle}{\langle \lambda,
+%      \pi_{11}\rangle}; \quad p_{11} = \tfrac{(\langle \lambda, \pi_{11}
+%      \rangle)^{2}}{\langle \lambda^{(2)},\, \pi_{11} \rangle} \\
+%  C_{10} = \tfrac{\langle \lambda^{(2)}, \pi_{11} \rangle}{\langle \lambda,
+%      \pi_{10}\rangle}; \quad p_{10} = \tfrac{(\langle \lambda, \pi_{10}
+%      \rangle)^{2}}{\langle \lambda^{(2)},\, \pi_{10} \rangle} 
+%  \end{gather}
+%  We note that $p_{00}$, $p_{01}$, and $p_{11}$ are all elements of
+%  $[0,1]$. Now let $Y_{\zeta} \sim C_{11}
+%  \mathrm{Bin}\Bigl(\tbinom{l_{\zeta}}{2}, p_{11}\Bigr)$, $Y_{\xi} \sim
+%  C_{00} \mathrm{Bin}\Bigl(\tbinom{l_\xi}{2}, p_{00}\Bigr)$ and
+%  $Y_{\omega} \sim C_{10} \mathrm{Bin}\Bigl( l_{\zeta} l_{\xi}, p_{10}
+%  \Bigr)$. We also set $Y = Y_{\zeta} + Y_{\xi} + Y_{\omega}$. By the
+%  central limit theorem, we have
+% \begin{equation}
+%   \label{eq:21}
+%  \frac{\phi_{\lambda}(v) - \rho}{\varsigma}
+%  \overset{\mathrm{d}}{\longrightarrow}  \frac{Y - \rho}{\varsigma}.
+% \end{equation}
+% Eq.~\eqref{eq:21} states that the locality statistics
+% $\phi_\lambda(v)$ for our attributed random graphs model at time $t =
+% t^{*}$ can be approximated by the locality statistics $Y(v)$ for an
+% unattributed kidney and egg model. The limiting distribution for the
+% scan statistics in unattributed kidney-egg graphs had previously been
+% considered in \cite{rukhin:_limit_distr_graph_scan_statis}. We
+% provided a sketch of the arguments from
+% \cite{rukhin:_limit_distr_graph_scan_statis} below, along with some
+% minor changes to handle the case where the probability of
+% kidney-kidney and
+% kidney-egg connections are different. \\ \\
+% \noindent
+% Let $G$ be an instance of
+% $\kappa(n,m,p_{11}, p_{10}, p_{00})$, an unattributed kidney-egg graph
+% with the probability of egg-egg, egg-kidney, and kidney-kidney
+% connections being $p_{11}$, $p_{10}$, and $p_{00}$,
+% respectively. $D(v) = M(v) + W(v)$ is then the degree of $v$ in
+% $G$. We now show two inequalities relating the tail distribution of
+% $\Delta(G)$ and $\Upsilon(G) = \max_{v \in V(G)} Y(v)$.
+% \begin{gather}
+%   \label{eq:27}
+%     \limsup\,\, \mathbb{P}( \Upsilon(G) \geq a_{n,m} ) \leq \lim
+%    \mathbb{P}( \Delta(G) \geq N_\kappa), \\
+%    \label{eq:30}
+%   \liminf\,\, \mathbb{P}( \Upsilon(G) \geq a_{n,m} ) \geq \lim \mathbb{P}(
+%   \Delta(G) \geq N_{\kappa}).
+% \end{gather}
+% \begin{IEEEproof}[Eq.~\eqref{eq:27}]
+%  Let $C^{*} = \max\{C_{11},
+% C_{10}, C_{00}\}$ and $d_{n,m} = \sqrt{2 a_{n,m}/C^{*}}$. We first
+% note that
+% \begin{equation*}
+% \Upsilon(G) \geq a_{n,m} \Rightarrow C^{*} \tbinom{D(v)}{2} \geq
+% a_{n,m} \Rightarrow D(v) \geq d_{n,m}.
+% \end{equation*}
+% Let us define $h(v) = \mathbb{E}[Y(v)]$, i.e., 
+% \begin{equation*}
+%   \begin{split}
+%   h(v) = C_{00}p_{00} \tbinom{D(v)}{2} &+ (C_{11} p_{11} - C_{00}
+%   p_{00}) \tbinom{M(v)}{2} \\ &+ (C_{10} p_{10} - C_{00} p_{00}) M(v)
+%   W(v).
+%   \end{split}
+% \end{equation*}
+% We then have
+%   \begin{equation*}
+%     \label{eq:31}
+%     \begin{split}
+%     \mathbb{P}(\Upsilon(G) \geq a_{n,m}) &= \mathbb{P}\Bigl( \bigcup_{v
+%       \in V(G)} Y(v) \geq a_{n,m}\Bigr) \\
+%     &= \mathbb{P}\Bigl( \bigcup_{v
+%       \in V(G)} Y(v) \geq a_{n,m}, \, D(v) \geq d_{n,m} \Bigr) \\
+%     &\leq P_1 + P_2
+%     \end{split}
+%   \end{equation*}
+%   where 
+%   \begin{align*}
+%     \vartheta_n &= C_{00} \Bigl[ \tbinom{n}{2} p_{00} (1 -
+%     p_{00})\Bigr]^{1/2} \log{n} \\
+%     P_1 &= \mathbb{P}(\bigcup_{v \in V(G)} D(v) \geq d_{n,m}, h(v) \geq
+%     a_{n,m} - \vartheta_n) \\
+%     P_2 &= \mathbb{P}(\bigcup_{v \in V(G)} D(v) \geq d_{n,m},
+%     Y(v) - h(v) \geq \vartheta_n).
+%   \end{align*}
+%   We now show that $P_2$ is negligible as $n \rightarrow \infty$. To
+%   proceed, let $A$ be the event $\{M(v) = e, W(v) = f\}$ and let
+%   $p_{e,f} = \mathbb{P}(A)$. $P_2$ can then be bounded as follows
+% \begin{equation*}
+%   \begin{split}
+%     \frac{P_2}{n} & \leq \sum_{e + f \geq
+%         d_{n,m}}{\mathbb{P}( Y(v) - h(v) \geq
+%       \vartheta_{n} \, | \, A)} p_{e,f}  \\
+%   &=  \sum_{e + f \geq d_{n,m}}{\mathbb{P}\Bigl(
+%     \tfrac{Y(v) - h(v)}{\mathrm{Var}[Y(v)]^{1/2}} \geq
+%     \tfrac{\vartheta_n}{\mathrm{Var}[Y(v)]^{1/2}} \, \Bigl| \, A\Bigr) p_{e,f}} \\
+%     &\leq \sum_{e + f \geq d_{n,m}} (1 + o(1))
+%     \mathbb{P}(Z \geq \Theta(\log{n})) p_{e,f} \\ &= o(n^{-1}).
+%   \end{split}
+% \end{equation*}
+% We now consider $P_1$. We note that $P_1 \leq R_1 + R_2$
+% where
+% \begin{align*}
+%   R_1 &= \mathbb{P}\Bigl(\bigcup_{v \in [m]} D(v) \geq
+%   d_{n,m}, h(v) \geq a_{n,m} - \vartheta_n \Bigr), \\  
+%   R_2 &= \mathbb{P}\Bigl(\bigcup_{v \in [n] \setminus [m]} D(v) \geq
+%   d_{n,m}, h(v) \geq a_{n,m} - \vartheta_n \Bigr).
+% \end{align*}
+% Let us define $g(v) = h(v) - C_{00}p_{00} \tbinom{D(v)}{2}$.
+% $R_1$ is then bounded as follows
+% \begin{equation}
+%   \begin{split}
+%     \label{eq:36}
+%     R_1 &\leq \mathbb{P}\Bigl( \bigcup_{v \in [m]} h(v) \geq
+%     a_{n,m} - \vartheta_{n} \Bigr) \\
+%     % &\leq \mathbb{P}\Bigl( \bigcup_{v \in [n_1]}  C_{00} p_{00}
+%     % \tbinom{D(v)}{2} \geq a_{n,m} - \vartheta_{n} - g(v) \Bigr) \\
+%     &\leq \mathbb{P}\Bigl(\bigcup_{v \in [m]} D(v) \geq
+%       \sqrt{\tfrac{2 (a_{n,m} - \vartheta_n -
+%         g(v))}{C_{00} p_{00}}} \Bigr).
+%   \end{split}
+% \end{equation}
+% We now consider the term $a_{n,m} - g(v)$. We have
+% \begin{equation*}
+%   \begin{split}
+%   a_{n,m} - g(v) &= C_{00} p_{00} \tbinom{N_\kappa}{2} \\ &+ (C_{11}p_{11} -
+%   C_{00} p_{00})(\tbinom{\mu_E}{2} - \tbinom{M(v)}{2})
+%   \\ &+ (C_{10} p_{10} - C_{00} p_{00})(\mu_E\mu_F - M(v)W(v)).
+%   \end{split}
+% \end{equation*}
+% Let $\mathfrak{E}$ and $\mathfrak{F}$ be sets of vertices defined by
+% \begin{align}
+% \mathfrak{E} &=
+% \{v \colon |M(v) - \mu_E| \leq \sigma_E \log{m}\} \\ \mathfrak{F} &=
+% \{v \colon |W(v) - \mu_F| \leq \sigma_F \log{(n-m)}\}.
+% \end{align}
+% Then we have, for $v \in \mathfrak{E} \cap \mathfrak{F}$
+% \begin{equation}
+%   \label{eq:34}
+%   \begin{split}
+%   a_{n,m} - g(v) =  C_{00} p_{00} \tbinom{N_\kappa}{2} &+
+%   \Theta(m^{3/2} \log{m}) \\ &+ 
+%   \Theta(m \sqrt{n - m}) \\
+%   \end{split}
+% \end{equation}
+% When $m = \Omega(\sqrt{n \log n})$, Eq.~\eqref{eq:34} gives
+% \begin{equation}
+%   \label{eq:35}
+%   a_{n,m} - g(v) = N_{\kappa}^{2}\Bigl(\tfrac{C_{00}p_{00}}{2} + O(n^{-1/2 - a}
+%   \log{n})\Bigr).
+% \end{equation}
+% for some $a > 0$. The set $\{v \in [m]\}$ can be partition into
+% $\{v \in [m] \cap (\mathfrak{E} \cap\mathfrak{F})\}$ and $\{v \in [m]
+% \setminus (\mathfrak{E} \cap \mathfrak{F})\}$. We can show that
+% $\mathbb{P}\{v \in [m] \setminus (\mathfrak{E} \cap \mathfrak{F})\} =
+% o(1)$ by using a concentration inequality, e.g., Hoeffding's
+% bound. We thus have
+% \begin{equation}
+%   \label{eq:37}
+%   \begin{split}
+%     R_1 &\leq \mathbb{P}\biggl( \bigcup_{\substack{v \in [m] \\ v
+%         \in \mathfrak{E} \cap \mathfrak{F}}} D(v) \geq
+%     N_{\kappa} \sqrt{1 + O(\tfrac{\log{n}}{n^{1/2+a}})} \Bigr) + o(n^{-1}) \\
+%     & = \mathbb{P}\Bigl(\bigcup_{v \in [m]} D(v) \geq N_\kappa +
+%     O(n^{1/2 - a} \log{n})\Bigr) + o(n^{-1}) \\
+%     &= \mathbb{P}\Bigl(\Delta \geq \mu_{E+F} +
+%     \sigma_{E+F}(z_m + O(\tfrac{\log{n}}{n^{a}}))\Bigr) + o(n^{-1}) \\ 
+%     & \rightarrow \mathbb{P}(\Delta \geq N_{\kappa}).
+%     \end{split}
+% \end{equation}
+% The same argument can be applied to $R_2$ to show that
+% \begin{equation}
+%   \label{eq:38}
+%   R_2 \leq \mathbb{P}\Bigl(\bigcup_{v \in [n] \setminus [m]} D(v) \geq
+%   N_{\kappa}(1 + o(1))\Bigr) = o(1).
+% \end{equation}
+% Eq.~\eqref{eq:27} is therefore established.
+% \end{IEEEproof}
+% \begin{IEEEproof}[Eq.~\eqref{eq:30}]
+%   We start by noting that
+%   \begin{equation*}
+%     \begin{split}
+%       \mathbb{P}(\Upsilon(G) \geq a_{n,m}) &=
+%       \mathbb{P}\Bigl(\bigcup_{v \in [n]}Y(v) \geq
+%       a_{n,m}\Bigr) \\
+%       & \geq \mathbb{P}\Bigl(\bigcup_{v \in [m]}Y(v) \geq
+%       a_{n,m}, D(v) \geq N_\kappa \Bigr) \\
+%       & \geq \mathbb{P}\Bigl(\bigcup_{v \in [m]} D(v) \geq
+%       N_\kappa\Bigr) \\ &- \mathbb{P}\Bigl( \bigcup_{v
+%         \in [m]} Y(v) < a_{n,m}, D(v) \geq N_\kappa\Bigr).
+%     \end{split}
+%   \end{equation*}
+%   We now show that $\mathbb{P}( \cup_{v
+%         \in [m]} Y(v) < a_{n,m}, D(v) \geq N_\kappa) \rightarrow 0$ as
+%       $n \rightarrow \infty$. Let $v \in [m]$ be arbitrary. It is then
+%       sufficient to show that $m\mathbb{P}(Y(v) < a_{n,m}, D(v) \geq
+%       N_{\kappa}) = o(1)$. We note that $\mathbb{P}(Y(v) < a_{n,m}, D(v) \geq
+%       N_{\kappa})$ can be rewritten as
+%       \begin{equation}
+%         \label{eq:24}
+%         \sum_{e + f \geq N_{\kappa}}{\mathbb{P}(Y(v) \leq a_{n,m} \, |
+%           \, M(v) = e, W(v) =
+%           f)}p_{e,f}.
+%       \end{equation}
+% We now split the indices set $e + f \geq N_{\kappa}$ in
+% Eq.~\eqref{eq:24} into three parts $S_1$, $S_2$ and $S_3$, namely
+% \begin{gather}
+%   \label{eq:32}
+%     S_1 = \{  e \geq
+%         \mu_E + \sigma_E \log{m}\} \\
+%     S_2 = \{  e \leq
+%         \mu_E + \sigma_E \log{m},e + f \leq
+%         N_\kappa + \varphi(n)\} \\
+%     S_3 = \{ e \leq \mu_E + \sigma_E \log{m}, e + f \geq
+%         N_\kappa + \varphi(n)\}
+% \end{gather}
+% where $\varphi(n) = \Theta(n^{1/2 - a})$ for some $a > 0$. We can then
+% show that $m\mathbb{P}(M(v) = e,
+% W(v) =f, \{e,f\} \in S_1) = o(1)$ by applying a concentration
+% inequality. Similarly, $e + f \geq N_{\kappa}$ and $e \leq \mu_{E}
+% + \sigma_{E} \log{m}$ implies that
+% \begin{equation}
+%   \label{eq:33}
+%   f \geq \mu_{F} + (z_{m} - o(1)) \sigma_F 
+% \end{equation}
+% and once again, by a concentration inequality, we can show that $m
+% \mathbb{P}(M(v) = e, W(v) = f, \{e,f\} \in S_2) = o(1)$. As for
+% $S_3$, from the fact that $e + f \geq N_{\kappa} + \varphi(n)$, we have the bound
+%   \begin{equation}
+%     \begin{split}
+%     a_{n,m} - h(v) &\leq (C_{11} p_{11} - C_{10} p_{10})[m \sigma_E
+%     \log{m} + \tbinom{\log{m}}{2}] \\ &- C_{00}p_{00} N_\kappa
+%     \varphi(n).
+%     \end{split}
+%   \end{equation}
+%   As $\mathrm{Var}[Y(v)] = \Theta(N_\kappa)$ for $\{M(v), W(v)\} \in
+%   S_3$, we have
+%   \begin{equation}
+%     \label{eq:39}
+%     \begin{split}
+%       p_{S_3} &= \sum_{\{e,f\} \in S_3} \mathbb{P}( Y(v) < a_{n,m}) p_{e,f} 
+%       \\ &\leq \sum_{\{e,f\} \in S_3} \mathbb{P}\Bigl(\tfrac{Y(v) - h(v))}{\mathrm{Var}[Y(v)]^{1/2}} \leq \tfrac{a_{n,m} -
+%       h(v)}{\mathrm{Var}[Y(v)]^{1/2}}\Bigr)p_{e,f} \\
+%     &\leq \sum_{\{e,f\} \in S_3} \mathbb{P}\Bigl[Z \leq
+%     O\bigl(\tfrac{m^{3/2} \log m}{N_{\kappa}} - \varphi(n)\bigr)\Bigr]
+%     p_{e,f}.
+%     \end{split}
+%   \end{equation}
+%   We now set $a = \tfrac{1}{2(k+1)}$. Then for $m =
+%   O(n^{k/(k+1)})$ and $\varphi(n) = O(n^{1/2 - a})$ we have
+%   \begin{equation}
+%     \label{eq:41}
+%     \tfrac{m^{3/2} \log m}{N_\kappa} - \varphi(n) =
+%     -O(n^{k/2(k+1))})
+%   \end{equation}
+%   which then implies
+%   \begin{equation}
+%     \label{eq:44}
+%     m p_{S_3} \leq m \sum_{\{e,f\} \in S_3} \mathbb{P} \Bigl[Z \leq
+%     - O(n^{k/2(k+1)}\Bigr] p_{e,f} = o(1).
+%   \end{equation}
+%   Thus $\mathbb{P}(Y(v) < a_{n,m}, D(v) \geq
+%       N_{\kappa}) \rightarrow 0$ as desired.
+% \end{IEEEproof}
+% From Eq.~\eqref{eq:27} and Eq.~\eqref{eq:30}, we have
+% \begin{equation}
+%   \label{eq:40}
+%  \lim
+% \mathbb{P}(\Upsilon(G) \geq a_{n,m}) = \lim \mathbb{P}(\Delta(G) \geq
+% N_{\kappa}).
+%  \end{equation}
+% Let $N_{\kappa,y} = N_\kappa + y \tfrac{\sigma_{E+F}}{\sqrt{2
+%     \log{m}}}$. We now define $a_{n,m,y}$ as 
+% \begin{equation*}
+%   \langle \lambda, \pi_{00} \rangle
+%     \tbinom{N_{\kappa,y}}{2} +
+%   \langle \lambda, \pi_{11} - \pi_{00} \rangle \tbinom{\mu_E}{2}  +
+%   \langle \lambda, \pi_{10} - \pi_{00} \rangle \mu_E \mu_F.
+% \end{equation*}
+% The above expression is equal to 
+% \begin{equation}
+%   \label{eq:57}
+%  a_{n,m} + \langle \lambda, \pi_{00} \rangle y
+%   \frac{\sigma_{E+F}}{\sqrt{2 \log m}} \Bigl(N_{\kappa} + y
+%   \frac{\sigma_{E+F}^{2}}{2 \sqrt{2 \log{m}}} + O(1) \Bigr).
+% \end{equation}
+% We thus have
+% \begin{equation*}
+%    a_{n,m,y} = a_{n,m} + (y + o(1)) b_{n,m}.
+% \end{equation*}
+% We therefore have
+% \begin{equation*}
+%   \begin{split}
+%   \lim \mathbb{P}(\Upsilon(G) \geq a_{n,m,y}) &= 
+%   \lim \mathbb{P}\Bigl(\frac{\Upsilon(G) - a_{n,m}}{b_{n,m}} \geq y \Bigr) \\
+%   &= \lim \mathbb{P}(\Delta(G) \geq N_{\kappa,y}) \\
+%   &= \lim \mathbb{P}\Bigl(\frac{\Delta(G) -
+%     N_{\kappa}}{\sigma_{E+F}} \geq \frac{y}{\sqrt{2 \log{m}}} \Bigr). \\
+%   \end{split}
+% \end{equation*}
+% Because $\Delta(G)$ converges weakly to a Gumbel
+% distribution in the limit
+% (\cite{bollobas85:_random_graph,rukhin:_limit_distr_graph_scan_statis}),
+% we have
+% \begin{equation}
+%   \label{eq:47}
+%   \mathbb{P}\Big(\frac{\Upsilon(G) - a_{n,m}}{b_{n,m}} \leq
+%     y\Bigr) \rightarrow e^{- e^{-y}} 
+% \end{equation}
+% and Eq.~\eqref{eq:29} follows.
+% \end{IEEEproof}
 \bibliography{ssp2011}

### 2011-12-16 ssp2011.tex
Resubmitted to IEEE TPAMI

@@
 \section{Introduction}
+\label{sec:introduction}
 
 \subsection{Latent Process Model}
+\label{sec:latent-process-model}
 The latent process model for time series of attributed graphs was
@@
 %\label{sec:experimental-results}
-\section{Inference Example}
-We present here an inference example with the following
-parameters
+\section{Inference Examples}
+We present here two inference examples, one on simulated data and the
+other on the Enron email data set. In the first inference example, we
+simulated data from the model in \S~\ref{sec:latent-process-model}
+with the following parameters:
 \begin{equation*}
@@
   \end{bmatrix}
-  \end{matrix}
+  \end{matrix},
 \end{equation*}
@@
 \begin{equation*}
-  \pi_0 = (0.10,0.30,0.60)^{T}, \quad \pi_1 = (0.25,0.40,0.35)^{T}
+  \pi_0 = (0.10,0.30,0.60)^{T}, \quad \pi_1 = (0.25,0.40,0.35)^{T}.
 \end{equation*}
@@
 \end{figure*}
+
+Our second example uses the Enron data set which consists of email
+messages between 184 employees of the Enron corporation during a time
+period from 1998 to 2002. The Enron email messages for most of the
+2001 calendar year have been annotated into 32 different topics 
+\cite{berry01:_topic_annot_enron_email_data_set} and thus form the
+basis of our analysis. We chose to condense these 32 different
+topics into two groups. The first group consists of
+general enery-related topics and the second group consists of
+topics that are specifically related to the Enron corporation. 
+From the collection of email messages, we construct a time series of
+graphs. Each graph consists of email messages sent during a week in
+2001. The vertices of the graphs represent the employees and the edges
+represent email communication between the employees. The attributes on
+the edges are given by the grouping of the email topics as mentioned
+above.
+
+The detection of a chatter anomaly in the Enron data set during the
+first week of May 2001 was previously
+reported in \cite{priebe05:_scan_statis_enron_graph}, but with 
+unattributed edges. We chose to investigate the effect
+of attribute fusion for that same week in our inference example. 
+\figurename~\ref{fig:enron} presents a plot of the normalized
+statistic $T_{\lambda}^{l}$ with $l = 20$ for the four graph
+invariants against the fusion parameter
+$\lambda = (cos(\theta), sin(\theta))$. \figurename~\ref{fig:enron}
+indicates that the fusing of attributes leads to better detection
+as exemplified by the fact that the maximum for each of the normalized
+statistics $T_{\lambda}$ occurs for $\theta \not \in
+\{0,\pi/2\}$. Furthermore, the optimal fusion parameters are dependent
+on the specific graph invariants.
 \section{Conclusions}
@@
 
-The experiment in \S \ref{eq:55} indicates that the power estimates
+The simulation experiment in \S \ref{eq:55} indicates that the power estimates
 are accurate, even for the moderate value of $n = 100$. Furthermore,
@@
 attributes through an attribute confusion matrix.
+\begin{figure}[tbp]
+  \centering
+ \includegraphics[width=8cm]{graphics/enron152.pdf} 
+  \caption{Detecting chatter anomaly in the Enron time series of
+    graphs. The graph in question corresponds to the first week of May
+    2001. Attribute fusion provides superior detection.}
+  \label{fig:enron}
+\end{figure}
 % \appendix[Proofs of some stated results]

### 2012-06-22 response.tex
Revision as submitted to IEEE Trans on SP; Move codes to different repository

We thank the referees for their feedback. We have
revised the paper in light of their comments and criticism, especially 
on issues regarding the paper appropriateness for the Trans on SP
readership. A more detailed response to the comments from each referee
is included below.

=================
Referee 1

Although the idea of linearly fusing attributes seems appealing and
the authors present their ideas in a technically sound way, nicely
structured and well supported by theoretical analysis and derivations,
I have some critical reservations:

1. The practicality of the approach: Both examples consider the case
of graphs with k=2 attributes and a convenient single parameter
representation ($\theta$). However for larger k, sets of different
optimal values would be harder to argue about. Also given a set of
real graph snapshots the determination (or approximation) of the
corresponding Markov processes - assuming all properties assumed hold
- is not commented on.

*** Response to point 1:
    The cases where $ k \geq 3$ was not considered in the experiments,
    as we deemed them to be more complex but not more
    difficult. Theoretically, the optimal $\lambda$ for $k \geq 3$ can
    be found for all of the graph invariants by numerical techniques,
    i.e., find the $\lambda$ that maximizes non-central parameters
    $\mu_{\lambda}$ in the cases for size and number of triangles, or
    the ratio $\rho_{\lambda}/\zeta_{\lambda}$ in the case of max
    degree or scan. As for empirical evaluation, one can parametrize 
    the set $\{\lambda \colo \| \lambda \| = 1\}$ for $k \geq 3$
    using hypershperical coordinates and the problem of finding the
    optimal $\lambda$ can be done by exhaustive search. This is 
    inefficient or even intractable for $k \geq 5$, but this is a
    common issue for most global optimization problems.

    The issue of determining or estimating the parameters of the
    underlying Markov chain given a set of snapshots of the graphs is an
    important issue that we failed to comment on explicitly in the
    previous submission. We have added in a paragraph to the revision that
    allude to this issue. In general, it is intractable to estimate the
    parameters of the underlying Markov chains given the snapshots. It is
    possible, however, to estimate the latent vectors associated with the
    first and second-order approximation via a spectral embedding
    technique [1]. We also note that more refined models, where the
    messaging events between each pairs of vertices is modeled as point
    process, e.g. [2,3] can also be formulated. The snapshot of the graphs
    is then a binning of these point processes and the issue of parameters
    estimation is fundamental but feasible in these point processes
    approaches.

    [1] Sussman et. al. ``A consistent dot product embedding for
    stochastic blockmodel graphs'', Online at http://arxiv.org/abs/1108.2228

    [2] Heard et. al. ``Bayesian anomaly detection methods for social
    networks'', Annals of Applied Statistics, (4):645--662, 2010.

    [3] P. Perry and P. J. Wolfe. ``Point process modeling for directed
    interaction networks'', Online at http://arxiv.org/abs/1011.1703v2

***

2. Journal relevance: This is very important since there does not seem
to exist some clear identification of a concrete application from
signal processing. The content would be much more relevant to a
statistics journal or to network analysis audience.

*** Response to point 2:

We have added a new section to motivates the consideration of
time-series of attributed graphs. We believe that the notion of a
time-series is a fundamental concept in signal processing and
furthermore the representation of data as (attributed) graphs is
ubiquitous in many applications domain. Also, anomaly/change-point
detection is one of the main problems in time-series analysis. As
such, anomaly detection on time-series of graphs is a natural and
challenging problem. There have been recent work on signal processing
on graphs, with many of them on the construction of wavelets on
graphs. Our paper is similar in spirit to these wavelets paper in that
they all consider signal processing on non-Euclidean data (graphs in
particular), but we have taken a more time-series and statistical 
point of view, as evidenced by our setup of the anomaly detection
problem via hypothesis testings along with the derivations of the
limiting behaviour of the test statistics.  
***

=======
Referee 2

*** Comments
The contributions of this paper are timely, relevant, and novel. The
development of signal processing methods for graphs is an important
topic to the signal processing community, as noted by the special
sessions at recent ICASSP and SSP conferences. The literature on
analysis methods for dynamic graphs is limited, and even more so for
attributed graphs. Furthermore, theoretical results that are also
practically useful are extremely rare.

The main weakness of this paper is that it is not organized well and
is not self-contained.

As such, it is difficult to understand the latent process model
without referring to the previous work (reference [1]). There really
is no introduction to the paper, no context is provided for the
problem--aside from the first sentence of the abstract, the reader is
left with no idea why change point detection in dynamic graphs is
useful, and specifically why one may want to use attributed graphs
rather than graphs without attributes. Finally, the latent process
model is a new model, and it would be beneficial to specify early in
the introduction the relationship between this model and other models
that the reader may be familiar with, namely the mixed-membership
stochastic blockmodel and the latent space models of Hoff et al. To
address these weakness, I would suggest to add a few paragraphs
preceding the current section I.A providing context and relationship
to existing models. The authors should find it useful to refer to
other papers published in the Trans on SP to get an idea on the type
of format, organization and style of writing that the TSP reader
expects.

Furthermore, there are terms and quantities that are introduced
without definition, e.g., the bracket notation "[]", e.g., "[K+1]",
the "cadlag process", and the "rdpm" in Sec 1.A. These are not
notations and quantities that are familiar to a signal processing
audience and should be carefully defined before they are introduced.

Specific comments:
- Page 3, figure 1: Please provide a more descriptive caption with
meanings of the regions and trajectories.
- Page 11, line 38: From the definitions of E and F, they appear to be
scalars, but E+F is defined as the convolution of E and F, which does
not make sense.
- Page 13, lines 10-11: What is the change point t* in this example?
- Page 14, line 49: Change "yields" to "yield"
- Page 15, line 4: A plot of each of the normalized test statistics
T_lambda^l (with the optimal lambda for each statistic) against time
should also be included so the reader can get a sense for how
anomalous this particular time step happens to be.
- Page 17, figure 6: Why are there multiple lines for the second order
approximation and exact model? Are they for different values of r? If
so, the values of r should be indicated somewhere in the plots
themselves (perhaps by reducing the number of values of r shown) or by
listing them in the caption.
- Appendix, page 1, line 31: Change "U-statistics" to "U-statistic"

*** Response

We have reorganized the paper to incorporate the referees comments
about the lack of a proper introduction (Section 2 in the new
manuscript was orignally Section 1 and the new Section 1 now discusses
the motivation behind time-series of attributed graphs). As we allude
to in the manuscript, representations of data as
graphs are ubiquitous in many application
domains and as the graphs representations do change over time,
the notion of a time-series of graphs is natural. Furthermore, in many
application domains, the edges are attributed, e.g., in neuroscience,
the edges can represent either inhibitory or excitatory synapses, in
social networks, the edges can represent the medium of communication
(twitter, email, sms). It is thus desirable for 
any approach that analyzes time-series of
graphs to also extends to attributed graphs
in a transparent manner.

We have also added several paragraphs to Section 2 to clarify/motivate the
latent process model and to compare it with other models such as the
latent vector model or the dot product model. We have also went
through the paper to carefully note/clarify notations for
terms/quantities such as [K+1] or rdpm.

For the specific comments, we addressed them in the paper. In
particular, 
1) the caption for Figure 1 is now updated to contains
description of the regions and tracjectories 
2) It is noted that E and F are meant to be random variables. The
statement that defined E and F had been adjusted accordingly. 
3) t* for the synthetic example is noted to be 11.
4) Figure 7 in the paper now contains  a plot of the
normalized test statistics T_{\lambda}^{l} (with the optimal lambda
for each statistic) against time.
5) The multiple lines for the exact model and the second-order
approximation are for different values of r. The set of vertex process
parameters r considered is also noted in the caption of Figure 5.

### 2012-06-22 decision.tex
Revision as submitted to IEEE Trans on SP; Move codes to different repository

06-Apr-2012

Prof. Carey Priebe
Johns Hopkins University
Whitehead Hall
Baltimore
Maryland
United States
21218-2682

Manuscript: T-SP-13180-2012 "Attribute fusion in a latent process
model for time series of graphs"

Dear Prof. Carey Priebe,

Your manuscript, T-SP-13180-2012 "Attribute fusion in a latent process
model for time series of graphs", which you submitted to the
Transactions on Signal Processing has been reviewed. The comments from
the reviewers are included at the bottom of this letter (**See note
below about attachments).

In view of the criticisms of the reviewers, I must reject the
manuscript for publication in the IEEE Transactions on Signal
Processing at this time. However, a new manuscript may be submitted
which takes into consideration these comments.

Your new manuscript must be submitted back to Manuscript Central
http://mc.manuscriptcentral.com/tsp-ieee together with a
point-by-point reply that explains how you addressed the reviewers'
comments.

Please note that resubmitting your manuscript does not guarantee
eventual acceptance, and that your resubmission will be subject to
re-review by the reviewers before a decision is rendered.

You will be unable to make your revisions on the originally submitted
version of your manuscript. Once you have revised your manuscript, log
into http://mc.manuscriptcentral.com/tsp-ieee and enter your Author
Center, where you will find your manuscript title listed under
"Manuscripts with Decisions". Under "Actions", click on "Create a
Resubmission" then follow the steps for resubmitting your manuscript.

If you have any questions, please contact the Admin for this journal
Ziggy Kowalski at z.kowalski@ieee.org.

Sincerely,

Prof. Maciej Niedzwiecki
Associate Editor
IEEE Transactions on Signal Processing
maciekn@eti.pg.gda.pl, maciekn@pg.gda.pl

Ziggy Kowalski
Coordinator Society Publications
IEEE Signal Processing Society
z.kowalski@ieee.org

** {This applies to SUBMITTING AUTHOR Accounts ONLY: You can find any
   possible ATTACHMENTS FROM THE REVIEWERS by going to the "Manuscript
   with Decisions" status link in your Author Center and clicking on
   "view decision letter". They are located at the bottom of decision
   letter under "Files attached" heading}

Reviewer Comments:

Reviewer: 1

Recommendation: R - Reject (Paper Is Not Of Sufficient Quality Or
Novelty To Be Published In This Transactions)

Comments:
Let's say that an graph edge can carry one of k different
attributes. Then each vertex is equipped with a vector of k elements:
there is an entry in this vector representing the affinity of the
vertex to act as an endpoint for each of the k possible types of
attributed edges. Based on these hidden vectors the probability of two
vertices to be connected is the dot product of their independent
vectors and more specifically the conditional probability that a
connecting edge will be labelled by attribute i is simply the product
of the ith vector entries. Practically, given the vectors attached to
each vertex, we can then compute "wiring" and "labelling"
probabilities and thus construct a graph instance based on them.

For a time series of graphs the authors extend to hidden vectors with
time-varying entries. Their goal is to identify the time when a
chatter anomaly - defined as perturbations in the links connecting
only a subset of the vertices - occurs in this series. At this point
they introduce extra assumptions in how the vectors can vary in time:
In any time interval $[t, t+1)$, a stationary, continuous-time Markov
process with k+1 states is assumed behind the scenes for computing the
time evolution of the vector (the extra state is absence of connection
for the vertex). Identical transition-matrix ($Q_1$) Markov processes
are suggested for all nodes before the anomaly, while after the
anomaly occurs they assume two Markov processes over the graph: the
previous one with stationary distribution $\pi_1$ running at nodes
with no incident link perturbations and $\pi_2$ at the others.

They next introduce two approximations of this assumed model: The
first order approximation considers attaching a hidden vector equal to
the stationary distribution of the Markov chain at works there; this
means that only perturbation-incident vertices will shift from $\pi_1$
to $\pi_2$ vectors at the time the anomaly happens. The second order
approximation assumes hidden vectors sampled from within an interval
around the first order approximation (stationary-distribution)
vectors.

The next step is to define their test statistics. For a given graph
they count the number of edges, the number of triangles, the maximum
degree and the maximum number of edges between neighbors over all
vertices, however inserting a weighting vector $\lambda$ with k
entries as a parameter, effectively changing the contribution of
different-attribute edges in the counting process. For each of these
four quantities they define a respective test statistic, as the
normalized deviation of the quantity from its average over a period of
the last $l$ graph history snapshots.

Selecting the weighting vector $\lambda$ that maximizes the power of
their approach is their next stop. This is the probability their test
will reject the null hypothesis when the null hypothesis is actually
false (the null hyposthesis states that the anomaly occurs after the
actual time it occurs, and this is obviously erroneous). They compute
this maximum-power $\lambda$ by actually finding the distributions
followed by their test statistics (Student t for the first two and
Gumbel for the rest two - maximum related - ones).

In the experimental section they work with two graphs, with 2
attributes each (k=2). A synthetic one where they explicitly set the
two Markov processes and then explore the dependence of the power for
exponentially decreasing waiting times for the processes (increasing
r) for their exact model and its two approximations. They also reduce
the Enron dataset into a k=2 attributed graph and plot their test
statistics as a function of $\theta$ (the magnitude of optimum
$\lambda$ vector is known to be 1, so for k=2 dimensions it could be
parameterized as $(\cos(\theta), \sin(\theta))$.

Although the idea of linearly fusing attributes seems appealing and
the authors present their ideas in a technically sound way, nicely
structured and well supported by theoretical analysis and derivations,
I have some critical reservations:

1. The practicality of the approach: Both examples consider the case
of graphs with k=2 attributes and a convenient single parameter
representation ($\theta$). However for larger k, sets of different
optimal values would be harder to argue about. Also given a set of
real graph snapshots the determination (or approximation) of the
corresponding Markov processes - assuming all properties assumed hold
- is not commented on.

*** 
    The cases where $ k \geq 3$ was not considered in the experiments,
    as we deemed them to be more complex but not more
    difficult. Theoretically, the optimal $\lambda$ for $k \geq 3$ can
    be found for all of the graph invariants by numerical techniques,
    i.e., find the $\lambda$ that maximizes non-central parameters
    $\mu_{\lambda}$ in the cases for size and number of triangles, or
    the ratio $\rho_{\lambda}/\zeta_{\lambda}$ in the case of max
    degree or scan. As for empirical evaluation, one can parametrize 
    the set $\{\lambda \colo \| \lambda \| = 1\}$ for $k \geq 3$
    using hypershperical coordinates and the problem of finding the
    optimal $\lambda$ can be done by exhaustive search. This is 
    inefficient or even intractable for $k \geq 5$, but this is a
    common issue for most global optimization problems.

    The issue of determining or estimating the parameters of the
    underlying Markov chain given a set of snapshots of the graphs is
    an important issue that we failed to comment on explicitly in the
    previous submission. We have added in a paragraph to the revision
    that allude to this issue. In general, it is intractable to
    estimate the parameters of the underlying Markov chains given the
    snapshots. It is possible, however, to estimate the latent vectors
    associated with the first and second-order approximation via
    a spectral embedding technique [1]. We also
    note that more refined models, where the messaging events between each pairs of
    vertices is modeled as point process,
    e.g. [2,3] can also be formulated. The
    snapshot of the graphs is then a binning of these point processes and
    the issue of parameters estimation is fundamental but feasible in 
    these point processes approaches.

[1] Sussman et. al. ``A consistent dot product embedding for
stochastic blockmodel graphs'', Online at http://arxiv.org/abs/1108.2228

[2] Heard et. al. ``Bayesian anomaly detection methods for social
networks'', Annals of Applied Statistics, (4):645--662, 2010.

[3] P. Perry and P. J. Wolfe. ``Point process modeling for directed
interaction networks'', Online at http://arxiv.org/abs/1011.1703v2

***

2. Journal relevance: This is very important since there does not seem
to exist some clear identification of a concrete application from
signal processing. The content would be much more relevant to a
statistics journal or to network analysis audience.

*** 
We have added a new section to motivates the consideration of
time-series of attributed graphs. We believe that the notion of a
time-series is a fundamental concept in signal processing and
furthermore the representation of data as (attributed) graphs is
ubiquitous in many applications domain. Also, anomaly/change-point
detection is one of the main problems in time-series analysis.  As
such, anomaly detection on time-series of graphs is a natural and
challenging problem. There have been recent work on signal processing
on graphs, with many of them on the construction of wavelets on
graphs. Our paper is similar in spirits to these wavelets paper but we
have taken a more statistical point of view, as evidenced by our 
setup of the anomaly detection problem via hypothesis testings along
with the derivations of the limiting behaviour of the test statistics.

Additional Questions:
1. Is the topic appropriate for publication in these transactions?: No

2. Is the topic important to colleagues working in the field?: No (explain):

Explain: As inferred by the comprehensive description of the paper
content included in the comments to authors, there is no explicit link
to the signal processing field e.g. in the form of its corresponding
application potential.

1. Is the paper technically sound?: Yes

why not?:

2. Is the coverage of the topic sufficiently comprehensive and balanced?: Yes

3. How would you describe technical depth of paper?: Appropriate for
the Generally Knowledgeable Individual Working in the Field or a
Related Field

4. How would you rate the technical novelty of the paper?: Not Novel

1. How would you rate the overall organization of the paper?: Satisfactory

2. Are the title and abstract satisfactory?: Yes

Explain:

3. Is the length of the paper appropriate? If not, recommend how the
length of the paper should be amended, including a possible target
length for the final manuscript.: Yes

4. Are symbols, terms, and concepts adequately defined?: Yes

5. How do you rate the English usage? : Satisfactory

6. Rate the Bibliography: Satisfactory

null:

1. How would you rate the technical contents of the paper?: Good

2. How would you rate the novelty of the paper?: Not Novel

3. How would you rate the "literary" presentation of the paper?: Mostly Accessible

4. How would you rate the appropriateness of this paper for
publication in this IEEE Transactions?: Poor Match

Reviewer: 2

Recommendation: RQ - Review Again After Major Changes

Comments:
The paper presents an attribute fusion approach for detecting change
points in dynamic graphs that evolve over time according to a latent
process model. The graphs considered are attributed graphs where each
edge can take one of K possible categories. Four types of graph
invariants for detection are considered, namely the number of edges,
the number of triangles, the maximum degree, and the scan statistic.
Attribute fusion refers to taking non-negative linear combinations of
these invariants computed for each category of edge.

The main contribution of the paper is an asymptotic analysis of the
power of the tests for each invariant as a function of the fusion
parameter lambda, which corresponds to a weighting of the different
attributes. For certain invariants, a closed-form solution for the
optimal lambda is also given. The analysis is performed under a
first-order approximation to the latent process model, which amounts
to a time series of independent Erdos-Renyi graphs (prior to the
change point) and independent graphs sampled from a special instance
of the mixed-membership stochastic blockmodel (after the change
point). Simulation results suggest that the asymptotic estimates of
the power under the first-order approximation are accurate, and that
the optimal choice of fusion parameter lambda under the first-order
approximation is close to the optimal fusion parameter under the exact
model.

The contributions of this paper are timely, relevant, and novel. The
development of signal processing methods for graphs is an important
topic to the signal processing community, as noted by the special
sessions at recent ICASSP and SSP conferences. The literature on
analysis methods for dynamic graphs is limited, and even more so for
attributed graphs. Furthermore, theoretical results that are also
practically useful are extremely rare.

The main weakness of this paper is that it is not organized well and
is not self-contained.

As such, it is difficult to understand the latent process model
without referring to the previous work (reference [1]). There really
is no introduction to the paper, no context is provided for the
problem--aside from the first sentence of the abstract, the reader is
left with no idea why change point detection in dynamic graphs is
useful, and specifically why one may want to use attributed graphs
rather than graphs without attributes. Finally, the latent process
model is a new model, and it would be beneficial to specify early in
the introduction the relationship between this model and other models
that the reader may be familiar with, namely the mixed-membership
stochastic blockmodel and the latent space models of Hoff et al. To
address these weakness, I would suggest to add a few paragraphs
preceding the current section I.A providing context and relationship
to existing models. The authors should find it useful to refer to
other papers published in the Trans on SP to get an idea on the type
of format, organization and style of writing that the TSP reader
expects.

Furthermore, there are terms and quantities that are introduced
without definition, e.g., the bracket notation "[]", e.g., "[K+1]",
the "cadlag process", and the "rdpm" in Sec 1.A. These are not
notations and quantities that are familiar to a signal processing
audience and should be carefully defined before they are introduced.

Specific comments:
- Page 3, figure 1: Please provide a more descriptive caption with
meanings of the regions and trajectories.
- Page 11, line 38: From the definitions of E and F, they appear to be
scalars, but E+F is defined as the convolution of E and F, which does
not make sense.
- Page 13, lines 10-11: What is the change point t* in this example?
- Page 14, line 49: Change "yields" to "yield"
- Page 15, line 4: A plot of each of the normalized test statistics
T_lambda^l (with the optimal lambda for each statistic) against time
should also be included so the reader can get a sense for how
anomalous this particular time step happens to be.
- Page 17, figure 6: Why are there multiple lines for the second order
approximation and exact model? Are they for different values of r? If
so, the values of r should be indicated somewhere in the plots
themselves (perhaps by reducing the number of values of r shown) or by
listing them in the caption.
- Appendix, page 1, line 31: Change "U-statistics" to "U-statistic"

Additional Questions:
1. Is the topic appropriate for publication in these transactions?: Yes

2. Is the topic important to colleagues working in the field?: Yes

Explain:

1. Is the paper technically sound?: Yes

why not?:

2. Is the coverage of the topic sufficiently comprehensive and
balanced?: Important Information is missing or superficially treated.

3. How would you describe technical depth of paper?: Suitable only for an expert

4. How would you rate the technical novelty of the paper?: Somewhat Novel

1. How would you rate the overall organization of the paper?: Poor

2. Are the title and abstract satisfactory?: Yes

Explain:

3. Is the length of the paper appropriate? If not, recommend how the
length of the paper should be amended, including a possible target
length for the final manuscript.: Yes

4. Are symbols, terms, and concepts adequately defined?: No

5. How do you rate the English usage? : Satisfactory

6. Rate the Bibliography: Satisfactory

null:

1. How would you rate the technical contents of the paper?: Excellent

2. How would you rate the novelty of the paper?: Sufficiently Novel

3. How would you rate the "literary" presentation of the paper?:
Partially Accessible

4. How would you rate the appropriateness of this paper for
publication in this IEEE Transactions?: Weak Match

### 2012-06-22 ssp2011.tex
Fixed some typo
Revision as submitted to IEEE Trans on SP; Move codes to different repository

@@
-\documentclass[10pt,journal,compsoc]{IEEEtran}
+\documentclass[10pt,twocolumn]{IEEEtran}
 \usepackage{fontenc}
@@
 %\usepackage{lmodern}
-\usepackage[utopia]{mathdesign}
+%\usepackage[utopia]{mathdesign}
 \usepackage{graphicx}
@@
 \usepackage{array}
-%\usepackage{amssymb}
+\usepackage{amssymb}
 \usepackage{amsthm}
@@
 \newtheorem{definition}{Definition}
-\usepackage[colorlinks=true,pagebackref,linkcolor=magenta]{hyperref}
+%\usepackage[colorlinks=true,pagebackref,linkcolor=magenta]{hyperref}
 \usepackage[noadjust]{cite}
@@
   graphs}
-\author{Minh~Tang, Youngser~Park, Nam~H.~Lee, and Carey~E.~Priebe%
-\IEEEcompsocitemizethanks{\IEEEcompsocthanksitem Minh~Tang, Nam~H.~Lee
- and Carey~E.~Priebe are with the Department of Applied Mathematics
- and Statistics, Johns Hopkins University.\protect \\
-  Email: \{mtang10, nhlee, cep\}@jhu.edu
-\IEEEcompsocthanksitem Youngser Park is with the Center for Imaging
-Science , Johns Hopkins University.\protect \\
-  Email: youngser@jhu.edu}%
-\thanks{}}
-\markboth{IEEE Transactions on Pattern Analysis and Machine
-  Intelligence (TPAMI)}{}
-\IEEEcompsoctitleabstractindextext{%
+\author{Minh~Tang, Youngser~Park, Nam~H.~Lee, and Carey~E.~Priebe*%
+\thanks{Minh~Tang is with the Department of Applied Mathematics and
+  Statistics, Johns Hopkins University, Baltimore, MD 21218
+  USA. (email: mtang10@jhu.edu)}%
+\thanks{Youngser~Park is with the Center of Imaging Science, Johns
+  Hopkins University, Baltimore, MD 21218
+  USA. (email:youngser@jhu.edu)}%
+\thanks{Nam~H.~Lee is with the Department of Applied Mathematics and
+  Statistics, Johns Hopkins University, Baltimore, MD 21218
+  USA. (email: nhlee@jhu.edu)}%
+\thanks{Carey~E.~Priebe is with the Department of Applied Mathematics and
+  Statistics, Johns Hopkins University, Baltimore, MD 21218
+  USA. (phone: 410-516-7200; fax:410-516-7459; email: cep@jhu.edu)}}%
+%\markboth{IEEE Transactions on Signal Processing}{}
+% \begin{IEEEkeywords}
+%   Anomaly detection, Attributed Random Graphs, Random Dot
+%   Product Graphs.
+% \end{IEEEkeywords}}
+
+\maketitle
 \begin{abstract}
@@
 \end{abstract}
-\begin{IEEEkeywords}
-  Anomaly detection, Attributed Random Graphs, Random Dot
-  Product Graphs.
-\end{IEEEkeywords}}
-\maketitle
+\ifCLASSOPTIONpeerreview
+\begin{center} \bfseries EDICS Category: SSP-SSAN, SSP-DETC \end{center}
+\fi
+%\pagebreak
 \section{Introduction}
 \label{sec:introduction}
-
-\subsection{Latent Process Model}
+The notion of data as a time series is fundamental to signal
+processing. However, time-series analysis had been mostly confined to
+data in Euclidean spaces, while the representation of data as graphs
+with the vertices as the entities and the edges as the relationships
+between the entities is now ubiquitous in many application domains,
+e.g., social networks (wherein vertices represent individual actors or
+organizations), neuroscience (wherein vertices are neurons or brain
+regions), and text processing (wherein vertices represent authors or
+documents). Furthermore, in many of these application domains, the
+edges between the vertices, in addition to representing the presence
+of a relationship, can also be use to identify the attributes
+associated with that relationship. For example, in social network
+graphs where edges represent email communications, the attributes
+signify the context of the email messages. Finally, in many of these
+application domains, the underlying data changes over time, and thus a
+representation of data as a time-series of attributed graphs is
+natural. The analysis of time-series of (attributed) graphs thus
+presents a natural and challenging extension to the signal processing
+community.
+
+We mention here some related work. The notion of signal
+processing for graphs appears to be in an emerging
+state, with significant research activity in constructing wavelet
+representations for graphs, e.g., 
+\cite{hammond10:_wavel,r.coifman06:_diffus,crovella03:_graph,narangss:_perfec}. 
+The formulation of graph analysis problems in a signal processing framework
+is also of potential interest, e.g, \cite{miller10:_towar_euclid}.
+
+One of the main exploitation tasks in time-series analysis is the
+problem of anomaly/change-point detection, where anomaly is broadly
+interpreted to mean deviation from some ``normal'' pattern and
+change-point is the time window at which the anomalous deviation
+occurs. In the context of a time-series of graphs, an anomaly can be
+for example the presence of a specific subgraph, or frequent occurence
+of some subgraphs, or other more vague notions such as existence of a
+community structure.
+
+In this paper, we investigate the anomaly/change-point detection
+problem for time-series of attributed graphs. In the spirit of
+time-series analysis, we approach this problem via test statistics
+based on the moving average of some graph invariants. We derive
+limiting distributions for these test statistics under a generative
+model for the attributed graphs. The experimental evidence indicate that these
+test statistics have sufficient power against the null hypothesis for
+a general class of change-point problem but that many interesting
+questions remain to ponder.
+
+Our paper is structured as follows. We present an overview of the
+generative model for time-series of attributed graphs \cite{lee11} in
+\S\ref{sec:latent-process-model}. The change-point detection problem
+along with the relevant test statistics are described in
+\S\ref{sec:change-point-detect}. The distributions of the test
+statistics and the power estimates for hypothesis testing using
+these test statistics are given in \S\ref{sec:power-estimates}. 
+\S\ref{sec:inference-examples} presents a
+synthetic data example and an example using the Enron email corpus to
+illustrate our methodology.
+\section{Latent Process Model}
 \label{sec:latent-process-model}
-The latent process model for time series of attributed graphs was
-presented in \cite{lee11}. We summarize here the ideas that are
-relevant to our discussion.  Let $G = (V,E)$ be an undirected graph,
-equipped with an edge-attribution function $\phi \colon \tbinom{V}{2}
-\mapsto \{1,2,\dots, K+1\}$ for some $K$ such that $\phi(e) \leq K$
-for $e \in E$ and $\phi(e) \equiv K+1$ for $e \not \in E$. We refer to
-$\phi(e)$ as the attribute of edge $e \in E$, and the pair $(G,\phi)$
-as an attributed graph. Let $\mathscr{S}$ be the unit simplex in
-$\mathbb{R}^{K}$, i.e.,
+The abundance of graph representations in diverse application domains
+leads to a proliferation of random graph models to model the
+association among the entities. In addition to the classical
+Erd\"{o}s-R\'{e}nyi model \cite{Erdos1959}, there is, the exponential
+graph models \cite{holland81}, the stochastic block model
+\cite{Holland1983,Wang1987}, the latent position model
+\cite{hoff02:_laten}, the dot product model for unattributed graphs
+\cite{young07:_random} and the latent process model for attributed
+graphs \cite{lee11}. We now describe briefly the latent position model
+of \cite{hoff02:_laten} and the dot product model of
+\cite{young07:_random} as they are closely related to the latent
+process model in \cite{lee11}. The latent process model serves as
+the generative model for our attributed graphs and thus plays a
+key role in our setup of the anomaly detection problem in 
+\S~\ref{sec:change-point-detect}.
+
+The latent space model is one where each vertex is associated with a
+latent random vector. There may also be additional covariate
+information but those are not relevant to the current exposition. The
+vectors are independent and identically distributed and the
+probability of an edge between two nodes depends only on their latent
+vectors. Conditioned on the latent vectors, the presence of each edge
+is an independent Bernoulli trial. For example, if $p_{uv}$ is the
+probability of an edge between the vertices $u$ and $v$, then $p_{uv}
+= \tfrac{1}{1 + \exp( - \|z_u - z_v\|)}$ where $z_u$ and $z_v$ are the
+latent vectors associated with vertex $u$ and $v$, respectively.
+Another example of a latent space model is the random dot product
+graph model \cite{young07:_random}. Under the random dot product graph
+model, the probability of an edge between two vertices is given
+by the dot product of their respective latent vectors, i.e., $p_{uv} =
+\langle z_u, z_v \rangle$. Parts of the motivation of the random dot
+product graph model is that, in a social network with edges
+indicating friendships, the components of the vector may be
+interpreted as the relative interest of the individual in various
+topics. The magnitude of the vector can be interpreted as how
+talkative the individual is, with more talkative individuals more
+likely to form relationships. Talkative individuals interested in the
+same topics are most likely to form relationships while individuals
+who do not share interests are unlikely to form relationships.
+
+The latent process model for time-series of attributed graphs was
+presented in \cite{lee11}. The main ideas underlying the model is as
+follows. The model is motivated by the assumption that each vertex is
+associated with a stochastic process, in this case a finite-state
+continuous time Markov chain. The stochastic processes then associate
+to each vertex $v$, for the time interval $(t-1,t]$, a (latent) random
+vector $X_v(t)$ in the unit simplex with the $k$-th entry of $X_v(t)$
+denoting the proportion of time the stochastic process spent in state
+$k$. The probability of interactions between vertices $u$
+and $v$ during $(t-1, t]$ is then given by the dot product of $X_u$
+and $X_v$ a la the dot product model of \cite{young07:_random}, with a
+slight modification to account for the presence of attributes on the
+edges.
+
+We now give the necessary details to make the above ideas precise. Let $G =
+(V,E)$ be an undirected graph, equipped with an edge-attribution
+function $\phi \colon \tbinom{V}{2} \mapsto [K+1] = \{1,2,\dots, K+1\}$ for
+some $K$ such that $\phi(e) \leq K$ for $e \in E$ and $\phi(e) \equiv
+K+1$ for $e \not \in E$. We refer to $\phi(e)$ as the attribute of
+edge $e \in E$, and the pair $(G,\phi)$ as an attributed graph. Let
+$\mathscr{S}$ be the unit simplex in $\mathbb{R}^{K}$, i.e.,
 \begin{equation}
@@
 A {\em random dot product space} for attributed graphs with vertices
-in $[n]$ and edge attributes $[K]$ is a pair $(\mathbf{X},G)$ of
+in $[n]$ ($[n] = \{1,2,\dots,n\}$) and edge attributes $[K]$ ($[K] =
+\{1,2,\dots,K\}$) is a pair $(\mathbf{X},G)$ of
 random elements such that
@@
   independent $\mathscr{S}$-valued random vectors.
-\item $G$ is a random undirected graph with vertex set $[n]$ such that
+\item $G$ is a random undirected graph with vertex set $[n]$ such
+  that the edges of $G$ are conditionally independent given
+  $\mathbf{X}$ and that
   \begin{equation}
@@
     \mathbb{P}(u \sim v \,|\, \mathbf{X}) = \mathbb{P}(u \sim v \, |
-    \, X_u,X_v) = \langle x_u, x_v \rangle
-  \end{equation}
-  and $\bm{1}(u \sim v \,|\, \mathbf{X})$ and $\bm{1}(u' \sim
-  v' \,|\, \mathbf{X})$ are independent whenever $(u,v) \not =
-  (u',v')$. Furthermore, we also have 
-  \begin{equation*}
-    \mathbb{P}(\phi(\{u,v\} = k \, | \, u \sim
-    v) = x_{u,k} x_{v,k}. 
-  \end{equation*}
+    \, X_u,X_v) = \langle x_u, x_v \rangle.
+  \end{equation}
+ Furthermore, we also have 
+  \begin{equation}
+    \label{eq:11}
+    \mathbb{P}(\phi(\{u,v\}) = k \, | \, u \sim
+    v) = \frac{x_{u,k} x_{v,k}}{\langle x_u, x_v \rangle}
+  \end{equation}
+  i.e., the pair $\{u,v\}$ is an edge in $G$ with attribute $k$ with
+  probability $x_{u,k} x_{v,k}$.  
 \end{enumerate}
-We say that a c\'{a}dl\'{a}g process $W \colon [0,\infty) \mapsto
-[K+1]^{n}$ induces the sequence of random dot product spaces
-$\mathscr{V} = (\mathbf{X}(t), G(t))_{t = 1}^{\infty}$ if
+We say that a c\'{a}dl\'{a}g (right continuous with left limit)
+process $W \colon [0,\infty) \mapsto [K+1]^{n}$ induces the sequence
+of random dot product spaces $\mathscr{V} = (\mathbf{X}(t), G(t))_{t =
+1}^{\infty}$ if
 \begin{enumerate}
@@
 We will call any pair $(\mathscr{V}, W)$ that satisfies the above
-properties a random dot process model. In particular, we are
-interested in the pairs $(\mathscr{V}, W)$ possessing the following
-properties:
+properties a random dot process model.
+
+The random dot process model can be interpreted as follows. During
+each time interval $(t-1,t]$, a particular vertex is inclined to
+communicate with other vertices on a variety of topics (the topics are
+enumerated as the elements of $[K]$). As the inclination of a vertex
+$v$ is governed by its underlying stochastic process $W_v$, we can
+view the $\{W_v\}$ as encapsulating a notion of changes in the
+inclination of the vertices over time. The propensity for
+vertex $v$ to communicate about a particular topic $k$ is $X_{v,k}(t)$
+and two vertices $u$ and $v$ are more likely to exchange communication
+on topic $k$ if the propensity to communicate about topic $k$ is high
+for both $u$ and $v$. Eq.~\eqref{eq:1} and Eq.~\eqref{eq:11} attempt
+to capture these two assumptions.
+
+In this paper, we are interested in the pairs $(\mathscr{V}, W)$
+possessing the following properties:
 \begin{enumerate}
@@
   ${\mathbf{Q}^{(v)}(t)}$, and stationary distribution
-  $\pi^{(v)}(t)$. $W$ is thus a piecewise stationary, continuous-time
+  $\pi^{(v)}(t)$. $W$ is thus a piece-wise stationary, continuous-time
   Markov chain with state space $[K+1]^{n}$ and intensity matrix
@@
     \begin{gather*}
-      \pi^{(1)}(t) = \dots = \pi^{(m)}(t) = \pi_1 \\
+      \pi^{(1)}((t)) = \dots = \pi^{(m)}(t) = \pi_1 \\
       \pi^{(m+1)}(t)  = \dots = \pi^{(n)}(t) = \pi_0 \\
@@
 The above properties characterize a random dot process model with a
-change-point phenomena for $(X(t),G(t))$ at time $t = t^{*}$. We chose $\{1,2,\dots,m\}$
-as the set of vertices with a change in the stationary distribution
-and intensity matrix at time $t = t^{*} - 1$ for ease of
-discussion. Permutation of the vertex labels does not affect our
-subsequent analysis. We will refer to $(t^{*}, m, \pi_0, \pi_1,
-\mathbf{Q}_0, \mathbf{Q}_1)$ as the change parameters.  Because $W$ is
-completely determined by the change parameters, we often choose to
-omit $W$ and only mention $\mathscr{V}$ when referring to random dot
-process models (rdpm) with change-point phenomena. For a rdpm
+change-point phenomena for $(X(t),G(t))$ at time $t = t^{*}$. We chose
+$\{1,2,\dots,m\}$ as the set of vertices with a change in the
+stationary distribution and intensity matrix at time $t = t^{*} - 1$
+for ease of discussion. Permutation of the vertex labels does not
+affect our subsequent analysis. We will refer to $(t^{*}, m, \pi_0,
+\pi_1, \mathbf{Q}_0, \mathbf{Q}_1)$ as the change parameters.  Because
+$W$ is completely determined by the change parameters, we often choose
+to omit $W$ and only mention $\mathscr{V}$ when referring to random
+dot process models with change-point phenomena. For a random dot
+process model
 $\mathscr{V}$ with change parameters $(t^{*}, m, \pi_0, \pi_1,
@@
   \label{def:1}
-  Let $\mathscr{V}$ be a rdpm with change parameters $(t^{*}, m,
-  \pi_0, \pi_1, \mathbf{Q}_0, \mathbf{Q}_1)$. The first order approximation
-  $\bar{\mathscr{V}}$ of $\mathscr{V}$ is the sequence $\{(\bar{X}(t),
-  \bar{G}(t)\}_{t = 1}^{\infty}$ of {\em independent} random dot product
-  spaces such that
+  Let $\mathscr{V}$ be a random dot process model (rdpm) with change
+  parameters $(t^{*}, m, \pi_0, \pi_1, \mathbf{Q}_0,
+  \mathbf{Q}_1)$. The first order approximation $\bar{\mathscr{V}}$ of
+  $\mathscr{V}$ is the sequence $\{(\bar{X}(t), \bar{G}(t)\}_{t =
+    1}^{\infty}$ of {\em independent} random dot product spaces such
+  that
  \begin{enumerate}
@@
   \includegraphics[width=5cm]{graphics/Fig2-SSP2011-hat1.pdf}
-  \caption{An illustration of the kidney-egg model for $G(t^{*})$.}
+  \caption{An illustration of the kidney-egg model for $G(t^{*})$. The
+    probability of an edge is $\langle \hat{\pi}_0, \hat{\pi}_0
+    \rangle$ for the connections inside the kidney set (black), $\langle
+    \hat{\pi}_1, \hat{\pi}_1 \rangle$ for the connections inside the egg set
+    (red), and $\langle \hat{\pi}_0, \hat{\pi}_1 \rangle$ for the connections
+    between the kidney and egg set.}
   \label{fig:kidney-egg}
@@
 A second-order approximation yields a sequence of independent latent
-position graphs \cite{marchette08:_predic,scheinerman10:_model,hoff02:_laten}.
+position graphs
+\cite{marchette08:_predic,scheinerman10:_model,hoff02:_laten}.
 
@@
 \bar{\mathscr{V}}$. This indicates that for sufficiently large $r$,
-there is little statistical difference amongst the
+there is little statistical difference among the
 $\bar{\mathscr{V}}$, $\mathscr{V}^{r}$ and $\widehat{\mathscr{V}}^{r}$
@@
 clear. $\bar{\mathscr{V}}$ will thus serve as the basis for our
-subsequent analysis on graph invariants for attributed random graphs.
-\subsection{Change-point detection}
+subsequent analysis on graph invariants for attributed random
+graphs.
+
+A comment should also be made about the utility of the exact
+generative model. It is computationally intractable to estimate the
+parameters of the underlying continuous time Markov chains, i.e. the
+$\{\mathbf{Q}^{(v)}(t)\}$, given a snapshot of the graphs. Therefore,
+the main interest of \cite{lee11}, and consequently of this paper,
+lies not in the exact generative model but in its first and
+second-order approximation. We will not be concerned with the
+estimation of the latent position vectors for the first and
+second-order approximation in this paper, but we note that they can be
+done via spectral embedding technique a la \cite{STFP-2011}. We also
+note that more refined models, where the messaging events between each pairs of
+vertices is modeled as point process,
+e.g. \cite{Heard2010,PerryWolfe2010}, can also be formulated. The
+snapshot of the graphs is then a binning of these point processes and
+the issue of parameters estimation is fundamental but feasible for
+these point processes approaches.
+\section{Change-point detection}
+\label{sec:change-point-detect}
 \begin{figure}[htbp]
@@
 for scale invariant test statistics is attainable in the set $\{ \lambda \colon \|
-\lambda \| = 1 \}$. \\ \\
+\lambda \| = 1 \}$.
 
@@
 \section{Power estimates}
+\label{sec:power-estimates}
 \subsection{Power estimates for $\mathcal{E}_\lambda$}
@@
 random graphs was considered in
-\cite{rukhin:_limit_distr_graph_scan_statis}. We note here the changes
+\cite{rukhin12}. We note here the changes
 that allow us to extend the results in
-\cite{rukhin:_limit_distr_graph_scan_statis} to our attributed graphs
+\cite{rukhin12} to our attributed graphs
 model. Let $z_n$ be defined, for $n \in \mathbb{N}$, by
@@
 \end{equation}
-Let us also define $E$ and $F$ by
+Let us also define two random variables $E$ and $F$ by
 \begin{gather*}
@@
 \section{Inference Examples}
+\label{sec:inference-examples}
 We present here two inference examples, one on simulated data and the
@@
 \end{equation*}
+The change-point $t^{*}$ for this example is $t^{*} = 11$. 
 Power estimates for our attribute fusion statistics for this example
@@
     four invariants at test size $\alpha = 0.05$. The horizontal lines
-    represents first-order approximation $\pm$ three
-    standard deviations, and the two curves represent the second
-    approximation (green) and exact model (blue). The 10000 Monte
-    Carlo replicates yields standard deviations not exceeding $0.005$ for the power
-    estimates . The second approximation results match well with the exact model results, and
-    both match well for large $r$ with the first-order approximation results.
-  }
+    represents first-order approximation $\pm$ three standard
+    deviations, and the two curves represent the second approximation
+    (green) and exact model (blue). The 10000 Monte Carlo replicates
+    yield standard deviations not exceeding $0.005$ for the power
+    estimates . The second approximation results match well with the
+    exact model results, and both match well for large $r$ with the
+    first-order approximation results.  }
   \label{fig:power-scale}
@@
     approximation (green), and exact model (blue) estimates for the
-    various invariants via Monte Carlo. The 10000 Monte Carlo
+    various invariants via Monte Carlo. The multiple green and blue
+    lines correspond to different values of the vertex process rate
+    $r$ (here $r \in \{1,2,4,8,16,32,64,128,256,512,1024\}$). 
+    The 10000 Monte Carlo
     replicates yields standard deviations not exceeding $0.005$ for
@@
 Our second example uses the Enron data set which consists of email
-messages between 184 employees of the Enron corporation during a time
+messages between 184 executives of the Enron corporation during a time
 period from 1998 to 2002. The Enron email messages for most of the
@@
 topics into two groups. The first group consists of
-general enery-related topics and the second group consists of
+general energy-related topics and the second group consists of
 topics that are specifically related to the Enron corporation. 
@@
 graphs. Each graph consists of email messages sent during a week in
-2001. The vertices of the graphs represent the employees and the edges
-represent email communication between the employees. The attributes on
+2001. The vertices of the graphs represent the executives and the edges
+represent email communication between the executives. The attributes on
 the edges are given by the grouping of the email topics as mentioned
@@
 
+\begin{figure}[tbp]
+  \centering
+ \includegraphics[width=8cm]{graphics/enron152.pdf} 
+ \caption{Detecting chatter anomaly in the Enron time series of
+   graphs. The plot shows the normalized statistics
+   $T_{\lambda}^{l}(t)$ as a function of the fusion parameter $\lambda
+   = (\cos(\theta), sin(\theta))$ for $l = 20$ and $t = 152$. The
+   graph in question ($t = 152$) corresponds to the first week of May
+   2001. The dashed lines correspond to the $\theta^{*}$ for the
+   different graph invariants ($\theta^{*}_{\mathcal{E}_{\lambda}}
+   \approx \theta^{*}_{\Delta_{\lambda}} \approx 0.96$,
+   $\theta^{*}_{\Psi_{\lambda}} \approx 1.06$ and
+   $\theta^{*}_{\tau_{\lambda}} \approx 0.83$). Attribute fusion
+   provides superior detection.}
+  \label{fig:enron}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+ \includegraphics[width=8cm]{graphics/Tstat_thetastar.pdf} 
+ \caption{The fluctuations of $T_{\lambda}^{l}(t)$ over time for the
+   four graph invariants. The value of $\lambda = (\cos(\theta),
+   sin(\theta))$ for each graph invariants correspond to the optimal
+   fusion parameters for the detection as illustrated in
+   \figurename~\ref{fig:enron} and they are
+   $\theta^{*}_{\mathcal{E}_{\lambda}} \approx
+   \theta^{*}_{\Delta_{\lambda}} \approx 0.96$,
+   $\theta^{*}_{\Psi_{\lambda}} \approx 1.06$ and
+   $\theta^{*}_{\tau_{\lambda}} \approx 0.83$. The fluctuations
+   indicate that there are possible anomalies around the weeks 120,
+   132, and 146, which were also reported and analyzed in 
+   \cite{priebe05:_scan_statis_enron_graph}.}
+\label{fig:enron_time}
+\end{figure}
 The detection of a chatter anomaly in the Enron data set during the
-first week of May 2001 was previously
+first week of May 2001 ($t = 152$) was previously
 reported in \cite{priebe05:_scan_statis_enron_graph}, but with 
@@
 \figurename~\ref{fig:enron} presents a plot of the normalized
-statistic $T_{\lambda}^{l}$ with $l = 20$ for the four graph
-invariants against the fusion parameter
-$\lambda = (cos(\theta), sin(\theta))$. \figurename~\ref{fig:enron}
+statistic $T_{\lambda}^{l}(t)$ at $t = 152$ with $l = 20$ for the four graph
+invariants against the fusion parameter $\lambda = (cos(\theta),
+sin(\theta))$. \figurename~\ref{fig:enron_time} presents a plot of the
+normalized statistics $T_{\lambda}^{l}(t)$ with $l = 20$ for the four
+graph invariants over the time interval corresponding to the
+weeks $t = 96$ through $t = 168$. The value of $\lambda$ used
+for each graph invariants is the $\lambda$ that maximizes
+$T_{\lambda}^{l}(152)$. \figurename~\ref{fig:enron}
 indicates that the fusing of attributes leads to better detection
@@
 
+% The exact generative model for time-series
+% of attributed graphs as presented in \S~\ref{sec:power-estimates}
+% contains assumptions that are not readily verified. However, as our
+% analysis
+
 Hypothesis testing on time series of attributed graphs has
@@
 attributes through an attribute confusion matrix.
-\begin{figure}[tbp]
-  \centering
- \includegraphics[width=8cm]{graphics/enron152.pdf} 
-  \caption{Detecting chatter anomaly in the Enron time series of
-    graphs. The graph in question corresponds to the first week of May
-    2001. Attribute fusion provides superior detection.}
-  \label{fig:enron}
-\end{figure}
-% \appendix[Proofs of some stated results]
-% \label{sec:proofs-some-stated}
-% \begin{IEEEproof}[Corollary~\ref{cor:1}]
-%   The maximizer of $\mu_\lambda$ also maximizes
-%   \begin{equation*}
-%     \mu_{\lambda}^{2} = \frac{\lambda^{T} \zeta \zeta^{T}
-%       \lambda}{\lambda^{T} \xi \lambda}
-%   \end{equation*}
-%   Because $\xi$ is positive definite, there exists a positive definite matrix
-%   $\xi^{1/2}$ such that $\xi^{1/2} \xi^{1/2} = \xi$. Letting $\nu = \xi^{1/2}
-%   \lambda$, the above expression can be rewritten as
-%   \begin{equation*}
-%     \mu_{\lambda}^{2} = \frac{\nu^{T} \xi^{-1/2} \zeta \zeta^{T}
-%       \xi^{-1/2} \nu}{ \nu^{T} \nu}
-%   \end{equation*}
-%   The claim then follows directly from the Rayleigh-Ritz theorem for
-%   Hermitian matrices.
-% \end{IEEEproof}
-% \begin{IEEEproof}[Lemma~\ref{lem:3}]
-%   $\tau_{\lambda}(G)$ is a U-statistics with kernel function
-%   $h(Y_1, Y_2, Y_3) = Y_1 Y_2 Y_3$. By the theory of U-statistics, we
-%   know that
-%   \begin{equation}
-%     \label{eq:48}
-%     \frac{\tau_{\lambda}(G) -
-%       \mathbb{E}[\tau_{\lambda}^{*}(G)]}{\sqrt{\mathrm{Var}[\tau_{\lambda}^{*}(G)]}}
-%        \overset{\mathrm{d}}{\longrightarrow}  N(0,1)
-%   \end{equation}
-%   provided that $\mathrm{Var}[\tau_{\lambda}(G) -
-%   \tau_{\lambda}^{*}(G)] = o(\mathrm{Var}[\tau_{\lambda}^{*}(G)])$.
-
-%   By the independent edge assumption, we have
-%   \begin{align}
-%     \mathbb{E}[h(Y_i, Y_j, Y_k) &= \mathbb{E}[Y_i]
-%   \mathbb{E}[Y_j] \mathbb{E}[Y_k] \\ 
-%   \mathbb{E}[h(Y_i, Y_j, Y_k) |
-%   Y_i] &= Y_i \mathbb{E}[Y_j] \mathbb{E}[Y_k].
-%   \end{align}
-%  Thus, for $t < t^{*}$, we have $\mathbb{E}[\tau_{\lambda}^{*}(G(t))] = \tbinom{n}{3} \langle
-%   \lambda, \pi_{00} \rangle^{3}$ and
-%   \begin{equation}
-%     \begin{split}
-%       \mathrm{Var}[\tau_{\lambda}^{*}(G(t))] &=
-%       \mathrm{Var}\Bigl[\sum_{\{u,v,w\}} Y_{uv} \mathbb{E}[Y_{uw}]
-%       \mathbb{E}[Y_{vw}]\Bigr] \\
-%       &= (n-2)^{2} \langle \lambda, \pi_{00} \rangle^{4}
-%       \mathrm{Var}\Bigl[\sum_{\{u,v\}} Y_{uv} \Bigr] \\
-%       &= (n-2)^{2} \langle \lambda, \pi_{00} \rangle^{4} \tbinom{n}{2}
-%       \langle \lambda, \eta_{00} \lambda \rangle.
-%     \end{split}
-%   \end{equation}
-%   We now sketch the derivation of
-%   $\mathrm{Var}[\tau_{\lambda}^{*}(G(t))]$ for $t = t^{*}$. We partition the set
-%   $\{u,v\} \in \tbinom{V}{2}$ into the sets 
-% \begin{gather*}
-% \mathcal{S}_1 = \{ u,v \in [m]
-%   \}, \\ \mathcal{S}_2 = \{ u \in [m], v \in [n] \setminus [m]\}, \\
-%   \mathcal{S}_3 = \{ u, v \in [n] \setminus[m]\}.
-% \end{gather*} 
-% We can thus decompose $\mathrm{Var}[\tau_{\lambda}^{*}(G(t))]$ as 
-% \begin{equation}
-%   \begin{split}
-%   \mathrm{Var}[\tau_{\lambda}^{*}(G(t))] &= S_1^{2} \mathrm{Var}[\sum_{\{u,v\} \in \mathcal{S}_1} Y_{uv}] +
-%   S_2^{2}
-%   \mathrm{Var}[\sum_{\{u,v\} \in \mathcal{S}_2} Y_{uv}] \\ &+
-%   S_3^{2}
-%   \mathrm{Var}[\sum_{\{u,v\} \in \mathcal{S}_3} Y_{uv}] 
-%   \end{split}
-% \end{equation}
-% Now, for $\{u,v\} \in \mathcal{S}_1$, we have
-% \begin{equation}
-%   \label{eq:58}
-%   \begin{split}
-% S_1 Y_{uv} &=\sum_{w \not = u,v} \mathbb{E}[h(Y_{uv}, Y_{uw}, Y_{vw})
-% \, | \, Y_{uv}] \\
-%  &= ((m-2) \langle \lambda, \pi_{11} \rangle^{2} + (n-m)
-%     \langle \lambda, \pi_{10} \rangle^{2})Y_{uv}.
-%   \end{split}
-% \end{equation}
-% The above expression is reasoned as follows. If $w \in [m]$, then
-% $\mathbb{E}[Y_{uw}] = \mathbb{E}[Y_{vw}] = \langle \lambda,
-% \pi_{11} \rangle$ and there are $m-2$ possible choices for $w \in [m]$
-% different from $u$ and $v$. If $w \in [n] \setminus [m]$, then
-% $\mathbb{E}[Y_{vw}] = \mathbb{E}[Y_{uw}] = \langle \lambda, \pi_{10}
-% \rangle$ and there are $n - m$ possible choices for $w$. Analogous
-% reasoning gives the expressions for $S_2$ and $S_3$ in the statement
-% of the lemma.
-
-% We also have
-%  \begin{equation}
-%    \label{eq:56}
-%    \mathrm{Var}[Y_{uv}] = \begin{cases}
-%      \langle \lambda, \eta_{00} \lambda \rangle & \text{if $\{u,v\} \in
-%        \mathcal{S}_1$} \\
-%      \langle \lambda, \eta_{01} \lambda \rangle & \text{if $\{u,v\} \in
-%        \mathcal{S}_2$} \\
-%      \langle \lambda, \eta_{11} \lambda \rangle & \text{if $\{u,v\} \in
-%        \mathcal{S}_3$} \\
-%      \end{cases}.
-%  \end{equation}
-% and thus
-% \begin{equation*}
-%   \begin{split}
-%     \mathrm{Var}[\tau_{\lambda}^{*}(G(t))] &=
-%     \tbinom{m}{2} \langle \lambda, \eta_{00} \lambda \rangle S_1^{2} +
-%     m(n-m) \langle \lambda, \eta_{01} \lambda \rangle S_2^{2} \\ &+
-%     \tbinom{n-m}{2} \langle \lambda, \eta_{00} \lambda \rangle S_3^{2}
-%   \end{split}
-% \end{equation*}
-% as desired. To complete the proof one must show that
-% $\mathrm{Var}[\tau_{\lambda}(G) - \tau_{\lambda}^{*}(G)] =
-% o(\mathrm{Var}[\tau_{\lambda}^{*}(G)])$ and this follows directly from
-% the argument in \cite{nowicki88:_subgr_u_statis_method}
-% or \cite{rukhin09:_asymp_analy_various_statis_random_graph_infer}.
-% \end{IEEEproof}
-% \begin{IEEEproof}[Proposition~\ref{prop:3}]
-%   Let $v \in V(t)$ and denote by $d_{\lambda}(v;t)$ the (fused) degree
-%   of vertex $v$, i.e.,
-%   \begin{equation*}
-%     d_{\lambda}(v;t) = \sum_{w \in N(v)} \langle \lambda,
-%     \Gamma_{vw} \rangle.
-%   \end{equation*}
-%   For $t < t^{*}$, each of the $\Gamma_{vw}$ is a multinomial
-%   trial with probability vector $\pi_{00}$. The following statements are
-%   made as $n \rightarrow \infty$ for fixed
-%   $K$.  By the central limit theorem, we have
-%   \begin{equation}
-%     \label{eq:17}
-%     \frac{d_{\lambda}(v;t) - (n-1) \langle \lambda, \pi_{00}
-%       \rangle}{\sqrt{(n-1) \langle \lambda, \eta_{00} \lambda \rangle}}
-%     \overset{\mathrm{d}}{\longrightarrow} \mathcal{N}(0, 1).
-%   \end{equation}
-%   We can thus consider the degree sequence of $G(t)$ for $t < t^{*}$
-%   as a sequence of {\em dependent} normally distributed random
-%   variables. By an argument analogous to the argument for
-%   Erd\"{o}s-Renyi random graphs in \cite[\S
-%   III.1]{bollobas85:_random_graph} we can show that the dependency
-%   among the $\{d_{\lambda}(v;t)\}_{v \in V(t)}$ can be
-%   ignored. Another way of doing this is to note that the covariance
-%   between $X_u$ and $X_v$, where $X_u$ and $X_v$ are the ratio in
-%   Eq.~\eqref{eq:17} for vertices $u$ and $v$, is given by
-%   \begin{equation}
-%     \label{eq:63}
-%     r = \mathrm{Cov}(X_u,X_v) = 
-%     \frac{3 \langle \lambda, \pi_{00} \rangle}{\sqrt{(n-1)
-%         \langle \lambda, \eta_{00} \lambda \rangle}}.
-%   \end{equation}
-%   Because $r \log{n} \rightarrow 0$ as $n \rightarrow \infty$, the
-%   sample maximum of the $X_u$ converges to the sample maximum of a
-%   sequence of {\em independent} $\mathcal{N}(0,1)$ random variables.
-%   $d_{\lambda}(v;t)$, can thus be considered as a sequence
-%   of independent random variables from a normal distribution. It is
-%   well known that the sample maximum of standard normal random
-%   variables converges weakly to a Gumbel distribution \cite[\S
-%   2.3]{galambos87:_asymp_theor_extrem_order_statis}. It is, however,
-%   not clear whether the convergence of $\Delta_{\lambda}(t)$ to a
-%   Gumbel distribution continues to hold under the composition of
-%   weak convergence as outlined above. We avoid this problem by
-%   showing directly that
-%   \begin{equation}
-%     \label{eq:22}
-%     \mathbb{P}\Bigl(\tfrac{\Delta_{\lambda}(t) - (n-1)
-%       \langle \lambda, \pi_{00} \rangle}{\sqrt{(n-1) \langle
-%         \lambda, \eta_{00} \lambda \rangle}} \leq a_n + b_n x\Big)
-%     \rightarrow 
-%     e^{-e^{-x}}. 
-%   \end{equation}
-%   Let $\zeta_v = \tfrac{d_{\lambda}(v;t) - (n-1) \langle \lambda,
-%     \pi_{00} \rangle}{\sqrt{(n-1) \langle \lambda, \eta_{00} \lambda
-%       \rangle}}$ and $F_n(u) = \mathbb{P}(\zeta_v \leq u)$. If $n
-%   \rightarrow \infty$ and $u = O(\sqrt{\log{n}})$, we have the
-%   following moderate deviations result \cite[Theorem~2, \S
-%   XVI.7]{feller71:_introd_probab_theor_its_applic,rubin65:_probab}.
-%   \begin{equation}
-%     \label{eq:23}
-%     \frac{1 - F_{n}(u)}{1 - \Phi(u)} = \Bigl[1 + (C\tfrac{u^{3}}{\sqrt{n}}) + O(\tfrac{u^{6}}{n}) \Bigr]
-%   \end{equation}
-%   for some constant $C$. Letting $u_n = a_n + b_n x$ in
-%   Eq.~\eqref{eq:23}, we have
-%   \begin{equation*}
-%     \begin{split}
-%       F_n(u_n) &= 1 - (1 - \Phi(u_n))(1 + C \tfrac{u_n^{3}}{\sqrt{n}} +
-%       O(\tfrac{u_n^{6}}{n})) \\
-%       &= \Phi(u_n) + (1 - \Phi(u_n))(C \tfrac{u_n^{3}}{\sqrt{n}} +
-%       O(\tfrac{u_n^6}{n})) \\
-%       &= \Phi(u_n) + O(\tfrac{1}{u_n n^{1- \delta}})(C \tfrac{u_n^{3}}{\sqrt{n}} +
-%       O(\tfrac{u_n^6}{n})) \\
-%       &= \Phi(u_n) + O(\tfrac{u_n^{5}}{n^{3/2 - \delta}})
-%     \end{split}
-%   \end{equation*}
-%   for some sufficiently small $\delta > 0$. We therefore have
-%   \begin{equation}
-%     \label{eq:25}
-%     \begin{split}
-%       \mathbb{P}(\max_{v \in [n]} \zeta(v) \leq u_n) &= (F_n(u_n))^{n} \\
-%       &= \Bigl[\Phi(u_n) + O(\tfrac{u_n^{5}}{n^{3/2 - \delta}})\Bigr]^{n} \\
-%       &= (\Phi(u_n))^{n} + O(\tfrac{u_n^{5}}{n^{1/2 - \delta}}) \\
-%       & \rightarrow e^{-e^{-x}}. 
-%     \end{split}
-%   \end{equation}
-%   Eq.~\eqref{eq:22} is established and we obtain the limiting Gumbel distribution for
-%   $\Delta_{\lambda}(t)$ for $t < t^{*}$ in Eq.~\eqref{eq:14}.
-
-%   The case when $t = t^{*}$ can be derive in a similar manner. We
-%   first show that if $m = \Omega(\sqrt{n \log n})$ then
-%   $\Delta_{\lambda}(v;t^{*}) \overset{\mathrm{d}}{\longrightarrow}
-%   \max_{v \in [m]}{d_{\lambda}(v;t^{*})}$ \cite[Lemma
-%   3.1]{rukhin:_limit_distr_graph_scan_statis}. We then show, again by
-%   the central limit theorem, that for $v \in [m]$,
-%   $\tfrac{d_{\lambda}(v;t^{*}) - \mu_2}{\sigma_2}
-%   \overset{\mathrm{d}}{\longrightarrow} \mathcal{N}(0,1)$. It then
-%   follows, similar to our previous reasoning for the case where $t <
-%   t^{*}$, that $\max_{v \in [m]} \tfrac{d_{\lambda}(v;t^{*}) -
-%     \mu_2}{\sigma_2}
-%   \overset{\mathrm{d}}{\longrightarrow}\mathcal{G}(a_m,b_m)$ and we
-%   obtain Eq.~\eqref{eq:14} for $t = t^{*}$.
-% \end{IEEEproof}
-% \begin{IEEEproof}[Theorem~\ref{thm:8}]
-%   Let $ X \sim \mathcal{G}(\alpha, \beta)$. We consider the
-%   normalization $\tfrac{X - \mu}{\sigma}$. We have
-%   \begin{equation*}
-%     \begin{split}
-%     \mathbb{P}\Bigl[ \tfrac{X - \mu}{\sigma} \leq z\Bigr]  &= \mathbb{P}[X \leq z
-%     \sigma + \mu] 
-%     = e^{-e^{-(z \sigma + \mu - \alpha)/\beta}} \\
-%       &= e^{- e^{-(z - (\alpha - \mu)/\sigma)/(\beta/\sigma)}}.
-%     \end{split}
-%   \end{equation*}
-%   Thus, $\tfrac{X - \mu}{\sigma} \sim \mathcal{G}(\tfrac{\alpha -
-%     \mu}{\sigma}, \tfrac{\beta}{\sigma})$. Because the sample
-%   mean and the sample variance are consistent estimators, the claim
-%   follows after an application of Slutsky's theorem.
-% \end{IEEEproof}
-% \begin{IEEEproof}[Lemma~\ref{lem:5}]
-% Let $\phi_{\lambda}(v;t) = \psi_{\lambda}(v;t) - d_{\lambda}(v;t)$ be
-% the (fused) locality statistics for
-% vertex $v$ at time $t$ not including the (fused) degree of $v$, i.e.,
-% \begin{equation}
-%   \label{eq:11}
-%   \phi_{\lambda}(v;t) = \sum_{\substack{uw
-%       \in N(v) \\ u,w \not = v}} \langle \lambda,
-%   \Gamma_{uw} \rangle.
-% \end{equation}
-% The following statements are conditional on $|N(v)| = l$. First
-% of all, we have
-% \begin{equation*}
-%   \phi_{\lambda}(v;t) = \sum_{k=1}^{K}{\lambda_k z_k}
-% \end{equation*}
-% where the $(z_1, \dots, z_K)$ are distributed as
-% \begin{gather*}
-%   (z_1,z_2,\dots,z_K) \sim \textrm{multinomial}\Bigl(
-%   \tbinom{l}{2}, \pi_{00}\Bigr). 
-% \end{gather*}
-% By the central limit theorem, we have
-% \begin{equation*}
-%   \frac{\phi_\lambda(v;t) - \tbinom{l}{2} \langle \lambda, \pi_{00}
-%     \rangle}{\sqrt{\tbinom{l}{2} \langle \lambda, \eta_{00} \lambda \rangle}}
-%   \overset{\mathrm{d}}{\longrightarrow} \mathcal{N}(0,1).
-% \end{equation*}
-% Let $\lambda^{(2)}$ be the element-wise square of $\lambda$. Define
-% $C_{00}$ and $p_{00}$ to be 
-%  \begin{gather}
-%    \label{eq:26}
-%    C_{00} = \tfrac{\langle \lambda^{(2)}, \pi_{00} \rangle}{\langle \lambda,
-%      \pi_{00}\rangle}, \quad p_{00} = \tfrac{(\langle \lambda, \pi_{00}
-%      \rangle)^{2}}{\langle \lambda^{(2)},\, \pi_{00} \rangle}.
-%  \end{gather}
-%  We note that $p_{00} \in [0,1]$. Now let $Y_{l} = C_{00}
-%  \mathrm{Bin}(\tbinom{l}{2}, p_{00})$. Then $\mathbb{E}[Y_l] =
-%  \tbinom{l}{2} \langle \lambda, \pi_{00} \rangle$ and
-%  $\mathrm{Var}[Y_l] = \tbinom{l}{2} \langle \lambda, \eta_{00} \lambda
-%  \rangle$ and again by the central limit theorem, we have
-% \begin{equation}
-%   \label{eq:12}
-%   \frac{\psi_{\lambda}(v;t) - \tbinom{l}{2} \langle \lambda, \pi_{00}
-%     \rangle}{\sqrt{\tbinom{l}{2} \langle \lambda, \eta_{00} \lambda
-%       \rangle}}   \overset{\mathrm{d}}{\longrightarrow} \frac{Y_l -
-%     \tbinom{l}{2} \langle \lambda, \pi_{00} \rangle}{\sqrt{\tbinom{l}{2}
-%     \langle \lambda, \eta_{00} \lambda \rangle}}.
-% \end{equation}
-% Eq.~\eqref{eq:12} states that the locality statistics for our
-% attributed random graphs model with $t < t^{*}$
-% can be approximated by the locality statistics for an Erd\"{o}s-Renyi
-% graph with edge probability $p_{00}$. The lemma then follows
-% from Theorem~1.1 in \cite{rukhin:_limit_distr_graph_scan_statis}.
-% \end{IEEEproof}
-% \begin{IEEEproof}[Lemma~\ref{lem:6}]
-%   For ease of exposition we drop the index $t^{*}$ from our discussion. Let
-%   $\phi_{\lambda}(v) = \psi_{\lambda}(v) - d_{\lambda}(v)$. Let
-%   $M(v)$ be the number of neighbors of $v$ that lies in $[m]$ and
-%   $W(v)$ be the number of neighbors of $v$ that lies in $[n]
-% \setminus [m]$. The following statements are conditional on
-% $M(v) = l_{\zeta}$ and $W(v) = l_{\xi}$. We have
-% \begin{equation}
-%   \phi_{\lambda}(v) = \sum_{k=1}^{K} \lambda_k ( y^{(\zeta)}_k +
-%   y^{(\xi)}_k + y^{(\omega)}_k)
-% \end{equation}
-% where $(y^{(\zeta)}_1, \dots, y^{(\zeta)}_K)$, $(y^{(\xi)}_1,\dots,
-%  y^{(\xi)}_K)$,  $(y^{(\omega)}_1, \dots, y^{(\omega)}_K)$ are
-%  distributed as
-% \begin{gather*}
-% (y^{(\zeta)}_1,\dots,y^{(\zeta)}_K) \sim \textrm{multinomial}\Bigl(
-% \tbinom{l_\zeta}{2}, \pi_{11}\Bigr) \\ 
-% (y^{(\xi)}_1,\dots,y^{(\xi)}_K) \sim \textrm{multinomial}\Bigl(
-% \tbinom{l_\xi}{2}, \pi_{00}\Bigr) \\
-% (y^{(\omega)}_1,\dots,y^{(\omega)}_m) \sim \textrm{multinomial}\Bigl(
-% l_\zeta l_\xi, \pi_{10}\Bigr).
-% \end{gather*}
-% Let $\rho$ and $\varsigma$ be defined as
-% \begin{gather*}
-%   \rho = \langle \lambda, \tbinom{l_{\zeta}}{2} \pi_{11} +
-%   \tbinom{l_{\xi}}{2} \pi_{00} + l_{\zeta} l_{\xi} \pi_{10} \rangle \\
-%   \varsigma = \langle \lambda, \Bigl(\tbinom{l_{\zeta}}{2} \eta_{11} +
-%   \tbinom{l_{\xi}}{2} \eta_{00} + l_{\zeta} l_{\xi} \eta_{10}\Bigr)
-%   \lambda.
-%   \rangle
-% \end{gather*}
-% By the central limit theorem, as $l_{\zeta} \rightarrow
-% \infty$ and $l_{\xi} \rightarrow \infty$
-% \begin{equation}
-%   \label{eq:16}
-%   \frac{\phi_{\lambda}(v) - \rho}{\varsigma}  \overset{\mathrm{d}}{\longrightarrow}  \mathcal{N}(0,1)
-% \end{equation}
-% Let $\lambda^{(2)}$ be the
-% element-wise square of $\lambda$. Define $C_{00}$, $C_{01}$, $C_{11}$
-% and $p_{00}$, $p_{01}$, $p_{11}$ to be
-%  \begin{gather}
-%    \label{eq:18}
-%    C_{00} = \tfrac{\langle \lambda^{(2)}, \pi_{00} \rangle}{\langle \lambda,
-%      \pi_{00}\rangle}; \quad p_{00} = \tfrac{(\langle \lambda, \pi_{00}
-%      \rangle)^{2}}{\langle \lambda^{(2)},\, \pi_{00} \rangle} \\
-%  C_{11} = \tfrac{\langle \lambda^{(2)}, \pi_{11} \rangle}{\langle \lambda,
-%      \pi_{11}\rangle}; \quad p_{11} = \tfrac{(\langle \lambda, \pi_{11}
-%      \rangle)^{2}}{\langle \lambda^{(2)},\, \pi_{11} \rangle} \\
-%  C_{10} = \tfrac{\langle \lambda^{(2)}, \pi_{11} \rangle}{\langle \lambda,
-%      \pi_{10}\rangle}; \quad p_{10} = \tfrac{(\langle \lambda, \pi_{10}
-%      \rangle)^{2}}{\langle \lambda^{(2)},\, \pi_{10} \rangle} 
-%  \end{gather}
-%  We note that $p_{00}$, $p_{01}$, and $p_{11}$ are all elements of
-%  $[0,1]$. Now let $Y_{\zeta} \sim C_{11}
-%  \mathrm{Bin}\Bigl(\tbinom{l_{\zeta}}{2}, p_{11}\Bigr)$, $Y_{\xi} \sim
-%  C_{00} \mathrm{Bin}\Bigl(\tbinom{l_\xi}{2}, p_{00}\Bigr)$ and
-%  $Y_{\omega} \sim C_{10} \mathrm{Bin}\Bigl( l_{\zeta} l_{\xi}, p_{10}
-%  \Bigr)$. We also set $Y = Y_{\zeta} + Y_{\xi} + Y_{\omega}$. By the
-%  central limit theorem, we have
-% \begin{equation}
-%   \label{eq:21}
-%  \frac{\phi_{\lambda}(v) - \rho}{\varsigma}
-%  \overset{\mathrm{d}}{\longrightarrow}  \frac{Y - \rho}{\varsigma}.
-% \end{equation}
-% Eq.~\eqref{eq:21} states that the locality statistics
-% $\phi_\lambda(v)$ for our attributed random graphs model at time $t =
-% t^{*}$ can be approximated by the locality statistics $Y(v)$ for an
-% unattributed kidney and egg model. The limiting distribution for the
-% scan statistics in unattributed kidney-egg graphs had previously been
-% considered in \cite{rukhin:_limit_distr_graph_scan_statis}. We
-% provided a sketch of the arguments from
-% \cite{rukhin:_limit_distr_graph_scan_statis} below, along with some
-% minor changes to handle the case where the probability of
-% kidney-kidney and
-% kidney-egg connections are different. \\ \\
-% \noindent
-% Let $G$ be an instance of
-% $\kappa(n,m,p_{11}, p_{10}, p_{00})$, an unattributed kidney-egg graph
-% with the probability of egg-egg, egg-kidney, and kidney-kidney
-% connections being $p_{11}$, $p_{10}$, and $p_{00}$,
-% respectively. $D(v) = M(v) + W(v)$ is then the degree of $v$ in
-% $G$. We now show two inequalities relating the tail distribution of
-% $\Delta(G)$ and $\Upsilon(G) = \max_{v \in V(G)} Y(v)$.
-% \begin{gather}
-%   \label{eq:27}
-%     \limsup\,\, \mathbb{P}( \Upsilon(G) \geq a_{n,m} ) \leq \lim
-%    \mathbb{P}( \Delta(G) \geq N_\kappa), \\
-%    \label{eq:30}
-%   \liminf\,\, \mathbb{P}( \Upsilon(G) \geq a_{n,m} ) \geq \lim \mathbb{P}(
-%   \Delta(G) \geq N_{\kappa}).
-% \end{gather}
-% \begin{IEEEproof}[Eq.~\eqref{eq:27}]
-%  Let $C^{*} = \max\{C_{11},
-% C_{10}, C_{00}\}$ and $d_{n,m} = \sqrt{2 a_{n,m}/C^{*}}$. We first
-% note that
-% \begin{equation*}
-% \Upsilon(G) \geq a_{n,m} \Rightarrow C^{*} \tbinom{D(v)}{2} \geq
-% a_{n,m} \Rightarrow D(v) \geq d_{n,m}.
-% \end{equation*}
-% Let us define $h(v) = \mathbb{E}[Y(v)]$, i.e., 
-% \begin{equation*}
-%   \begin{split}
-%   h(v) = C_{00}p_{00} \tbinom{D(v)}{2} &+ (C_{11} p_{11} - C_{00}
-%   p_{00}) \tbinom{M(v)}{2} \\ &+ (C_{10} p_{10} - C_{00} p_{00}) M(v)
-%   W(v).
-%   \end{split}
-% \end{equation*}
-% We then have
-%   \begin{equation*}
-%     \label{eq:31}
-%     \begin{split}
-%     \mathbb{P}(\Upsilon(G) \geq a_{n,m}) &= \mathbb{P}\Bigl( \bigcup_{v
-%       \in V(G)} Y(v) \geq a_{n,m}\Bigr) \\
-%     &= \mathbb{P}\Bigl( \bigcup_{v
-%       \in V(G)} Y(v) \geq a_{n,m}, \, D(v) \geq d_{n,m} \Bigr) \\
-%     &\leq P_1 + P_2
-%     \end{split}
-%   \end{equation*}
-%   where 
-%   \begin{align*}
-%     \vartheta_n &= C_{00} \Bigl[ \tbinom{n}{2} p_{00} (1 -
-%     p_{00})\Bigr]^{1/2} \log{n} \\
-%     P_1 &= \mathbb{P}(\bigcup_{v \in V(G)} D(v) \geq d_{n,m}, h(v) \geq
-%     a_{n,m} - \vartheta_n) \\
-%     P_2 &= \mathbb{P}(\bigcup_{v \in V(G)} D(v) \geq d_{n,m},
-%     Y(v) - h(v) \geq \vartheta_n).
-%   \end{align*}
-%   We now show that $P_2$ is negligible as $n \rightarrow \infty$. To
-%   proceed, let $A$ be the event $\{M(v) = e, W(v) = f\}$ and let
-%   $p_{e,f} = \mathbb{P}(A)$. $P_2$ can then be bounded as follows
-% \begin{equation*}
-%   \begin{split}
-%     \frac{P_2}{n} & \leq \sum_{e + f \geq
-%         d_{n,m}}{\mathbb{P}( Y(v) - h(v) \geq
-%       \vartheta_{n} \, | \, A)} p_{e,f}  \\
-%   &=  \sum_{e + f \geq d_{n,m}}{\mathbb{P}\Bigl(
-%     \tfrac{Y(v) - h(v)}{\mathrm{Var}[Y(v)]^{1/2}} \geq
-%     \tfrac{\vartheta_n}{\mathrm{Var}[Y(v)]^{1/2}} \, \Bigl| \, A\Bigr) p_{e,f}} \\
-%     &\leq \sum_{e + f \geq d_{n,m}} (1 + o(1))
-%     \mathbb{P}(Z \geq \Theta(\log{n})) p_{e,f} \\ &= o(n^{-1}).
-%   \end{split}
-% \end{equation*}
-% We now consider $P_1$. We note that $P_1 \leq R_1 + R_2$
-% where
-% \begin{align*}
-%   R_1 &= \mathbb{P}\Bigl(\bigcup_{v \in [m]} D(v) \geq
-%   d_{n,m}, h(v) \geq a_{n,m} - \vartheta_n \Bigr), \\  
-%   R_2 &= \mathbb{P}\Bigl(\bigcup_{v \in [n] \setminus [m]} D(v) \geq
-%   d_{n,m}, h(v) \geq a_{n,m} - \vartheta_n \Bigr).
-% \end{align*}
-% Let us define $g(v) = h(v) - C_{00}p_{00} \tbinom{D(v)}{2}$.
-% $R_1$ is then bounded as follows
-% \begin{equation}
-%   \begin{split}
-%     \label{eq:36}
-%     R_1 &\leq \mathbb{P}\Bigl( \bigcup_{v \in [m]} h(v) \geq
-%     a_{n,m} - \vartheta_{n} \Bigr) \\
-%     % &\leq \mathbb{P}\Bigl( \bigcup_{v \in [n_1]}  C_{00} p_{00}
-%     % \tbinom{D(v)}{2} \geq a_{n,m} - \vartheta_{n} - g(v) \Bigr) \\
-%     &\leq \mathbb{P}\Bigl(\bigcup_{v \in [m]} D(v) \geq
-%       \sqrt{\tfrac{2 (a_{n,m} - \vartheta_n -
-%         g(v))}{C_{00} p_{00}}} \Bigr).
-%   \end{split}
-% \end{equation}
-% We now consider the term $a_{n,m} - g(v)$. We have
-% \begin{equation*}
-%   \begin{split}
-%   a_{n,m} - g(v) &= C_{00} p_{00} \tbinom{N_\kappa}{2} \\ &+ (C_{11}p_{11} -
-%   C_{00} p_{00})(\tbinom{\mu_E}{2} - \tbinom{M(v)}{2})
-%   \\ &+ (C_{10} p_{10} - C_{00} p_{00})(\mu_E\mu_F - M(v)W(v)).
-%   \end{split}
-% \end{equation*}
-% Let $\mathfrak{E}$ and $\mathfrak{F}$ be sets of vertices defined by
-% \begin{align}
-% \mathfrak{E} &=
-% \{v \colon |M(v) - \mu_E| \leq \sigma_E \log{m}\} \\ \mathfrak{F} &=
-% \{v \colon |W(v) - \mu_F| \leq \sigma_F \log{(n-m)}\}.
-% \end{align}
-% Then we have, for $v \in \mathfrak{E} \cap \mathfrak{F}$
-% \begin{equation}
-%   \label{eq:34}
-%   \begin{split}
-%   a_{n,m} - g(v) =  C_{00} p_{00} \tbinom{N_\kappa}{2} &+
-%   \Theta(m^{3/2} \log{m}) \\ &+ 
-%   \Theta(m \sqrt{n - m}) \\
-%   \end{split}
-% \end{equation}
-% When $m = \Omega(\sqrt{n \log n})$, Eq.~\eqref{eq:34} gives
-% \begin{equation}
-%   \label{eq:35}
-%   a_{n,m} - g(v) = N_{\kappa}^{2}\Bigl(\tfrac{C_{00}p_{00}}{2} + O(n^{-1/2 - a}
-%   \log{n})\Bigr).
-% \end{equation}
-% for some $a > 0$. The set $\{v \in [m]\}$ can be partition into
-% $\{v \in [m] \cap (\mathfrak{E} \cap\mathfrak{F})\}$ and $\{v \in [m]
-% \setminus (\mathfrak{E} \cap \mathfrak{F})\}$. We can show that
-% $\mathbb{P}\{v \in [m] \setminus (\mathfrak{E} \cap \mathfrak{F})\} =
-% o(1)$ by using a concentration inequality, e.g., Hoeffding's
-% bound. We thus have
-% \begin{equation}
-%   \label{eq:37}
-%   \begin{split}
-%     R_1 &\leq \mathbb{P}\biggl( \bigcup_{\substack{v \in [m] \\ v
-%         \in \mathfrak{E} \cap \mathfrak{F}}} D(v) \geq
-%     N_{\kappa} \sqrt{1 + O(\tfrac{\log{n}}{n^{1/2+a}})} \Bigr) + o(n^{-1}) \\
-%     & = \mathbb{P}\Bigl(\bigcup_{v \in [m]} D(v) \geq N_\kappa +
-%     O(n^{1/2 - a} \log{n})\Bigr) + o(n^{-1}) \\
-%     &= \mathbb{P}\Bigl(\Delta \geq \mu_{E+F} +
-%     \sigma_{E+F}(z_m + O(\tfrac{\log{n}}{n^{a}}))\Bigr) + o(n^{-1}) \\ 
-%     & \rightarrow \mathbb{P}(\Delta \geq N_{\kappa}).
-%     \end{split}
-% \end{equation}
-% The same argument can be applied to $R_2$ to show that
-% \begin{equation}
-%   \label{eq:38}
-%   R_2 \leq \mathbb{P}\Bigl(\bigcup_{v \in [n] \setminus [m]} D(v) \geq
-%   N_{\kappa}(1 + o(1))\Bigr) = o(1).
-% \end{equation}
-% Eq.~\eqref{eq:27} is therefore established.
-% \end{IEEEproof}
-% \begin{IEEEproof}[Eq.~\eqref{eq:30}]
-%   We start by noting that
-%   \begin{equation*}
-%     \begin{split}
-%       \mathbb{P}(\Upsilon(G) \geq a_{n,m}) &=
-%       \mathbb{P}\Bigl(\bigcup_{v \in [n]}Y(v) \geq
-%       a_{n,m}\Bigr) \\
-%       & \geq \mathbb{P}\Bigl(\bigcup_{v \in [m]}Y(v) \geq
-%       a_{n,m}, D(v) \geq N_\kappa \Bigr) \\
-%       & \geq \mathbb{P}\Bigl(\bigcup_{v \in [m]} D(v) \geq
-%       N_\kappa\Bigr) \\ &- \mathbb{P}\Bigl( \bigcup_{v
-%         \in [m]} Y(v) < a_{n,m}, D(v) \geq N_\kappa\Bigr).
-%     \end{split}
-%   \end{equation*}
-%   We now show that $\mathbb{P}( \cup_{v
-%         \in [m]} Y(v) < a_{n,m}, D(v) \geq N_\kappa) \rightarrow 0$ as
-%       $n \rightarrow \infty$. Let $v \in [m]$ be arbitrary. It is then
-%       sufficient to show that $m\mathbb{P}(Y(v) < a_{n,m}, D(v) \geq
-%       N_{\kappa}) = o(1)$. We note that $\mathbb{P}(Y(v) < a_{n,m}, D(v) \geq
-%       N_{\kappa})$ can be rewritten as
-%       \begin{equation}
-%         \label{eq:24}
-%         \sum_{e + f \geq N_{\kappa}}{\mathbb{P}(Y(v) \leq a_{n,m} \, |
-%           \, M(v) = e, W(v) =
-%           f)}p_{e,f}.
-%       \end{equation}
-% We now split the indices set $e + f \geq N_{\kappa}$ in
-% Eq.~\eqref{eq:24} into three parts $S_1$, $S_2$ and $S_3$, namely
-% \begin{gather}
-%   \label{eq:32}
-%     S_1 = \{  e \geq
-%         \mu_E + \sigma_E \log{m}\} \\
-%     S_2 = \{  e \leq
-%         \mu_E + \sigma_E \log{m},e + f \leq
-%         N_\kappa + \varphi(n)\} \\
-%     S_3 = \{ e \leq \mu_E + \sigma_E \log{m}, e + f \geq
-%         N_\kappa + \varphi(n)\}
-% \end{gather}
-% where $\varphi(n) = \Theta(n^{1/2 - a})$ for some $a > 0$. We can then
-% show that $m\mathbb{P}(M(v) = e,
-% W(v) =f, \{e,f\} \in S_1) = o(1)$ by applying a concentration
-% inequality. Similarly, $e + f \geq N_{\kappa}$ and $e \leq \mu_{E}
-% + \sigma_{E} \log{m}$ implies that
-% \begin{equation}
-%   \label{eq:33}
-%   f \geq \mu_{F} + (z_{m} - o(1)) \sigma_F 
-% \end{equation}
-% and once again, by a concentration inequality, we can show that $m
-% \mathbb{P}(M(v) = e, W(v) = f, \{e,f\} \in S_2) = o(1)$. As for
-% $S_3$, from the fact that $e + f \geq N_{\kappa} + \varphi(n)$, we have the bound
-%   \begin{equation}
-%     \begin{split}
-%     a_{n,m} - h(v) &\leq (C_{11} p_{11} - C_{10} p_{10})[m \sigma_E
-%     \log{m} + \tbinom{\log{m}}{2}] \\ &- C_{00}p_{00} N_\kappa
-%     \varphi(n).
-%     \end{split}
-%   \end{equation}
-%   As $\mathrm{Var}[Y(v)] = \Theta(N_\kappa)$ for $\{M(v), W(v)\} \in
-%   S_3$, we have
-%   \begin{equation}
-%     \label{eq:39}
-%     \begin{split}
-%       p_{S_3} &= \sum_{\{e,f\} \in S_3} \mathbb{P}( Y(v) < a_{n,m}) p_{e,f} 
-%       \\ &\leq \sum_{\{e,f\} \in S_3} \mathbb{P}\Bigl(\tfrac{Y(v) - h(v))}{\mathrm{Var}[Y(v)]^{1/2}} \leq \tfrac{a_{n,m} -
-%       h(v)}{\mathrm{Var}[Y(v)]^{1/2}}\Bigr)p_{e,f} \\
-%     &\leq \sum_{\{e,f\} \in S_3} \mathbb{P}\Bigl[Z \leq
-%     O\bigl(\tfrac{m^{3/2} \log m}{N_{\kappa}} - \varphi(n)\bigr)\Bigr]
-%     p_{e,f}.
-%     \end{split}
-%   \end{equation}
-%   We now set $a = \tfrac{1}{2(k+1)}$. Then for $m =
-%   O(n^{k/(k+1)})$ and $\varphi(n) = O(n^{1/2 - a})$ we have
-%   \begin{equation}
-%     \label{eq:41}
-%     \tfrac{m^{3/2} \log m}{N_\kappa} - \varphi(n) =
-%     -O(n^{k/2(k+1))})
-%   \end{equation}
-%   which then implies
-%   \begin{equation}
-%     \label{eq:44}
-%     m p_{S_3} \leq m \sum_{\{e,f\} \in S_3} \mathbb{P} \Bigl[Z \leq
-%     - O(n^{k/2(k+1)}\Bigr] p_{e,f} = o(1).
-%   \end{equation}
-%   Thus $\mathbb{P}(Y(v) < a_{n,m}, D(v) \geq
-%       N_{\kappa}) \rightarrow 0$ as desired.
-% \end{IEEEproof}
-% From Eq.~\eqref{eq:27} and Eq.~\eqref{eq:30}, we have
-% \begin{equation}
-%   \label{eq:40}
-%  \lim
-% \mathbb{P}(\Upsilon(G) \geq a_{n,m}) = \lim \mathbb{P}(\Delta(G) \geq
-% N_{\kappa}).
-%  \end{equation}
-% Let $N_{\kappa,y} = N_\kappa + y \tfrac{\sigma_{E+F}}{\sqrt{2
-%     \log{m}}}$. We now define $a_{n,m,y}$ as 
-% \begin{equation*}
-%   \langle \lambda, \pi_{00} \rangle
-%     \tbinom{N_{\kappa,y}}{2} +
-%   \langle \lambda, \pi_{11} - \pi_{00} \rangle \tbinom{\mu_E}{2}  +
-%   \langle \lambda, \pi_{10} - \pi_{00} \rangle \mu_E \mu_F.
-% \end{equation*}
-% The above expression is equal to 
-% \begin{equation}
-%   \label{eq:57}
-%  a_{n,m} + \langle \lambda, \pi_{00} \rangle y
-%   \frac{\sigma_{E+F}}{\sqrt{2 \log m}} \Bigl(N_{\kappa} + y
-%   \frac{\sigma_{E+F}^{2}}{2 \sqrt{2 \log{m}}} + O(1) \Bigr).
-% \end{equation}
-% We thus have
-% \begin{equation*}
-%    a_{n,m,y} = a_{n,m} + (y + o(1)) b_{n,m}.
-% \end{equation*}
-% We therefore have
-% \begin{equation*}
-%   \begin{split}
-%   \lim \mathbb{P}(\Upsilon(G) \geq a_{n,m,y}) &= 
-%   \lim \mathbb{P}\Bigl(\frac{\Upsilon(G) - a_{n,m}}{b_{n,m}} \geq y \Bigr) \\
-%   &= \lim \mathbb{P}(\Delta(G) \geq N_{\kappa,y}) \\
-%   &= \lim \mathbb{P}\Bigl(\frac{\Delta(G) -
-%     N_{\kappa}}{\sigma_{E+F}} \geq \frac{y}{\sqrt{2 \log{m}}} \Bigr). \\
-%   \end{split}
-% \end{equation*}
-% Because $\Delta(G)$ converges weakly to a Gumbel
-% distribution in the limit
-% (\cite{bollobas85:_random_graph,rukhin:_limit_distr_graph_scan_statis}),
-% we have
-% \begin{equation}
-%   \label{eq:47}
-%   \mathbb{P}\Big(\frac{\Upsilon(G) - a_{n,m}}{b_{n,m}} \leq
-%     y\Bigr) \rightarrow e^{- e^{-y}} 
-% \end{equation}
-% and Eq.~\eqref{eq:29} follows.
-% \end{IEEEproof}
+
 \bibliography{ssp2011}

### 2012-06-22 Rcodes/attributed_graph.R
Remove moved files

@@ -1,98 +1,0 @@
-library("evd")
-
-kidney.egg.attributed <- function(n,m,pi0,piA){
-  
-  pi00 <- pi0*pi0
-  pi0A <- pi0*piA; piA0 <- pi0A
-  piAA <- piA*piA
-  
-  runif.mat <- matrix(0,nrow = n, ncol = n)
-  runif.mat[col(runif.mat) > row(runif.mat)] <- runif(n*(n-1)/2)
-  runif.mat <- (runif.mat + t(runif.mat))
-
-  edge.mat <- matrix(0, nrow = n, ncol =n)
-  edge.mat[1:m,1:m] <- sum(piAA)
-  edge.mat[1:m,(m+1):n] <- sum(pi0A) 
-  edge.mat[(m+1):n,1:m] <- sum(pi0A)
-  edge.mat[(m+1):n,(m+1):n] <- sum(pi00)
-
-  red.mat <- matrix(0, nrow = n, ncol = n)
-  red.mat[1:m,1:m] <- piAA[1]
-  red.mat[1:m,(m+1):n] <- pi0A[1]
-  red.mat[(m+1):n,1:m] <- pi0A[1]
-  red.mat[(m+1):n,(m+1):n] <- pi00[1]
-
-  adjacency.mat <- matrix(0,nrow = n, ncol = n)
-  red.idx <- (runif.mat <= red.mat)
-  green.idx <- (runif.mat > red.mat & runif.mat <= edge.mat)
-
-  adjacency.mat[red.idx] <- 1
-  adjacency.mat[green.idx] <- 2
-  diag(adjacency.mat) <- 0
-
-  vertex.colors <- c(rep("red",length.out=m),
-                     rep("green",length.out=(n-m)))
-
-  return(list(adjacency=adjacency.mat,
-              v.colors = vertex.colors))
-}
-
-maxd.statistic <- function(x,g){
-  t1 <- rowSums(g$adjacency == 1)
-  t2 <- rowSums(g$adjacency == 2)
-  t <- t1*x[1] + t2*x[2]
-  return(max(t))
-}
-
-num.triangle.trace <- function(w, g){
-  A <- g$adjacency
-  A1 <- (A == 1) + 0
-  A2 <- (A == 2) + 0
-  A.weighted <- w[1]*A1 + w[2]*A2
-
-  return(sum(diag(A.weighted %*% A.weighted %*% A.weighted))/6)
-}
-
-scan.statistic <- function(x,g){
-  x.red <- x[1]
[…]

### 2012-06-22 Rcodes/lp2010.R

@@ -1,72 +1,0 @@
-#library("igraph")
-
-namasy <- function(a=c(0.6,0.1,0.3),b=c(0.35,0.25,0.4))
-{
-# oripi <- pi
-#  a = c(0.6, 0.1, 0.3)
-#  b = c(0.35, 0.25, 0.40)
-
- pi = c(1-sum((a * a)[2:3]), (a * a)[2:3])
- phi = c(1-sum((a * b)[2:3]), (a * b)[2:3])
- nu = c(1-sum((b * b)[2:3]), (b * b)[2:3])
-
- W = rbind(
-   c(0,1,1),
-   c(0,1,0),
-   c(0,2,1)
-   )
-
- x1seq = seq(0,2*3.14,by=0.01)
- W=matrix(0,nrow=length(x1seq),ncol=3)
-
- for(i in 1:length(x1seq))
-   W[i,] = c(0,cos(x1seq[i]),sin(x1seq[i]))
-
-
- for( scale in 1:1 ) {
-
-   n =10
-   nvertex = 100*scale
-   abnorm = 9#*scale
-   chart = numeric(abnorm)
-
-   my = matrix(nrow=abnorm,ncol=length(x1seq))
-
-   for (row in 1:length(x1seq)) {
-     for ( i in abnorm:abnorm) {
-       alpha = 0.05
-       m = i
-
-       xi_pi = t(W[row,])%*% out(pi) %*% W[row,]
-       xi_phi = t(W[row,])%*% out(phi) %*% W[row,]
-       xi_nu = t(W[row,])%*% out(nu) %*% W[row,]
-
-       quartile_1 = qt(alpha,n-1,ncp = 0, lower.tail = FALSE)
-       quartile_2 = 1 + (n/(n+1))*(choose(m,2)/choose(nvertex,2)*(xi_nu/xi_pi - 1) +
-         m*(nvertex - m)/choose(nvertex,2)*(xi_phi/xi_pi - 1))
-       quartile = quartile_1 / sqrt(quartile_2)
-
-       kappa_num = choose(m,2) * W[row,] %*% (nu-pi) + m * (nvertex -m) * W[row,] %*% (phi-pi)
-       kappa_den_1 = (1+1/n)*choose(nvertex,2)* xi_pi
-       kappa_den_2 = choose(m,2) * ( xi_nu - xi_pi )
-       kappa_den_3 = m*(nvertex -m)*( xi_phi - xi_pi)
[…]

### 2012-06-22 Rcodes/maxd.R

@@ -1,485 +1,0 @@
-max.asy <- function(nvertex, nvertex.abnormal, pi0, piA, past.len, mc,
-                        from.egg = TRUE, adjustment = 0){
-  
-  pi00 <- c(1 - sum((pi0*pi0)[2:3]), (pi0*pi0)[2:3])
-  pi0A <- c(1 - sum((pi0*piA)[2:3]), (pi0*piA)[2:3])
-  piA0 <- pi0A
-  piAA <- c(1 - sum((piA*piA)[2:3]), (piA*piA)[2:3])
-
-  gamma <- 0.577215665
-  alpha <- 0.05
-  x1seq <- seq(0,pi/2, by = 0.01)
-  W <- matrix(0,nrow = length(x1seq), ncol = 3)
-  cv <- numeric(length(x1seq))
-  power <- numeric(length(x1seq))
-  
-  for(i in 1:length(x1seq))
-    W[i,] <- c(0,cos(x1seq[i]), sin(x1seq[i]))
-
-  for(i in 1:length(x1seq)){
-    params.list <- maxd.0A.params(nvertex, nvertex.abnormal, pi00, pi0A,
-                                  piAA, W[i,], from.egg)
-
-    an0 <- params.list$an0
-    anA <- params.list$anA
-    bn0 <- params.list$bn0
-    bnA <- params.list$bnA
-
-    ## sigma0 <- pi/sqrt(6)*bn0
-    ## sigmaA <- pi/sqrt(6)*bnA
-
-    ## ncp <- (anA - an0 + (bnA - bn0)*gamma)/sqrt(sigma0^2/past.len + sigmaA^2)
-    ## scale <- bnA/(pi/sqrt(6)*bn0)
-
-    ## quartile.1<- qt(alpha, df = past.len - 1, ncp = 0, lower.tail = FALSE)
-    ## quartile.2 <- (1 + (past.len)/(past.len + 1)*(sigmaA^2/sigma0^2 - 1))
-    ## quartile <- quartile.1/sqrt(quartile.2) + adjustment
-
-    tmp <- gumbel.power.test(an0, bn0, anA, bnA, past.len, mc)
-    cv[i] <- tmp$cv
-    #power[i] <- pt(quartile, df = past.len - 1, ncp = ncp, lower.tail = FALSE)
-    power[i] <- tmp$power
-  }
[…]

### 2012-06-22 Rcodes/numtri.R

@@ -1,97 +1,0 @@
-normal.power.test <- function(mu0,sd0,mu1,sd1,past.len,mc,cv){
-  g0.normalized <- seq(0,0,length.out = mc)
-  gA.normalized <- seq(0,0,length.out = mc)
-
-  g0mat <- matrix(rnorm(mc*(past.len + 1), mu0, sd0), nrow = mc, ncol = past.len + 1)
-  g0seq.mean1 <- rowMeans(g0mat[,1:past.len])
-  g0seq.sd1 <- sd(t(g0mat[,1:past.len]))
-  g0.normalized <-  (g0mat[,past.len+1] - g0seq.mean1)/g0seq.sd1
-
-  gAvec <- rnorm(mc,mu1,sd1)
-  g0seq.mean2 <- rowMeans(g0mat[,2:(past.len+1)])
-  g0seq.sd2 <- sd(t(g0mat[,2:(past.len+1)]))
-  gA.normalized <- (gAvec - g0seq.mean2)/g0seq.sd2
-
-  power <- length(which(gA.normalized > cv))/mc
-  return(list(cv = cv, power = power))
-}
-
-## numtri.pwr <- numeric(158)
-## numtri.cv <- numeric(158)
-## for(i in 1:158){
-##   tmp <-  normal.power.test(numtri.null.mean[i],numtri.null.sd[i],numtri.alt.mean[i],
-##                             numtri.alt.sd[i], 10,10000,numtri.stat$cv[i])
-##   numtri.cv[i] <- tmp$cv
-##   numtri.pwr[i] <- tmp$power
-## }
-  
-num.triangles.asy <- function(nvertex, nvertex.abnormal, pi0, piA,past.len){
-  
-  pi00 <- c(1 - sum((pi0*pi0)[-1]), (pi0*pi0)[-1])
-  pi0A <- c(1 - sum((pi0*piA)[-1]), (pi0*piA)[-1])
-  piA0 <- pi0A
-  piAA <- c(1 - sum((piA*piA)[-1]), (piA*piA)[-1])
-
-  alpha <- 0.05
-  x1seq <- seq(0, pi/2, by = 0.01)
-  W <- matrix(0, nrow = length(x1seq), ncol = 3)
-  cv <- numeric(length(x1seq))
-  power <- numeric(length(x1seq))
-
-  for(i in 1:length(x1seq))
[…]

### 2012-06-22 Rcodes/scan.R

@@ -1,449 +1,0 @@
-youngser1 <- function(tstat.mat, past.len, mc){
-  gamma <- 0.577215665
-  d1 <- dim(tstat.mat)[1]
-  d2 <- dim(tstat.mat)[2]
-  power.vec <- numeric(d2)
-  cv.vec <- numeric(d2)
-  for(i in 1:d2){
-    a.i <- tstat.mat[,i,]
-    a.i.null <- a.i[1:(d1-1),]
-    a.i.null.mean <- mean(a.i.null)
-    a.i.null.sd <- sd(as.vector(a.i.null))
-
-    a.i.alt <- a.i[d1,]
-    a.i.alt.mean <- mean(a.i.alt)
-    a.i.alt.sd <- sd(a.i.alt)
-
-    bn0 <- a.i.null.sd*sqrt(6)/pi
-    an0 <- a.i.null.mean - bn0*gamma
-
-    bnA <- a.i.alt.sd*sqrt(6)/pi
-    anA <- a.i.alt.mean - bnA*gamma
-
-    gpt <- gumbel.power.test(an0, bn0, anA, bnA, past.len, mc)
-    power.vec[i] <- gpt$power
-    cv.vec[i] <- gpt$cv
-  }
-  return(list(cv = cv.vec, power = power.vec))
-}
-
-pwr1.test <- function(){
-  theta.seq <- seq(from = 0, to = pi/4, by = 0.01)
-  power.vec <- seq(0,0,length.out = length(theta.seq))
-  cv.vec <- seq(0,0,length.out = length(theta.seq))
-  for(i in 1:length(theta.seq)){
-    print(i)
-    tmp <- power.test(theta.seq[i])
-    power.vec[i] <- tmp$power
-    cv.vec[i] <- tmp$cv
-  }
-  return(list(cv = cv.vec, power = power.vec))
-}
-
-scan.mc.mat <- function(nvertex,nvertex.abnormal,pi0.vec, piA.vec, mc){
-  theta.seq <- seq(from = 0, to = pi/4, by = 0.01)
-  g0.mat <- matrix(0,nrow=length(theta.seq), ncol = mc)
-  gA.mat <- matrix(0,nrow=length(theta.seq), ncol = mc)
-
-  print("Long ass computation: theta = ")
-  for(i in 1:length(theta.seq)){
-    print(theta.seq[i])
[…]

### 2012-06-22 Rcodes/snippet.R

@@ -1,153 +1,0 @@
-kidney.egg.attributed <- function(n,m,theta,pi0,piA){
-  
-  pi00 <- pi0*pi0
-  pi0A <- pi0*piA
-  piA0 <- pi0A
-  piAA <- piA*piA
-  x.red <- cos(theta)
-  x.green <- sin(theta)
-  
-  runif.mat <- matrix(0,nrow = n, ncol = n)
-  runif.mat[col(runif.mat) > row(runif.mat)] <- runif(n*(n-1)/2)
-  runif.mat <- (runif.mat + t(runif.mat))
-
-  edge.mat <- matrix(0, nrow = n, ncol =n)
-  edge.mat[1:m,1:m] <- sum(piAA)
-  edge.mat[1:m,(m+1):n] <- sum(pi0A) 
-  edge.mat[(m+1):n,1:m] <- sum(pi0A)
-  edge.mat[(m+1):n,(m+1):n] <- sum(pi00)
-
-  red.mat <- matrix(0, nrow = n, ncol = n)
-  red.mat[1:m,1:m] <- piAA[1]
-  red.mat[1:m,(m+1):n] <- pi0A[1]
-  red.mat[(m+1):n,1:m] <- pi0A[1]
-  red.mat[(m+1):n,(m+1):n] <- pi00[1]
-
-  adjacency.mat <- matrix(0,nrow = n, ncol = n)
-  edge.idx <- (runif.mat < edge.mat)
-  adjacency.mat[edge.idx] <- 1
-
-  labels.mat <- matrix("none", nrow = n, ncol = n)
-  red.idx <- (runif.mat <= red.mat)
-  green.idx <- (runif.mat > red.mat & runif.mat <= edge.mat)
-
-  labels.mat[red.idx] <- "red"
-  labels.mat[green.idx] <- "green"
-  diag(labels.mat) <- "none"
-  diag(adjacency.mat) <- 0
-
-  d.red <- x.red*apply(labels.mat,1, count.red)
-  d.green <- x.green*apply(labels.mat, 1, count.green)
-  deg <- d.red + d.green
-  
-  vertex.colors <- c(seq("red","red",length.out=m),
-                     seq("green","green",length.out=(n-m)))
-
-  return(list(adjacency=adjacency.mat,
-              labels=labels.mat,
-              dred=d.red,
-              dgreen=d.green,
-              degree=deg,
-              v.colors = vertex.colors))
-}
-
-## Compute the scan statistics
-## If the scan statistic belong
[…]

### 2012-06-22 Rcodes/tstat0-MC10k-1st-maxd-n100-m9.R

@@ -1,171 +1,0 @@
-read.maxd <- function(){
-
-  load("tstat0-MC10k-1st-maxd-n100-m9.RData")
-
-  maxd0.mat <- matrix(0, ncol = 11*length(tstat0), nrow = length(tstat0[[1]]))
-
-  for(i in 1:nrow(maxd0.mat)){
-    for(j in 1:length(tstat0)){
-      maxd0.mat[i,((j-1)*11+1):(11*j)] <- tstat0[[j]][[i]][1:11]
-    }
-  }
-
-  maxdA.mat <- matrix(0, ncol = length(tstat0), nrow = length(tstat0[[1]]))
-  for(i in 1:nrow(maxdA.mat)){
-    for(j in 1:length(tstat0)){
-      maxdA.mat[i,j] <- tstat0[[j]][[i]][12]
-    }
-  }
-}
-
-read.scan <- function(){
-  
-  load("tstat1-MC10k-1st-scan-n100-m9.Rbin")
-  scan.null.mat <- matrix(0, ncol = 11*length(tstat1), nrow = length(tstat1[[1]]))
-
-  for(i in 1:nrow(scan.null.mat)){
-    for(j in 1:(ncol(scan.null.mat)/11)){
-      scan.null.mat[i,((j-1)*11+1):(j*11)] <- tstat1[[j]][[i]][1:11]
-    }
-  }
-
-  scan.alt.mat <- matrix(0, ncol = length(tstat1), nrow = length(tstat1[[1]]))
-  for(i in 1:nrow(scan.alt.mat)){
-    for(j in 1:ncol(scan.alt.mat)){
-      scan.alt.mat[i,j] <- tstat1[[j]][[i]][12]
-    }
-  }
-}
-
-
-read.numtri <- function(){
-  tstat3 <- dget("tstat3-MC10k-1st-ntri-n100-m9.RData.gz")
-  numtri.null.mat <- matrix(0, ncol = 11*length(tstat2), nrow = length(tstat2[[1]]))
-
-  for(i in 1:nrow(numtri.null.mat)){
-    for(j in 1:(ncol(numtri.null.mat)/11)){
-      numtri.null.mat[i,((j-1)*11+1):(j*11)] <- tstat2[[j]][[i]][1:11]
-    }
-  }
-
-  numtri.alt.mat <- matrix(0, ncol = length(tstat2), nrow = length(tstat2[[1]]))
[…]

### 2013-02-27 response.tex
Version accepted to TSP

@@
-We thank the referees for their feedback. We have
-revised the paper in light of their comments and criticism, especially 
-on issues regarding the paper appropriateness for the Trans on SP
-readership. A more detailed response to the comments from each referee
-is included below.
+Thank you for the careful reading of our manuscript and the referee
+report and we deeply appreciate your comments and critiques on the
+manuscript. The specific comments and suggestions for review have been
+followed, and the result is an improved manuscript. In particular,
+the discussions surrounding the theoretical results in Section IV and
+the experiments in Section V had been expanded, most importantly the
+addition of Figure 5, illustrating, through Q-Q plots, 
+the convergence of the statistics to their limiting distribution. Below we
+give specific responses to the comments of the reviewers.  Again, we
+thank the editor and reviewers for their valuable comments.
 

### 2013-02-27 decision2.tex
Version accepted to TSP

Thank you for the careful reading of our manuscript and the referee
report and we deeply appreciate your comments and critiques on the
manuscript. The specific comments and suggestions for review have been
followed, and the result is an improved manuscript. In particular,
the discussions surrounding the theoretical results in Section IV and
the experiments in Section V had been expanded, most importantly the
addition of Figure 5, illustrating, through Q-Q plots, 
the convergence of the statistics to their limiting distribution. Below we
give specific responses to the comments of the reviewers.  Again, we
thank the editor and reviewers for their valuable comments.

==================================================
Reviewer: 1

Recommendation: AQ - Publish In Minor, Required Changes

Comments:
(1) Expand the discussion on the connection of your approach with the
wavelet representations for graphs; a small paragraph, 3-4 sentences,
would suffice.

*** Response: 
We have expanded the discussion on related works. In
particular, we described the similarities between the construction and
use of the wavelet representation for traffic analysis in [Crovella & Kolaczyk, 2003] and
anomaly detection using locality/scan statistics in our manuscript.

(2) Comment more explicitly on the choice of the running-average window l. Is there a guideline?

*** Response: 
We had added a comment about the choice of $l$ right before
the end of Section 3. In general, the choice of $l$ depends on the
practitioner. Small values of $l$ could
induce large fluctuations in the temporal standardization statistics,
which might lead to a higher false positive rate. Large values of $l$,
on the other hand, could induce over-smoothing, leading to a higher
false negative rate. As for the Enron data
experiment, $l = 20$ was used in the earlier scan paper on Enron graph
(Priebe et al. 2005) so we used it to keep the comparisons between the
two papers meaningful.

(3) Add reference [*] [*] C. E. Priebe, N. H. Lee, Y. Park, and
M. Tang, "Attribute Fusion in a Latent Process Model for Time Series
of Graphs," 2011 IEEE Workshop on Statistical Signal Processing
(SSP2011), July 2011.
*** Response: This had been done.

==================================
Reviewer: 2

Recommendation: RQ - Review Again After Major Changes

Comments:

(1) The paper has been improved somewhat but it is still written in a
terse mathematical style that is not consistent with the signal
processing audience. The introductory section is from [1] but the
reader would not know this if [1] had not been read.  The Lemmas and
Theorems in the power analysis section are inadequately discussed in
terms of their practical applicability to problems of signal
processing and time series analysis. In particular, the weak
convergence theory of Thms 4, 6 and 9 is interesting but the utility
of these theorems is not adequately illustrated.  The Gumbel limits
are not explained, interpreted or illustrated in the numerical
section. The authors could, for example, illustrate how these results
can be used to set thresholds or select the linear parameter
lambda. How large does n and l have to be for these limits to become
good apprxoimation? Q-Q plots of simulation or real (Enron) data
against student-t and Gumbel would give an idea of how fast these
approximations converge.  In any case, any theoretical results that
are not illustrated for a SP problem should be removed from the paper.

*** Response 
We have reorganized and expanded the paper to make the connections
between the theoretical results in Section IV and their applicability
to signal processing and time-series analysis more explicit. In
particular, section IV now starts off with a discussion relating the
change-point detection framework in Section III with the theoretical
results, i.e., the theoretical results provided power estimates for
each choice of the fusion parameter $\lambda$. We have also note how
the theoretical results in this paper are extensions of results that 
exist in the literature.

The rate of convergence for the limiting distribution is an important
result that we had ignored in the paper. The paper of [1] contains
evaluation (via Monte Carlo estimates) of rate of convergence of size,
max degree, number of triangles and scan to the corresponding limiting
distributions, i.e., normal, Gumbel, normal and Gumbel in the
Erdos-Renyi and kindey-egg settings. Note that they consider only a
single (unattributed) graph at a time. The paper Pao, Coppersmith and
Priebe (citation below) showed that the limiting distribution with the
associated parameters is sufficiently accurate for the size and max
degree statistic starting at $n = 100$ and for number of of triangles
and scan statistics starting at $n = 1000$.

In general, for the case of degree and number of triangles provided
that the normal distribution is a good large-sample approximation,
then the weak convergence of the temporal standardization statistics
to the Student's t-distribution holds independent of $l$, as long as
the underlying time-series of graphs is stationary during that time
interval.

For the case of max degree and scan, the weak convergence of
their temporal standardization to the Gumbel distribution requires
both that $n$ is sufficiently large (so that the Gumbel distribution
is a good large-sample approximation at any time $t$) and that $l$ is
sufficiently large, e.g., $l \geq 100$. However, if $n$ is
sufficiently large, then the limiting distribution of the temporal
standardization for any value of $l \geq 2$ converges weakly to the
convolution of $l$ Gumbel distributed random variables as long as the
underlying time-series is stationary during that time interval. Power
estimates in this case (where both the null and alternative is a
convolution of Gumbel random variables) is also straightforward but tedious.

The manuscript has now been revised to include parts of the above
discussion on the limiting distribution (right after the statement of
the relevant results) and how it is applied to the simulation
experiment setup (second paragraph of Section V). In particular, Q-Q
plots for the temporal standardization of the max degree, number of
triangles and scan statistics against the limiting distributions had
been added to the manuscript. These Q-Q plots help to illustrate the
convergence of these temporal standardization statistics to their
limiting distribution.

[1] Pao, Coppersmith, and Priebe, ``Statistical inference of random graphs: Comparative
power analysis via Monte Carlo'' Journal of Computational and Graphical Statistics, 2011.

***

(2) The Introduction should very clearly state the differences between [1]
and the present work. The reader should not have to read [1], which
this reviewer did, in order to figure this out.

*** Response
The manuscript now include a short paragraph at the end of the introductory
section describing the relationships between [1], another paper that
was an earlier version of the manuscript and was presented at the 2011
SSP workshop in Nice, France, and the manuscript. In particular the
current manuscript used the generative model for the time-series of graphs
from [1]. Also, the setup of anomaly/change-point detection and the
use of temporal standardization of the graph invariants as the test
statistics are also identical to that done in [1] (this setup or
its variation had been used previously by some of the authors, see
e.g., Priebe et al ``Scan statistics on Enron graphs''). However, [1] only
considered the use of the size invariant. The earlier version of the
manuscript that was presented at the 2011 SSP workshop motivates the
current manuscript and include a preliminary version of the simulation
experiment in Section V.  
***

(3) In Fig 4 the 1st and 2nd order approximations appear to upper bound
the exact curve for all cases studied.  Is this provable? The authors
should comment.

*** Response
Two of the authors of the manuscript had noticed the above
phenomenon (and the fact that the 2nd-order approximation is monotone
increasing in $r$, the process rate parameter) in their previous paper
[1]. However, they have not been able to explain the phenomenon. It
might be possible to show that the
second-order approximations is monotone increasing in $r$, which also implies
that the first-order approximation is an upper bound for the second order
approximations, for the size and number of triangle statistic using some
recent results in [2]. However, to the best of our knowledge,
the explanation for the full phenomenon is still elusive. We would be
very much interested in knowing an explanation behind this phenomenon.

[2] Priebe and Rukhin, ``Invariant theory for hypothesis testing on
graphs'', Proceedings of the 58th World Statistic Congress, 2011. 
***

(4) Non-standard notation (e.g. [n], [K+1]) has now been defined but
it should be aligned with a more standard notation (e.g. {1,...,n} and
{1,...,K+1}) familar to SP audience. There are also many typographical
errors in the manuscript. The authors need to go through and carefully
correct errors of syntax and omissions of important assumptions. A
sampling of the ones I found is:

* Eqn (2) , <x_u,x_v> should be <X_u,X_v>.
*Line 14 on p. 5: "phenoma" should be "phenomenon"
*Line 19 on p. 5; "Permutation of the vertex labels does not affect
our subsequent analysis"
*Line 23 p 5: "Of general interests" should be replaced by "Of general interest"
*Line 31 on p 7: "parameters" should be "parameter"
*Line 4 on p 8: "interests" should be "interest"
*Line 12 on p 8: the "I" notation used to define \Gamma_{uv}(k) shoudl
be defined explicitly as a vector of indicator functions since this is
not standard notation. Furthermore, on the next line the statement
\Gamma_{uv}=0 is confusing since \Gamma_{uv} is a vector. A better
notation will be \Gamma_{uv} =[0,\ldots,0]^T.
*Thm 1 needs to be stated more precisely with all necessary
assumptions, as in [1]. The quantites defined are functions of m,n,l
and involve matrices eta_{ij}. In [1] these matrices are assumed to be
positive definite and the matrix \zeta is assumed to be
non-zero. These assumptions need to be stated here too.

*** Response
The above errors had all been fixed. In particular the statement of
the theoretical results had been revised or corrected. An additional
assumption regarding the matrix \zeta being positive definite is now
included in Theorem 1. All occurrences of the fraction $\sqrt{\pi}/6$ in Theorem 6 and
Theorem 9 had now been changed/corrected to $\sqrt{6}/pi$.

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2013-02-27 ref_comments.tex
Version accepted to TSP

Paper:T-SP-14347-2012, "Attribute fusion in a latent process model for
time series of graphs"

Dear Prof.  Priebe,

I am writing to you concerning the above referenced manuscript, which
you submitted to the IEEE Transactions on Signal Processing.

Based on the enclosed set of reviews (**See note below about
attachments), I have decided that the manuscript be REVISED AND
RESUBMITTED (RQ). Judging by the recommendations (RQ and A), one may
have impression that the reviewers differ in their opinions
substantially. As a matter of fact they don't. They both are very much
concerned by the fact that your paper still lacks the focus on
applicability and practicality (Reviewer #2 points this out very
strongly in the confidential part of his review). Reviewer #1 proposed
changes that could make your paper more practically oriented, and
hence more interesting for the signal processing community. I strongly
recommend that you follow his advice. This could result in a good
paper and would prevent us from wasting your efforts (which are very
much appreciated) and the efforts of the reviewers.

Your revised manuscript must be submitted back to Manuscript Central
http://mc.manuscriptcentral.com/tsp-ieee no later than 6 weeks from
the date of this letter together with a point-by-point reply that
explains how you addressed the reviewers' comments.

Please note that the reviewers will review your revised article only
one more time. The only decisions available to an AE after a second
round of reviews are A(Accepted), AQ(Accepted with Mandatory
Revisions), and R(Reject).

If we do not receive your revised manuscript within 6 weeks from the
date of this letter, your manuscript will be considered withdrawn.

To revise your manuscript, log into
http://mc.manuscriptcentral.com/tsp-ieee and enter your Author Center,
where you will find your manuscript title listed under "Manuscripts
with Decisions."  Under "Actions," click on "Create a Revision."  Your
manuscript number has been appended to denote a revision.

You will be unable to make your revisions on the originally submitted
version of the manuscript.  Instead, revise your manuscript using a
word processing program and save it on your computer.

Once the revised manuscript is prepared, you can upload it and submit
it through your Author Center.

When submitting your revised manuscript, you will be able to respond
to the comments made by the reviewer(s) in the space provided.  You
can use this space to document any changes you make to the original
manuscript.  In order to expedite the processing of the revised
manuscript, please be as specific as possible in your response to the
reviewer(s).

IMPORTANT: Your original files are available to you when you upload
your revised manuscript.  Please delete any redundant files before
completing the submission.

If you have any questions regarding the reviews, please contact me.
Any other inquiries should be directed to Rebecca Wollman.
Additionally, please provide a detailed explanation how the revised
manuscript addresses each of the comments from the reviewers.

Best regards,

Prof. Maciej Niedzwiecki
Associate Editor
IEEE Transactions on Signal Processing
maciekn@eti.pg.gda.pl, maciekn@pg.gda.pl

Rebecca Wollman
Coordinator Society Publications
IEEE Signal Processing Society
r.wollman@ieee.org

** {This applies to SUBMITTING AUTHOR Accounts ONLY: You can find any
  possible ATTACHMENTS FROM THE REVIEWERS by going to the "Manuscript
  with Decisions" status link in your Author Center and clicking on
  "view decision letter". They are located at the bottom of decision
  letter under "Files attached" heading}

Reviewer Comments:

Reviewer: 1

Recommendation: RQ - Review Again After Major Changes

Comments: The revision is much improved. The authors have included
better motivation of their approach, related the approach to signal
processing applications, included results on convergence analysis, and
reported diagnostic goodness of fit tests validating some of the
theoretical predictions.

This reviewer especially appreciates the inclusion of a review of the
weak convergence results that can be applied to specify asymptotic
distributions of the proposed test statistics.  These results are used
to compute power approximations that are in turn used to select
optimal parameters, e.g. lambda.  However, especially for a paper
emphasizing testing and anomaly detection, the principal utility of
these results are to specification of approximate p-values. Yet, the
authors do not take advantage of the stated theory on asymptotic
distributions to provide such p-values to quantify Type I error
control on statements that are made about possible anomalies- e.g. in
Figs. 7 and 8. Given the asymptotic results provided, this does not
seem difficult to do and the reviewer is somewhat puzzled that the
authors did not do it. Without such illustration of the theory, the
utility of the convergence analysis will likely be lost on the reader
and the author's final sentence "...these statistics can serve as the
basis for simple and robust inference procedures on time-series of
(attributed) graphs." suffers loss in credibility. Thus the authors
need to address this point in a next round of review.

This reviewer still found some typographical and stylistic errors in
the revision. I suggest the last author give the paper a thorough
proofread next time to improve the english syntax.  Here are some that
I found:

Page 2 of manuscript: 
Line 10: "...can also be use to identify..." ->
"...can also be used to identify..."  
Line 46: "...(emphasis from
[4])..." -> "...(emphasis in [4])..."

Page 5 of manuscript: 
Line 13: "...an edge in G with attribute k with
probability..." -> "...an edge in G having attribute k with
probability..."

Page 9 of manuscript:
Line 7: "...done via spectral embedding technique..." ->  
"...done via spectral embedding techniques..."
Line 12: "....the issue of parameter estimation is fundamental but
feasible..." -> "....parameter estimation is  feasible..."

Caption of Fig. 8: "each graph invariants" -> "each graph invariant"

Additional Questions:
1. Is the topic appropriate for publication in these transactions?: Yes

2. Is the topic important to colleagues working in the field?: Yes

Explain:

1. Is the paper technically sound?: Yes

why not?:

2. Is the coverage of the topic sufficiently comprehensive and balanced?: Yes

3. How would you describe technical depth of paper?: Appropriate for
the Generally Knowledgeable Individual Working in the Field or a
Related Field

4. How would you rate the technical novelty of the paper?: Somewhat Novel

1. How would you rate the overall organization of the paper?: Satisfactory

2. Are the title and abstract satisfactory?: Yes

Explain:

3. Is the length of the paper appropriate? If not, recommend how the
length of the paper should be amended, including a possible target
length for the final manuscript.: Yes

4. Are symbols, terms, and concepts adequately defined?: Yes

5. How do you rate the English usage? : Needs improvement

6. Rate the Bibliography: Satisfactory

null:

1. How would you rate the technical contents of the paper?: Good

2. How would you rate the novelty of the paper?: Sufficiently Novel

3. How would you rate the "literary" presentation of the paper?: Mostly Accessible

4. How would you rate the appropriateness of this paper for
publication in this IEEE Transactions?: Good Match

Reviewer: 2

Recommendation: A - Publish Unaltered

Comments: 
The authors improve their previous version of the manuscript
by introducing incremental changes including the following:

1. An expansion of the literature on corresponding wavelet
representations and the connection of this manuscript to previous
works (citations [1] and [7]) in Section 1.

2. A comment on the choice of the value of l and a minor section
restructuring (at the boundaries of Section 3 and 4).

3. Q-Q plots and a small discussion on relating the theoretical
results to their first simulation example (mainly second paragraph of
Section 5).

4. Potential benefits from generalizations of their results (the last
two paragraphs of Section 6).

Very minor typos: i) the size of a n-hop neighborhood -> the size of
an n-hop neighborhood (page 2, line 48) ii) all the n-hop neighborhood
-> all n-hop neighborhoods (page 2, line 52)

Additional Questions:
1. Is the topic appropriate for publication in these transactions?: Perhaps

2. Is the topic important to colleagues working in the field?: Moderately So

Explain:

1. Is the paper technically sound?: Yes

why not?:

2. Is the coverage of the topic sufficiently comprehensive and balanced?: Yes

3. How would you describe technical depth of paper?: Appropriate for
the Generally Knowledgeable Individual Working in the Field or a
Related Field

4. How would you rate the technical novelty of the paper?: Not Novel

1. How would you rate the overall organization of the paper?: Satisfactory

2. Are the title and abstract satisfactory?: Yes

Explain:

3. Is the length of the paper appropriate? If not, recommend how the
length of the paper should be amended, including a possible target
length for the final manuscript.: Yes

4. Are symbols, terms, and concepts adequately defined?: Yes

5. How do you rate the English usage? : Satisfactory

6. Rate the Bibliography: Satisfactory

null:

1. How would you rate the technical contents of the paper?: Good

2. How would you rate the novelty of the paper?: Not Novel

3. How would you rate the "literary" presentation of the paper?: Mostly Accessible

4. How would you rate the appropriateness of this paper for
publication in this IEEE Transactions?: Weak Match
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2013-02-27 response2.tex
Version accepted to TSP

--- 2013-02-27 decision2.tex
@@
+\documentclass{article}
+\pdfminorversion=4
+\usepackage{parskip}
+\usepackage{fontenc}
+\begin{document}
+\title{Response to reviewers}
+\maketitle
+\date{}
 Thank you for the careful reading of our manuscript and the referee
@@
 the convergence of the statistics to their limiting distribution. Below we
-give specific responses to the comments of the reviewers.  Again, we
+give specific responses to the comments of the reviewers (the
+reviewers comments are in italic). Again, we
 thank the editor and reviewers for their valuable comments.
 
-==================================================
-Reviewer: 1
-
+\section{Comments from Reviewer 1}
 Recommendation: AQ - Publish In Minor, Required Changes
@@
 Comments:
-(1) Expand the discussion on the connection of your approach with the
+{\em (1) Expand the discussion on the connection of your approach with the
 wavelet representations for graphs; a small paragraph, 3-4 sentences,
-would suffice.
+would suffice.}
 
-*** Response: 
-We have expanded the discussion on related works. In
+*** Response: We have expanded the discussion on related works. In
 particular, we described the similarities between the construction and
-use of the wavelet representation for traffic analysis in [Crovella & Kolaczyk, 2003] and
-anomaly detection using locality/scan statistics in our manuscript.
+use of the wavelet representation for traffic analysis in [Crovella \&
+Kolaczyk, 2003] and anomaly detection using locality/scan statistics
+in our manuscript.
 
-(2) Comment more explicitly on the choice of the running-average window l. Is there a guideline?
+{\em (2) Comment more explicitly on the choice of the running-average
+window l. Is there a guideline?}
 
-*** Response: 
-We had added a comment about the choice of $l$ right before
-the end of Section 3. In general, the choice of $l$ depends on the
-practitioner. Small values of $l$ could
-induce large fluctuations in the temporal standardization statistics,
-which might lead to a higher false positive rate. Large values of $l$,
-on the other hand, could induce over-smoothing, leading to a higher
-false negative rate. As for the Enron data
-experiment, $l = 20$ was used in the earlier scan paper on Enron graph
-(Priebe et al. 2005) so we used it to keep the comparisons between the
-two papers meaningful.
+*** Response: We had added a comment about the choice of $l$ right
+before the end of Section 3. In general, the choice of $l$ depends on
+the practitioner. Small values of $l$ could induce large fluctuations
+in the temporal standardization statistics, which might lead to a
+higher false positive rate. Large values of $l$, on the other hand,
+could induce over-smoothing, leading to a higher false negative
+rate. As for the Enron data experiment, $l = 20$ was used in the
+earlier scan paper on Enron graph (Priebe et al. 2005) so we used it
+to keep the comparisons between the two papers meaningful.
 
-(3) Add reference [*] [*] C. E. Priebe, N. H. Lee, Y. Park, and
+{\em (3) Add reference [*] C. E. Priebe, N. H. Lee, Y. Park, and
 M. Tang, "Attribute Fusion in a Latent Process Model for Time Series
 of Graphs," 2011 IEEE Workshop on Statistical Signal Processing
-(SSP2011), July 2011.
+(SSP2011), July 2011.}
+
 *** Response: This had been done.
 
-==================================
-Reviewer: 2
+\section{Comments from Reviewer 2}
 
@@
 
-(1) The paper has been improved somewhat but it is still written in a
+{\em (1) The paper has been improved somewhat but it is still written in a
 terse mathematical style that is not consistent with the signal
@@
 approximations converge.  In any case, any theoretical results that
-are not illustrated for a SP problem should be removed from the paper.
+are not illustrated for a SP problem should be removed from the paper.}
 
-*** Response 
-We have reorganized and expanded the paper to make the connections
-between the theoretical results in Section IV and their applicability
-to signal processing and time-series analysis more explicit. In
-particular, section IV now starts off with a discussion relating the
-change-point detection framework in Section III with the theoretical
-results, i.e., the theoretical results provided power estimates for
-each choice of the fusion parameter $\lambda$. We have also note how
-the theoretical results in this paper are extensions of results that 
-exist in the literature.
+*** Response: We have reorganized and expanded the paper to make the
+connections between the theoretical results in Section IV and their
+applicability to signal processing and time-series analysis more
+explicit. In particular, section IV now starts off with a discussion
+relating the change-point detection framework in Section III with the
+theoretical results, i.e., the theoretical results provided power
+estimates for each choice of the fusion parameter $\lambda$. We have
+also note how the theoretical results in this paper are extensions of
+results that exist in the literature.
 
@@
 
-[1] Pao, Coppersmith, and Priebe, ``Statistical inference of random graphs: Comparative
-power analysis via Monte Carlo'' Journal of Computational and Graphical Statistics, 2011.
+[1] Pao, Coppersmith, and Priebe, ``Statistical inference of random
+graphs: Comparative power analysis via Monte Carlo'' Journal of
+Computational and Graphical Statistics, 2011.
 
-***
+{\em (2) The Introduction should very clearly state the differences between [1]
+and the present work. The reader should not have to read [1], which
+this reviewer did, in order to figure this out.}
 
-(2) The Introduction should very clearly state the differences between [1]
-and the present work. The reader should not have to read [1], which
-this reviewer did, in order to figure this out.
+*** Response: The manuscript now include a short paragraph at the end
+of the introductory section describing the relationships between [1],
+another paper that was an earlier version of the manuscript and was
+presented at the 2011 SSP workshop in Nice, France, and the
+manuscript. In particular the current manuscript used the generative
+model for the time-series of graphs from [1]. Also, the setup of
+anomaly/change-point detection and the use of temporal standardization
+of the graph invariants as the test statistics are also identical to
+that done in [1] (this setup or its variation had been used previously
+by some of the authors, see e.g., Priebe et al ``Scan statistics on
+Enron graphs''). However, [1] only considered the use of the size
+invariant. The earlier version of the manuscript that was presented at
+the 2011 SSP workshop motivates the current manuscript and include a
+preliminary version of the simulation experiment in Section V.  ***
 
-*** Response
-The manuscript now include a short paragraph at the end of the introductory
-section describing the relationships between [1], another paper that
-was an earlier version of the manuscript and was presented at the 2011
-SSP workshop in Nice, France, and the manuscript. In particular the
-current manuscript used the generative model for the time-series of graphs
-from [1]. Also, the setup of anomaly/change-point detection and the
-use of temporal standardization of the graph invariants as the test
-statistics are also identical to that done in [1] (this setup or
-its variation had been used previously by some of the authors, see
-e.g., Priebe et al ``Scan statistics on Enron graphs''). However, [1] only
-considered the use of the size invariant. The earlier version of the
-manuscript that was presented at the 2011 SSP workshop motivates the
-current manuscript and include a preliminary version of the simulation
-experiment in Section V.  
-***
+{\em (3) In Fig 4 the 1st and 2nd order approximations appear to upper bound
+the exact curve for all cases studied.  Is this provable? The authors
+should comment.}
 
-(3) In Fig 4 the 1st and 2nd order approximations appear to upper bound
-the exact curve for all cases studied.  Is this provable? The authors
-should comment.
-
-*** Response
-Two of the authors of the manuscript had noticed the above
-phenomenon (and the fact that the 2nd-order approximation is monotone
-increasing in $r$, the process rate parameter) in their previous paper
-[1]. However, they have not been able to explain the phenomenon. It
-might be possible to show that the
-second-order approximations is monotone increasing in $r$, which also implies
-that the first-order approximation is an upper bound for the second order
-approximations, for the size and number of triangle statistic using some
-recent results in [2]. However, to the best of our knowledge,
-the explanation for the full phenomenon is still elusive. We would be
-very much interested in knowing an explanation behind this phenomenon.
+*** Response: Two of the authors of the manuscript had noticed the
+above phenomenon (and the fact that the 2nd-order approximation is
+monotone increasing in $r$, the process rate parameter) in their
+previous paper [1]. However, they have not been able to explain the
+phenomenon. It might be possible to show that the second-order
+approximations is monotone increasing in $r$, which also implies that
+the first-order approximation is an upper bound for the second order
+approximations, for the size and number of triangle statistic using
+some recent results in [2]. However, to the best of our knowledge, the
+explanation for the full phenomenon is still elusive. We would be very
+much interested in knowing an explanation behind this phenomenon.
 
@@
 
-(4) Non-standard notation (e.g. [n], [K+1]) has now been defined but
+{\em (4) Non-standard notation (e.g. [n], [K+1]) has now been defined but
 it should be aligned with a more standard notation (e.g. {1,...,n} and
@@
 
-* Eqn (2) , <x_u,x_v> should be <X_u,X_v>.
-*Line 14 on p. 5: "phenoma" should be "phenomenon"
-*Line 19 on p. 5; "Permutation of the vertex labels does not affect
+\begin{enumerate}
+  \item Eqn (2) , $<x_u,x_v>$ should be $<X_u,X_v>$.
+  \item Line 14 on p. 5: "phenoma" should be "phenomenon"
+  \item Line 19 on p. 5; "Permutation of the vertex labels does not affect
 our subsequent analysis"
-*Line 23 p 5: "Of general interests" should be replaced by "Of general interest"
-*Line 31 on p 7: "parameters" should be "parameter"
-*Line 4 on p 8: "interests" should be "interest"
-*Line 12 on p 8: the "I" notation used to define \Gamma_{uv}(k) shoudl
+\item Line 23 p 5: "Of general interests" should be replaced by "Of general interest"
+\item Line 31 on p 7: "parameters" should be "parameter"
+\item Line 4 on p 8: "interests" should be "interest"
+\item Line 12 on p 8: the "I" notation used to define $\Gamma_{uv}(k)$ should
 be defined explicitly as a vector of indicator functions since this is
 not standard notation. Furthermore, on the next line the statement
-\Gamma_{uv}=0 is confusing since \Gamma_{uv} is a vector. A better
-notation will be \Gamma_{uv} =[0,\ldots,0]^T.
-*Thm 1 needs to be stated more precisely with all necessary
+$\Gamma_{uv}=0$ is confusing since $\Gamma_{uv}$ is a vector. A better
+notation will be $\Gamma_{uv} =[0,\ldots,0]^T$.
+\item Thm 1 needs to be stated more precisely with all necessary
 assumptions, as in [1]. The quantites defined are functions of m,n,l
-and involve matrices eta_{ij}. In [1] these matrices are assumed to be
-positive definite and the matrix \zeta is assumed to be
+and involve matrices $eta_{ij}$. In [1] these matrices are assumed to be
+positive definite and the matrix $\zeta$ is assumed to be
 non-zero. These assumptions need to be stated here too.
+\end{enumerate}}
 
-*** Response
-The above errors had all been fixed. In particular the statement of
-the theoretical results had been revised or corrected. An additional
-assumption regarding the matrix \zeta being positive definite is now
-included in Theorem 1. All occurrences of the fraction $\sqrt{\pi}/6$ in Theorem 6 and
-Theorem 9 had now been changed/corrected to $\sqrt{6}/pi$.
+*** Response: The above errors had all been fixed. In particular the
+statement of the theoretical results had been revised or corrected. An
+additional assumption regarding the matrix $\zeta$ being positive
+definite is now included in Theorem 1. All occurrences of the fraction
+$\sqrt{\pi}/6$ in Theorem 6 and Theorem 9 had now been
+changed/corrected to $\sqrt{6}/pi$.
+\end{document}
 

### 2013-02-27 response3.tex
Version accepted to TSP

--- 2013-02-27 ref_comments.tex
@@
-Paper:T-SP-14347-2012, "Attribute fusion in a latent process model for
-time series of graphs"
-
-Dear Prof.  Priebe,
-
-I am writing to you concerning the above referenced manuscript, which
-you submitted to the IEEE Transactions on Signal Processing.
-
-Based on the enclosed set of reviews (**See note below about
-attachments), I have decided that the manuscript be REVISED AND
-RESUBMITTED (RQ). Judging by the recommendations (RQ and A), one may
-have impression that the reviewers differ in their opinions
-substantially. As a matter of fact they don't. They both are very much
-concerned by the fact that your paper still lacks the focus on
-applicability and practicality (Reviewer #2 points this out very
-strongly in the confidential part of his review). Reviewer #1 proposed
-changes that could make your paper more practically oriented, and
-hence more interesting for the signal processing community. I strongly
-recommend that you follow his advice. This could result in a good
-paper and would prevent us from wasting your efforts (which are very
-much appreciated) and the efforts of the reviewers.
-
-Your revised manuscript must be submitted back to Manuscript Central
-http://mc.manuscriptcentral.com/tsp-ieee no later than 6 weeks from
-the date of this letter together with a point-by-point reply that
-explains how you addressed the reviewers' comments.
-
-Please note that the reviewers will review your revised article only
-one more time. The only decisions available to an AE after a second
-round of reviews are A(Accepted), AQ(Accepted with Mandatory
-Revisions), and R(Reject).
-
-If we do not receive your revised manuscript within 6 weeks from the
-date of this letter, your manuscript will be considered withdrawn.
-
-To revise your manuscript, log into
-http://mc.manuscriptcentral.com/tsp-ieee and enter your Author Center,
-where you will find your manuscript title listed under "Manuscripts
-with Decisions."  Under "Actions," click on "Create a Revision."  Your
-manuscript number has been appended to denote a revision.
-
-You will be unable to make your revisions on the originally submitted
-version of the manuscript.  Instead, revise your manuscript using a
-word processing program and save it on your computer.
-
-Once the revised manuscript is prepared, you can upload it and submit
-it through your Author Center.
-
-When submitting your revised manuscript, you will be able to respond
-to the comments made by the reviewer(s) in the space provided.  You
-can use this space to document any changes you make to the original
-manuscript.  In order to expedite the processing of the revised
-manuscript, please be as specific as possible in your response to the
-reviewer(s).
-
-IMPORTANT: Your original files are available to you when you upload
-your revised manuscript.  Please delete any redundant files before
-completing the submission.
-
-If you have any questions regarding the reviews, please contact me.
-Any other inquiries should be directed to Rebecca Wollman.
-Additionally, please provide a detailed explanation how the revised
-manuscript addresses each of the comments from the reviewers.
-
-Best regards,
-
-Prof. Maciej Niedzwiecki
-Associate Editor
-IEEE Transactions on Signal Processing
-maciekn@eti.pg.gda.pl, maciekn@pg.gda.pl
-
-Rebecca Wollman
-Coordinator Society Publications
-IEEE Signal Processing Society
-r.wollman@ieee.org
-
-** {This applies to SUBMITTING AUTHOR Accounts ONLY: You can find any
-  possible ATTACHMENTS FROM THE REVIEWERS by going to the "Manuscript
-  with Decisions" status link in your Author Center and clicking on
-  "view decision letter". They are located at the bottom of decision
-  letter under "Files attached" heading}
-
-Reviewer Comments:
-
-Reviewer: 1
-
+\documentclass{article}
+\pdfminorversion=4
+\usepackage{parskip}
+\usepackage{fontenc}
+\begin{document}
+\title{Response to reviewers}
+\maketitle
+\date{} Thank you for the careful re-reading of our manuscript and the
+referee report and we deeply appreciate your comments and critiques on
+the manuscript. The specific comments and suggestions for review have
+been followed. The
+comments on the lack of p-values are particularly relevant and we thank
+the referees for pointing it out once again. We went back to the 
+experiments on the Enron email corpus to obtain p-values for using
+$T_{\lambda}^{l}$ as a statistic for hypothesis testing. The results
+are detailed in Section 5 (on pages 9 \& 10 of the double column
+version of the manuscript). Below we
+give specific responses to the comments of the reviewers (the
+reviewers comments are in italic). 
+\section{Comments from Reviewer 1}
 Recommendation: RQ - Review Again After Major Changes
 
-Comments: The revision is much improved. The authors have included
+Comments: 
+{\em (1) The revision is much improved. The authors have included
 better motivation of their approach, related the approach to signal
@@
 need to address this point in a next round of review.
+}
 
-This reviewer still found some typographical and stylistic errors in
+*** Response: The p-values for the Enron email corpus were something we
+should have done in earlier versions of the manuscript and we agree
+with the referee that the principal utility of the theoretical results
+in Section IV is to the specification of these approximate
+p-values. We believe that the discussion on p-values in this new
+version is a succinct example of the utility of the theoretical results.
+
+{\em (2): This reviewer still found some typographical and stylistic errors in
 the revision. I suggest the last author give the paper a thorough
@@
 Caption of Fig. 8: "each graph invariants" -> "each graph invariant"
+}
 
-Additional Questions:
-1. Is the topic appropriate for publication in these transactions?: Yes
+*** Response*** 
+We have gone through the manuscript to check for errors in grammatical usage.
 
-2. Is the topic important to colleagues working in the field?: Yes
-
-Explain:
-
-1. Is the paper technically sound?: Yes
-
-why not?:
-
-2. Is the coverage of the topic sufficiently comprehensive and balanced?: Yes
-
-3. How would you describe technical depth of paper?: Appropriate for
-the Generally Knowledgeable Individual Working in the Field or a
-Related Field
-
-4. How would you rate the technical novelty of the paper?: Somewhat Novel
-
-1. How would you rate the overall organization of the paper?: Satisfactory
-
-2. Are the title and abstract satisfactory?: Yes
-
-Explain:
-
-3. Is the length of the paper appropriate? If not, recommend how the
-length of the paper should be amended, including a possible target
-length for the final manuscript.: Yes
-
-4. Are symbols, terms, and concepts adequately defined?: Yes
-
-5. How do you rate the English usage? : Needs improvement
-
-6. Rate the Bibliography: Satisfactory
-
-null:
-
-1. How would you rate the technical contents of the paper?: Good
-
-2. How would you rate the novelty of the paper?: Sufficiently Novel
-
-3. How would you rate the "literary" presentation of the paper?: Mostly Accessible
-
-4. How would you rate the appropriateness of this paper for
-publication in this IEEE Transactions?: Good Match
-
-Reviewer: 2
-
+\section{Comments from Reviewer 2}
 Recommendation: A - Publish Unaltered
@@
 Comments: 
-The authors improve their previous version of the manuscript
+{\em The authors improve their previous version of the manuscript
 by introducing incremental changes including the following:
-
-1. An expansion of the literature on corresponding wavelet
-representations and the connection of this manuscript to previous
-works (citations [1] and [7]) in Section 1.
-
-2. A comment on the choice of the value of l and a minor section
-restructuring (at the boundaries of Section 3 and 4).
-
-3. Q-Q plots and a small discussion on relating the theoretical
-results to their first simulation example (mainly second paragraph of
-Section 5).
-
-4. Potential benefits from generalizations of their results (the last
-two paragraphs of Section 6).
 
@@
 an n-hop neighborhood (page 2, line 48) ii) all the n-hop neighborhood
--> all n-hop neighborhoods (page 2, line 52)
+-> all n-hop neighborhoods (page 2, line 52)}
 
-Additional Questions:
-1. Is the topic appropriate for publication in these transactions?: Perhaps
+*** Response ***
+We have fixed these and other typos noted by the first referee in the text.
+\end{document}
 
-2. Is the topic important to colleagues working in the field?: Moderately So
-
-Explain:
-
-1. Is the paper technically sound?: Yes
-
-why not?:
-
-2. Is the coverage of the topic sufficiently comprehensive and balanced?: Yes
-
-3. How would you describe technical depth of paper?: Appropriate for
-the Generally Knowledgeable Individual Working in the Field or a
-Related Field
-
-4. How would you rate the technical novelty of the paper?: Not Novel
-
-1. How would you rate the overall organization of the paper?: Satisfactory
-
-2. Are the title and abstract satisfactory?: Yes
-
-Explain:
-
-3. Is the length of the paper appropriate? If not, recommend how the
-length of the paper should be amended, including a possible target
-length for the final manuscript.: Yes
-
-4. Are symbols, terms, and concepts adequately defined?: Yes
-
-5. How do you rate the English usage? : Satisfactory
-
-6. Rate the Bibliography: Satisfactory
-
-null:
-
-1. How would you rate the technical contents of the paper?: Good
-
-2. How would you rate the novelty of the paper?: Not Novel
-
-3. How would you rate the "literary" presentation of the paper?: Mostly Accessible
-
-4. How would you rate the appropriateness of this paper for
-publication in this IEEE Transactions?: Weak Match
 %%% Local Variables: 
 %%% mode: latex
-%%% TeX-master: t
 %%% End:

### 2013-02-27 ssp2011.tex
Fixed some notations issues
Version accepted to TSP

@@
-\documentclass[10pt,twocolumn]{IEEEtran}
+\documentclass[10pt,draftclsnofoot,onecolumn]{IEEEtran}
 \usepackage{fontenc}
@@
 \author{Minh~Tang, Youngser~Park, Nam~H.~Lee, and Carey~E.~Priebe*%
+  \thanks{Copyright (c) 2012 IEEE.
+Personal use of this material is permitted.
+However, permission to use this material for any other purposes must be obtained from the IEEE by sending a request to pubs-permissions@ieee.org.}
 \thanks{Minh~Tang is with the Department of Applied Mathematics and
@@
   USA. (phone: 410-516-7200; fax:410-516-7459; email: cep@jhu.edu)}}%
-%\markboth{IEEE Transactions on Signal Processing}{}
-% \begin{IEEEkeywords}
-%   Anomaly detection, Attributed Random Graphs, Random Dot
-%   Product Graphs.
-% \end{IEEEkeywords}}
-
+\markboth{IEEE Transactions on Signal Processing}{}
 \maketitle
@@
 \end{abstract}
-\ifCLASSOPTIONpeerreview
-\begin{center} \bfseries EDICS Category: SSP-SSAN, SSP-DETC \end{center}
-\fi
+ \begin{IEEEkeywords}
+   Anomaly detection, Attributed Random Graphs, Random Dot
+   Product Graphs.
+ \end{IEEEkeywords}
+%\begin{center} \bfseries EDICS Category: SSP-SSAN, SSP-DETC \end{center}
 %\pagebreak
@@
 edges between the vertices, in addition to representing the presence
-of a relationship, can also be use to identify the attributes
+of a relationship, can also be used to identify the attributes
 associated with that relationship. For example, in social network
@@
 
-We mention here some related work. The notion of signal
-processing for graphs appears to be in an emerging
-state, with significant research activity in constructing wavelet
-representations for graphs, e.g., 
-\cite{hammond10:_wavel,r.coifman06:_diffus,crovella03:_graph,narangss:_perfec}. 
-The formulation of graph analysis problems in a signal processing framework
-is also of potential interest, e.g, \cite{miller10:_towar_euclid}.
-
 One of the main exploitation tasks in time-series analysis is the
@@
 occurs. In the context of a time-series of graphs, an anomaly can be
-for example the presence of a specific subgraph, or frequent occurence
+for example the presence of a specific subgraph, or frequent occurrences
 of some subgraphs, or other more vague notions such as existence of a
 community structure.
+
+The notion of signal processing for graphs appears to be in an
+emerging state, with significant research activity in constructing
+wavelet representations for graphs, e.g.,
+\cite{hammond10:_wavel,r.coifman06:_diffus,crovella03:_graph,narangss:_perfec}.
+The formulation of graph analysis problems in a signal processing
+framework is also of potential interest, e.g,
+\cite{miller10:_towar_euclid}, wherein a subgraph detection problem is
+presented, test statistics are defined, noise and signal models are
+introduced, and ROC analysis is performed. The construction of
+wavelets representations on graphs is analogous to the classical
+wavelets constructions, but adapted to use the topology of the graphs
+instead of the usual Euclidean space topology. For example, the
+wavelet representations of \cite{hammond10:_wavel} and
+\cite{r.coifman06:_diffus} are constructed using the combinatorial and
+normalized Laplacian matrices of the graphs, respectively, while
+\cite{crovella03:_graph} defined wavelets via the $n$-hop
+neighborhoods. The wavelet construction in \cite{crovella03:_graph}
+and its use in {\em spatial} traffic analysis (emphasis in 
+\cite{crovella03:_graph}) is similar to the use of locality/scan
+statistics for anomaly detection in
+\cite{priebe05:_scan_statis_enron_graph} and the current
+paper. Indeed, the locality statistic at a vertex $v$ is the size of an
+$n$-hop neighborhood starting at $v$ defined via shortest path
+distance and the scan statistic is the maximum of the locality
+statistics over all the $n$-hop neighborhoods. Traffic analysis by
+tracking the coefficients of the wavelet representations is similar to
+anomaly detection by tracking the values of the scan statistics.
 
@@
 limiting distributions for these test statistics under a generative
-model for the attributed graphs. The experimental evidence indicate that these
+model for the attributed graphs. The experimental evidences indicate that these
 test statistics have sufficient power against the null hypothesis for
@@
 
-Our paper is structured as follows. We present an overview of the
+The current paper builds upon ideas previously presented in
+\cite{lee11} and \cite{priebe11:_attrib}, among others. The generative
+model for time-series of attributed graphs used in this paper is from
+\cite{lee11}. Hypothesis testing for time-series of graphs and
+attribute fusion using a linear fusion parameter $\lambda$ were
+considered in \cite{lee11,priebe11:_attrib}; limiting distribution for
+the size graph invariant was given in \cite{lee11}. A version of the
+experimental results for simulated data included in this paper was first
+presented in \cite{priebe11:_attrib}.
+
+The paper is structured as follows. We present an overview of the
 generative model for time-series of attributed graphs \cite{lee11} in
-\S\ref{sec:latent-process-model}. The change-point detection problem
-along with the relevant test statistics are described in
-\S\ref{sec:change-point-detect}. The distributions of the test
+\S~\ref{sec:latent-process-model}. A change-point detection problem
+along with some relevant test statistics are described in
+\S~\ref{sec:change-point-detect}. The distributions of these test
 statistics and the power estimates for hypothesis testing using
-these test statistics are given in \S\ref{sec:power-estimates}. 
-\S\ref{sec:inference-examples} presents a
+these test statistics are given in \S~\ref{sec:power-estimates}. 
+\S~\ref{sec:inference-examples} presents a
 synthetic data example and an example using the Enron email corpus to
 illustrate our methodology.
+
 \section{Latent Process Model}
@@
 association among the entities. In addition to the classical
-Erd\"{o}s-R\'{e}nyi model \cite{Erdos1959}, there is, the exponential
+Erd\"{o}s-R\'{e}nyi model \cite{Erdos1959}, there is the exponential
 graph models \cite{holland81}, the stochastic block model
@@
 The latent space model is one where each vertex is associated with a
-latent random vector. There may also be additional covariate
+latent random vector. There may also be additional covariates
 information but those are not relevant to the current exposition. The
@@
 by the dot product of their respective latent vectors, i.e., $p_{uv} =
-\langle z_u, z_v \rangle$. Parts of the motivation of the random dot
+\langle z_u, z_v \rangle$. A motivation behind the random dot
 product graph model is that, in a social network with edges
@@
 same topics are most likely to form relationships while individuals
-who do not share interests are unlikely to form relationships.
+who do not share interest are unlikely to form relationships.
 
@@
 
-We now give the necessary details to make the above ideas precise. Let $G =
-(V,E)$ be an undirected graph, equipped with an edge-attribution
-function $\phi \colon \tbinom{V}{2} \mapsto [K+1] = \{1,2,\dots, K+1\}$ for
-some $K$ such that $\phi(e) \leq K$ for $e \in E$ and $\phi(e) \equiv
-K+1$ for $e \not \in E$. We refer to $\phi(e)$ as the attribute of
-edge $e \in E$, and the pair $(G,\phi)$ as an attributed graph. Let
-$\mathscr{S}$ be the unit simplex in $\mathbb{R}^{K}$, i.e.,
+We now give the necessary details to make the above ideas precise. For
+any positive integer $n$, we shall denote by $[n]$ the set of numbers
+$\{1,2,\dots,n\}$. Let $G = (V,E)$ be an undirected graph, equipped
+with an edge-attribution function $\phi \colon \tbinom{V}{2} \mapsto
+[K+1]$ for some positive integer $K$. We shall require that $\phi$
+satisfies $\phi(e) \leq K$ for $e \in E$ and $\phi(e) \equiv K+1$ for
+$e \not \in E$. We refer to $\phi(e)$ as the attribute of edge $e \in
+E$, and the pair $(G,\phi)$ as an attributed graph. Let $\mathscr{S}$
+be the unit simplex in $\mathbb{R}^{K}$, i.e.,
 \begin{equation}
@@
 \end{equation}
+
 A {\em random dot product space} for attributed graphs with vertices
-in $[n]$ ($[n] = \{1,2,\dots,n\}$) and edge attributes $[K]$ ($[K] =
-\{1,2,\dots,K\}$) is a pair $(\mathbf{X},G)$ of
+in $[n]$ and edge attributes $[K]$ is a pair $(\mathbf{X},G)$ of
 random elements such that
@@
     \mathbb{P}(u \sim v \,|\, \mathbf{X}) = \mathbb{P}(u \sim v \, |
-    \, X_u,X_v) = \langle x_u, x_v \rangle.
+    \, X_u,X_v) = \langle X_u, X_v \rangle.
   \end{equation}
@@
     \mathbb{P}(\phi(\{u,v\}) = k \, | \, u \sim
-    v) = \frac{x_{u,k} x_{v,k}}{\langle x_u, x_v \rangle}
-  \end{equation}
-  i.e., the pair $\{u,v\}$ is an edge in $G$ with attribute $k$ with
-  probability $x_{u,k} x_{v,k}$.  
+    v) = \frac{X_{u,k} X_{v,k}}{\langle X_u, X_v \rangle}
+  \end{equation}
+  i.e., the pair $\{u,v\}$ is an edge in $G$ having attribute $k$ with
+  probability $X_{u,k} X_{v,k}$.  
 \end{enumerate}
@@
 The above properties characterize a random dot process model with a
-change-point phenomena for $(X(t),G(t))$ at time $t = t^{*}$. We chose
+change-point phenomenon for $(X(t),G(t))$ at time $t = t^{*}$. We chose
 $\{1,2,\dots,m\}$ as the set of vertices with a change in the
 stationary distribution and intensity matrix at time $t = t^{*} - 1$
-for ease of discussion. Permutation of the vertex labels does not
+for ease of discussion. Permutations of the vertex labels do not
 affect our subsequent analysis. We will refer to $(t^{*}, m, \pi_0,
-\pi_1, \mathbf{Q}_0, \mathbf{Q}_1)$ as the change parameters.  Because
-$W$ is completely determined by the change parameters, we often choose
+\pi_1, \mathbf{Q}_0, \mathbf{Q}_1)$ as the change-parameters.  Because
+$W$ is completely determined by the change-parameters, we often choose
 to omit $W$ and only mention $\mathscr{V}$ when referring to random
-dot process models with change-point phenomena. For a random dot
+dot process models with change-point phenomenon. For a random dot
 process model
-$\mathscr{V}$ with change parameters $(t^{*}, m, \pi_0, \pi_1,
+$\mathscr{V}$ with change-parameters $(t^{*}, m, \pi_0, \pi_1,
 \mathbf{Q}_0, \mathbf{Q}_1)$, we can construct several approximations
-to $\mathscr{V}$. Of particular interests are the following two
+to $\mathscr{V}$. Of particular interest are the following two
 approximations.
@@
 \cite{rukhin11} (see \figurename~\ref{fig:kidney-egg}), which in
-itself is a special instance of the mixed membership stochastic
-blockmodel \cite{airoldi08:_mixed}. The unattributed kidney-egg model
+itself is a special instance of the stochastic
+block model \cite{Holland1983}. The unattributed kidney-egg model
 can be denoted as $\kappa(n,m,p,q,s)$ with the quantities $p$, $q$,
@@
   \label{def:2}
-  Let $\mathscr{V}$ be a rdpm with change parameters $(t^{*}, m,
+  Let $\mathscr{V}$ be a rdpm with change-parameters $(t^{*}, m,
   \pi_0, \pi_1, \mathbf{Q}_0, \mathbf{Q}_1)$. Define
@@
 rdpm with vertices $[n]$ and attributes $[K]$ where for each $r > 0$,
-$\mathscr{V}^{r}$ has change parameters $(t^{*}, m, \pi_0, \pi_1, r
+$\mathscr{V}^{r}$ has change-parameters $(t^{*}, m, \pi_0, \pi_1, r
 \mathbf{Q}_0, r \mathbf{Q}_1)$. The parameter $r$ can be thought of as
@@
 second-order approximation in this paper, but we note that they can be
-done via spectral embedding technique a la \cite{STFP-2011}. We also
+done via spectral embedding techniques a la \cite{STFP-2011}. We also
 note that more refined models, where the messaging events between each pairs of
-vertices is modeled as point process,
+vertices are modeled as point process,
 e.g. \cite{Heard2010,PerryWolfe2010}, can also be formulated. The
 snapshot of the graphs is then a binning of these point processes and
-the issue of parameters estimation is fundamental but feasible for
-these point processes approaches.
+parameter estimation is fundamental to
+these approaches.
 \section{Change-point detection}
@@
 \end{figure}
-Let $\mathscr{V}$ be a random dot process model with change parameters
+Let $\mathscr{V}$ be a random dot process model with change-parameters
 $(t^{*}, m, \pi_0, \pi_1, \mathbf{Q}_0, \mathbf{Q}_1)$. The
@@
 This will be done using the notion of fusion of attributed graph
-invariants. The particular invariants of interests are the size
+invariants. The particular invariants of interest are the size
 $\mathcal{E}$, number of triangles $\tau$, scan $\Psi$, and max degree
@@
 problem of detecting chatter anomalies in
-\cite{priebe05:_scan_statis_enron_graph}. The use of various graph
-invariants as test statistics was considered in
+\cite{priebe05:_scan_statis_enron_graph}. The number of triangles is
+the simplest graph invariant based on clique counts and one can define
+other test statistics for $k$-clique counts with $k \geq 4$.  The use
+of various graph invariants as test statistics was considered in
 \cite{pao11:_statis_infer_random_graph} and it was shown there, via
@@
 
-Let $(G,\phi)$ be an attributed graph. For a given $\{u,v\}
-\in \tbinom{V}{2}$, we define a $\Gamma_{uv} \in \mathbb{R}^{K}$ by
-$\Gamma_{uv}(k) = \mathbb{I}\{\phi(\{u,v\}) = k\}$. Thus $\Gamma_{uv}
-= \bm{0}$ unless $\{u,v\} \in E$. Under the independent edges
-assumption, the $\Gamma_{uv}$ are independent. We consider linear
+Let $(G,\phi)$ be an attributed graph. For a given $\{u,v\} \in
+\tbinom{V}{2}$, we define a $\Gamma_{uv} \in \mathbb{R}^{K}$ by
+$\Gamma_{uv}(k) = \mathbb{I}\{\phi(\{u,v\}) = k\}$ where $\mathbb{I}\{
+\cdot \}$ is the indicator function. Thus $\Gamma_{uv} = \bm{0} =
+(0,0,\dots,0)$ unless $\{u,v\} \in E$. Under the independent edges
+assumption, the $\{\Gamma_{uv}\}$ are independent. We consider linear
 attribute fusion of graph invariants with parameter $\lambda \in
@@
 %  \end{gather}
-
 \begin{align}
@@
 \end{equation}
-where $l \in \mathbb{N}$ specified the width of the running-average
+where $l \in \mathbb{N}$ specifies the width of the running-average
 window. Our main interest is in the normalized fusion statistic
@@
 \end{equation}
-for $l \geq 2$, i.e., we want to find a parameter $\lambda$ such that
-the power of the test using $T_{\lambda}^{l}$ is maximized. We note that
+for $l \geq 2$. The choice of values for $l$ depends on the
+practitioner, in that small values of $l$ can
+induce large fluctuations in the temporal standardization statistics,
+which may lead to a higher false positive rate while large values of $l$,
+can induce over-smoothing, leading to a higher
+false negative rate.
+
+We are interested in finding the optimal fusion parameter $\lambda$,
+i.e., we want to find a $\lambda$ such that
+the power of the test using $T_{\lambda}^{l}$ is maximized. The
+theoretical results in \S~\ref{sec:power-estimates} will be useful for
+this purpose. We note that
 $T_{\lambda}^{l}$ is scale invariant in $\lambda$ for all of our graph
@@
 \lambda \| = 1 \}$. 
-
-As we have mentioned earlier, we will assume that the number of
-vertices $n$ is large and that the use of the first order
-approximation $\bar{\mathscr{V}}$ of $\mathscr{V}$ is appropriate in
-our study of the asymptotic theory for these graphs invariants. We
-strive to obtain approximations for the power in testing $t^{*} > t$
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=8cm]{graphics/Fig4-SSP2011.pdf}
+  \caption{Temporal standardization: when testing for change at time
+    $t$, the recent past (graphs $G(t - l), \dots, G(t-1))$ is used to
+    standardize the invariants}
+  \label{fig:temporal}
+\end{figure}
+\section{Power estimates}
+\label{sec:power-estimates}
+\S~\ref{sec:change-point-detect} described the framework of hypothesis
+testing for anomaly/change-point detection in a time-series of
+graphs. In particular, it was assumed that the graphs were generated
+according to a random dot process model with change-parameters
+$(t^{*}, m, \pi_0, \pi_1, \mathbf{Q}_0, \mathbf{Q}_1)$ and the test 
+statistics were temporal standardization of several graph invariants, 
+namely size, max degree, scan, and number of triangles.
+
+We derive the limiting distributions for the above-mentioned test
+statistics in this section. As we 
+mentioned earlier, we will assume that the number of
+vertices $n$ is large so that the use of the first order
+approximation $\bar{\mathscr{V}}$ of $\mathscr{V}$ is appropriate for
+studying the asymptotic theory for the above-mentioned graphs
+invariants. We strive to obtain approximations for the power 
+in testing $t^{*} > t$
 against $t^{*} = t$ using $T_{\lambda}^{l}(t)$ and from these
-approximations, find the $\lambda$ that maximize the power. We now
-introduce additional notation that will be used later on in the
-paper. First, let $\pi_{00}, \pi_{01}$, and $\pi_{11}$ be
+approximations, find the $\lambda$ that maximize the power. 
+The limiting distributions for graph
+invariants in the {\em unattributed} setting are well-known, see 
+e.g., \cite{bollobas85:_random_graph} for max-degree,
+\cite{nowicki88:_subgr_u_statis_method} 
+for subgraph counts, and \cite{rukhin12} for scan. The results
+for the attributed and temporal standardization settings are thus 
+straightforward extensions of
+their counterparts in the unattributed settings.
+
+We now introduce additional notation that will be used later on in the
+paper. Let $\pi_{00}, \pi_{01}$, and $\pi_{11}$ be
 sub-probability vectors whose components are given by
@@
 \end{gather*}
-% The structure of the remaining sections of the paper is as follows. We
-% discussed the power estimates for $\mathcal{E}_{\lambda},
-% \tau_{\lambda}, \Delta_{\lambda}$ and $\Psi_{\lambda}$ in
-% \S~\ref{sec:power-estim-mathc}
-%  through \S~\ref{sec:power-estim-psi_l}. We illustrate our analysis with some
-% simulation experiments in \S~\ref{sec:experimental-results}  
-\begin{figure}[htbp]
-  \centering
-  \includegraphics[width=8cm]{graphics/Fig4-SSP2011.pdf}
-  \caption{Temporal standardization: when testing for change at time
-    $t$, the recent past (graphs $G(t - l), \dots, G(t-1))$ is used to
-    standardize the invariants}
-  \label{fig:temporal}
-\end{figure}
-\section{Power estimates}
-\label{sec:power-estimates}
+
 \subsection{Power estimates for $\mathcal{E}_\lambda$}
@@
   \end{gather*}
+  Suppose that $\xi$ is positive definite.
   Define the random variable $\psi^{l}_{\lambda}(t)$ by
@@
 $\tau_{\lambda}(t)$, does not have a simple distribution for small or
-moderate values of $l$. The following result give the limiting
+moderate values of $l$. The following result gives the limiting
 distribution for $T_{\lambda}^{l}(t)$ under the assumption that $l$ is
@@
   \rho_{\lambda} &= \begin{cases}
-      - \frac{ \sqrt{\pi}}{6} \gamma & \text{if $t < t^{*}$} \\
-    \frac{\sqrt{\pi}}{6} \frac{\mu_A - \mu_0 + a_m\sigma_A - (a_n + b_n
+      - \frac{ \sqrt{6}}{\pi} \gamma & \text{if $t < t^{*}$} \\
+    \frac{\sqrt{6}}{\pi} \frac{\mu_A - \mu_0 + a_m\sigma_A - (a_n + b_n
       \gamma)\sigma_0}{b_n \sigma_0} & \text{if $t =
@@
   \varsigma_{\lambda} &= \begin{cases}
-    \frac{\sqrt{\pi}}{6} & \text{if $t < t^{*}$} \\
-    \frac{\sqrt{\pi} b_m \sigma_A}{6 b_n \sigma_0} & \text{if $t =
+    \frac{\sqrt{6}}{\pi} & \text{if $t < t^{*}$} \\
+    \frac{\sqrt{6}}{\pi}\frac{b_m \sigma_A}{ b_n \sigma_0} & \text{if $t =
       t^{*}$} \\
@@
     \rho_{\lambda} &= \begin{cases}
-      - \tfrac{\sqrt{\pi}}{6} \gamma & \text{if $t < t^{*}$} \\
-      \tfrac{\sqrt{\pi}}{6} \tfrac{a_{n,m} - a_n - b_n \gamma}{b_n} & \text{if
+      - \tfrac{\sqrt{6}}{\pi} \gamma & \text{if $t < t^{*}$} \\
+      \tfrac{\sqrt{6}}{\pi} \tfrac{a_{n,m} - a_n - b_n \gamma}{b_n} & \text{if
         $t = t^{*}$} 
@@
       \varsigma_{\lambda} &= \begin{cases}
-        \tfrac{\sqrt{\pi}}{6} & \text{if $t < t^{*}$} \\
-        \tfrac{\sqrt{\pi} b_{n,m}}{6 b_n} & \text{if $t = t^{*}$}. \\
+        \tfrac{\sqrt{6}}{\pi} & \text{if $t < t^{*}$} \\
+        \tfrac{\sqrt{6}}{\pi} \tfrac{b_{n,m}}{6 b_n} & \text{if $t = t^{*}$}. \\
       \end{cases}
@@
 angle $\theta$, where $\lambda = (cos(\theta), sin(\theta))$. 
+Finally, \figurename~\ref{fig:qqplot-maxd} presents Q-Q plots
+illustrating convergence of the temporal standardization statistics to
+the limiting distributions given in \S~\ref{sec:power-estimates}.
+
+A comment should be made regarding the application of the
+theoretical results in \S~\ref{sec:power-estimates} to this simulation
+example. The results in \S~\ref{sec:power-estimates} on the limiting
+distributions of the temporal standardization statistics specified both
+the type of distribution, i.e., Gumbel or Student's t-distribution,
+along with the associated parameters, i.e., location and scale for the Gumbel
+distribution and degrees of freedom and non-centrality parameter for
+the Student's t-distribution. 
+Empirical investigations demonstrate that, for the temporal standardization
+statistics based on max degree, number of triangles, and scan, the limiting distributions
+with the parameters as specified in Theorem~\ref{thm:5},
+Theorem~\ref{thm:8} and Theorem~\ref{thm:6} are accurate large-sample
+approximations for these statistics provided that the graphs have $n \geq 1000$ and $m \geq 50$.
+The variance parameters as specified by the theoretical result
+require correction for small $n$, as used in our experiment ($n = 100$).
+For example, $\mathrm{Var}[\tau_{\lambda}^{*}(G(t))]$ in Lemma~\ref{lem:3} is a
+good approximation of the variance term in the normal approximation
+only if the ratio of $\mathrm{Var}[\tau_{\lambda}^{*}(G(t))] -
+\mathrm{Var}[\tau_{\lambda}(G(t))]$, the difference in the variance
+between the Hajek's projection and the true variance, to
+$\mathrm{Var}[\tau_{\lambda}(G(t))]$ is small; this does not hold
+for $n = 100$. Thus, the results for the limiting distributions for the above experiment are obtained by
+correcting for the variance. In particular, we used the sample variance of the
+graph invariants under the first-order approximation as the variance
+for the limiting distribution.
+
+% A comment should be made regarding the application of the
+% theoretical results in \S~\ref{sec:power-estimates} to this simulation
+% example. The results in \S~\ref{sec:power-estimates} on the limiting
+% distribution of the temporal standardization statistics specified both
+% the type of distribution, i.e., Gumbel or Student's t-distribution,
+% along with the associated parameters, i.e., location and scale for the Gumbel
+% distribution and degree of freedom and non-centrality parameter for
+% the Student's t-distribution. According to empirical evaluations that
+% are not reported in this paper, for the temporal standardization
+% statistics based on max degree, number of triangles, and scan, the limiting distributions
+% with the parameters as specified in Theorem~\ref{thm:5},
+% Theorem~\ref{thm:8} and Theorem~\ref{thm:6} are accurate large-sample
+% approximations for these statistics provided that the graphs have $n
+% \geq 1000$ and $m \geq 50$ and not for $n = 100$ as used in the above
+% experiment. This is due mostly to the fact that the variance parameters as
+% specified by the theoretical result is
+% inaccurate for these small values of $n$. For example,
+% $\mathrm{Var}[\tau_{\lambda}^{*}(G(t))]$ in Lemma~\ref{lem:3} is a
+% good approximation of the variance term in the normal approximation
+% only if the ratio of $\mathrm{Var}[\tau_{\lambda}^{*}(G(t))] -
+% \mathrm{Var}[\tau_{\lambda}(G(t))]$, the difference in the variance
+% between the Hajek's projection and the true variance, to
+% $\mathrm{Var}[\tau_{\lambda}(G(t))]$ is small and this does not hold
+% for $n = 100$. Thus, the results for the limiting distributions for the above experiment are obtained by
+% correcting (and only correcting) for the variance. In particular, we used the sample variance of the
+% graph invariants under the first-order approximation as the variance
+% for the limiting distribution.
 
 The main implication that can
-be inferred from \figurename~\ref{fig:power-scale} and
+be inferred from \figurename~\ref{fig:power-scale}, \figurename~\ref{fig:qqplot-maxd} and
 \figurename~\ref{fig:power-estimate}
@@
 \end{figure*}
+
+\begin{figure*}[!t]
+  \centering
+  \subfloat[$T_{\Delta}$ under $H_0$]{
+  \includegraphics[width=5cm]{graphics/maxd_null.pdf}
+  }
+  \hfil
+  \subfloat[$T_{\tau}$ under $H_0$]{
+  \includegraphics[width=5cm]{graphics/numtri_null.pdf}
+  }
+  \hfil
+  \subfloat[$T_{\psi}$ under $H_0$]{
+  \includegraphics[width=5cm]{graphics/scan_null.pdf}
+  }
+  \hfil
+  \subfloat[$T_{\Delta}$ under $H_A$]{
+  \includegraphics[width=5cm]{graphics/maxd_alt.pdf}
+  }
+  \hfil
+  \subfloat[$T_{\tau}$ under $H_A$]{
+  \includegraphics[width=5cm]{graphics/numtri_alt.pdf}
+  }
+  \hfil
+  \subfloat[$T_{\psi}$ under $H_A$]{
+  \includegraphics[width=5cm]{graphics/scan_alt.pdf}
+  }
+  \caption{Q-Q plots of the temporal standardization statistics
+    $T_{\Delta}$, $T_{\tau}$ and $T_{\Psi}$ against the corresponding
+    limiting distributions as given in Theorem~\ref{thm:5},
+    Theorem~\ref{thm:8} and Theorem~\ref{thm:6}, respectively. The
+    sample quantile for the temporal standardization statistics are
+    based on 10000 Monte Carlo replicates of the time-series of
+    graphs. The graphs are generated according to the second-order
+    approximation with $r = 1024$. Refer to the text at the beginning
+    of \S~\ref{sec:inference-examples} for details on the parameters
+    of the random graph model. The fusion parameter $\lambda =
+    (cos(\theta), sin(\theta))$ for each temporal standardization
+    statistics correspond to the $\theta^{*}$ that maximizes the power
+    as depicted in \figurename~\ref{fig:power-estimate}, i.e.,
+    $\theta^{*}_{\Delta} \approx 0.32$, $\theta^{*}_{\tau} \approx 0.3$,
+    $\theta^{*}_{\psi} \approx 0.14$.  For each plot, a linear regression
+    between the sample quantile and the theoretical quantile was
+    performed and the resulting best linear fit is plotted. The $R^2$
+    statistics for the linear regressions exceed $0.995$ in all
+    cases. }
+  \label{fig:qqplot-maxd}
+\end{figure*}
+
 \begin{figure*}[!t]
@@
   \subfloat[$\Delta_{\lambda}$]{
-    \includegraphics[width=7cm]{graphics/pwr-maxd.pdf}
+    \includegraphics[width=7cm]{graphics/pwr-maxd-new.pdf}
   }
@@
   \subfloat[$\Psi_{\lambda}$]{
-    \includegraphics[width=7cm]{graphics/pwr-scan.pdf}
+    \includegraphics[width=7cm]{graphics/pwr-scan-new.pdf}
     \label{fig5:subfig_scan}
@@
   \subfloat[$\tau_{\lambda}$]{
-    \includegraphics[width=7cm]{graphics/pwr-ntri.pdf}
+    \includegraphics[width=7cm]{graphics/pwr-ntri-new.pdf}
   }
@@
     lines correspond to different values of the vertex process rate
-    $r$ (here $r \in \{1,2,4,8,16,32,64,128,256,512,1024\}$). 
+    $r$ (here $r \in \{2^{0}, 2^{1}, \dots, 2^{10}\}$). 
     The 10000 Monte Carlo
@@
 Our second example uses the Enron data set which consists of email
-messages between 184 executives of the Enron corporation during a time
+messages among 184 executives of the Enron corporation during a time
 period from 1998 to 2002. The Enron email messages for most of the
@@
    four graph invariants. The value of $\lambda = (\cos(\theta),
-   sin(\theta))$ for each graph invariants correspond to the optimal
-   fusion parameters for the detection as illustrated in
+   sin(\theta))$ for each graph invariant correspond to the optimal
+   fusion parameter for the detection as illustrated in
    \figurename~\ref{fig:enron} and they are
@@
    indicate that there are possible anomalies around the weeks 120,
-   132, and 146, which were also reported and analyzed in 
-   \cite{priebe05:_scan_statis_enron_graph}.}
+   132, and 152, which were also reported and analyzed in 
+   \cite{priebe05:_scan_statis_enron_graph}. }
 \label{fig:enron_time}
@@
 invariants against the fusion parameter $\lambda = (cos(\theta),
-sin(\theta))$. \figurename~\ref{fig:enron_time} presents a plot of the
+sin(\theta))$. By using the limiting results of
+\S~\ref{sec:power-estimates}, approximate p-values for hypothesis testing using these
+$T_{\lambda}^{l}$ statistics can also be obtained. Under
+the null hypothesis of homogeneity or no chatter groups, the
+large-sample results of \S~\ref{sec:power-estimates} suggest that
+$T_{\lambda}^{l}$ based on size and number of triangle graph
+invariants follows a Student's t-distribution with $l - 1$ degrees of
+freedom, while $T_{\lambda}^{l}$ based on max degree and scan graph
+invariants follows a Gumbel distribution with location parameter
+$-\tfrac{\sqrt{6}}{\pi} \gamma$ and scale parameter
+$\tfrac{\sqrt{6}}{\pi}$. Thus we obtain p-values of
+$0.01$, $0.002$, $0.003$, and $0.01$ for
+$T_{\lambda}^{l}$ based on size, max degree, number of triangles and
+scan, at $\theta^{*}_{\mathcal{E}_{\lambda}},
+\theta^{*}_{\Delta_{\lambda}}, \theta^{*}_{\tau_{\lambda}},
+\theta^{*}_{\Psi_{\lambda}}$, respectively. Ignoring the attributes on
+the edges gave p-values of $0.13$, $0.02$, $0.51$ and $0.04$ for
+$T_{\lambda}^{l}$ based on size, max degree, number of triangles, and
+scan respectively. Finally, ignoring the edges with edge attribute 1
+gave $p$-values of $0.02$, $0.004$, $0.005$, and $0.01$. Thus, in
+general, attribute fusion provides superior detection as 
+exemplified by the fact that the maximum for each of the normalized
+statistics $T_{\lambda}$, and hence the minimum of the p-values, 
+occurs for $\theta \not \in \{0,\pi/2\}$. Furthermore, the optimal 
+fusion parameters are dependent on the specific graph invariants.
+
+\figurename~\ref{fig:enron_time} presents a plot of the
 normalized statistics $T_{\lambda}^{l}(t)$ with $l = 20$ for the four
 graph invariants over the time interval corresponding to the
-weeks $t = 96$ through $t = 168$. The value of $\lambda$ used
-for each graph invariants is the $\lambda$ that maximizes
-$T_{\lambda}^{l}(152)$. \figurename~\ref{fig:enron}
-indicates that the fusing of attributes leads to better detection
-as exemplified by the fact that the maximum for each of the normalized
-statistics $T_{\lambda}$ occurs for $\theta \not \in
-\{0,\pi/2\}$. Furthermore, the optimal fusion parameters are dependent
-on the specific graph invariants.
+weeks $t = 115$ through $t = 187$. The value of $\lambda$ used
+for each graph invariant is the $\lambda$ that maximizes
+$T_{\lambda}^{l}(152)$. The fluctuations
+indicate that there are possible anomalies around the weeks 120,
+132, and 152, which were also reported and analyzed in 
+\cite{priebe05:_scan_statis_enron_graph}.  Approximate p-values for
+hypothesis testing using these $T_{\lambda}^{l}$ are
+also available. For example, at week $t = 129$, the p-values are
+$\approx 7 \times 10^{-4}, 4 \times 10^{-5}, 4 \times 10^{-5}, 2
+\times 10^{-6}$ for $T_{\lambda}^{l}$ based on the size, max degree, number of
+triangles, and scan statistic, respectively. At week $t = 125$, the
+approximate p-values are $1 \times 10^{-5}, 9 \times 10^{-3}, 1
+\times 10^{-6}$, and $8 \times10^{-4}$.
 \section{Conclusions}
@@
 
-The simulation experiment in \S \ref{eq:55} indicates that the power estimates
+The simulation experiment in \S~\ref{eq:55} indicates that the power estimates
 are accurate, even for the moderate value of $n = 100$. Furthermore,
@@
 
+The principal utility of the large-approximation
+results of \S~\ref{sec:power-estimates} is to the specification of
+approximate p-values and the investigation on the Enron
+corpus data set illustrates this succinctly.
+
 % The exact generative model for time-series
@@
 results and the model in \cite{lee11} to directed, multi, and weighted
-graphs, as well as the consideration of inference with errorful edge
-attributes through an attribute confusion matrix.
-
+graphs, to other class of graph invariants, and to 
+consideration of inference with errorful edge
+attributes through an attribute confusion matrix. For example, the
+paper considered a test statistic based on the number of triangles
+which is the simplest clique counts statistic. One can define
+attribute fusion for $k$-clique counts for $k \geq 4$. Using the
+theory of $U$-statistics for subgraphs counts
+(cf. \cite{nowicki88:_subgr_u_statis_method}), the limiting
+distribution for the temporal standardization statistics based on 
+these $k$-clique counts can be derived in an analogous manner to the 
+case for $k = 3$ in this paper.
+
+Finally, we remark that applicability of the statistics
+described in \S~\ref{sec:change-point-detect} extends beyond the
+statistical inference perspective. Indeed, temporal standardization of
+graph invariants can be computed irrespective of any underlying model
+on the graphs. As such, these statistics can
+serve as the basis for simple and robust inference procedures on
+time-series of (attributed) graphs. 
+\section*{Acknowledgements}
+The authors thank the anonymous reviewers for their comments which
+have improved the presentation and quality of the paper. This work was 
+partially supported by National Security Science and Engineering
+Faculty Fellowship (NSSEFF) and by Johns Hopkins University Human
+Language Technology Center of Excellence (JHU HLT COE).
 \bibliography{ssp2011}
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{./minh.jpg}}]{Minh Tang}
+  received the BS degree from Assumption University,
+  Thailand in 2001, the MS degree from the University of
+  Wisconsin-Milwaukee in 2004 and the Ph.D degree from Indiana
+  University Bloomington in 2010. He is currently a postdoctoral
+  fellow in the Department of Applied Mathematics and Statistics at
+  Johns Hopkins University. His research interests include statistical
+  pattern recognition, dimensionality reduction, and high-dimensional
+  data analysis.
+  \end{IEEEbiography}
+
+  \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{./youngser.jpg}}]{Youngser Park}
+    received the B.E. degree in electrical engineering from Inha
+    University in Seoul, Korea in 1985, the M.S. and Ph.D. degrees in
+    computer science from The George Washington University in 1991 and
+    2011 respectively. From 1998 to 2000 he worked at the Johns
+    Hopkins Medical Institutes as a senior research engineer. From
+    2003 until 2011 he worked as a senior research analyst, and has
+    been an associated research scientist since 2011 in the Center for
+    Imaging Science at the Johns Hopkins University. At Johns Hopkins,
+    he holds joint appointments in the Department of Applied
+    Mathematics and Statistics and the Human Language Technology
+    Center of Excellence. He has reviewed papers for ACM Transactions
+    on Knowledge Discovery in Data, Statistical Analysis and Data
+    Mining, and WIREs Computational Statistics. His current research
+    interests are clustering algorithm, pattern classification, and
+    data mining for high-dimensional and graph data.
+\end{IEEEbiography}
+
+  \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{./nam.jpg}}]{Nam H. Lee}
+    Nam Lee received the Ph.D degree in 2008 from University of California ,
+San Diego, from which he also received the MS degree in 2004 and the
+BA degree in 2002. He is currently a faculty member of Department of Applied Mathematics
+and Statistics at Johns Hopkins University.  His research interests
+include stochastic processes and their applications to statistical pattern
+recognition and optimal control.
+\end{IEEEbiography}
+
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{./cep.jpg}}]{Carey E. Priebe}
+  received the B.S. degree in
+  mathematics from Purdue University in 1984, the M.S. degree in
+  computer science from San Diego State University in 1988, and the
+  Ph.D. degree in information technology (computational statistics)
+  from George Mason University in 1993. From 1985 to 1994 he worked as
+  a mathematician and scientist in the US Navy research and
+  development laboratory system. Since 1994 he has been a professor in
+  the Department of Applied Mathematics and Statistics, Whiting School
+  of Engineering, Johns Hopkins University, Baltimore, Mary- land. At
+  Johns Hopkins, he holds joint appointments in the Department of
+  Computer Science, the Department of Electrical and Computer
+  Engineering, the Center for Imaging Science, the Human Language
+  Technology Center of Excellence, and the Whitaker Biomedical
+  Engineering Institute. He is a past President of the Interface
+  Foundation of North America - Computing Science \& Statistics, a past
+  Chair of the American Statistical Association Section on Statistical
+  Computing, a past Vice President of the International Association
+  for Statistical Computing, and on the editorial boards of Journal of
+  Computational and Graphical Statistics, Computational Statistics and
+  Data Analysis, and Computational Statistics. His research interests
+  include computational statistics, kernel and mixture estimates,
+  statistical pattern recognition, statistical image analysis,
+  dimensionality reduction, model selection, and statistical inference
+  for high-dimensional and graph data.  He is a Senior Member of the
+  IEEE, a Lifetime Member of the Institute of Mathematical Statistics,
+  an Elected Member of the International Statistical Institute, and a
+  Fellow of the American Statistical Association.
+
+\end{IEEEbiography}
+
 \end{document}
